### 2018-04-03 Thesis plan/Thesis plan.tex
Thesis plan

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[a4paper, total={6.5in,9.5in}]{geometry}
\newcommand\tab[1][1cm]{\hspace*{#1}}
\newcommand\vtab[1][0.2cm]{\vspace*{#1}}

\begin{document}
\begin{titlepage}
\title{Thesis plan\\Version 1.0}
\author{Arjan Meijer\\11425555}
\maketitle
\thispagestyle{empty}
\end{titlepage}
\tableofcontents\newpage
\section{Introduction}
This thesis will be about document embedding, embedding, in this context, means: "A method which converts a piece of text, such as title, abstract or an entire document, to a multidimensional numerical vector"\footnote{As given by Dr. R. Karimi (Elsevier)}. The current works on document embedding focusses on finding new, or optimizing existing embedding methods and applying these embedding vectors for (new) tasks. This work is based on publicly available everyday-language texts (like Wikipedia and forums). While the word-to-vec model, which produces word embeddings, works for most text, researchers encountered problems with the technique when using text that contained sarcasm\cite{le2014distributed}. This exception shows that the model is not without it flaws. Furthermore, the word-to-vec model can be trained with varying settings/variables, resulting in different levels of accuracy\footnote{Embedding accuracy can be measured by its usefulness for the task at hand.  A good embedding will perform greatly for many various tasks. Generally, a good embedding will map similar texts to close-by vectors as long as they are semantically closely related. Moreover, ideal embedding will create vectors that can be used algebraically such that summation and differences maintain semantic relations.}. The goal of this thesis is to apply the word-to-vec model to academic texts, which differ in layout and the usage of language from the everyday-language texts , to find optimal the optimal settings/variables for these texts and to detect possible anomalies. This thesis will be done in cooperation with Elsevier, which has a large collection of scientific papers that can be used for this thesis.
\newpage
\section{Project Information}
\textbf{Project title:}\\
\tab Embedding for scientific texts.\vtab\\
\textbf{Student name:}\\\tab
Harm Jan (Arjan) Meijer.\vtab\\
\textbf{Host organization:}\\\tab
Elsevier (Amsterdam).\vtab\\
\textbf{Contact information Elsevier:}\\\tab
\vtab\begin{tabular}{ll}
Name      & R. Karimi                                              \\
Title     & Dr.                                                    \\
Function  & Lead Data Scientist in Search \& Data Science Division \\
Mail      & r.karimi@elsevier.com                                  \\
Telephone & +31 (0)20 485 3514                                    
\end{tabular}\\
\textbf{Contact information Student:}\\\tab
\vtab\begin{tabular}{ll}
Name      & H.J. Meijer\\
Title     & Ing.\\
Function  & Internship/Student \\
Mail      & meijerarjan@live.nl \\
Telephone & +31 (0)6 3388 5147  \\                                 
\end{tabular}\\
\textbf{Terminology}\footnote{As given by Dr. R. Karimi}\textbf{:}
\vtab\\\textit{Embedding:}\\ A method which converts a piece of text, such as title, abstract or an entire document, to a multidimensional numerical vector
\vtab\\\textit{Accuracy:}\\Embedding accuracy can be measured by its usefulness for the task at hand.  A good embedding will perform greatly for many various tasks. Generally, a good embedding will map similar texts to close-by vectors as long as they are semantically closely related. Moreover, ideal embedding will create vectors that can be used algebraically such that summation and differences maintain semantic relations.
\newpage
\subsection{Project Summary}
This project looks at the usefulness of embedding for academic texts. More specifically, can embedding methods have a higher accuracy than the more traditional TD-IDF approach. This topic is closely related to machine learning, since the document embeddings are obtained through machine learning. This project produces an overview of the accuracy of embedding methods and the TF-IDF method for representing academic texts. With this information, researchers or people from industry can make a rational decision about using an embedding method for academic texts. This project gives an answer to three research questions:
\begin{itemize}
\item{Has the bag-of-words embedding method a higher accuracy for academic texts than TF-IDF?}
\subitem{Which parameter values create embeddings with the highest accuracy for academic texts?}
\item{What is the relationship between the accuracy of an embedding method and the type of text?}
\end{itemize}
To answer the first research question, the optimal parameters for the embedding method have to be found. The comparison between embedding and TF-IDF must only be done with the optimal parameters for the embedding method.
\section{Problem Analysis}
Researchers have shown in previous studies that text related tasks, like search or recommendation, can be accomplished with embeddings of texts. There are a number of different embedding methods proposed. In this research, I want to see if embedding methods have a higher accuracy than the more traditional approach, TF-IDF. I want to do this for the domain of academic texts, which differ in their document-build up and language from earlier researched online sources, forum like sites and Wikipedia. Elsevier has a large set of academic texts and already applies different embeddings to these texts. Their collection and experience on this topic will enable me to do this research.

\section{Research method}
\subsection{Method \& Validation}
\paragraph{Method} To answer the stated research questions, a fitted approach must be applied. For this project, the research method '\textit{Controlled Experiments}' will be applied. Using this methodology, the goal of this project is to validate these two hypothesis:
\begin{itemize}
\item{The bag-of-words embedding method can have an higher accuracy for academic texts than the TF-IDF algorithm.}
\item{The accuracy of embedding methods is related to the type of text.}
\end{itemize}
\paragraph{Validation} This research will be validated via a clear presentation of all compared results. The usage of a publicly available collection and via a clear presentation of the used parameters for each method.

\subsection{Experiments:}
This research exists out of multiple experiments, the usage of the methods on two collections, one containing non-academic texts, while the other consists of academic texts. The results mentioned in this paragraph is the accuracy score on the categorization tasks. Each document in the test set will be labelled except for 20\%, these unlabelled documents have to be matched to the right set of documents. The correct matched percentage will be the result score for the algorithm/embedding method.\\
\paragraph{First experiment}The goal of the first experiment is to compare the results of my algorithm to earlier researches by comparing the results for the Wikipedia set\footnote{Which is also used in earlier researches}. This will ensure that the algorithm I use is comparable, and thus add legitimacy to the research. I expect that this is a small experiment, since it should only recreate already found results.\\
\paragraph{Second experiment}The second experiment is finding the optimal parameters for the set of academic papers. This will be done by fine-tuning the parameters in search for an optimal result, furthermore, the results of this process must be registered for comparison. This fine-tuning process is a calculation-intensive process, because of this, I expect that this experiment will take most of the time. This experiment also includes data gathering for the comparison of the methods.\\
\paragraph{Third experiment}The third experiment is creating the TF-IDF algorithm in the research environment and collecting data on its search results. This experiment will not take much time, since the TF-IDF is a simple algorithm to implement.\\
\paragraph{Comparison}
The final step is the comparison of the collected data from experiments 2 and 3, with this information, I will be able to accept or dismiss the hypothesis, and with that, answer the research questions.\\

\subsection{Sources:}
Multiple articles of the explanation of the embedding methods will be used to create the embedding methods. These sources will be included in the Bibliography. Furthermore, the example set that is used in the papers will also be used for this project, the link to this publicly available source will be added as a footnote when the collection is used/discussed. The other collection that will be used belongs to Elsevier and is not publicly available. This set will be described (type of texts, size) and it will be mentioned that the collection is not publicly available since it is property of Elsevier.

\subsection{Problems:}
Difficulties in this project will likely be caused by finding the optimal parameters for an embedding method. This is a hard and not jet solved problem, it can theoretically be achieved with a brute-force-approach. But the training of the embedding methods is a computational-expensive method. A brute-force over multiple parameters is therefore a very computational-expensive process. A machine learning solution for this process would be a batch-approach. This approach would take a small set of data and use it to predict the (semi) optimal parameters for larger sets. The problem with embedding is that the parameter settings are not scalable, parameters like corpus-word-size can influence the learning result in unexpected ways due to the variation of this value in larger a corpus(i.e. a word corpus size of 100 may be sufficient for a small subset of texts, but may be insufficient for the entire set).

\section{Expected project results}
This research results in the following findings:
\begin{itemize}
\item{Comparison of multiple embedding methods for a collection of academic texts}
\subitem{- If possible, a best-to-use method}
\item{Validation of the hypothesis 'The accuracy of embedding methods is related to the type of text.'}
\subitem{- If these are related, an analysis of relationship in accuracy of the methods for the academic and non-academic texts.}
\end{itemize}
\section{Required expertise for this project}
This project requires:
\begin{itemize}
\item{Basic understanding of Machine Learning}
\item{Knowledge of Databricks/Spark (AWS)}
\item{Knowledge of embedding (methods \& evaluation)}
\item{SQL programming}
\item{Python programming}
\end{itemize}
\section{Timeline}
\begin{center}
\begin{tabular}{lll}
\textbf{Focus} & \textbf{Number of weeks} & \textbf{Date} \\
Setting up workspace & 1 & April 3 - April 6\\
Implementing methods & 2 & April 9 - April 20\\
Finding optimal & 3 & April 23 - May 11\\
embedding parameters & & \\
Data gathering experiment 1 & 1 & May 14 - May 18\\
Data gathering experiment 2 & 1 & May 21 - May 25\\
Writing & 2 & May 28 - June 8\\
Correction & 1 & June 11 - June 15\\
Submission & 1 & June 18 - June 22\\
Total & 12 & presentation date (NOT YET CONFIRMED) July 10\\
\end{tabular}\\
\end{center}
*  for non-academic texts\\ ** for academic texts

\section{Risks}
\begin{tabular}{ll}
\textbf{Risk} & \textbf{Prevention / Solution}\\
Unavailability of previously used & The dataset is already on an local PC\\datasets&\\&\\
Problems with implementing the& Elsevier has a range of experts on this topic,
\\methods&who are willing to help out if needed.\\&\\
Due to unforseen problems, there &The research consist of multiple hypothesis, atleast \\is not enough time to complete & one must be achievable\\the entire research &\\&\\
Student has a knowledge gab & I am taking an online course to understand basis of \\
 &Machine Learning and to get used to Databricks\\
\end{tabular}\\
\newpage
\section{Literature survey}
The literature survey provides the explanation of the embedding methods that will be compared in this research. Furthermore, they provide  non-academic texts\footnote{The papers contain references to publicly available sets that they used for their research.} that can be used to validate the implementation of the methods. This set will also be used to compare the non-academic texts to the academic texts.

\subsection{Deep Neural Networks for YouTube \\Recommendations}
The paper 'Deep Neural Networks for YouTube Recommendations' by Covington et al.\cite{covington2016deep} describes the current (16 September 2016) YouTube candidate generation and ranking neural networks. The candidate generation network works with limited data inorder to reduce the needed time for the candidate generation. This process reduces the amount of possible videos for the ranking network, which uses more parameters to increase the accuracy of the ranking. The paper also discusses variables to influence the results of the networks, such as age of the training example and watch-time vs click-through prediction. The paper also discusses the impact that layers of depth have at the results.
\subsection{Distributed Representations of Sentences and Documents}
The paper 'Distributed Representations of Sentences and Documents' by le et al.\cite{le2014distributed} proposes the Paragraph Vector as a replacement for the popular bag-of-words or bag-of-n-grams. The Paragraph Vector framework is based on the word vectors framework. The difference between the frameworks is the calculation of the probability, the Paragraph Vector framework uses an matrix D, which consists of every paragraph. This matrix is used to replace a concatenation or average of word vectors. The Paragraph Vector out preforms the state-of-the art techniques on several text classification and sentiment analysis tasks.
\subsection{Distributed Representations of Words and Phrases and their Compositionality}
The paper 'Distributed Representations of Words and Phrases and their Compositionality' by Mikolov et al.\cite{mikolov2013distributed} presents several extensions that improve the quality of vector training and its speed. This is achieved by introducing Hierarchical Softmax, Negative Sampling and the subsampling of frequent words to the Skip-gram approach. This does not only speed up the learning process, but also improves the quality for rare words.
\subsection{Document Embedding with Paragraph Vectors}
The paper 'Document Embedding with Paragraph Vectors' by Dai et al.\cite{dai2015document} describes a larger/more thorough evaluation of the Paragraph Vectors model. The writers compare this technique with the Bag of Words model and the Latend Dirichlet Allocation model. The paper states that the Paragraph Vectors model preforms well for grouping, triplet finding and related object/article finding tasks. The paper states that the Paragraph Vectors model is significantly better then the other models in these tasks on the Wikipedia and arXiv articles.
\subsection{Stochastic Neighbor Embedding}
The paper 'Stochastic Neighbor Embedding' by Hinton et al.\cite{hinton2003stochastic} describes a probabilistic approach to transform objects form a high-dimensional space to a low-dimensional spaces so that  neighbour identities are preserved. To achieve this the objects are transformed to images. A Gaussian is then used to define the (context) probability. This method has the ability to be extended to mixtures in which ambiguous high-dimensional objects can have several widely-separated images in the low-dimensional space.
\subsection{An empirical evaluation of doc2vec with practical \\insights into document embedding generation}
The paper 'An empirical evaluation of doc2vec with practical insights into document embedding generation' by Lau et al.\cite{lau2016empirical} empirically evaluates the quality of the documents embedding created with the method 'doc2vec' compared to 'word2vec' and the 'n-gram' model. They conclude that doc2vec preforms well and that the 'dbow' approach works better than the 'dmpv' approach for the doc2vec method. They also provide recommendations for the optimal parameters for the doc2vec method.
\subsection{Efficient estimation of word representations in vector space}
The paper 'Efficient estimation of word representations in vector space' by Mikolov et al.\cite{mikolov2013efficient} 
shows that, with newly applied techniques, the size of the training sets can increase while the time needed for the training operation does not increase. This new approach greatly reduces the training time per word and allows for bigger sets of texts. This results in a higher accuracy of the created embeddings. The authors state that the newly applied techniques can also be used on other, already existing embedding methods. 
\subsection{GloVe: Global Vectors for Word Representation}
The paper 'GloVe: Global Vectors for Word Representation' by Pennington et al.\cite{pennington2014glove} proposes a new model, named GloVe, which is a log-bilinear regression model for unsupervised learning of word representations. This model out preforms other models on three specific tasks, these are: word analogy, word similarity and named entity recognition.
\subsection{MapReduce: Simplified data processing on large \\clusters}
The paper 'MapReduce: Simplified data processing on large clusters' by Dean et al.\cite{dean2008mapreduce} explains the MapReduce programming model. The model is inspired by functional programming languages. It requires programmers to specify a map function which processes key-value pairs to generate intermediate key-value pairs. It requires furthermore a reduce function, that merges all intermediate values associated with the same intermediate key. This method allows for an execution on a large distributed computer network. This allows the processing of large input (and output) sets in reasonable time.
\subsection{Spark SQL: Relational data processing in spark}
The paper 'Spark SQL: Relational data processing in spark' by Armbrust et al.\cite{armbrust2015spark} explains Spark SQL. Spark SQL lest programmers leverage the benefits of relational processing and lets SQL users call complex analytix libraries in Spark. This allows for much tighter intergration between relational and procedural processing. The paper further states that Spark SQL makes it significanly simpler and more efficient to write data piplines that mix relational and procedural processing, while offering substantial speedups over previous SQL-on-Spark engines\footnote{Based on user feedback}.

\newpage
\bibliographystyle{plain}
\bibliography{Bibliography}
\end{document}

### 2018-04-05 Thesis/Parts/Abstract/Abstract.tex
Initial thesis setup

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\section{Abstract}
[TODO: Abstract]
\end{document}

### 2018-04-05 Annotations/Annotations.tex
Added annotations

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}
\section{How to Generate a Good Word Embedding?}
Paper by Lai et al.\cite{lai2016generate}
\begin{itemize}
\item{Word embedding, also known as distributed word
representation, can capture both the semantic and syntactic
information of words from a large unlabeled corpus
and has attracted considerable attention from many researchers.
In recent years, several models have been proposed,
and they have yielded state-of-the-art results in many
natural language processing (NLP) tasks.}
\item{We observe that almost
all methods for training word embeddings are based on the
same distributional hypothesis: words that occur in similar
contexts tend to have similar meanings.}
\item{Training on a large corpus
generally improves the quality of word embeddings,
and training on an in-domain corpus can significantly
improve the quality of word embeddings for a specific
task.}
\item{Previous works have shown that models that predict the target word capture the paradigmatic relations between words}
\item{we can conclude that using a larger corpus can yield a better embedding, when the corpora are in the same domain}
\item{In most of the tasks, the influence of the corpus domain is
dominant. In different tasks, it impacts performance in the
different ways}
\item{The corpus
domain is more important than the corpus size. Using an indomain
corpus significantly improves the performance for a
given task, whereas using a corpus in an unsuitable domain
may decrease performance. }
\end{itemize}
\bibliographystyle{unsrt}
\bibliography{Bibliography}
\end{document}

### 2018-04-06 Thesis plan/Thesis plan.tex
Updated hypothesis and research question

@@
 \begin{itemize}
-\item{Has the bag-of-words embedding method a higher accuracy for academic texts than TF-IDF?}
+\item{Has the word-to-vec embedding method a higher accuracy for academic texts than TF-IDF?}
 \subitem{Which parameter values create embeddings with the highest accuracy for academic texts?}
@@
 \begin{itemize}
-\item{The bag-of-words embedding method can have an higher accuracy for academic texts than the TF-IDF algorithm.}
-\item{The accuracy of embedding methods is related to the type of text.}
+\item{The word-to-vec embedding method can have an higher accuracy for academic texts than the TF-IDF algorithm.}
+\item{The accuracy of academic embedding methods can be validated using categorization tasks}
 \end{itemize}

### 2018-04-06 Thesis/Parts/Introduction/Introduction.tex
Initial thesis setup
Added annotations
updated introduction

--- 2018-04-05 Thesis/Parts/Abstract/Abstract.tex
@@
 \begin{document}
-\section{Abstract}
-[TODO: Abstract]
+\section{Document Embedding}
+The basic theory of word embedding can be explained by the following quote of J.R. Firth: "You shall know a word by the company it keeps". \\
+Word embedding as described by Lai et al, can capture both the semantic and syntactic
+information of words from a large unlabeled corpus.\cite{lai2016generate} Word embeddings are vector based representations of words, that can, depending on the model either predict the target word given context words, or predict context words, given the target word.
+Techniques based on word vectors have improved various NLP areas such as machine translation, [todo: add fields and references]
+
+\subsection{domain specific}
+Earlier work on this topic, concerning academic articles, by Truong[TODO: CITE] states the following: "Our findings clearly evinced that in-domain training of the
+word embeddings can drastically improve the process of document clustering. In fact, the
+effect is even stronger than the number of training examples and the model architecture.
+However, too isolated training can lead to a failure of several clustering algorithms, such
+as DBSCAN, due to a too dense vocabulary".
+This was also found by Lai et al, who state: "The corpus domain is more important than the corpus size.
+Using an indomain corpus significantly improves the performance for a given task, whereas using a corpus in an unsuitable domain may decrease performance".
+These statements both indicate that an indomain corpus improves the performance of word-vectors for those specific domains.
+However, domain specific validation techniques do not exist currently.
+Multiple generic validation sets have been published [TODO: insert comparison methods].
+These sets have been used in multiple studies of word-vectors[TODO REFERENCE] whom corpus existed of simular generic information [TODO: INSERT CORPUS DETAILS].
+These validation methods are limited to the non domain specific fields.
+\subsection{Embedding validation}[IS THIS TRUE?]Not published results of the study by Truong show high error rates on the validation scores, while the word-vectors seem to work well on document clustering.
+This seems to indicate that the word-vectors are well suited, but no objective validation method can confirm or deny this.
+Therefore, we propose the validation of word-embeddings through [SOLUTION].
+
 \end{document}

### 2018-04-09 Thesis plan/Thesis plan.tex
Updated research question and hypothesis

@@
 \subitem{Which parameter values create embeddings with the highest accuracy for academic texts?}
-\item{What is the relationship between the accuracy of an embedding method and the type of text?}
+\item{Which metric(s) can be used to measure the accuracy of word embeddings for scientific articles?}
 \end{itemize}
@@
 \item{The word-to-vec embedding method can have an higher accuracy for academic texts than the TF-IDF algorithm.}
-\item{The accuracy of academic embedding methods can be validated using categorization tasks}
+\item{The accuracy of academic embedding methods can be validated using classification tasks}
 \end{itemize}

### 2018-04-09 Annotations/Annotations.tex
Updated introduction

@@
 \end{itemize}
+\section{Better Word Representations with Recursive Neural Networks for Morphology}
+Paper by Luong et al.\cite{luong2013better}
+\begin{itemize}
+\item{The use of word representations or word clusters
+pretrained in an unsupervised fashion from lots of
+text has become a key “secret sauce” for the success
+of many NLP systems in recent years, across
+tasks including named entity recognition, part-ofspeech
+tagging, parsing, and semantic role labeling.}
+\item{The main advantage of having such a distributed
+representation over word classes is that it can capture
+various dimensions of both semantic and syntactic
+information in a vector where each dimension
+corresponds to a latent feature of the word. As
+a result, a distributed representation is compact,
+less susceptible to data sparsity, and can implicitly
+represent an exponential number of word clusters.}
+\item{The Rare-word dataset introduced by Luong et al.}
+\end{itemize}
 \bibliographystyle{unsrt}

### 2018-04-09 Thesis/Parts/Introduction/Introduction.tex
Updated introduction

@@
 This was also found by Lai et al, who state: "The corpus domain is more important than the corpus size.
-Using an indomain corpus significantly improves the performance for a given task, whereas using a corpus in an unsuitable domain may decrease performance".
-These statements both indicate that an indomain corpus improves the performance of word-vectors for those specific domains.
+Using an in-domain corpus significantly improves the performance for a given task, whereas using a corpus in an unsuitable domain may decrease performance".
+These statements both indicate that an in-domain corpus improves the performance of word-vectors for those specific domains.
 However, domain specific validation techniques do not exist currently.
-Multiple generic validation sets have been published [TODO: insert comparison methods].
-These sets have been used in multiple studies of word-vectors[TODO REFERENCE] whom corpus existed of simular generic information [TODO: INSERT CORPUS DETAILS].
+Multiple generic validation sets have been published such as:
+
+the Rare-word dataset introduced by Luong et al in their paper "Better Word Representations with Recursive Neural Networks for Morphology"\cite{luong2013better}, 
+the MEN test collection\cite{EBruniMENCollection} and the WordSimilarity-353 test collection\cite{EGabrilovichWScollection}.
+
+These sets have been used in multiple studies of word-vectors[TODO REFERENCE] which corpus existed of similar generic information [TODO: INSERT CORPUS DETAILS].
 These validation methods are limited to the non domain specific fields.
-\subsection{Embedding validation}[IS THIS TRUE?]Not published results of the study by Truong show high error rates on the validation scores, while the word-vectors seem to work well on document clustering.
+\subsection{Embedding validation}Not published results of the study by Truong show high error rates on the validation scores, while the word-vectors seem to work well on document clustering.
 This seems to indicate that the word-vectors are well suited, but no objective validation method can confirm or deny this.
@@
 
+\begin{tabular}{c c c c}
+&WordSim & Men & RareWords\\
+Lowest & 0.38 & 0.54 & 0.29 \\
+Highest & 0.49 & 0.61 & 0.32\\
+Average & 0.45 & 0.59 & 0.32\\
+Baseline & 0.64 & 0.68 & 0.34\\
+\end{tabular}
+
 \end{document}

### 2018-04-09 Thesis/Parts/Introduction/Introduction.tex
Updated thesis introduction

--- 2018-04-05 Thesis/Parts/Abstract/Abstract.tex
@@
 \begin{document}
-\section{Abstract}
-[TODO: Abstract]
+\header{Embedding}
+The basic theory of word embedding can be explained by the following quote of J.R.
+Firth: "You shall know a word by the company it keeps".
+Word embeddings are distributed representations of words (\citet{mikolov2013distributed}), which can capture both the semantic and syntactic information of words from a large unlabeled corpus (\citet{lai2016generate}).
+Word embeddings are vector based representations of words, that can, depending on the model either predict the target word given context words, or predict context words, given the target word.
+Techniques based on word vectors have improved various NLP areas such as named entity recognition, part-of-speech tagging, parsing, and semantic role labelling (\citet{luong2013better}).
+The word2vec model converts words via a learned lookuptable into real valued vectors \cite{mikolov2013linguistic}.
+\citet{mikolov2013linguistic} show that calculations with these vectors is also possible:
+\begin{displayquote}
+	X\textsubscript{apple} - X\textsubscript{apples} $\approx$  X\textsubscript{car} - X\textsubscript{cars}
+\end{displayquote}
+Furthermore they show that de distance in the vector space between "king" and "man" approximates the distance between "queen" and "women".
+Variations on the word2vec model have also been proposed, \citet{le2014distributed} introduced the paragraph vector, based on the word2vec model.
+The paragraph vector model uses additional variables to improve the accuracy of the word-embeddings.
+An advantage of the paragraph vector model is that it takes the word order into consideration, atleast in a small context \cite{le2014distributed}.
+For this reaseach, only word2vec will be used.
+\header{Domain specific}
+Earlier work on this topic, concerning academic articles, by (\citet{Truong2017Thesis}) states the following: 
+\begin{displayquote}
+"Our findings clearly evinced that in-domain training of the
+word embeddings can drastically improve the process of document clustering. In fact, the
+effect is even stronger than the number of training examples and the model architecture.
+However, too isolated training can lead to a failure of several clustering algorithms, such as DBSCAN, due to a too dense vocabulary" (\citet{Truong2017Thesis}).
+\end{displayquote}
+This was also found by Lai et al, who state: 
+\begin{displayquote}
+"The corpus domain is more important than the corpus size.
+Using an in-domain corpus significantly improves the performance for a given task, whereas using a corpus in an unsuitable domain may decrease performance" (\citet{lai2016generate}).
+\end{displayquote}
+These statements both indicate that an in-domain corpus improves the performance of word-vectors for those specific domains.
+However, domain specific validation techniques do not exist currently.
+Multiple generic validation sets are publicly available such as:
+the Rare-word dataset introduced in the paper "Better Word Representations with Recursive Neural Networks for Morphology" (\citet{luong2013better}), 
+the MEN test collection (\citet{EBruniMENCollection}) and the WordSimilarity-353 test collection (\citet{EGabrilovichWScollection}).
+These sets have been used in multiple studies of word-vectors, whom are referenced by the respective sources.
+These validation methods are limited to the non domain specific texts, since they do not contain words of specific domains.
+
+\header{Embedding validation}Not published results of the study by Truong show high error rates on the validation scores, this is presented in Table~\ref{table:truongErrorRates}.
+However, the word-vectors work well on document clustering, this seems to indicate that the word-vectors are able to represent the words.
+The problem is then that the currently used validation methods do not confirm or this.
+Therefore, we propose the validation of word-embeddings through [TODO: SOLUTION - classification - abstract/text/title matching - keyword categorization - ...].
+
+\begin{table}
+\begin{tabular}{c c c c}
+&WordSim & Men & RareWords\\
+Lowest & 0.38 & 0.54 & 0.29 \\
+Highest & 0.49 & 0.61 & 0.32\\
+Average & 0.45 & 0.59 & 0.32\\
+Baseline & 0.64 & 0.68 & 0.34
+\end{tabular}
+\caption{Table 1}\label{table:truongErrorRates}
+\end{table}
+\newpage
 \end{document}

### 2018-04-10 Thesis/Parts/Introduction/Introduction.tex
eod, updated introduction

--- 2018-04-06 Thesis/Parts/Introduction/Introduction.tex
@@
 \begin{document}
-\section{Document Embedding}
-The basic theory of word embedding can be explained by the following quote of J.R. Firth: "You shall know a word by the company it keeps". \\
-Word embedding as described by Lai et al, can capture both the semantic and syntactic
-information of words from a large unlabeled corpus.\cite{lai2016generate} Word embeddings are vector based representations of words, that can, depending on the model either predict the target word given context words, or predict context words, given the target word.
-Techniques based on word vectors have improved various NLP areas such as machine translation, [todo: add fields and references]
+\header{Embedding}
+%The basic theory of word embedding can be explained by the following quote of J.R. Firth: "You shall know a word by the company it keeps". 
+ML tasks rely on a numerical (vectorial) representation of text which we refer to as an embedding.
+This embedding can be calculated for texts of different lengths such as a title, sentence, paragraph or an entire document\cite{Karimi2017Deep}.
+Word embeddings are these numerical representations of a word, which, since the representation is a vector, is an distributed word representation over multiple (vector) dimensions(\citet{mikolov2013distributed}).
+Word embeddings can capture both the semantic and syntactic information of words from a large unlabeled corpus (\citet{lai2016generate}).
+%Word embeddings are vector based representations of words, that can, depending on the model either predict the target word given context words, or predict context words, given the target word. 
+Techniques based on word embeddings have improved various NLP areas such as named entity recognition, part-of-speech tagging, parsing, and semantic role labelling (\citet{luong2013better}).
+The word2vec model is a way of creating word embeddings.
+The model converts words via a learned lookuptable into real valued vectors\cite{mikolov2013linguistic}.
+\citet{mikolov2013linguistic} show that calculations with these vectors is possible:
+\begin{displayquote}
+	X\textsubscript{apple} - X\textsubscript{apples} $\approx$  X\textsubscript{car} - X\textsubscript{cars}
+\end{displayquote}
+Furthermore they show that de distance in the vector space between "king" and "man" approximates the distance between "queen" and "women".
+Variations on the word2vec model have also been proposed, \citet{le2014distributed} introduced the paragraph vector, based on the word2vec model.
+The paragraph vector model uses additional variables to improve the accuracy of the word-embeddings.
+An advantage of the paragraph vector model is that it takes the word order into consideration, atleast in a small context \cite{le2014distributed}.
+For this research, only word2vec will be used.
+\header{Domain specific}
+Earlier work on this topic, concerning domain specific articles, by (\citet{Truong2017Thesis}), found that  
+%start of literal quote
+in-domain training of the word embeddings can drastically improve the process of document clustering.
+In fact, the effect is even stronger than the number of training examples and the model architecture.
+However, too isolated training can lead to a failure of several clustering algorithms, such as DBSCAN, due to a too dense vocabulary\cite{Truong2017Thesis}.
+%end of literal quote
+\citet{lai2016generate} found that 
+%start literal quote
+the corpus domain is more important than the corpus size.
+Using an in-domain corpus significantly improves the performance for a given task, whereas using a corpus in an unsuitable domain may decrease performance.
+%end literal quote
+These findings both indicate that an in-domain corpus improves the performance of word embeddings for the specific domains. 
+\header{Embedding validation}
+Multiple validations of word embeddings have been used, including: Word analogy, text similarity, categorization and positional visualization.
+\subheader{Word Analogy}
+Word analogy validation is based on a labelled validation set, containing, commonly, word pairs of four, that can be logically divided into two parts. As  Table
+~\ref{table:wordAnalogies} shows, each last word can be derived from the three words before.
+The score is the fraction of correctly given fourth words, given the first three words.
+This validation metric is used in multiple studies\cite{mikolov2013distributed, mikolov2013efficient, dai2015document, pennington2014glove}.
+\begin{table}
+\begin{center}
+\begin{tabular}{c c c c}
+Man & Women & King & Queen \\
+Athens & Greece & Oslo & Norway\\
+great & greater & tough & tougher
+\end{tabular}
+\end{center}
+\caption{Word analogies used in word embedding validation}\label{table:wordAnalogies}
+\end{table}
+\subheader{Word Similarity}
+A method to test the quality of word embeddings is the word similarity test.
+For these test, the distance between the word embeddings (vectors) is measured and compared to similarity scores defined by humans.
+Multiple non domain specific validation sets are publicly available including: the Rare-word dataset introduced in the paper "Better Word Representations with Recursive Neural Networks for Morphology" by \citet{luong2013better},
+the MEN test collection by \citet{EBruniMENCollection} and the WordSimilarity-353 test collection by \citet{EGabrilovichWScollection}.
+These sets, among others, have been used in multiple studies of word embeddings\cite{pennington2014glove, mikolov2013efficient}. This validation metric also relies on labelled data.
+\subheader{Classification}
+The classification validation method is a simple task which compares multiple texts.
+\citet{lau2016empirical} used data from StackExchange and tried to determine if a pair was a duplicate.
+Even though the validation method is simple, it too used labelled data to validate the acquired results.
+\subheader{Categorization}
+\citet{le2014distributed} used for their research a dataset of IMDB with 100,000 movie review.
+They validated their proposed paragraph vector model by determining whether a review was positive or negative.
+\subheader{Position Visualization}
+(Unlabelled, Needs human validation)\citet{dai2015document} and \citet{hinton2003stochastic} mapped their word embeddings to a two dimensional vector to be able to display them in a graph and applied colors to various categories.
+The advantage of this is that a human can directly see that the embeddings make sense, however this approach is not applicable by a computer.
 
-\subsection{domain specific}
-Earlier work on this topic, concerning academic articles, by Truong[TODO: CITE] states the following: "Our findings clearly evinced that in-domain training of the
-word embeddings can drastically improve the process of document clustering. In fact, the
-effect is even stronger than the number of training examples and the model architecture.
-However, too isolated training can lead to a failure of several clustering algorithms, such
-as DBSCAN, due to a too dense vocabulary".
-This was also found by Lai et al, who state: "The corpus domain is more important than the corpus size.
-Using an indomain corpus significantly improves the performance for a given task, whereas using a corpus in an unsuitable domain may decrease performance".
-These statements both indicate that an indomain corpus improves the performance of word-vectors for those specific domains.
-However, domain specific validation techniques do not exist currently.
-Multiple generic validation sets have been published [TODO: insert comparison methods].
-These sets have been used in multiple studies of word-vectors[TODO REFERENCE] whom corpus existed of simular generic information [TODO: INSERT CORPUS DETAILS].
-These validation methods are limited to the non domain specific fields.
-\subsection{Embedding validation}[IS THIS TRUE?]Not published results of the study by Truong show high error rates on the validation scores, while the word-vectors seem to work well on document clustering.
-This seems to indicate that the word-vectors are well suited, but no objective validation method can confirm or deny this.
-Therefore, we propose the validation of word-embeddings through [SOLUTION].
+% Explanation of the word simularity
+ Even though this validation method is not limited to domains, the validation sets are, since they do not contain words of specific domains.
+At this moment, there are no sets for every domain which make it difficult to compare the accuracy of domain specific word embeddings to non domain specific word embeddings.
+% end explanation
+Unpublished results of the study by Truong encounter this problem, they show high error rates on the validation scores, presented in Table~\ref{table:truongErrorRates}.
+However, the word embeddings created correct document clusterings\cite{Truong2017Thesis}, this seems to indicate that the word-vectors are able to represent the words correctly.
+The problem is then that the available validation sets cannot confirm this.
+Therefore, we propose the validation of word-embeddings through [TODO: SOLUTION - classification - abstract/text/title matching - keyword categorization - ...] to eliminate the need for labelled data in the validation of word embeddings.
+This will enable us to find optimal parameters for the embedding of domain specific articles.
+\begin{table}
+\begin{center}
+\begin{tabular}{c c c c}
+&WordSim & Men & RareWords\\
+Lowest & 0.38 & 0.54 & 0.29 \\
+Highest & 0.49 & 0.61 & 0.32\\
+Average & 0.45 & 0.59 & 0.32\\
+Baseline & \textbf{0.64} & \textbf{0.68} & \textbf{0.34}
+\end{tabular}
+\end{center}
+\caption{Results for the different validation sets of word simularity validations on domain specific texts from the study by \citet{Truong2017Thesis}}\label{table:truongErrorRates}
+\end{table}
 

### 2018-04-11 Thesis/Parts/Introduction/Introduction.tex
Updated introduction

@@
 Techniques based on word embeddings have improved various NLP areas such as named entity recognition, part-of-speech tagging, parsing, and semantic role labelling (\citet{luong2013better}).
-The word2vec model is a way of creating word embeddings.
-The model converts words via a learned lookuptable into real valued vectors\cite{mikolov2013linguistic}.
-\citet{mikolov2013linguistic} show that calculations with these vectors is possible:
-\begin{displayquote}
-	X\textsubscript{apple} - X\textsubscript{apples} $\approx$  X\textsubscript{car} - X\textsubscript{cars}
-\end{displayquote}
-Furthermore they show that de distance in the vector space between "king" and "man" approximates the distance between "queen" and "women".
+\begin{jumpin}
+\subheader{Word2Vec}
+Word2vec word embeddings are created using neural network, Word2vec learns word embeddings via maximizing the log conditional probability of the word given the context word(s) occurring within a fixed-sized window.
+Therefore the learnt embeddings contain useful knowledge about word co-occurrence\cite{nalisnick2016improving}.
+There are multiple input/output possibilities for the neural network, best known are Skip-gram and the Continuous Bag-of-Words model (CBOW).
+The Skip-gram model takes a target word as input and outputs the predicted output words, while CBOW takes the context words as input and outputs the predicted target word\cite{nalisnick2016improving, pennington2014glove}.
+\subheader{Paragraph vectors}
 Variations on the word2vec model have also been proposed, \citet{le2014distributed} introduced the paragraph vector, based on the word2vec model.
@@
 An advantage of the paragraph vector model is that it takes the word order into consideration, atleast in a small context \cite{le2014distributed}.
+\subheader{GloVe}
+\citet{pennington2014glove} introduced the GloVe (Global Vectors) model.
+This model captures the global corpus statistics.
+The model transforms the word co-occurrences of all words in the corpus to chances, it excludes all the zero values and uses that as initial input for the neural network.\\
+\end{jumpin}
 For this research, only word2vec will be used.
@@
 These findings both indicate that an in-domain corpus improves the performance of word embeddings for the specific domains.
+
+\newpage
 \header{Embedding validation}
 Multiple validations of word embeddings have been used, including: Word analogy, text similarity, categorization and positional visualization.
+\begin{jumpin}
 \subheader{Word Analogy}
@@
 \end{table}
+Both this validation technique and the Word Similarity technique use vector distance calculations to validate the embeddings, this can therefore also be written as:
+\begin{displayquote}
+	X\textsubscript{Man} - X\textsubscript{King} $\approx$  X\textsubscript{Women} - X\textsubscript{Queen}
+\end{displayquote}
 \subheader{Word Similarity}
@@
 (Unlabelled, Needs human validation)\citet{dai2015document} and \citet{hinton2003stochastic} mapped their word embeddings to a two dimensional vector to be able to display them in a graph and applied colors to various categories.
-The advantage of this is that a human can directly see that the embeddings make sense, however this approach is not applicable by a computer.
-
-% Explanation of the word simularity
- Even though this validation method is not limited to domains, the validation sets are, since they do not contain words of specific domains.
+The advantage of this is that a human can directly see that the embeddings make sense, however this approach is not applicable by a computer.\\
+\end{jumpin}
+Even though these validation methods are not limited to domains, the labelled data they use are, since they do not contain words of specific domains.
 At this moment, there are no sets for every domain which make it difficult to compare the accuracy of domain specific word embeddings to non domain specific word embeddings.
-% end explanation
+\header{Problems in validation}
 Unpublished results of the study by Truong encounter this problem, they show high error rates on the validation scores, presented in Table~\ref{table:truongErrorRates}.
-However, the word embeddings created correct document clusterings\cite{Truong2017Thesis}, this seems to indicate that the word-vectors are able to represent the words correctly.
-The problem is then that the available validation sets cannot confirm this.
+However, the word embeddings created correct document clusterings\cite{Truong2017Thesis}, this seems to indicate that the word-vectors are able to represent the words correctly but that the available validation sets cannot confirm this.
 Therefore, we propose the validation of word-embeddings through [TODO: SOLUTION - classification - abstract/text/title matching - keyword categorization - ...] to eliminate the need for labelled data in the validation of word embeddings.

### 2018-04-16 Thesis plan/Thesis plan.tex
updated thesis plan

@@
 \item{Has the word-to-vec embedding method a higher accuracy for academic texts than TF-IDF?}
-\subitem{Which parameter values create embeddings with the highest accuracy for academic texts?}
+\item{Which parameter values create embeddings with the highest accuracy for academic texts?}
 \item{Which metric(s) can be used to measure the accuracy of word embeddings for scientific articles?}
@@
 \begin{itemize}
-\item{The word-to-vec embedding method can have an higher accuracy for academic texts than the TF-IDF algorithm.}
+\item{The word-to-vec embedding method can have an higher accuracy or more utility\footnote{as in, reduced storing capacity and scalability to document/journal level} for academic texts than the TF-IDF algorithm.}
 \item{The accuracy of academic embedding methods can be validated using classification tasks}
@@
 \begin{itemize}
-\item{Comparison of multiple embedding methods for a collection of academic texts}
+\item{Comparison of multiple embedding validation methods for a collection of academic texts}
 \subitem{- If possible, a best-to-use method}
-\item{Validation of the hypothesis 'The accuracy of embedding methods is related to the type of text.'}
+\item{Validation of the hypothesis 'The word-to-vec embedding method can have an higher accuracy for academic texts than the TF-IDF algorithm.'}
 \subitem{- If these are related, an analysis of relationship in accuracy of the methods for the academic and non-academic texts.}

### 2018-04-16 Thesis plan/Thesis plan.tex
update thesis plan v1.1

@@
 \begin{titlepage}
-\title{Thesis plan\\Version 1.0}
+\title{Thesis plan\\Version 1.1}
 \author{Arjan Meijer\\11425555}
@@
 \item{Has the word-to-vec embedding method a higher accuracy for academic texts than TF-IDF?}
-\item{Which parameter values create embeddings with the highest accuracy for academic texts?}
 \item{Which metric(s) can be used to measure the accuracy of word embeddings for scientific articles?}
+\item{Which parameter values create embeddings with the highest accuracy for academic texts?\footnote{This research question will only be answered if there is sufficient time left}}
 \end{itemize}
-To answer the first research question, the optimal parameters for the embedding method have to be found.
-The comparison between embedding and TF-IDF must only be done with the optimal parameters for the embedding method.
 \section{Problem Analysis}
@@
 \end{itemize}
+The utility will be measured by the vector size of the resulting representation, for word embeddings but also for the TF-IDF algorithm.
+Furthermore, the utility will be measured by the accuracy on higher level (article/journal) representation.
+
 \paragraph{Validation} This research will be validated via a clear presentation of all compared results.
@@
 The correct matched percentage will be the result score for the algorithm/embedding method.\\
-\paragraph{First experiment}The goal of the first experiment is to compare the results of my algorithm to earlier researches by comparing the results for the Wikipedia set\footnote{Which is also used in earlier researches}.
-This will ensure that the algorithm I use is comparable, and thus add legitimacy to the research.
-I expect that this is a small experiment, since it should only recreate already found results.\\
-\paragraph{Second experiment}The second experiment is finding the optimal parameters for the set of academic papers.
+\paragraph{First experiment}The goal of the first experiment is to measure the accuracy of the (already present) word embeddings, and to collect the found accuracy results for the word embeddings.
+\paragraph{Second experiment}The second experiment is creating the TF-IDF algorithm in the research environment and collecting data on its search results.
+This experiment will not take much time, since the TF-IDF is a simple algorithm to implement.\\
+\paragraph{Comparison}
+Thereafter, the the collected data from experiments 2 and 3 will be compared, with this information, I will be able to accept or dismiss the hypothesis, and with that, answer the research questions.\\
+\paragraph{Third experiment}The third experiment is finding the optimal parameters for the set of academic papers.
 This will be done by fine-tuning the parameters in search for an optimal result, furthermore, the results of this process must be registered for comparison.
@@
 This experiment also includes data gathering for the comparison of the methods.\\
-\paragraph{Third experiment}The third experiment is creating the TF-IDF algorithm in the research environment and collecting data on its search results.
-This experiment will not take much time, since the TF-IDF is a simple algorithm to implement.\\
-\paragraph{Comparison}
-The final step is the comparison of the collected data from experiments 2 and 3, with this information, I will be able to accept or dismiss the hypothesis, and with that, answer the research questions.\\
+\paragraph{Final comparison}
+The final step is to compare the accuracy score of the obtained word-vectors to the results of the previous comparison. This will enable me to validate the remaining research question.
 
@@
 \textbf{Focus} & \textbf{Number of weeks} & \textbf{Date} \\
-Setting up workspace & 1 & April 3 - April 6\\
-Implementing methods & 2 & April 9 - April 20\\
-Finding optimal & 3 & April 23 - May 11\\
-embedding parameters & & \\
-Data gathering experiment 1 & 1 & May 14 - May 18\\
-Data gathering experiment 2 & 1 & May 21 - May 25\\
-Writing & 2 & May 28 - June 8\\
-Correction & 1 & June 11 - June 15\\
-Submission & 1 & June 18 - June 22\\
-Total & 12 & presentation date (NOT YET CONFIRMED) July 10\\
+Setting up workspace & 1 & April 3 - April 13\\
+Initial validation set-up & 2 & April 16 - April 20\\
+Applying validation methods to large scale set & 3 & April 23 - April 27\\
+Data gathering experiment 1 & 1 & April 30 - May 4\\
+Data gathering experiment 2 & 1 & May 7 - May 11\\
+Comparison & 1 & May 14 - May 18\\
+Data gathering experiment 3 & 2 & May 21 - June 1 \\
+Comparison & 1 & June 4 - June 8\\
+Finishing writing & 2 & June 11 - June 22\\
+Total & 12 & presentation date, July 10\\
 \end{tabular}\\
 \end{center}
-*  for non-academic texts\\ ** for academic texts
-
 \section{Risks}

### 2018-05-01 Annotations/Annotations.tex
Updated annotations

--- 2018-04-05 Annotations/Annotations.tex
@@
 \end{itemize}
+\section{Better Word Representations with Recursive Neural Networks for Morphology}
+Paper by Luong et al.\cite{luong2013better}
+\begin{itemize}
+\item{The use of word representations or word clusters
+pretrained in an unsupervised fashion from lots of
+text has become a key “secret sauce” for the success
+of many NLP systems in recent years, across
+tasks including named entity recognition, part-ofspeech
+tagging, parsing, and semantic role labeling.}
+\item{The main advantage of having such a distributed
+representation over word classes is that it can capture
+various dimensions of both semantic and syntactic
+information in a vector where each dimension
+corresponds to a latent feature of the word. As
+a result, a distributed representation is compact,
+less susceptible to data sparsity, and can implicitly
+represent an exponential number of word clusters.}
+\item{The Rare-word dataset introduced by Luong et al.}
+\end{itemize}
+\section{Evaluation methods for unsupervised word embeddings}
+Paper by Schnabel et al. \cite{schnabel2015evaluation}
+\begin{itemize}
+\item{Neural word embeddings represent meaning via
+geometry. A good embedding provides vector representations
+of words such that the relationship between
+two vectors mirrors the linguistic relationship
+between the two words.}
+\item{Existing schemes fall into two major categories: extrinsic and intrinsic evaluation.
+In extrinsic evaluation, we use word embeddings as input features to a downstream task and measure changes in performance metrics specific to that task.
+Examples include part-of-speech tagging and named-entity recognition (Pennington et al., 2014).
+Extrinsic evaluation only provides one way to specify the goodness of an embedding, and it is not clear how it connects to other measures.
+Intrinsic evaluations directly test for syntactic or semantic relationships between words (Mikolov et al., 2013a; Baroni et al., 2014).}
+\item{This is the first
+paper to conduct a comprehensive study covering a wide range of evaluation criteria and popular embedding techniques.
+In particular, we study how outcomes from three different evaluation criteria are connected: word relatedness, coherence, downstream performance.}
+\item{Embedding methods should be compared in the context of a specific task, e.g., linguistic insight or good downstream performance.}
+\item{We observe that word embeddings encode
+a surprising degree of information about
+word frequency.
+We found this was true even in models that explicitly reserve parameters to compensate for frequency effects.
+This finding may explain some of the variability across embeddings and across evaluation methods.
+It also casts doubt on the common practice of using the vanilla cosine similarity as a similarity measure in the embedding space.}
+\item{Extrinsic evaluations measure the contribution of
+a word embedding model to a specific task.
+There is an implicit assumption in the use of such evaluations that there is a consistent, global ranking of word embedding quality, and that higher quality embeddings will necessarily improve results on any downstream task.
+We find that this assumption does not hold: different tasks favor different embeddings}
+\item{Performance on downstream tasks is not consistent across tasks, and may not be consistent with intrinsic evaluations.
+Comparing performance across tasks may provide insight into the information encoded by an embedding, but we should not expect any specific task to act as a proxy for abstract quality.}
+\item{Word frequency information in the embedding space also affects cosine similarity}
+\item{ Also, the above results mean that the commonly-used cosine similarity in the embedding space for the intrinsic tasks gets polluted by frequency-based effects}
+\item{Factors such as word frequency
+play a significant and previously unacknowledged role. Word frequency also interferes with the commonly-used cosine similarity measure.}
+\end{itemize}
 \bibliographystyle{unsrt}

### 2018-05-22 Annotations/Annotations.tex
Laptop switch

@@
 Intrinsic evaluations directly test for syntactic or semantic relationships between words (Mikolov et al., 2013a; Baroni et al., 2014).}
-\item{This is the first
-paper to conduct a comprehensive study covering a wide range of evaluation criteria and popular embedding techniques.
+\item{This is the first paper to conduct a comprehensive study covering a wide range of evaluation criteria and popular embedding techniques.
 In particular, we study how outcomes from three different evaluation criteria are connected: word relatedness, coherence, downstream performance.}
 \item{Embedding methods should be compared in the context of a specific task, e.g., linguistic insight or good downstream performance.}
-\item{We observe that word embeddings encode
-a surprising degree of information about
-word frequency.
+\item{We observe that word embeddings encode a surprising degree of information about word frequency.
 We found this was true even in models that explicitly reserve parameters to compensate for frequency effects.
@@
 It also casts doubt on the common practice of using the vanilla cosine similarity as a similarity measure in the embedding space.}
-\item{Extrinsic evaluations measure the contribution of
-a word embedding model to a specific task.
+\item{Extrinsic evaluations measure the contribution of a word embedding model to a specific task.
 There is an implicit assumption in the use of such evaluations that there is a consistent, global ranking of word embedding quality, and that higher quality embeddings will necessarily improve results on any downstream task.

### 2018-05-22 Thesis/Parts/Background/Background.tex
Laptop switch

--- 2018-04-11 Thesis/Parts/Introduction/Introduction.tex
@@
 \begin{document}
+\section{Background}
 \header{Embedding}
 %The basic theory of word embedding can be explained by the following quote of J.R. Firth: "You shall know a word by the company it keeps". 
-ML tasks rely on a numerical (vectorial) representation of text which we refer to as an embedding.
-This embedding can be calculated for texts of different lengths such as a title, sentence, paragraph or an entire document\cite{Karimi2017Deep}.
-Word embeddings are these numerical representations of a word, which, since the representation is a vector, is an distributed word representation over multiple (vector) dimensions(\citet{mikolov2013distributed}).
-Word embeddings can capture both the semantic and syntactic information of words from a large unlabeled corpus (\citet{lai2016generate}).
-%Word embeddings are vector based representations of words, that can, depending on the model either predict the target word given context words, or predict context words, given the target word. 
-Techniques based on word embeddings have improved various NLP areas such as named entity recognition, part-of-speech tagging, parsing, and semantic role labelling (\citet{luong2013better}).
+Machine learning (ML) tasks rely on a numerical (vectorial) representation of text which we refer to as an embedding.
+These can be calculated for texts of different lengths such as a title, sentence, paragraph or an entire document\cite{Karimi2017Deep}.
+Word embeddings are these numerical representations of a word, these vectors are an distributed representation of the word over the multiple (vector) dimensions(\citet{mikolov2013distributed}).
+The word embeddings can be used to construct embedding of larger texts.
+Word embeddings can capture both the semantic and syntactic information of words.
+The advantage of the machine learning models is that it can be done without human-interaction(\citet{lai2016generate}).
+Word embeddings have improved various Natural Language Processing (NLP) areas such as named entity recognition, part-of-speech tagging, parsing, and semantic role labelling (\citet{luong2013better}).
 \begin{jumpin}
@@
 The model transforms the word co-occurrences of all words in the corpus to chances, it excludes all the zero values and uses that as initial input for the neural network.\\
+\subheader{TF-IDF}
+TF-IDF is an abbreviation for Term Frequency - Inversed Document Frequency.
+This method does not rely on a neural network, and does not require training.
+According to a paper by \citet{beel2016paper} from 2016, "TF-IDF was the most popular weighting scheme (70\%) among those approaches for which the scheme was specified" (in the recommendation class 'Content-based filtering').
+The TFIDF score is the product of the term frequency in a text and the inversed document frequency of the same term in a corpus of texts.
+Both of which can be calculated in a variety of ways.
 \end{jumpin}
-For this research, only word2vec will be used.
-\header{Domain specific}
-Earlier work on this topic, concerning domain specific articles, by (\citet{Truong2017Thesis}), found that  
-%start of literal quote
-in-domain training of the word embeddings can drastically improve the process of document clustering.
-In fact, the effect is even stronger than the number of training examples and the model architecture.
-However, too isolated training can lead to a failure of several clustering algorithms, such as DBSCAN, due to a too dense vocabulary\cite{Truong2017Thesis}.
-%end of literal quote
-\citet{lai2016generate} found that 
-%start literal quote
-the corpus domain is more important than the corpus size.
-Using an in-domain corpus significantly improves the performance for a given task, whereas using a corpus in an unsuitable domain may decrease performance.
-%end literal quote
-These findings both indicate that an in-domain corpus improves the performance of word embeddings for the specific domains.
 
-\newpage
 \header{Embedding validation}
+Embedding validation techniques are methods that are used to validate the quality\footnote{With quality we mean the extend to which the task is completed correctly} of an embedding for a specific task(\citet{schnabel2015evaluation}).
 Multiple validations of word embeddings have been used, including: Word analogy, text similarity, categorization and positional visualization.
@@
 \end{displayquote}
+This means that the resulting vector of embedding of "Man" minus the embedding of "King" is approximately the embedding of "Woman" minus the embedding of "Queen".
+This resulting vector may be close to a vector "monarch" for example.
 \subheader{Word Similarity}
@@
 \end{jumpin}
-Even though these validation methods are not limited to domains, the labelled data they use are, since they do not contain words of specific domains.
+Even though these validation methods are not limited to domains, the labelled data they use are, since they do not consist of words of specific domains.
 At this moment, there are no sets for every domain which make it difficult to compare the accuracy of domain specific word embeddings to non domain specific word embeddings.
-\header{Problems in validation}
-Unpublished results of the study by Truong encounter this problem, they show high error rates on the validation scores, presented in Table~\ref{table:truongErrorRates}.
-However, the word embeddings created correct document clusterings\cite{Truong2017Thesis}, this seems to indicate that the word-vectors are able to represent the words correctly but that the available validation sets cannot confirm this.
-Therefore, we propose the validation of word-embeddings through [TODO: SOLUTION - classification - abstract/text/title matching - keyword categorization - ...] to eliminate the need for labelled data in the validation of word embeddings.
-This will enable us to find optimal parameters for the embedding of domain specific articles.
-\begin{table}
-\begin{center}
-\begin{tabular}{c c c c}
-&WordSim & Men & RareWords\\
-Lowest & 0.38 & 0.54 & 0.29 \\
-Highest & 0.49 & 0.61 & 0.32\\
-Average & 0.45 & 0.59 & 0.32\\
-Baseline & \textbf{0.64} & \textbf{0.68} & \textbf{0.34}
-\end{tabular}
-\end{center}
-\caption{Results for the different validation sets of word simularity validations on domain specific texts from the study by \citet{Truong2017Thesis}}\label{table:truongErrorRates}
-\end{table}
-
 \end{document}

### 2018-05-22 Thesis/Parts/Introduction/Introduction.tex
Laptop switch

--- 2018-04-09 Thesis/Parts/Introduction/Introduction.tex
@@
 \begin{document}
-\header{Embedding}
-The basic theory of word embedding can be explained by the following quote of J.R.
-Firth: "You shall know a word by the company it keeps".
-Word embeddings are distributed representations of words (\citet{mikolov2013distributed}), which can capture both the semantic and syntactic information of words from a large unlabeled corpus (\citet{lai2016generate}).
-Word embeddings are vector based representations of words, that can, depending on the model either predict the target word given context words, or predict context words, given the target word.
-Techniques based on word vectors have improved various NLP areas such as named entity recognition, part-of-speech tagging, parsing, and semantic role labelling (\citet{luong2013better}).
-The word2vec model converts words via a learned lookuptable into real valued vectors \cite{mikolov2013linguistic}.
-\citet{mikolov2013linguistic} show that calculations with these vectors is also possible:
-\begin{displayquote}
-	X\textsubscript{apple} - X\textsubscript{apples} $\approx$  X\textsubscript{car} - X\textsubscript{cars}
-\end{displayquote}
-Furthermore they show that de distance in the vector space between "king" and "man" approximates the distance between "queen" and "women".
-Variations on the word2vec model have also been proposed, \citet{le2014distributed} introduced the paragraph vector, based on the word2vec model.
-The paragraph vector model uses additional variables to improve the accuracy of the word-embeddings.
-An advantage of the paragraph vector model is that it takes the word order into consideration, atleast in a small context \cite{le2014distributed}.
-For this reaseach, only word2vec will be used.
-\header{Domain specific}
-Earlier work on this topic, concerning academic articles, by (\citet{Truong2017Thesis}) states the following: 
-\begin{displayquote}
-"Our findings clearly evinced that in-domain training of the
-word embeddings can drastically improve the process of document clustering. In fact, the
-effect is even stronger than the number of training examples and the model architecture.
-However, too isolated training can lead to a failure of several clustering algorithms, such as DBSCAN, due to a too dense vocabulary" (\citet{Truong2017Thesis}).
-\end{displayquote}
-This was also found by Lai et al, who state: 
-\begin{displayquote}
-"The corpus domain is more important than the corpus size.
-Using an in-domain corpus significantly improves the performance for a given task, whereas using a corpus in an unsuitable domain may decrease performance" (\citet{lai2016generate}).
-\end{displayquote}
-These statements both indicate that an in-domain corpus improves the performance of word-vectors for those specific domains.
-However, domain specific validation techniques do not exist currently.
-Multiple generic validation sets are publicly available such as:
-the Rare-word dataset introduced in the paper "Better Word Representations with Recursive Neural Networks for Morphology" (\citet{luong2013better}), 
-the MEN test collection (\citet{EBruniMENCollection}) and the WordSimilarity-353 test collection (\citet{EGabrilovichWScollection}).
-These sets have been used in multiple studies of word-vectors, whom are referenced by the respective sources.
-These validation methods are limited to the non domain specific texts, since they do not contain words of specific domains.
 
-\header{Embedding validation}Not published results of the study by Truong show high error rates on the validation scores, this is presented in Table~\ref{table:truongErrorRates}.
-However, the word-vectors work well on document clustering, this seems to indicate that the word-vectors are able to represent the words.
-The problem is then that the currently used validation methods do not confirm or this.
-Therefore, we propose the validation of word-embeddings through [TODO: SOLUTION - classification - abstract/text/title matching - keyword categorization - ...].
-
-\begin{table}
-\begin{tabular}{c c c c}
-&WordSim & Men & RareWords\\
-Lowest & 0.38 & 0.54 & 0.29 \\
-Highest & 0.49 & 0.61 & 0.32\\
-Average & 0.45 & 0.59 & 0.32\\
-Baseline & 0.64 & 0.68 & 0.34
-\end{tabular}
-\caption{Table 1}\label{table:truongErrorRates}
-\end{table}
-\newpage
 \end{document}

### 2018-05-22 Thesis/Parts/Motivation/Motivation.tex
Laptop switch

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\section{Motivation}
\header{Domain specific}
Earlier work on this topic, concerning domain specific articles, by (\citet{Truong2017Thesis}), found that  
%start of literal quote
in-domain training of the word embeddings can drastically improve the process of document clustering. In fact, the effect is even stronger than the number of training examples and the model architecture. However, too isolated training can lead to a failure of several clustering algorithms, such as DBSCAN, due to a too dense vocabulary\cite{Truong2017Thesis}. 
%end of literal quote
\citet{lai2016generate} found that 
%start literal quote
the corpus domain is more important than the corpus size. Using an in-domain corpus significantly improves the performance for a given task, whereas using a corpus in an unsuitable domain may decrease performance. 
%end literal quote
These findings both indicate that an in-domain corpus improves the performance of word embeddings for the specific domains.

\newpage

\header{Problems in validation}
Unpublished results of the study by Truong encounter this problem, they show high error rates on the validation scores, presented in Table~\ref{table:truongErrorRates}. However, the word embeddings created correct document clusterings\cite{Truong2017Thesis}, this seems to indicate that the word-vectors are able to represent the words correctly but that the available validation sets cannot confirm this.\\
Furthermore, a study by \citet{schnabel2015evaluation} found that the quality of embeddings are tasks specific, \textit{different tasks favour different embeddings}. They also found that the embeddings encode information about word frequency, even in models that are created to prevent this. \textit{This casts doubt on the common practice of using vanilla cosine similarity as a similarity measure}.\\
Therefore, we propose the validation of domain specific word-embeddings through a classification tasks, using multiple vector-distance calculations. This eliminates the need for labelled data in the validation of these domain specific word embeddings, will validate the quality of word embeddings for domain specific texts, and will validate the impact of different vector-distance measures on a categorization task.
\begin{table}
\begin{center}
\begin{tabular}{c c c c}
&WordSim & Men & RareWords\\
Lowest & 0.38 & 0.54 & 0.29 \\
Highest & 0.49 & 0.61 & 0.32\\
Average & 0.45 & 0.59 & 0.32\\
Baseline & \textbf{0.64} & \textbf{0.68} & \textbf{0.34}
\end{tabular}
\end{center}
\caption{Results for the different validation sets of word simularity validations on domain specific texts from the study by \citet{Truong2017Thesis}}\label{table:truongErrorRates}
\end{table}
\end{document}

### 2018-05-22 Thesis/Parts/Research_setup/Research_setup.tex
Laptop switch

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}

\header{Experiment setup}
We used the following pipeline to collect the performance metrics for the categorization task:
\begin{enumerate}
\item{Create embeddings}
\item{Filter articles}
\item{Create training and validation set}
\item{Create journal embeddings}
\item{Categorize validation articles}
\item{Calculate performance metrics}
\end{enumerate}

\subheader{Create embeddings}
For this research, we used word-embeddings (created using the word2vec model) and TF-IDF embeddings. The word-embeddings were created with the word2vec model from PySparks MlLib library\cite{PysparkMlLib}. The embeddings have a vector size of 300. We used Elseviers' internal, pre-made word-embeddings for this research because of the training-time required for the word2vec model.
The TF-IDF embeddings were created with the TF-IDF model from pyspark's MlLib library\cite{PysparkMlLib}, in combination with a term hasher (HashingTF) from the same library. We used multiple hashing dimensions: 100, 256, 300 \& 512. Since the TF-IDF uses the output of the term hasher, the TF-IDF model produces the same dimensions.
\subheader{Filter articles}
We create our initial set of articles by collecting all articles from the journals that were published in the year 2017, and have at least 200 publications in 2017. This reduces the journal set to $2,679$ journals, resulting in a set of $18,870,446$ articles.
\subheader{Create training and validation set}
We split our initial set in an 80\% - 20\% split, we use the 80\% set as the training set for the journal embeddings, and the 20\% set as the validation set for the journal embeddings.
\subheader{Create journal embeddings}
From our training set we create the journal embeddings by averaging all title embeddings as the journal title embedding, and by averaging all abstract embeddings as the journal abstract embedding. We also normalized both embeddings. 
\subheader{Categorize validation articles}
To categorize the articles, we calculate the distance between the title- and abstract embedding of each article, from the validation set, to the title- and abstract embedding of each journal. To calculate the distance, we use cosine similarity (as provided by the SciPy library\cite{SciPy}). During this process we keep track of:
\begin{itemize}
\item{Title-based-rank of the actual journal}
\item{Abstract-based-rank of the actual journal}
\item{Best scored journal on the abstract similarity}
\item{Best scored journal on the title similarity}
\item{Abstract similarity between the actual journal and the article}
\item{Title similarity between the actual journal and the article}
\end{itemize}
\subheader{Performance measurement}
We use multiple metrics to indicate the performance of the embeddings on a categorization task. These metrics are:
\begin{enumerate}
\item{F1-score}
\item{Median abstract rank}
\item{Median title rank}
\end{enumerate}
\subheader{ - F1-score}
We calculate the F1 score per article, to do this, we use the following metrics:\\
$True Positive = $ Articles that are correctly matched to the current journal\\
$False Positive = $ Articles that are incorrectly matched to other journals\\
$False Negative = $ Articles that are incorrectly matched to the current journal\\
$Recall = \dfrac{True Positive}{True Positive + False Negative}$\\\\
$Precision = \dfrac{True Positive}{True Positive + False Positive}$\\\\
$F1 = \dfrac{2 * Precision * Recall}{Precision + Recall}$\\
\subheader{ - Median abstract rank}
We use the median abstract rank to indicate around which rank the 'standard' article would be ranked, based on its abstract. We do this by taking the median of the abstract rank from each article.
\subheader{ - Median title rank}
We use the median title rank to indicate around which rank the 'standard' article would be ranked, based on its title. We do this by taking the median of the title rank from each article.
\end{document}

### 2018-06-11 Thesis/Parts/Motivation/Motivation.tex
thesis update

@@
 %start of literal quote
-in-domain training of the word embeddings can drastically improve the process of document clustering.
-In fact, the effect is even stronger than the number of training examples and the model architecture.
-However, too isolated training can lead to a failure of several clustering algorithms, such as DBSCAN, due to a too dense vocabulary\cite{Truong2017Thesis}.
+in-domain training of the word embeddings can  improve the process of document clustering.
+This effect is even stronger than the number of training examples and the model architecture.\cite{Truong2017Thesis}.
 %end of literal quote
@@
 
-\newpage
-
 \header{Problems in validation}
+To assess the quality (or usability) of the embeddings, validation methods are used.
+This are tasks designed to produce a metric that gives an indication of the usability of the provided embeddings.
+\citet{schnabel2015evaluation} found that the validation method indicates only the quality of an embedding for a specific task.
+There is (yet) no methtod that can asses the usability of an embedding on all possible tasks, since each task may require other information to be embedded into the embedding.
+Validation methods use either labelled or unlabelled data.
+Labelled data is data that is in some way marked, so that the correct answer can be derived from it.
+Unlabelled is the opposite, this data is not marked.\\
+The usage of labelled data is common practice for validation methods, since the results produced by this data can be easily checked checked.
 Unpublished results of the study by Truong encounter this problem, they show high error rates on the validation scores, presented in Table~\ref{table:truongErrorRates}.
@@
 &WordSim & Men & RareWords\\
-Lowest & 0.38 & 0.54 & 0.29 \\
-Highest & 0.49 & 0.61 & 0.32\\
-Average & 0.45 & 0.59 & 0.32\\
-Baseline & \textbf{0.64} & \textbf{0.68} & \textbf{0.34}
+Best results from the research by Truong: & 0.49 & 0.61 & 0.32\\
+Average  results from the research by Truong & 0.45 & 0.59 & 0.32\\
 \end{tabular}

### 2018-06-11 Thesis/Parts/Research_results/Research_results.tex
thesis update

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Research results}
\subheader{Ranking}
\includegraphics[width=6in]{Plots/Abstract_rankings}\\
\\
\includegraphics[width=6in]{Plots/Title_rankings}\\
\subheader{Rank distribution}
\includegraphics[width=6in]{Plots/Abstract_rank_distribution}\\
\\
\includegraphics[width=6in]{Plots/Title_rank_distribution}\\
\subheader{F1-Score}
d
\end{document}

### 2018-06-11 Thesis/Parts/Research_setup/Research_setup.tex
thesis update

@@
 The word-embeddings were created with the word2vec model from PySparks MlLib library\cite{PysparkMlLib}.
-The embeddings have a vector size of 300.
-We used Elseviers' internal, pre-made word-embeddings for this research because of the training-time required for the word2vec model.
-The TF-IDF embeddings were created with the TF-IDF model from pyspark's MlLib library\cite{PysparkMlLib}, in combination with a term hasher (HashingTF) from the same library.
-We used multiple hashing dimensions: 100, 256, 300 \& 512.
+The embeddings were pre-trained and have a vector size of 300, which is an industry default.
+The TF-IDF embeddings were created with the TF-IDF model from pyspark's MlLib library\cite{PysparkMlLib}, in combination with a token hasher (HashingTF) from the same library.
+We used multiple hashing dimensions and multiple vocabulary sizes.
 Since the TF-IDF uses the output of the term hasher, the TF-IDF model produces the same dimensions.
+We will denote the tfidf sets as vocabulary size/hashing size.
+All of our sets, both embedding and TF-IDF, use tokenized texts.
+\subsubheader{Tokenization}
+== TODO ==
+\subsubheader{TF-IDF selection}
+To limit computational expenses, we used only the top performing which can reasonably be kept in RAM.
+The plot displays the ranking \& size for the 1000/1000, 4000/4000, 7000/7000 and 10.000/10.000 sets respectively.\\
+\includegraphics[width=6in]{Plots/tfidf_selection_plot}\\
+The plot show the median abstract \& title rank and the storage size in Gigabytes (1024 based) plotted over feature size, which is equal to the hashing size for these sets.
+The plot shows that both title and abstract are stagnating, while the memory usage is, slowly, going up.
+At a feature size of 10.000, we have a storage size of 11.6GB.
+Given this size and the stagnation of the rankings, we chose to use the 10.000/10.000 feature size tfidf vectors, we furthermore used the 10.000/5000 set and the 5000/5000 set for comparison.
+
+\subsubheader{Embeddings}
+We have made use of multiple embedding sets for this research.
+All sets share the same (default) embedding and have been (uniquely) modified.
+For this research we have used the following embedding sets:
+\begin{enumerate}
+\item{Default embedding}
+\subitem{The embedding as generated by word2vec, without further enhancements.}
+\item{TF-IDF embedding}
+\subitem{The embedding as generated by the word2vec, multiplied by their tfidf weights to embed word priorities. We use this enhancement to give the embeddings more information about the corpus.}
+\item{10K TF-IDF Embedding}
+\subitem{The embedding as generated by the word2vec, filtered on the top 10.000 most common words, multiplied by their tfidf weights.\\We use this enhancement to try to filter out possible noise created by lots of words with few occurrences.}
+\item{5K TF-IDF Embedding}
+\subitem{The embedding as generated by the word2vec, filtered on the top 5.000 most common words, multiplied by their tfidf weights.\\We use this enhancement to cancel out the noise caused be rare words more aggressively}
+\item{1K 6K TF-IDF Embedding}
+\subitem{The embeddings as generated by the word2vec, filtered on the top top 1.000 till top 5.000 most common words, multiplied by their tfidf weights.\\We use this enhancement to ignore the top 1.000 most common words, which are most likely generic words, since they occur often.
+And to cancel out the rare-words, by cutting off all words after 6K.
+This gives us a set of 5K words.}
+\end{enumerate}
+
 \subheader{Filter articles}
 We create our initial set of articles by collecting all articles from the journals that were published in the year 2017, and have at least 200 publications in 2017.
-This reduces the journal set to $2,679$ journals, resulting in a set of $18,870,446$ articles.
+This reduces the journal set to $3,759$ thousand journals, resulting in a set of $1,391,543$ million articles ().
 \subheader{Create training and validation set}
-We split our initial set in an 80\% - 20\% split, we use the 80\% set as the training set for the journal embeddings, and the 20\% set as the validation set for the journal embeddings.
+We split our initial set  $80\%$ - $20\%$,. We use the $80\%$ set as the training set for the journal representations, and the $20\%$ set as the validation set for the journal representations.
 \subheader{Create journal embeddings}
@@
 \item{F1-score}
-\item{Median abstract rank}
-\item{Median title rank}
+\item{Median \& average rank}
+\item{Rank distribution}
 \end{enumerate}
-\subheader{ - F1-score}
-We calculate the F1 score per article, to do this, we use the following metrics:\\
+\subsubheader{F1-score}
+We define the positive \& negative metrics as follows:\\
+\begin{jumpin}
 $True Positive = $ Articles that are correctly matched to the current journal\\
@@
 $False Negative = $ Articles that are incorrectly matched to the current journal\\
-$Recall = \dfrac{True Positive}{True Positive + False Negative}$\\\\
-$Precision = \dfrac{True Positive}{True Positive + False Positive}$\\\\
-$F1 = \dfrac{2 * Precision * Recall}{Precision + Recall}$\\
-\subheader{ - Median abstract rank}
-We use the median abstract rank to indicate around which rank the 'standard' article would be ranked, based on its abstract. We do this by taking the median of the abstract rank from each article.
-\subheader{ - Median title rank}
-We use the median title rank to indicate around which rank the 'standard' article would be ranked, based on its title. We do this by taking the median of the title rank from each article.
+\end{jumpin}
+We used these metrics to calculate the Recall, Precision \& F1 as follows:\\
+\begin{jumpin}
+$Recall = \dfrac{True Positive}{True Positive + False Negative}$\vspace{0.1in}\\
+$Precision = \dfrac{True Positive}{True Positive + False Positive}$\vspace{0.1in}\\
+$F1 = \dfrac{2 * Precision * Recall}{Precision + Recall}$
+\end{jumpin}
+\subsubheader{Median \& average rank}
+We use the median rank to indicate around which rank the 'standard' article would be ranked, based on its title or abstract.
+We do this by taking the median of the respective rank from each article.
+This gives us an indication of the behaviour of most articles in our validation set.
+This median rank (mostly) ignores the outliers, we therefore also use the average rank, which gives a more global indication, although this rank may be over-influenced by some outliers.
+\subsubheader{Rank distribution}
+To further analyse the ranking results, we plot the rank distribution to get an indication of the ranking-landscape.
+We limit ourselves to the following categories: 1 (absolute hits), top-10, top-20, top-30, top-40, top-50,  top-100 and 100+.
 \end{document}
+
+% RAW DATA:
+% 1,391,543 articles
+% 14,742,192 title tokens
+% 171,474,473 abstract tokens
+% 3,759 journals
+
+% split = 79.9509609117 - 20.0490390883
+
+% training numbers
+% 10K = percentage?}

### 2018-06-12 Thesis/Parts/Conclusion/Conclusion.tex
Results added

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Conclusion}
This research shows that the article embeddings, created with word embeddings, perform better than the reasonable TF-IDF alternatives for our categorization task, based on article titles. The TF-IDF alternatives give better results than the embeddings based on abstracts. The performance of the embeddings have been improved by weighting them with the TF-IDF values on word level. This improved embedding results in a median rank decrease of 8 on title and an median rank increase of 8 on title, compared to the best performing TF-IDF alternative.  The embedding also results in a memory decrease of 73.04\% making it more viable to keep it in memory.
We have furthermore shown that limiting vocabulary size to exclude rare words or common words decreases the performance of the embeddings. We thus come to the following conclusions:
\begin{enumerate}
\item{Article based embeddings perform better than TF-IDF on small texts}
\item{TF-IDF performs better than article based embeddings on larger texts}
\item{Embeddings give a significant decrease in memory usage compared to TF-IDF}
\end{enumerate}
\end{document}

### 2018-06-12 Thesis/Parts/Data/Data.tex
Results added

--- 2018-06-12 Thesis/Parts/Conclusion/Conclusion.tex
@@
 \begin{document}
-\header{Conclusion}
-This research shows that the article embeddings, created with word embeddings, perform better than the reasonable TF-IDF alternatives for our categorization task, based on article titles.
-The TF-IDF alternatives give better results than the embeddings based on abstracts.
-The performance of the embeddings have been improved by weighting them with the TF-IDF values on word level.
-This improved embedding results in a median rank decrease of 8 on title and an median rank increase of 8 on title, compared to the best performing TF-IDF alternative.
-The embedding also results in a memory decrease of 73.04\% making it more viable to keep it in memory.
-We have furthermore shown that limiting vocabulary size to exclude rare words or common words decreases the performance of the embeddings. We thus come to the following conclusions:
-\begin{enumerate}
-\item{Article based embeddings perform better than TF-IDF on small texts}
-\item{TF-IDF performs better than article based embeddings on larger texts}
-\item{Embeddings give a significant decrease in memory usage compared to TF-IDF}
-\end{enumerate}
+\header{Data}
 \end{document}

### 2018-06-12 Thesis/Parts/Discussion/Discussion.tex
Results added

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Discussion}
\subheader{1k 6k behaviour}
1k 6k embedding has lower storage than the other embeddings, this is most likely due to it's word filtering. Cutting off most-used words results probably in empty titles/abstracts which reduce the space that is needed for this embedding variant. All other embeddings have the same size, which indicates that this does not occur in the other situations, even in the 5k set, where the same amount of words are cut off.\\
The, relatively, much higher average rank compared to the median rank of the 1k 6k embedding can be explained with the data of table (RANKING DISTRIBUTION TABLE). This shows that the embedding goes up at the start, indicating that there are articles in the low ranks, flats out in the center more than the others do, indicating a relatively low amount of articles in the middle ranks, and a strong increase at the end. Indicating that there are  many titles on the high end of the distribution. This explains the relatively low median, which is dawn towards the lower end of the distribution, and the high average, which is drawn to the higher end of the distribution.

\subheader{Best performers}
The data shows that the 10.000/10.000 set preforms better than all other TF-IDF sets, although the difference with the 5.000/10.000 is low, 1 (7.14\%) on abstract and 3 (8.57\%) on title. For the embeddings the TF-IDF weighted embedding works better than the others, although it is near equal to the default embeddings, which 1 rank higher on abstract, and equal on title.

\subheader{TF-IDF weighting on embeddings}
The difference between the TFIDF weighted embedding and the default embedding can be explained as follows:
The embeddings seem to outperform the TF-IDF in situation when there is little information available, the titles in our case. This indicates that the embeddings store some kind of word meaning that enables them to perform relatively well on the titles. The abstracts on the other hand contain much more information. Our data seems to indicate that the amount of information available in the abstracts enable the TF-IDF to cope with the lack of embedded information. If this is the case, we could expect that there would little performance increase on the title, since the TF-IDF lacks the information to perform well. This can be seen in our data, only the average rank increased by 3, indicating that there is a difference between the two embeddings, but not a major one. We could expect on the abstract an increase in performance, since the TF-IDF has more information in this context. We would expect that the weighting applied by the TF-IDF improves the performance of the embedding by indicating word importance. Our data shows a minor improvement in performance of 1(4.35\%) median rank and 10(6.41\%) average ranks.

\subheader{Raw, readable results}
The TF-IDF outperform the embeddings on the abstract with a difference of 8 ranks for the best of each. On the title however, the best embedding outperforms the best TF-IDF by 8 ranks.

\subheader{Memory usage}
Although the TF-IDF outperforms the embeddings on the abstracts, the memory usage of the TF-IDF is higher than the memory usage of the embeddings. The top-performing embedding, TF-IDF weighted embedding, uses 3.13 GB, the top performing TF-IDF, 10.000/10.000 uses 11.61 GB, which is 270.93\% more. The closest TF-IDF configuration we used was 1.000/1.000, which uses 5.13 GB (SEE GRAPH XXX). This TF-IDF set has a median title rank of 183 and a median abstract rank of 44. Which is worse than the embedding, which also uses less memory.

\end{document}

### 2018-06-12 Thesis/Parts/Related_work/Related_work.tex
Results added

--- 2018-06-12 Thesis/Parts/Discussion/Discussion.tex
@@
 \begin{document}
-\header{Discussion}
-\subheader{1k 6k behaviour}
-1k 6k embedding has lower storage than the other embeddings, this is most likely due to it's word filtering.
-Cutting off most-used words results probably in empty titles/abstracts which reduce the space that is needed for this embedding variant.
-All other embeddings have the same size, which indicates that this does not occur in the other situations, even in the 5k set, where the same amount of words are cut off.\\
-The, relatively, much higher average rank compared to the median rank of the 1k 6k embedding can be explained with the data of table (RANKING DISTRIBUTION TABLE).
-This shows that the embedding goes up at the start, indicating that there are articles in the low ranks, flats out in the center more than the others do, indicating a relatively low amount of articles in the middle ranks, and a strong increase at the end.
-Indicating that there are  many titles on the high end of the distribution.
-This explains the relatively low median, which is dawn towards the lower end of the distribution, and the high average, which is drawn to the higher end of the distribution.
-
-\subheader{Best performers}
-The data shows that the 10.000/10.000 set preforms better than all other TF-IDF sets, although the difference with the 5.000/10.000 is low, 1 (7.14\%) on abstract and 3 (8.57\%) on title.
-For the embeddings the TF-IDF weighted embedding works better than the others, although it is near equal to the default embeddings, which 1 rank higher on abstract, and equal on title.
-
-\subheader{TF-IDF weighting on embeddings}
-The difference between the TFIDF weighted embedding and the default embedding can be explained as follows:
-The embeddings seem to outperform the TF-IDF in situation when there is little information available, the titles in our case.
-This indicates that the embeddings store some kind of word meaning that enables them to perform relatively well on the titles.
-The abstracts on the other hand contain much more information.
-Our data seems to indicate that the amount of information available in the abstracts enable the TF-IDF to cope with the lack of embedded information.
-If this is the case, we could expect that there would little performance increase on the title, since the TF-IDF lacks the information to perform well.
-This can be seen in our data, only the average rank increased by 3, indicating that there is a difference between the two embeddings, but not a major one.
-We could expect on the abstract an increase in performance, since the TF-IDF has more information in this context.
-We would expect that the weighting applied by the TF-IDF improves the performance of the embedding by indicating word importance.
-Our data shows a minor improvement in performance of 1(4.35\%) median rank and 10(6.41\%) average ranks.
-
-\subheader{Raw, readable results}
-The TF-IDF outperform the embeddings on the abstract with a difference of 8 ranks for the best of each. On the title however, the best embedding outperforms the best TF-IDF by 8 ranks.
-
-\subheader{Memory usage}
-Although the TF-IDF outperforms the embeddings on the abstracts, the memory usage of the TF-IDF is higher than the memory usage of the embeddings.
-The top-performing embedding, TF-IDF weighted embedding, uses 3.13 GB, the top performing TF-IDF, 10.000/10.000 uses 11.61 GB, which is 270.93\% more.
-The closest TF-IDF configuration we used was 1.000/1.000, which uses 5.13 GB (SEE GRAPH XXX).
-This TF-IDF set has a median title rank of 183 and a median abstract rank of 44.
-Which is worse than the embedding, which also uses less memory.
-
+\header{Related work}
 \end{document}

### 2018-06-13 Thesis/Parts/Background/Background.tex
Background

@@
 \section{Background}
-\header{Embedding}
+\header{Introduction and Background}
+\subheader{Information retrieval}
+Information Retrieval(IR)is the activity of gathering relevant information, given another initial piece of information.
+The most practical example of this is a search engine.
+Given one or more search words the search engine will attempt to find relevant information.
+For example, a Google search on "Information Retrieval" (initial piece of information) will give you a list of results (relevant information).
+To be able to do this, the computer (search engine) must know which texts are related.
+To achieve this, multiple techniques can be used, such as TF-IDF, Word2Vec, Paragraph Vectors and GloVe.
+These techiques can be divided into two categories, ones that use a neural network and ones that do not.
+\subheader{Neural Network}
+Neural Networks are computational structures, based on vector and/or matrix calculations.
+They can be applied to many different tasks, but need to be trained for each task.
+This training is the process of iteratively adjusting multiplication matrices or vectors to achieve the optimal result.
+Which is the result that is as close as possible to the given output for different input and output sets.
+In some IR techniques, Neural Networks are used to either predict words that may occur around a given word, or predict a word given words that surround it. For example, given the sentence\\
+\begin{center}
+\textit{"The search engine searches for relevant information"}
+\end{center}
+the Neural Network can be trained to either predict the words around "searches" (the, search, engine, for, relevant, information) or to predict the word "searches", given the surrounding (the, search, engine, for, relevant, information).
+This trained matrix (vector per word) now indicates "word relatedness" which, as mentioned earlier enables association (thus retrieval) with related(relevant) texts.
 %The basic theory of word embedding can be explained by the following quote of J.R. Firth: "You shall know a word by the company it keeps". 
-Machine learning (ML) tasks rely on a numerical (vectorial) representation of text which we refer to as an embedding.
-These can be calculated for texts of different lengths such as a title, sentence, paragraph or an entire document\cite{Karimi2017Deep}.
-Word embeddings are these numerical representations of a word, these vectors are an distributed representation of the word over the multiple (vector) dimensions(\citet{mikolov2013distributed}).
-The word embeddings can be used to construct embedding of larger texts.
-Word embeddings can capture both the semantic and syntactic information of words.
-The advantage of the machine learning models is that it can be done without human-interaction(\citet{lai2016generate}).
-Word embeddings have improved various Natural Language Processing (NLP) areas such as named entity recognition, part-of-speech tagging, parsing, and semantic role labelling (\citet{luong2013better}).
+\subheader{Embedding}
+The vector for a word is referred to as a word embedding, which represents the word as a vector.
+This vector is a distributed representation of the word over the multiple vector dimensions~\citet{mikolov2013distributed}.
+Which can capture both the semantic and syntactic information of the word.
+The advantage of the machine learning models that create these embeddings is that they do not need human interaction~\citet{lai2016generate}.
+Once trained, the word embeddings can be used to construct embeddings of larger texts, for example sentence, paragraph, document or corpus embeddings.
+The usage of word embeddings have improved various Natural Language Processing (NLP) areas such as named entity recognition, part-of-speech tagging, parsing, and semantic role labelling~\citet{luong2013better}.
+
+\subheader{Text analysis techniques}
+To enable a computer to process text, for embedding creation or for tasks, the text has to be processed by an algorithm.
+In this research we used embeddings created by Word2Vec and TF-IDF feature vectors.
 \begin{jumpin}
-\subheader{Word2Vec}
+\subsubheader{Word2Vec}
 Word2vec word embeddings are created using neural network, Word2vec learns word embeddings via maximizing the log conditional probability of the word given the context word(s) occurring within a fixed-sized window.
@@
 The Skip-gram model takes a target word as input and outputs the predicted output words, while CBOW takes the context words as input and outputs the predicted target word\cite{nalisnick2016improving, pennington2014glove}.
-\subheader{Paragraph vectors}
-Variations on the word2vec model have also been proposed, \citet{le2014distributed} introduced the paragraph vector, based on the word2vec model.
+\subsubheader{Paragraph vectors}
+Variations on the word2vec model have also been proposed,~\citet{le2014distributed} introduced the paragraph vector, based on the word2vec model.
 The paragraph vector model uses additional variables to improve the accuracy of the word-embeddings.
 An advantage of the paragraph vector model is that it takes the word order into consideration, atleast in a small context \cite{le2014distributed}.
-\subheader{GloVe}
+\subsubheader{GloVe}
 \citet{pennington2014glove} introduced the GloVe (Global Vectors) model.
@@
 The model transforms the word co-occurrences of all words in the corpus to chances, it excludes all the zero values and uses that as initial input for the neural network.\\
-\subheader{TF-IDF}
-TF-IDF is an abbreviation for Term Frequency - Inversed Document Frequency.
-This method does not rely on a neural network, and does not require training.
-According to a paper by \citet{beel2016paper} from 2016, "TF-IDF was the most popular weighting scheme (70\%) among those approaches for which the scheme was specified" (in the recommendation class 'Content-based filtering').
-The TFIDF score is the product of the term frequency in a text and the inversed document frequency of the same term in a corpus of texts.
+\subsubheader{TF-IDF}
+TF-IDF is an abbreviation for Term Frequency times Inverted Document Frequency.
+This method does not rely on a neural network and therefore does not require training.
+The TF-IDF score is the product of the term frequency in a text and the inverted document frequency of the same term in a corpus of texts.
 Both of which can be calculated in a variety of ways.
+The feature vectors produced by TF-IDF do not capture syntactic or semantic information about words, but capture information about word occurrences.
 \end{jumpin}
 
-\header{Embedding validation}
-Embedding validation techniques are methods that are used to validate the quality\footnote{With quality we mean the extend to which the task is completed correctly} of an embedding for a specific task(\citet{schnabel2015evaluation}).
-Multiple validations of word embeddings have been used, including: Word analogy, text similarity, categorization and positional visualization.
+\subheader{Validation methods}
+The results produced by the techniques have to be validated to determine their quality (in usage).
+The quality of the results can be validated through, among others the F1 score and, for classification tasks, the rank of the correct category.
+The embeddings can furthermore be validated through their performance on tasks such as word analogies, word similarities, categorization and position visualization.
+These tasks can be designed to produce a score that gives an indication of the performance on a specific task.
+\citet{schnabel2015evaluation} found that a single validation metric cannot produce a representative result for other tasks.
+Embeddings that perform well on one task do not have to perform well on another task.
+As a result, the findings about performance of an embedding method are limited to the task on which they are tested, their results cannot be generalized to state that the embedding are overall "performing well".
+Validation tasks use either labelled or unlabelled data. Labelled data is data that is in some way marked, so that the correct answer can be derived from it, in contrast to unlabelled data.
+
 \begin{jumpin}
-\subheader{Word Analogy}
+\subsubheader{Word Analogy}
 Word analogy validation is based on a labelled validation set, containing, commonly, word pairs of four, that can be logically divided into two parts. As  Table
@@
 The score is the fraction of correctly given fourth words, given the first three words.
-This validation metric is used in multiple studies\cite{mikolov2013distributed, mikolov2013efficient, dai2015document, pennington2014glove}.
-\begin{table}
+This validation metric is used in multiple studies\cite{mikolov2013distributed, mikolov2013efficient, dai2015document, pennington2014glove}.\\
+\begin{table}[hbt]
 \begin{center}
-\begin{tabular}{c c c c}
+\begin{tabular}{l l l l}
 Man & Women & King & Queen \\
@@
 \end{center}
-\caption{Word analogies used in word embedding validation}\label{table:wordAnalogies}
-\end{table}
+\caption{Word analogies examples}\label{table:wordAnalogies}
+\end{table}\\
 Both this validation technique and the Word Similarity technique use vector distance calculations to validate the embeddings, this can therefore also be written as:
@@
 This resulting vector may be close to a vector "monarch" for example.
-\subheader{Word Similarity}
+\subsubheader{Word Similarity}
 A method to test the quality of word embeddings is the word similarity test.
@@
 These sets, among others, have been used in multiple studies of word embeddings\cite{pennington2014glove, mikolov2013efficient}. This validation metric also relies on labelled data.
-\subheader{Classification}
-The classification validation method is a simple task which compares multiple texts.
+\subsubheader{Classification}
+A classification validation method is a simple task which assigns a label to a text.
 \citet{lau2016empirical} used data from StackExchange and tried to determine if a pair was a duplicate.
-Even though the validation method is simple, it too used labelled data to validate the acquired results.
-\subheader{Categorization}
+In their setup, the text was a pair of texts, and their categories were duplicate or non-duplicate,
+\subsubheader{Categorization}
 \citet{le2014distributed} used for their research a dataset of IMDB with 100,000 movie review.
 They validated their proposed paragraph vector model by determining whether a review was positive or negative.
-\subheader{Position Visualization}
-(Unlabelled, Needs human validation)\citet{dai2015document} and \citet{hinton2003stochastic} mapped their word embeddings to a two dimensional vector to be able to display them in a graph and applied colors to various categories.
-The advantage of this is that a human can directly see that the embeddings make sense, however this approach is not applicable by a computer.\\
+\subsubheader{Position Visualization}
+\citet{dai2015document} and \citet{hinton2003stochastic} mapped their word embeddings from a high dimensional vector to a two dimensional vector to be able to display them in a scatter plot and applied colors to various categories.
+These categories can be created with labelled or unlabelled data.
+The advantage of this is that a human can directly see the word distributions, and see if it is distributed in a way that seems logical.
+It gives furthermore insight in the overall spectrum of the words.
+However, this representation does not give a score, since it is not a evaluation of the data, but an alternative representation.
 \end{jumpin}
-Even though these validation methods are not limited to domains, the labelled data they use are, since they do not consist of words of specific domains.
-At this moment, there are no sets for every domain which make it difficult to compare the accuracy of domain specific word embeddings to non domain specific word embeddings.
+
 \end{document}

### 2018-06-13 Thesis/Parts/Motivation/Motivation.tex
Background

@@
 \begin{document}
-\section{Motivation}
-\header{Domain specific}
-Earlier work on this topic, concerning domain specific articles, by (\citet{Truong2017Thesis}), found that  
-%start of literal quote
-in-domain training of the word embeddings can  improve the process of document clustering.
-This effect is even stronger than the number of training examples and the model architecture.\cite{Truong2017Thesis}.
-%end of literal quote
-\citet{lai2016generate} found that 
-%start literal quote
-the corpus domain is more important than the corpus size.
+\header{Motivation}
+\subheader{Domain specific}
+Earlier research, concerning domain specific articles, by \citet{Truong2017Thesis}, found that in-domain training of the word embeddings can  improve the process of document clustering.
+This effect is even stronger than the number of training examples and the model architecture.
+\citet{lai2016generate} found that the corpus domain is more important than the corpus size.
 Using an in-domain corpus significantly improves the performance for a given task, whereas using a corpus in an unsuitable domain may decrease performance.
-%end literal quote
 These findings both indicate that an in-domain corpus improves the performance of word embeddings for the specific domains.
 
-\header{Problems in validation}
-To assess the quality (or usability) of the embeddings, validation methods are used.
+\subheader{Problems in validation}
+To assess the performance of the embeddings, validation methods are used.
 This are tasks designed to produce a metric that gives an indication of the usability of the provided embeddings.
@@
 Therefore, we propose the validation of domain specific word-embeddings through a classification tasks, using multiple vector-distance calculations.
-This eliminates the need for labelled data in the validation of these domain specific word embeddings, will validate the quality of word embeddings for domain specific texts, and will validate the impact of different vector-distance measures on a categorization task.
-\begin{table}
+This eliminates the need for labelled data in the validation of these domain specific word embeddings, will validate the quality of word embeddings for domain specific texts, and will validate the impact of different vector-distance measures on a categorization task.\\
+\begin{table}[hbt]
 \begin{center}
-\begin{tabular}{c c c c}
+\begin{tabular}{l l l l}
 &WordSim & Men & RareWords\\
@@
 \end{table}
+\\
+\subheader{Research Questions}
+\begin{itemize}
+\item{Have word-embeddings a higher accuracy for academic texts than TF-IDF for article classification?}
+\item{Which metric(s) can be used to measure the accuracy of word embeddings for scientific articles?}
+\end{itemize}
+
 \end{document}

### 2018-06-14 Thesis/Parts/Background/Background.tex
Background, motivation and related work

@@
 \subheader{Embedding}
-The vector for a word is referred to as a word embedding, which represents the word as a vector.
-This vector is a distributed representation of the word over the multiple vector dimensions~\citet{mikolov2013distributed}.
-Which can capture both the semantic and syntactic information of the word.
-The advantage of the machine learning models that create these embeddings is that they do not need human interaction~\citet{lai2016generate}.
-Once trained, the word embeddings can be used to construct embeddings of larger texts, for example sentence, paragraph, document or corpus embeddings.
-The usage of word embeddings have improved various Natural Language Processing (NLP) areas such as named entity recognition, part-of-speech tagging, parsing, and semantic role labelling~\citet{luong2013better}.
+The created vector for a word is referred to as a word embedding.
+An embedding is a distributed, numerical representation of a text which can capture both the semantic and syntactic information\cite{mikolov2013distributed}.
+In the case of a word embedding, the embedding represents the word.
+The advantage of the machine learning models that create these embeddings is that they do not need human interaction~\citet{lai2016generate}, they are so called "unsupervised learning algorithms".
+Once trained, the embeddings can be used to construct embeddings of larger texts.
+For example, a word embedding can be used to create a sentence, paragraph, document or corpus embedding.
+The usage of word embeddings have improved various Natural Language Processing areas such as named entity recognition, part-of-speech tagging, parsing, and semantic role labelling~\citet{luong2013better}.
 
@@
 \citet{lau2016empirical} used data from StackExchange and tried to determine if a pair was a duplicate.
-In their setup, the text was a pair of texts, and their categories were duplicate or non-duplicate,
-\subsubheader{Categorization}
+In their setup, the text was a pair of texts, and their categories were duplicate and non-duplicate.
 \citet{le2014distributed} used for their research a dataset of IMDB with 100,000 movie review.
@@
 \end{jumpin}
-
+\subheader{General and Domain specific}
+Since the word embeddings are created form a given text, these embeddings are bound to the text.
+All meaning embedded in the word embedding is derived from the original text.
+Because of this, embeddings can be "Domain specific" meaning that it only knows words (or a specific word) in a certain context.
+This becomes most clear when faced with words that can have different meanings in different contexts.
+For this research we categorize the embedding in two categories, general embeddings and domain specific embeddings.
+The general embeddings are trained on a collection of texts that use common English and contains a wide variety of topics.
+The domain specific embeddings are trained on a collection of texts that uses uncommon English (i.e.
+domain specific terms) and/or is limited to a small amount of topics.
+Given these terms, we regard the embeddings trained on the Wikipedia corpus\cite{lai2016generate, pennington2014glove, dai2015document, lau2016empirical, schnabel2015evaluation} as general, since Wikipedia uses common English and spans a wide range of topics.
+On the other hand we regard the embeddings created by \citet{Truong2017Thesis} as Domain specific, these embeddings were created on academic articles, which use domain-specific terms and notations and only consists of academic texts, which contains less general/generic words compared to the Wikipedia corpus.
 \end{document}

### 2018-06-14 Thesis/Parts/Motivation/Motivation.tex
Background, motivation and related work

--- 2018-05-22 Thesis/Parts/Motivation/Motivation.tex
@@
 \begin{document}
-\section{Motivation}
-\header{Domain specific}
-Earlier work on this topic, concerning domain specific articles, by (\citet{Truong2017Thesis}), found that  
-%start of literal quote
-in-domain training of the word embeddings can drastically improve the process of document clustering.
-In fact, the effect is even stronger than the number of training examples and the model architecture.
-However, too isolated training can lead to a failure of several clustering algorithms, such as DBSCAN, due to a too dense vocabulary\cite{Truong2017Thesis}.
-%end of literal quote
-\citet{lai2016generate} found that 
-%start literal quote
-the corpus domain is more important than the corpus size.
+\header{Motivation}
+\subheader{In-domain embeddings and validation}
+Earlier research, concerning domain specific articles, by \citet{Truong2017Thesis}, found that in-domain training of the word embeddings can  improve the process of document clustering.
+This effect is even stronger than the number of training examples and the model architecture.
+\citet{lai2016generate} found that the corpus domain is more important than the corpus size.
 Using an in-domain corpus significantly improves the performance for a given task, whereas using a corpus in an unsuitable domain may decrease performance.
-%end literal quote
-These findings both indicate that an in-domain corpus improves the performance of word embeddings for the specific domains.
+Truong et al.
+encountered a problem in the validation of these in-domain embeddings.
+The word embedding produced correct document clustering results, leading to the conclusion that these embeddings are of good quality, since they capture the document relatedness needed to create correct clusterings.
+However unpublished results by Truong et al.
+state that the embeddings show high error rates on the validation scores.
+This seems to indicate that the word-vectors are of good quality, but that the available validation metrics cannot confirm this.
+\citet{Truong2017Thesis} used multiple word similarity validations to asses the quality of the word embeddings.
+However, these set are created to validate the generic embeddings, they fail to asses the quality of the domain specific embeddings.
 
-\newpage
+\subheader{Research}
+To asses the problem of the limited availability of pre-labelled validation sets for domain specific articles, we compare the embeddings to  TF-IDF on a categorization task.
+This A) gives an indication of the embedding quality for categorization tasks and B) contrasts the performance of embeddings to the performance of the more traditional TF-IDF approach.
+To ensure the quality of the embeddings for our research, we reuse the embeddings created in the research of \citet{Truong2017Thesis}.
+\begin{jumpin}
+	\textbf{RQ.1} Have word-embeddings a higher accuracy for academic texts than TF-IDF for article classification?\\
+	\textbf{RQ.2} Which metric can be used to measure the accuracy of word embeddings for scientific articles?
+\end{jumpin}
+\subsubheader{Embedding and TF-IDF}
+Research question one focusses on the classification results of both embedding-based techniques and TF-IDF.
+To measure classification task we use the rank of the class to which the item belongs.
+Transforming the classification task from a binary metric to a ranking metric.
+For this task, we will use different versions of embeddings, and different TF-IDF versions to not only compare the two techniques, but also look for the optimal results of both techniques.
+For this part of the research, we will use the following hypothesis:
+\begin{center}
+\textit{Embedding based techniques give lower rankings than the TF-IDF based techniques}
+\end{center}
+By validating our invalidating  this hypothesis we get an indication of the performance of the embeddings compare to older techniques, and get insight into possible performance and resource trade-off's and if the computational power and AI expertise needed for the creation of embeddings is worth the investment .
 
-\header{Problems in validation}
-Unpublished results of the study by Truong encounter this problem, they show high error rates on the validation scores, presented in Table~\ref{table:truongErrorRates}.
-However, the word embeddings created correct document clusterings\cite{Truong2017Thesis}, this seems to indicate that the word-vectors are able to represent the words correctly but that the available validation sets cannot confirm this.\\
-Furthermore, a study by \citet{schnabel2015evaluation} found that the quality of embeddings are tasks specific, \textit{different tasks favour different embeddings}.
-They also found that the embeddings encode information about word frequency, even in models that are created to prevent this.
-\textit{This casts doubt on the common practice of using vanilla cosine similarity as a similarity measure}.\\
-Therefore, we propose the validation of domain specific word-embeddings through a classification tasks, using multiple vector-distance calculations.
-This eliminates the need for labelled data in the validation of these domain specific word embeddings, will validate the quality of word embeddings for domain specific texts, and will validate the impact of different vector-distance measures on a categorization task.
-\begin{table}
-\begin{center}
-\begin{tabular}{c c c c}
-&WordSim & Men & RareWords\\
-Lowest & 0.38 & 0.54 & 0.29 \\
-Highest & 0.49 & 0.61 & 0.32\\
-Average & 0.45 & 0.59 & 0.32\\
-Baseline & \textbf{0.64} & \textbf{0.68} & \textbf{0.34}
-\end{tabular}
-\end{center}
-\caption{Results for the different validation sets of word simularity validations on domain specific texts from the study by \citet{Truong2017Thesis}}\label{table:truongErrorRates}
-\end{table}
 \end{document}

### 2018-06-14 Thesis/Parts/Related_work/Related_work.tex
Background, motivation and related work

@@
 \header{Related work}
+\subheader{Deep Neural Networks for YouTube \\Recommendations}
+The paper 'Deep Neural Networks for YouTube Recommendations' by Covington et al.\cite{covington2016deep} describes the current (16 September 2016) YouTube candidate generation and ranking neural networks.
+The candidate generation network works with limited data inorder to reduce the needed time for the candidate generation.
+This process reduces the amount of possible videos for the ranking network, which uses more parameters to increase the accuracy of the ranking.
+The paper also discusses variables to influence the results of the networks, such as age of the training example and watch-time vs click-through prediction.
+The paper also discusses the impact that layers of depth have at the results.
+\subheader{Distributed Representations of Sentences and Documents}
+The paper 'Distributed Representations of Sentences and Documents' by le et al.\cite{le2014distributed} proposes the Paragraph Vector as a replacement for the popular bag-of-words or bag-of-n-grams.
+The Paragraph Vector framework is based on the word vectors framework.
+The difference between the frameworks is the calculation of the probability, the Paragraph Vector framework uses an matrix D, which consists of every paragraph.
+This matrix is used to replace a concatenation or average of word vectors.
+The Paragraph Vector out preforms the state-of-the art techniques on several text classification and sentiment analysis tasks.
+\subheader{Distributed Representations of Words and Phrases and their Compositionality}
+The paper 'Distributed Representations of Words and Phrases and their Compositionality' by Mikolov et al.\cite{mikolov2013distributed} presents several extensions that improve the quality of vector training and its speed.
+This is achieved by introducing Hierarchical Softmax, Negative Sampling and the subsampling of frequent words to the Skip-gram approach.
+This does not only speed up the learning process, but also improves the quality for rare words.
+\subheader{Document Embedding with Paragraph Vectors}
+The paper 'Document Embedding with Paragraph Vectors' by Dai et al.\cite{dai2015document} describes a larger/more thorough evaluation of the Paragraph Vectors model.
+The writers compare this technique with the Bag of Words model and the Latend Dirichlet Allocation model.
+The paper states that the Paragraph Vectors model preforms well for grouping, triplet finding and related object/article finding tasks.
+The paper states that the Paragraph Vectors model is significantly better then the other models in these tasks on the Wikipedia and arXiv articles.
+\subheader{Stochastic Neighbor Embedding}
+The paper 'Stochastic Neighbor Embedding' by Hinton et al.\cite{hinton2003stochastic} describes a probabilistic approach to transform objects form a high-dimensional space to a low-dimensional spaces so that  neighbour identities are preserved.
+To achieve this the objects are transformed to images.
+A Gaussian is then used to define the (context) probability.
+This method has the ability to be extended to mixtures in which ambiguous high-dimensional objects can have several widely-separated images in the low-dimensional space.
+\subheader{An empirical evaluation of doc2vec with practical \\insights into document embedding generation}
+The paper 'An empirical evaluation of doc2vec with practical insights into document embedding generation' by Lau et al.\cite{lau2016empirical} empirically evaluates the quality of the documents embedding created with the method 'doc2vec' compared to 'word2vec' and the 'n-gram' model.
+They conclude that doc2vec preforms well and that the 'dbow' approach works better than the 'dmpv' approach for the doc2vec method.
+They also provide recommendations for the optimal parameters for the doc2vec method.
+\subheader{Efficient estimation of word representations in vector space}
+The paper 'Efficient estimation of word representations in vector space' by Mikolov et al.\cite{mikolov2013efficient} 
+shows that, with newly applied techniques, the size of the training sets can increase while the time needed for the training operation does not increase.
+This new approach greatly reduces the training time per word and allows for bigger sets of texts.
+This results in a higher accuracy of the created embeddings.
+The authors state that the newly applied techniques can also be used on other, already existing embedding methods.
+\subheader{GloVe: Global Vectors for Word Representation}
+The paper 'GloVe: Global Vectors for Word Representation' by Pennington et al.\cite{pennington2014glove} proposes a new model, named GloVe, which is a log-bilinear regression model for unsupervised learning of word representations.
+This model out preforms other models on three specific tasks, these are: word analogy, word similarity and named entity recognition.
+\subheader{MapReduce: Simplified data processing on large \\clusters}
+The paper 'MapReduce: Simplified data processing on large clusters' by Dean et al.\cite{dean2008mapreduce} explains the MapReduce programming model.
+The model is inspired by functional programming languages.
+It requires programmers to specify a map function which processes key-value pairs to generate intermediate key-value pairs.
+It requires furthermore a reduce function, that merges all intermediate values associated with the same intermediate key.
+This method allows for an execution on a large distributed computer network.
+This allows the processing of large input (and output) sets in reasonable time.
+\subheader{Spark SQL: Relational data processing in spark}
+The paper 'Spark SQL: Relational data processing in spark' by Armbrust et al.\cite{armbrust2015spark} explains Spark SQL.
+Spark SQL lest programmers leverage the benefits of relational processing and lets SQL users call complex analytix libraries in Spark.
+This allows for much tighter intergration between relational and procedural processing.
+The paper further states that Spark SQL makes it significanly simpler and more efficient to write data piplines that mix relational and procedural processing, while offering substantial speedups over previous SQL-on-Spark engines\footnote{Based on user feedback}.
+
+\subheader{How to Generate a Good Word Embedding?}
+Paper by Lai et al.\cite{lai2016generate}
+\begin{itemize}
+\item{Word embedding, also known as distributed word
+representation, can capture both the semantic and syntactic
+information of words from a large unlabeled corpus
+and has attracted considerable attention from many researchers.
+In recent years, several models have been proposed,
+and they have yielded state-of-the-art results in many
+natural language processing (NLP) tasks.}
+\item{We observe that almost
+all methods for training word embeddings are based on the
+same distributional hypothesis: words that occur in similar
+contexts tend to have similar meanings.}
+\item{Training on a large corpus
+generally improves the quality of word embeddings,
+and training on an in-domain corpus can significantly
+improve the quality of word embeddings for a specific
+task.}
+\item{Previous works have shown that models that predict the target word capture the paradigmatic relations between words}
+\item{we can conclude that using a larger corpus can yield a better embedding, when the corpora are in the same domain}
+\item{In most of the tasks, the influence of the corpus domain is
+dominant. In different tasks, it impacts performance in the
+different ways}
+\item{The corpus
+domain is more important than the corpus size. Using an indomain
+corpus significantly improves the performance for a
+given task, whereas using a corpus in an unsuitable domain
+may decrease performance. }
+\end{itemize}
+\subheader{Better Word Representations with Recursive Neural Networks for Morphology}
+Paper by Luong et al.\cite{luong2013better}
+\begin{itemize}
+\item{The use of word representations or word clusters
+pretrained in an unsupervised fashion from lots of
+text has become a key “secret sauce” for the success
+of many NLP systems in recent years, across
+tasks including named entity recognition, part-ofspeech
+tagging, parsing, and semantic role labeling.}
+\item{The main advantage of having such a distributed
+representation over word classes is that it can capture
+various dimensions of both semantic and syntactic
+information in a vector where each dimension
+corresponds to a latent feature of the word. As
+a result, a distributed representation is compact,
+less susceptible to data sparsity, and can implicitly
+represent an exponential number of word clusters.}
+\item{The Rare-word dataset introduced by Luong et al.}
+\end{itemize}
+\subheader{Evaluation methods for unsupervised word embeddings}
+Paper by Schnabel et al. \cite{schnabel2015evaluation}
+\begin{itemize}
+\item{Neural word embeddings represent meaning via
+geometry. A good embedding provides vector representations
+of words such that the relationship between
+two vectors mirrors the linguistic relationship
+between the two words.}
+\item{Existing schemes fall into two major categories: extrinsic and intrinsic evaluation.
+In extrinsic evaluation, we use word embeddings as input features to a downstream task and measure changes in performance metrics specific to that task.
+Examples include part-of-speech tagging and named-entity recognition (Pennington et al., 2014).
+Extrinsic evaluation only provides one way to specify the goodness of an embedding, and it is not clear how it connects to other measures.
+Intrinsic evaluations directly test for syntactic or semantic relationships between words (Mikolov et al., 2013a; Baroni et al., 2014).}
+\item{This is the first paper to conduct a comprehensive study covering a wide range of evaluation criteria and popular embedding techniques.
+In particular, we study how outcomes from three different evaluation criteria are connected: word relatedness, coherence, downstream performance.}
+\item{Embedding methods should be compared in the context of a specific task, e.g., linguistic insight or good downstream performance.}
+\item{We observe that word embeddings encode a surprising degree of information about word frequency.
+We found this was true even in models that explicitly reserve parameters to compensate for frequency effects.
+This finding may explain some of the variability across embeddings and across evaluation methods.
+It also casts doubt on the common practice of using the vanilla cosine similarity as a similarity measure in the embedding space.}
+\item{Extrinsic evaluations measure the contribution of a word embedding model to a specific task.
+There is an implicit assumption in the use of such evaluations that there is a consistent, global ranking of word embedding quality, and that higher quality embeddings will necessarily improve results on any downstream task.
+We find that this assumption does not hold: different tasks favor different embeddings}
+\item{Performance on downstream tasks is not consistent across tasks, and may not be consistent with intrinsic evaluations.
+Comparing performance across tasks may provide insight into the information encoded by an embedding, but we should not expect any specific task to act as a proxy for abstract quality.}
+\item{Word frequency information in the embedding space also affects cosine similarity}
+\item{ Also, the above results mean that the commonly-used cosine similarity in the embedding space for the intrinsic tasks gets polluted by frequency-based effects}
+\item{Factors such as word frequency
+play a significant and previously unacknowledged role. Word frequency also interferes with the commonly-used cosine similarity measure.}
+\end{itemize}
+\subheader{Word frequencies: A comparison of Pareto type distributions}
+Paper by \citet{wiegand2018word}.
+They state that the pareto distribution offers a better fit to the word occurrences in natural language than zipf's law.
+Their models show that, due to the additional parameters in the pareto-III, the tail of the data fits better to the model.
+This shows the relation between the word occurrences rank, and the actual occurrences.
 \end{document}

### 2018-06-15 Thesis/Parts/Data/Data.tex
data initial
data update

@@
 \header{Data}
+The dataset we used for this research consists of all articles\footnote{From Elseviers corpus} published in 2017 which have been published in a journal that has, in 2017, atleast 150 publications.
+This results in a total dataset of $1.391.543$ articles from $3.759$ journals.
+
+\begin{tabular}{c c c}
+ & Total token count & Unique token count \\
+Title & $14.742.192$ & $230.805$ \\
+Abstract & $171.474.473$ & $738.961$ \\
+Total & $186.962.354$ & $763.475$ \\
+\end{tabular}
 \end{document}
+
+% RAW DATA:
+% 1,391,543 articles
+% 14 811 433 title tokens			230805 unique
+% 172 150 921 abstract tokens		738961 unique
+% 186 962 354 total tokens			763475 unique
+% 3,759 journals
+
+% split = 79.9509609117 - 20.0490390883
+
+% training numbers
+% 10K = percentage?}

### 2018-06-15 Thesis/Parts/Data/Data.tex
Updated word/token counts

@@
 This results in a total dataset of $1.391.543$ articles from $3.759$ journals.
-
-\begin{tabular}{c c c}
- & Total token count & Unique token count \\
-Title & $14.742.192$ & $230.805$ \\
-Abstract & $171.474.473$ & $738.961$ \\
-Total & $186.962.354$ & $763.475$ \\
+\begin{table}[hbt]
+\begin{center}
+\begin{tabular}{|l|c|c|c|c|}
+\hline
+ & Total word count & Unique word count & Total token count & Unique token count \\
+\hline
+Title & $18.822.399$ & $939.665$ & $14.742.192$ & $230.805$ \\
+\hline
+Abstract & $264.653.020$ & $5.853.077$ & $171.474.473$ & $738.961$ \\
+\hline
+Total & $283.475.419$ & $6.209.769$ & $186.962.354$ & $763.475$ \\
+\hline
 \end{tabular}
+\end{center}
+\caption{Corpus size}\label{table:corpusSize}
+\end{table}\\
+The word occurrences follow the pattern of a pareto distribution as described by~\citet{wiegand2018word}.
+This distribution is visualized in XXXXXX, which displays the occurrences of the first 2.000 tokens of the corpus.
+\includegraphics[width=6.5in]{Plots/word_occurrences}\\
 \end{document}
@@
 % 1,391,543 articles
-% 14 811 433 title tokens			230805 unique
-% 172 150 921 abstract tokens		738961 unique
-% 186 962 354 total tokens			763475 unique
+% 14 811 433 title tokens			230805 unique		18.822.399			939.665
+% 172 150 921 abstract tokens		738961 unique		264.653.020			5.853.077
+% 186 962 354 total tokens			763475 unique		283.475.419			6.209.769
 % 3,759 journals

### 2018-06-15 Thesis/Parts/Data/Data.tex
Data

@@
 \header{Data}
+\subheader{Corpus}
 The dataset we used for this research consists of all articles\footnote{From Elseviers corpus} published in 2017 which have been published in a journal that has, in 2017, atleast 150 publications.
@@
 The word occurrences follow the pattern of a pareto distribution as described by~\citet{wiegand2018word}.
-This distribution is visualized in XXXXXX, which displays the occurrences of the first 2.000 tokens of the corpus.
+This distribution is visualized in XXXXXX, which displays the occurrences of the first 500 tokens of the corpus.
 \includegraphics[width=6.5in]{Plots/word_occurrences}\\
+
+\subheader{Datasets}
+For this researched we used a (pre-made) tokenized dataset, which reduces the total amount of words by 34\%, from this tokenized set, we created the embeddings and the TF-IDF feature vectors.
+\subsubheader{Tokenization}
+The following steps have been applied to the words to create a tokenized set:
+\begin{enumerate}
+\item{Removed punctuation}
+\item{Removed all non-ascii characters}
+\item{Transformed all characters to lower-case}
+\item{Removed stop-words, as provided by the NLTK library}
+\item{Removed numbers}
+\item{Stemmed all words, using the stemmer provided by the NLTK library}
+\end{enumerate}
+These transformations reduced our dataset by 34\%, resulting in a tokenized set of $186.962.354$ tokens.
+
+\subsubheader{Embedding}
+For this research we reused the word embeddings created by \citet{Truong2017Thesis}.
+These embeddings have a vector size of 300, which is an industry default.
+They have been trained on the entire Elsevier corpus, not limited to the subset we used for this research.
+To construct article embeddings we take the average of all normalized word embeddings for that article.
+Journal embeddings are constructed in the same way, we averaged all the normalized article embeddings to create the journal embeddings.
+We have used multiple embedding configurations for this research
+\subsubsubheader{Default embedding}
+The default embedding is created form the pre-trained word embeddings, no modifications have been applied to this set.
+\subsubsubheader{TF-IDF embedding}
+The TF-IDF weighted embedding set, referred to as TF-IDF embedding, are the default word embeddings weighted with a TF-IDF score per word.\\
+The TF-IDF is calculated with a raw token count, and a smoothed inverted document frequency, calculated as follows:\\
+\begin{equation}
+IDF = \log_{10}(\dfrac{|A|}{|A_t|})
+\end{equation}
+Where $|A|$ is the total count of articles and $|A_t|$ is the count of articles containing term t.
+The articles embeddings are a normalized summation of each word vector multiplied by it TF-IDF value. Since we take a sum of all words, the Term Frequency is embedded as the raw count of each word.
+\subsubsubheader{10K TF-IDF embedding}
+The 10K embedding set is generated similarity to the TF-IDF embedding, this version only uses the 10.000 most common tokens, reducing the amount of tokens it uses.
+This set was created to see if the limitation to 10.000 tokens reduces the amount of noise, and with that increasing the performance.
+\subsubsubheader{5K TF-IDF embedding}
+The 5K TF-IDF embedding is the TF-IDF embedding set, limited to the 5.000 most common words. This set was created to more aggressively limit the amount of tokens, and with that, cancel out more noise.
+\subsubsubheader{1K-6K TF-IDF embedding}
+The 1K-6K TF-IDF embedding is the TF-IDF embedding limited to the top 6.000 most common words, without the top 1.000 most common words.
+The rationale for this is that common words will occur in many articles, creating noise, by cutting of the top 1.000 and cutting of everything below 6.000 we tried to reduce the noise by filtering common words.
+This cut results in a set of 5.000 tokens, which allows us to compare it to the 5K TF-IDF set.
+
+\subsubheader{TF-IDF}
+To create the TF-IDF feature vectors, we used the TF-IDF model and a hasher from pysparks the MlLib library.
+The TF-IDF feature vectors are created by hashing the tokens with the hasher, which has a set hash bucket size.
+These hashed values are passed on to the TF-IDF model, resulting in a feature vector which vector dimensions equals the amount of hash buckets.
+To limit the computational and storage expenses and to reduce noise by rare words, we limit our vocabulary size.
+We denote the TF-IDF configurations as follows: $vocabulary size/hashbucket size$.
+Furthermore, we denote 1.000 as 1K, since we deal with chosen values which can be exactly noted given this notation.\\
+\includegraphics[width=6in]{Plots/tfidf_selection_plot}\\
+The graph XXX shows the performance and storage size\footnote{in gigabyte, 1024 based} of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations.
+This plot shows that, while the required storage size keeps rising, the performance on title quickly stagnates, and the performance on abstract follows too.
+Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to.
+
 \end{document}

### 2018-06-15 Thesis/Parts/Research_setup/Research_setup.tex
data update
Data

@@
 \item{Calculate performance metrics}
-\end{enumerate}
-
-\subheader{Create embeddings}
-For this research, we used word-embeddings (created using the word2vec model) and TF-IDF embeddings.
-The word-embeddings were created with the word2vec model from PySparks MlLib library\cite{PysparkMlLib}.
-The embeddings were pre-trained and have a vector size of 300, which is an industry default.
-The TF-IDF embeddings were created with the TF-IDF model from pyspark's MlLib library\cite{PysparkMlLib}, in combination with a token hasher (HashingTF) from the same library.
-We used multiple hashing dimensions and multiple vocabulary sizes.
-Since the TF-IDF uses the output of the term hasher, the TF-IDF model produces the same dimensions.
-We will denote the tfidf sets as vocabulary size/hashing size.
-All of our sets, both embedding and TF-IDF, use tokenized texts.
-\subsubheader{Tokenization}
-== TODO ==
-\subsubheader{TF-IDF selection}
-To limit computational expenses, we used only the top performing which can reasonably be kept in RAM.
-The plot displays the ranking \& size for the 1000/1000, 4000/4000, 7000/7000 and 10.000/10.000 sets respectively.\\
-\includegraphics[width=6in]{Plots/tfidf_selection_plot}\\
-The plot show the median abstract \& title rank and the storage size in Gigabytes (1024 based) plotted over feature size, which is equal to the hashing size for these sets.
-The plot shows that both title and abstract are stagnating, while the memory usage is, slowly, going up.
-At a feature size of 10.000, we have a storage size of 11.6GB.
-Given this size and the stagnation of the rankings, we chose to use the 10.000/10.000 feature size tfidf vectors, we furthermore used the 10.000/5000 set and the 5000/5000 set for comparison.
-
-\subsubheader{Embeddings}
-We have made use of multiple embedding sets for this research.
-All sets share the same (default) embedding and have been (uniquely) modified.
-For this research we have used the following embedding sets:
-\begin{enumerate}
-\item{Default embedding}
-\subitem{The embedding as generated by word2vec, without further enhancements.}
-\item{TF-IDF embedding}
-\subitem{The embedding as generated by the word2vec, multiplied by their tfidf weights to embed word priorities. We use this enhancement to give the embeddings more information about the corpus.}
-\item{10K TF-IDF Embedding}
-\subitem{The embedding as generated by the word2vec, filtered on the top 10.000 most common words, multiplied by their tfidf weights.\\We use this enhancement to try to filter out possible noise created by lots of words with few occurrences.}
-\item{5K TF-IDF Embedding}
-\subitem{The embedding as generated by the word2vec, filtered on the top 5.000 most common words, multiplied by their tfidf weights.\\We use this enhancement to cancel out the noise caused be rare words more aggressively}
-\item{1K 6K TF-IDF Embedding}
-\subitem{The embeddings as generated by the word2vec, filtered on the top top 1.000 till top 5.000 most common words, multiplied by their tfidf weights.\\We use this enhancement to ignore the top 1.000 most common words, which are most likely generic words, since they occur often.
-And to cancel out the rare-words, by cutting off all words after 6K.
-This gives us a set of 5K words.}
 \end{enumerate}
@@
 \end{document}
-
-% RAW DATA:
-% 1,391,543 articles
-% 14,742,192 title tokens
-% 171,474,473 abstract tokens
-% 3,759 journals
-
-% split = 79.9509609117 - 20.0490390883
-
-% training numbers
-% 10K = percentage?}

### 2018-06-18 Thesis/Parts/Abstract/Abstract.tex
Results added
Thesis v0.1

@@
 \begin{document}
-\section{Abstract}
-[TODO: Abstract]
+\header{Abstract}
+Over the last few years, word embeddings have taken a dominant position in the Information Retrieval domain.
+Many studies have been done concerning the quality of word embeddings on general texts, such as wikipedia or review-websites.
+Giving promising results, the word embeddings have been studied and improved over resent years.
+However, these studies have been focused on generic text, overlooking the complexity of in-domain knowledge, such as rare domain specific words.
+This research focusses on the usefulness of word embeddings on domain specific texts, concerning scientific articles which have been published in 2017.
+This research compares the word embeddings  the TF-IDF algorithm on a corpus existing on a wide range of domain specific texts.
 \end{document}

### 2018-06-18 Thesis/Parts/Conclusion/Conclusion.tex
Thesis v0.1

@@
 \begin{enumerate}
-\item{Article based embeddings perform better than TF-IDF on small texts}
-\item{TF-IDF performs better than article based embeddings on larger texts}
+\item{Article based embeddings perform better than TF-IDF on titles, small texts, which contain limited information}
+\item{TF-IDF performs better than article based embeddings on abstracts, larger texts, which contain more information}
 \item{Embeddings give a significant decrease in memory usage compared to TF-IDF}

### 2018-06-18 Thesis/Parts/Data/Data.tex
Thesis v0.1

@@
 \begin{document}
-\header{Data}
-\subheader{Corpus}
+\header{Corpus}
 The dataset we used for this research consists of all articles\footnote{From Elseviers corpus} published in 2017 which have been published in a journal that has, in 2017, atleast 150 publications.
@@
 
-\subheader{Datasets}
+\header{Datasets}
 For this researched we used a (pre-made) tokenized dataset, which reduces the total amount of words by 34\%, from this tokenized set, we created the embeddings and the TF-IDF feature vectors.
-\subsubheader{Tokenization}
+\subheader{Tokenization}
 The following steps have been applied to the words to create a tokenized set:
@@
 
-\subsubheader{Embedding}
+\subheader{Embedding}
 For this research we reused the word embeddings created by \citet{Truong2017Thesis}.
@@
 We have used multiple embedding configurations for this research
-\subsubsubheader{Default embedding}
+\subsubheader{Default embedding}
 The default embedding is created form the pre-trained word embeddings, no modifications have been applied to this set.
-\subsubsubheader{TF-IDF embedding}
+\subsubheader{TF-IDF embedding}
 The TF-IDF weighted embedding set, referred to as TF-IDF embedding, are the default word embeddings weighted with a TF-IDF score per word.\\
@@
 The articles embeddings are a normalized summation of each word vector multiplied by it TF-IDF value. Since we take a sum of all words, the Term Frequency is embedded as the raw count of each word.
-\subsubsubheader{10K TF-IDF embedding}
+\subsubheader{10K TF-IDF embedding}
 The 10K embedding set is generated similarity to the TF-IDF embedding, this version only uses the 10.000 most common tokens, reducing the amount of tokens it uses.
 This set was created to see if the limitation to 10.000 tokens reduces the amount of noise, and with that increasing the performance.
-\subsubsubheader{5K TF-IDF embedding}
+\subsubheader{5K TF-IDF embedding}
 The 5K TF-IDF embedding is the TF-IDF embedding set, limited to the 5.000 most common words. This set was created to more aggressively limit the amount of tokens, and with that, cancel out more noise.
-\subsubsubheader{1K-6K TF-IDF embedding}
+\subsubheader{1K-6K TF-IDF embedding}
 The 1K-6K TF-IDF embedding is the TF-IDF embedding limited to the top 6.000 most common words, without the top 1.000 most common words.
@@
 
-\subsubheader{TF-IDF}
+\subheader{TF-IDF}
 To create the TF-IDF feature vectors, we used the TF-IDF model and a hasher from pysparks the MlLib library.
@@
 Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to.
+The TF-IDF features are created on article level.
+We average the set of article embeddings to create a journal embedding.
 
+\header{Pipeline}
+We procesessed the TF-IDF sets an the embedding sets via the same pipeline, based on vector calculations. This ensures comparable results. The pipeline is setup as follows:
+\begin{enumerate}
+\item{Create training and validation set}
+\item{Create journal embeddings}
+\item{Categorize validation articles}
+\item{Calculate performance metrics}
+\end{enumerate}
+
+\subheader{Create training and validation set}
+We split our initial set  $80\%$ - $20\%$,.
+We use the $80\%$ set as the training set for the journal representations, and the $20\%$ set as the validation set for the journal representations.
+This split is based on a random number given to article each record, ensuring that all set have the same (random) training and validation set.
+\subheader{Create journal embeddings}
+From our training set we create the journal embeddings, which are created for most sets\footnote{see XXXXX} by averaging the article embeddings or feature vectors.
+\subheader{Categorize validation articles}
+To categorize the articles, we calculate the distance between the title- and abstract embedding of each article, from the validation set, to the title- and abstract embedding of each journal, during this process we keep track of:
+\begin{itemize}
+\item{Title-based-rank of the actual journal}
+\item{Abstract-based-rank of the actual journal}
+\item{Best scored journal on the abstract similarity}
+\item{Best scored journal on the title similarity}
+\item{Abstract similarity between the actual journal and the article}
+\item{Title similarity between the actual journal and the article}
+\end{itemize}
+\subsubheader{Distance metrics}
+To calculate the distance between to vectors, cosine similarity is commonly used CITATIONS NEEDED.
+We validated the quality of cosine similarity as a distance metrics by comparing it to all other similarity matrices available in the SciPy library, which we used to calculate the distances.
+We calculate the similarities based on the normalized embeddings, and compared the distance metrics based on the default embedding set.
+XXXX shows the results of this validation.\\
+\begin{minipage}{6.5in}
+\begin{tabular}{|l|l|l|l|l|}
+\hline
+Metric\footnote{As defined and provided by the SciPy library} & Median title rank & Average title rank & Median abstract rank & Average abstract rank  \\
+\hline
+Braycurtis & 28 & 130 & 23 & 124  \\
+\hline
+Canberra & 33 & 148 & 26 & 133  \\
+\hline
+Chebyshev & 57 & 256 & 41 & 191  \\
+\hline
+\textit{Cityblock} & \textit{28} & \textit{130} & \textit{23} & \textit{124}  \\
+\hline
+\textit{Correlation} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
+\hline
+\textbf{Cosine} & \textbf{27} & \textbf{127} & \textbf{23} & \textbf{122}  \\
+\hline
+Dice & 1995 & 1929 & 1995 & 1929  \\
+\hline
+\textit{Euclidean} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
+\hline
+Hamming & 1995 & 1929 & 1995 & 1929  \\
+\hline
+Jaccard & 1995 & 1929 & 1995 & 1929  \\
+\hline
+Kulsinski & 1995 & 1929 & 1995 & 1929  \\
+\hline
+Mahalanobis & 136 & 544 & 75 & 449  \\
+\hline
+Matching & 1995 & 1929 & 1995 & 1929  \\
+\hline
+Rogerstanimoto & 1995 & 1929 & 1995 & 1929  \\
+\hline
+Russellrao & 1995 & 1929 & 1995 & 1929  \\
+\hline
+\textit{Seuclidean} & \textit{27} & \textit{124} & \textit{22} & \textit{115}  \\
+\hline
+Sokalmichener & 1995 & 1929 & 1995 & 1929  \\
+\hline
+Sokalsneath & 1995 & 1929 & 1995 & 1929  \\
+\hline
+\textit{Sqeuclidean} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
+\hline
+Yule & 1995 & 1929 & 1995 & 1929  \\
+\hline
+\end{tabular}
+\end{minipage}\\
+These results show high similarity between cosine-based metrics (Cosine \& Correlation) and euclidean based metrics (Euclidean, Seuclidean \& sqeuclidean).
+This similarity is expected, since the cosine and euclidean distances should yield the same results on normalized sets.
+The results show that some enhancement on the euclidean algorithm result in slightly improved results, although not significant XXX EXPLAIN?
+XXX.
+Also the Cityblock metric yields results close to the Cosine metric, it has a slightly worse performance, which is also not significant.
+Because of this, we will use the cosine-similarity as the distance matrix, which will make our results better comparable with other work.
+
+\subheader{Performance measurement}
+We use multiple metrics to validate the performance of the embedding sets and TF-IDF sets on the categorization task. These metrics are:
+\begin{enumerate}
+\item{F1-score}
+\item{Median \& average rank}
+\item{Rank distribution}
+\end{enumerate}
+\subsubheader{F1-score}
+We define the positive \& negative metrics as follows:\\
+\begin{jumpin}
+$True Positive = $ Articles that are correctly matched to the current journal\\
+$False Positive = $ Articles that are incorrectly matched to other journals\\
+$False Negative = $ Articles that are incorrectly matched to the current journal\\
+\end{jumpin}
+We used these metrics to calculate the Recall, Precision \& F1 as follows:\\
+\begin{jumpin}
+$Recall = \dfrac{True Positive}{True Positive + False Negative}$\vspace{0.1in}\\
+$Precision = \dfrac{True Positive}{True Positive + False Positive}$\vspace{0.1in}\\
+$F1 = \dfrac{2 * Precision * Recall}{Precision + Recall}$
+\end{jumpin}
+\subsubheader{Median \& average rank}
+We use the median rank to indicate around which rank the 'standard' article would be ranked, based on its title or abstract.
+We do this by taking the median of the respective rank from each article.
+This gives us an indication of the behaviour of most articles in our validation set.
+This median rank (mostly) ignores the outliers, we therefore also use the average rank, which gives a more global indication, although this rank may be over-influenced by some outliers.
+\subsubheader{Rank distribution}
+To further analyse the ranking results, we plot the rank distribution to get an indication of the ranking-landscape.
 \end{document}

### 2018-06-18 Thesis/Parts/Discussion/Discussion.tex
Thesis v0.1

@@
 \header{Discussion}
-\subheader{1k 6k behaviour}
-1k 6k embedding has lower storage than the other embeddings, this is most likely due to it's word filtering.
-Cutting off most-used words results probably in empty titles/abstracts which reduce the space that is needed for this embedding variant.
-All other embeddings have the same size, which indicates that this does not occur in the other situations, even in the 5k set, where the same amount of words are cut off.\\
-The, relatively, much higher average rank compared to the median rank of the 1k 6k embedding can be explained with the data of table (RANKING DISTRIBUTION TABLE).
-This shows that the embedding goes up at the start, indicating that there are articles in the low ranks, flats out in the center more than the others do, indicating a relatively low amount of articles in the middle ranks, and a strong increase at the end.
-Indicating that there are  many titles on the high end of the distribution.
-This explains the relatively low median, which is dawn towards the lower end of the distribution, and the high average, which is drawn to the higher end of the distribution.
+\subheader{Sets}
+\subheader{Best performers}
+The data shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank (7.14\%) on abstract and 3 median ranks (8.57\%) on title.
+For the embeddings the TF-IDF weighted embedding works better than the others, although it is has is not a significant improvement compared to the default embeddings, which 1 median rank higher on abstract, and equal on title.
+\subsubheader{TF-IDF}
+The TF-IDF feature vectors outperform the embeddings on the abstract, while the embeddings ourperform the TF-IDF feature vectors on the title.
+The main difference between the abstract \& title is that the title contains less unique tokens (see XXXXX), this means that the titles contain less unique information, making them more generic.
+Due to this, the TF-IDF method, which is purely based on word-occurrences \& counts cannot differentiate between the highly similar titles.
+The TF-IDF method works better on the abstract, which contain more unique words, which help in differentiating the different texts.
+Furthermore, increasing the vocabulary size increases the performance of the TF-IDF, since the vocabulary size is cut-off at word occurrences, which reduces the amount of unique words.
+\subsubheader{Embedding}
+\subsubsubheader{Limited tfidf embeddings}
+The limited TF-IDF embeddings all under perform, compared to the non-limited TF-IDF embedding, on the median and average ranking.
+Indicating that the noise reduction is too much, and it removes meaningful words.
+If the noise reduction would be too low, we would only see a slight increase or none at all.
+However, the rank lowers, indicating the reduction in embedding quality due to missing words.
+However, graphs XXX and XXX show that their rank distribution is different from the other embeddings.
+Their pattern show a decent performance indicates the following pattern: a high/average performance on the top-rankings, an under performance on the middle rankings and  a resulting stack-up of articles with a high-ranking.
+This is further supported by the TF-IDF score on titles (Graph XXX), on which the limited TF-IDF embeddings are the top performance.
+Indicating a better performance on the top-1 articles compared to the other sets.\\This leads us to believe that the cut-off was effective, but that is did not suit our purpose.
+The cut-off moved the "middle-ranked"  articles to either the high end of the rankings, or the lower end.
+Resulting in low median and average scores, but in (relatively) high accuracy scores.
+The reduction in vocabulary size did not reduce the storage size for the embeddings, except for the 1K-6K embedding.
+This indicates that only the 1K-6K cut actually removes entire titles and/or abstracts, since all vectors are stored as dense-vectors\footnote{Dense vectors are bigger in memory, since they store all their values, including zeros.
+However they can be processed more efficiently during calculations}.
+This results in a lower memory requirement.
 
-\subheader{Best performers}
-The data shows that the 10.000/10.000 set preforms better than all other TF-IDF sets, although the difference with the 5.000/10.000 is low, 1 (7.14\%) on abstract and 3 (8.57\%) on title.
-For the embeddings the TF-IDF weighted embedding works better than the others, although it is near equal to the default embeddings, which 1 rank higher on abstract, and equal on title.
-
-\subheader{TF-IDF weighting on embeddings}
+\subsubheader{TF-IDF \& embeddings}
 The difference between the TFIDF weighted embedding and the default embedding can be explained as follows:
@@
 
-\subheader{Raw, readable results}
-The TF-IDF outperform the embeddings on the abstract with a difference of 8 ranks for the best of each. On the title however, the best embedding outperforms the best TF-IDF by 8 ranks.
-
 \subheader{Memory usage}
 Although the TF-IDF outperforms the embeddings on the abstracts, the memory usage of the TF-IDF is higher than the memory usage of the embeddings.
-The top-performing embedding, TF-IDF weighted embedding, uses 3.13 GB, the top performing TF-IDF, 10.000/10.000 uses 11.61 GB, which is 270.93\% more.
-The closest TF-IDF configuration we used was 1.000/1.000, which uses 5.13 GB (SEE GRAPH XXX).
+The top-performing embedding, TF-IDF weighted embedding, uses 3.13 GB, the top performing TF-IDF, 10K/10K uses 11.61 GB, which is 270.93\% of the storage size needed for the embedding.
+The closest TF-IDF configuration we used was 1K/1K, which uses 5.13 GB (SEE GRAPH XXX).
 This TF-IDF set has a median title rank of 183 and a median abstract rank of 44.
 Which is worse than the embedding, which also uses less memory.
-
 \end{document}

### 2018-06-18 Thesis/Parts/Future_work/Future_work.tex
Thesis v0.1

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Future work}
- How do unique token count, token count and vocabulary size relate for TF-IDF?
- Can high quality word similarity sets be created from embedding for future benchmarking?
- Can embeddings give a visual representation of the evolution of scientific research over time?
- Does TF-IDF improve when top-occurring words are cut-off?
\end{document}

### 2018-06-18 Thesis/Parts/Research_results/Research_results.tex
Results added
Background, motivation and related work
Thesis v0.1

@@
 \subheader{Ranking}
-\includegraphics[width=6in]{Plots/Abstract_rankings}\\
+The graph XXX shows the ranking results for the different sets based on the title.
+Graph XXX displays the ranking results based on the abstract.
+Both graphs show both average and median ranks, based on the cosine-similarity between the article and journal embeddings or feature vectors.\\
+\includegraphics[width=6.5in]{Plots/Title_rankings}\\
+\vspace{0.2in}\\
+\includegraphics[width=6.5in]{Plots/Abstract_rankings}\\
+\clearpage
+\subheader{Rank distribution}
+Graph XXX shows the rank distribution for the titles on, graph XXX shows this for the ranks based on the abstract.
+Both graphs use a logarithmic scale.
+These graphs give a detailled view of the ranks presented in the respective graphs XXX and XXX.\\
+\includegraphics[width=6.5in]{Plots/Title_rank_distribution}\\
+\vspace{0.2in}\\
+\includegraphics[width=6.5in]{Plots/Abstract_rank_distribution}\\
+\clearpage
+\subheader{F1-Score}
+The graphs XXX and XXX show the F1 score for the title and abstract respectively.
+These scores are the average journals scores for each set, indicating the quality of the sets for absolute hits (top-1).\\
+\includegraphics[width=6.5in]{Plots/Title_avg_f1}\\
+\vspace{0.2in}\\
+\includegraphics[width=6.5in]{Plots/Abstract_avg_f1}\\
+\clearpage
+\subheader{Memory usage}
+XXX shows the total memory usage of each \textit{Validation set}, indicating their costs in memory storage \& RAM.\\
+\begin{tabular}{|l|l|}
+\hline
+Set & Size in GB\\
+\hline
+tfidf 5k 5K & $9.82$ \\
+\hline
+tfidf 5K 10K & $11.47$ \\
+\hline
+\textbf{tfidf 10K 10K} &\textbf{11.61}\\
+\hline
+embedding & $3.13$ \\
+\hline
+5k embedding & $3.13$ \\
+\hline
+10k embedding & $3.13$ \\
+\hline
+\textbf{tfidf embedding} & \textbf{3.13} \\
+\hline
+1k 6k embedding & $3.06$ \\
+\hline
+\end{tabular}
 \\
-\includegraphics[width=6in]{Plots/Title_rankings}\\
-\subheader{Rank distribution}
-\includegraphics[width=6in]{Plots/Abstract_rank_distribution}\\
-\\
-\includegraphics[width=6in]{Plots/Title_rank_distribution}\\
-\subheader{F1-Score}
-d
+
 \end{document}

### 2018-06-18 Thesis/Parts/Research_setup/Research_setup.tex
Thesis v0.1

@@
 \header{Experiment setup}
-We used the following pipeline to collect the performance metrics for the categorization task:
-\begin{enumerate}
-\item{Create embeddings}
-\item{Filter articles}
-\item{Create training and validation set}
-\item{Create journal embeddings}
-\item{Categorize validation articles}
-\item{Calculate performance metrics}
-\end{enumerate}
 
-\subheader{Filter articles}
-We create our initial set of articles by collecting all articles from the journals that were published in the year 2017, and have at least 200 publications in 2017.
-This reduces the journal set to $3,759$ thousand journals, resulting in a set of $1,391,543$ million articles ().
-\subheader{Create training and validation set}
-We split our initial set  $80\%$ - $20\%$,. We use the $80\%$ set as the training set for the journal representations, and the $20\%$ set as the validation set for the journal representations.
-\subheader{Create journal embeddings}
-From our training set we create the journal embeddings by averaging all title embeddings as the journal title embedding, and by averaging all abstract embeddings as the journal abstract embedding.
-We also normalized both embeddings.
-\subheader{Categorize validation articles}
-To categorize the articles, we calculate the distance between the title- and abstract embedding of each article, from the validation set, to the title- and abstract embedding of each journal.
-To calculate the distance, we use cosine similarity (as provided by the SciPy library\cite{SciPy}).
-During this process we keep track of:
-\begin{itemize}
-\item{Title-based-rank of the actual journal}
-\item{Abstract-based-rank of the actual journal}
-\item{Best scored journal on the abstract similarity}
-\item{Best scored journal on the title similarity}
-\item{Abstract similarity between the actual journal and the article}
-\item{Title similarity between the actual journal and the article}
-\end{itemize}
-\subheader{Performance measurement}
-We use multiple metrics to indicate the performance of the embeddings on a categorization task. These metrics are:
-\begin{enumerate}
-\item{F1-score}
-\item{Median \& average rank}
-\item{Rank distribution}
-\end{enumerate}
-\subsubheader{F1-score}
-We define the positive \& negative metrics as follows:\\
-\begin{jumpin}
-$True Positive = $ Articles that are correctly matched to the current journal\\
-$False Positive = $ Articles that are incorrectly matched to other journals\\
-$False Negative = $ Articles that are incorrectly matched to the current journal\\
-\end{jumpin}
-We used these metrics to calculate the Recall, Precision \& F1 as follows:\\
-\begin{jumpin}
-$Recall = \dfrac{True Positive}{True Positive + False Negative}$\vspace{0.1in}\\
-$Precision = \dfrac{True Positive}{True Positive + False Positive}$\vspace{0.1in}\\
-$F1 = \dfrac{2 * Precision * Recall}{Precision + Recall}$
-\end{jumpin}
-\subsubheader{Median \& average rank}
-We use the median rank to indicate around which rank the 'standard' article would be ranked, based on its title or abstract.
-We do this by taking the median of the respective rank from each article.
-This gives us an indication of the behaviour of most articles in our validation set.
-This median rank (mostly) ignores the outliers, we therefore also use the average rank, which gives a more global indication, although this rank may be over-influenced by some outliers.
-\subsubheader{Rank distribution}
-To further analyse the ranking results, we plot the rank distribution to get an indication of the ranking-landscape.
-We limit ourselves to the following categories: 1 (absolute hits), top-10, top-20, top-30, top-40, top-50,  top-100 and 100+.
 \end{document}

### 2018-06-18 Thesis/Parts/Abstract/Abstract.tex
abstract

--- 2018-04-05 Thesis/Parts/Abstract/Abstract.tex
@@
 \begin{document}
-\section{Abstract}
-[TODO: Abstract]
+\header{Abstract}
+Over the last few years, word embeddings have taken a dominant position in the Information Retrieval domain.
+Many studies have been done concerning the quality of word embeddings on general texts, such as the Wikipedia corpus and comments on review websites.
+Giving promising results, the word embeddings have been studied and improved over recent years.
+However, these studies have been focused on generic text, which do not contain the complexity of in-domain knowledge, such as rare domain specific words.
+This research focusses on the usefulness of word embeddings on domain specific texts, concerning scientific articles which have been published in 2017.
+The data shows that the word embeddings only perform better than TF-IDF, which was chosen as a traditional alternative, when the ranking is done on titles.
+The best ranking result is obtained through a TF-IDF with a vocabulary size of 10.000 applied on the abstracts, resulting in a median rank of 14, while the pure word embeddings result in a median rank of 23.
+This shows that word embeddings, although useful, are not unchallenged by older techniques.
 \end{document}

### 2018-06-18 Thesis/Parts/Abstract/Abstract.tex
Merged related work and background

@@
 However, these studies have been focused on generic text, which do not contain the complexity of in-domain knowledge, such as rare domain specific words.
-This research focusses on the usefulness of word embeddings on domain specific texts, concerning scientific articles which have been published in 2017.
+This research focusses on the usefulness of word embeddings on domain specific texts, concerning $1.391.543$ scientific articles which have been published in 2017.
 The data shows that the word embeddings only perform better than TF-IDF, which was chosen as a traditional alternative, when the ranking is done on titles.

### 2018-06-18 Thesis/Parts/Background/Background.tex
Thesis v0.1
Merged related work and background

@@
 \begin{document}
-\section{Background}
 \header{Introduction and Background}
@@
 This trained matrix (vector per word) now indicates "word relatedness" which, as mentioned earlier enables association (thus retrieval) with related(relevant) texts.
+Neural networks are also used for other tasks such as video recommendation on Google's YouTube, as described by \citet{covington2016deep}.
 %The basic theory of word embedding can be explained by the following quote of J.R. Firth: "You shall know a word by the company it keeps". 
@@
 The Skip-gram model takes a target word as input and outputs the predicted output words, while CBOW takes the context words as input and outputs the predicted target word\cite{nalisnick2016improving, pennington2014glove}.
+\citet{mikolov2013distributed}\cite{mikolov2013efficient} presented several extensions to the word2vec model that improve the quality of vector training and its speed, such as introducing Hierarchical Softmax, Negative Sampling and the subsampling of frequent words to the Skip-gram approach.
+Variations to the word2vec model have also been proposed, such as the doc2vec model described by \citet{lau2016empirical} which creates document embeddings instead of word embeddings.
+
 \subsubheader{Paragraph vectors}
-Variations on the word2vec model have also been proposed,~\citet{le2014distributed} introduced the paragraph vector, based on the word2vec model.
-The paragraph vector model uses additional variables to improve the accuracy of the word-embeddings.
+Variations on the word2vec model have also been proposed,~\citet{le2014distributed} introduced the paragraph vector based in their paper "Distributed representations of sentences and documents".
+The Paragraph Vector framework is based on the word vectors framework.
+The difference between the frameworks is the calculation of the probability, the Paragraph Vector framework uses an matrix D, which consists of every paragraph.
+This matrix is used to replace a concatenation or average of word vectors.
 An advantage of the paragraph vector model is that it takes the word order into consideration, atleast in a small context \cite{le2014distributed}.
+\citet{dai2015document} state in their paper "Document embedding with paragraph vectors" that the Paragraph Vectors model performs significantly better than other models on grouping, triplet finding and related object/article finding tasks on the Wikipeida and arXiv texts.
+
 \subsubheader{GloVe}
@@
 This model captures the global corpus statistics.
-The model transforms the word co-occurrences of all words in the corpus to chances, it excludes all the zero values and uses that as initial input for the neural network.\\
+The model transforms the word co-occurrences of all words in the corpus to chances, it excludes all the zero values and uses that as initial input for the neural network.
+This model out performs other models on three specific tasks, word analogy, word similarity and entity recognition.\\
+
 \subsubheader{TF-IDF}
@@
 \end{jumpin}
+As \citet{lai2016generate} state in their paper "How to generate a good word embedding?", all embedding methods rely on the same hypothesis, words that occur in similar contexts have similar meanings.
+They furthermore found that larger corpus' lead to better quality embeddings, but that the domain in which the embeddings are trained is dominant over the corpus size.
 
@@
 As a result, the findings about performance of an embedding method are limited to the task on which they are tested, their results cannot be generalized to state that the embedding are overall "performing well".
-Validation tasks use either labelled or unlabelled data. Labelled data is data that is in some way marked, so that the correct answer can be derived from it, in contrast to unlabelled data.
+Validation tasks use either labelled or unlabelled data.
+Labelled data is data that is in some way marked, so that the correct answer can be derived from it, in contrast to unlabelled data.
+The validation tasks can also be diveded into two groups, extrinsic evaluation, ones that use word embeddings as input for a downstream task.
+And Intrinsic evaluation, which directly test the relationships of the word embedding themselves.
+\citet{schnabel2015evaluation} note that the extrinsic evaluation may not be consistent with intrinsic evaluations, since the performance on downstream tasks is not consistent across tasks.
 
@@
 \subsubheader{Word Analogy}
-Word analogy validation is based on a labelled validation set, containing, commonly, word pairs of four, that can be logically divided into two parts. As  Table
-~\ref{table:wordAnalogies} shows, each last word can be derived from the three words before.
+Word analogy validation is based on a labelled validation set, containing, commonly, word pairs of four, that can be logically divided into two parts.
+As Table~\ref{table:wordAnalogies} shows, each last word can be derived from the three words before.
 The score is the fraction of correctly given fourth words, given the first three words.
@@
 On the other hand we regard the embeddings created by \citet{Truong2017Thesis} as Domain specific, these embeddings were created on academic articles, which use domain-specific terms and notations and only consists of academic texts, which contains less general/generic words compared to the Wikipedia corpus.
+\subheader{Research environment}
+The research will be done in a python-databricks environment, which uses spark, a library that offers tools to work with big-data.
+\citet{armburst2015} state that Spark SQL lest programmers leverage the benefits of relational processing and lets SQL users call complex analytix libraries in Spark.
+This allows for much tighter intergration between relational and procedural processing.
+The paper further states that Spark SQL makes it significanly simpler and more efficient to write data piplines that mix relational and procedural processing, while offering substantial speedups over previous SQL-on-Spark engines.
+\subheader{Text properties}
+\citet{wiegand2018word} state that the pareto distribution offers a good fit to the word occurrences in natural language.
+Their models show that, due to the additional parameters in the pareto-III, the tail of the data fits better to the model than the Zipf model.
+This shows the relation between the word occurrences rank, and the actual occurrences.
+This kind of word-occurrences distribution holds for many texts, including the writings of William Shakespeare and scientific texts and novels\cite{thurner2015understanding}.
 \end{document}

### 2018-06-18 Thesis/Parts/Abstract/Abstract.tex
Background feedback added

@@
 Giving promising results, the word embeddings have been studied and improved over recent years.
-However, these studies have been focused on generic text, which do not contain the complexity of in-domain knowledge, such as rare domain specific words.
+However, these studies have been focused on generic text, which do not contain the characteristics of in-domain knowledge, such as rare domain specific words.
 This research focusses on the usefulness of word embeddings on domain specific texts, concerning $1.391.543$ scientific articles which have been published in 2017.

### 2018-06-18 Thesis/Parts/Background/Background.tex
Background feedback added

@@
 Given one or more search words the search engine will attempt to find relevant information.
-For example, a Google search on "Information Retrieval" (initial piece of information) will give you a list of results (relevant information).
-To be able to do this, the computer (search engine) must know which texts are related.
-To achieve this, multiple techniques can be used, such as TF-IDF, Word2Vec, Paragraph Vectors and GloVe.
-These techiques can be divided into two categories, ones that use a neural network and ones that do not.
+For example, an online search for "Information Retrieval" (initial piece of information) will give you a list of results (relevant information).
+To be able to do this, the search engine must know which texts are related.
+This can be achieved with and without neural networks, a traditional technique which does not use a neural network is TF-IDF, shot for Term Frequency - Inverted Document Frequency.
+Techniques that use a neural network are newer, these are (among others) Word2Vec, Paragraph Vectors and GloVe.
+
 \subheader{Neural Network}
@@
 the Neural Network can be trained to either predict the words around "searches" (the, search, engine, for, relevant, information) or to predict the word "searches", given the surrounding (the, search, engine, for, relevant, information).
-This trained matrix (vector per word) now indicates "word relatedness" which, as mentioned earlier enables association (thus retrieval) with related(relevant) texts.
+This trained matrix, a vector per word which is referred to as a word embedding, now indicates "word relatedness" which, as mentioned earlier enables association (thus retrieval) with related(relevant) texts.
 Neural networks are also used for other tasks such as video recommendation on Google's YouTube, as described by \citet{covington2016deep}.
@@
 \subheader{Embedding}
-The created vector for a word is referred to as a word embedding.
-An embedding is a distributed, numerical representation of a text which can capture both the semantic and syntactic information\cite{mikolov2013distributed}.
+An embedding is a distributed, numerical representation of a text in a vector space\footnote{The vector space of separately trained word embeddings are not shared, since the trained vector dimensions are not fixed.
+This means that two separately trained word embeddings which have the same dimension do not share the same vector space.} which can capture both the semantic and syntactic information\cite{mikolov2013distributed}.
 In the case of a word embedding, the embedding represents the word.
-The advantage of the machine learning models that create these embeddings is that they do not need human interaction~\citet{lai2016generate}, they are so called "unsupervised learning algorithms".
-Once trained, the embeddings can be used to construct embeddings of larger texts.
+These embeddings are created using by machine learning models.
+These models create the embeddings without the need for human interaction~\cite{lai2016generate}, they are so called \textit{unsupervised learning algorithms}.
+Once trained, the embeddings can be used to construct embeddings for collections of texts.
 For example, a word embedding can be used to create a sentence, paragraph, document or corpus embedding.
@@
 The feature vectors produced by TF-IDF do not capture syntactic or semantic information about words, but capture information about word occurrences.
+These features are created by supplying the algorithm with the text it needs to "know".
+This text is then analysed on word occurrences on corpus and document and level, this results in a score per-word.
+This score can be converted to a feature vector, in which the indexes of these vector represent the words and the value is the TF-IDF score.
+The size of this feature vector can optionally be controlled by hashing the words in the text, which can then be reduced to a given size.
+If this is not applied, the size of the feature vector is equal to the amount of unique words in the corpus, also known as the (corpus) vocabulary.
+Some applications of this technique limit the amount of unique words in the text supplied to the TF-IDF algorithm, they do this by taking only a certain amount of top words, ordered on their occurrence.
+This reduces the amount of storage needed when hashing is not applied.
+It furthermore reduces the amount of words which occur rarely.
+Due to the nature of TF-IDF these rare words have a high score, cancelling out other more frequent words, while rarely occurring in the corpus.
+
 \end{jumpin}
@@
 The results produced by the techniques have to be validated to determine their quality (in usage).
-The quality of the results can be validated through, among others the F1 score and, for classification tasks, the rank of the correct category.
+The quality of the results can be validated through, among others the F1 score, which combines the precision score and the recall score in a single metric, and, for classification tasks, the rank of the correct category.
 The embeddings can furthermore be validated through their performance on tasks such as word analogies, word similarities, categorization and position visualization.
@@
 Validation tasks use either labelled or unlabelled data.
-Labelled data is data that is in some way marked, so that the correct answer can be derived from it, in contrast to unlabelled data.
-The validation tasks can also be diveded into two groups, extrinsic evaluation, ones that use word embeddings as input for a downstream task.
+Labelled data is data that is in some way marked, so that the correct answer can be derived from it, while this is not possible with unlabelled data.
+Labelled data enables the usage of unsupervised learning models, since  \textit{a system or model which is not involved in the actual learning} can automatically validate the given results and use it as feedback for the next learning iteration.
+Unlabelled data on the other hand requires human interaction to give a score for the produced result.
+The validation tasks can also be divided into two groups, extrinsic evaluation, ones that use word embeddings as input for a downstream task.
 And Intrinsic evaluation, which directly test the relationships of the word embedding themselves.
@@
 On the other hand we regard the embeddings created by \citet{Truong2017Thesis} as Domain specific, these embeddings were created on academic articles, which use domain-specific terms and notations and only consists of academic texts, which contains less general/generic words compared to the Wikipedia corpus.
+The domain specific texts can use the same word for unrelated topics, like clouds in computer science and meteorology.
 \subheader{Research environment}

### 2018-06-20 Thesis/Parts/Background/Background.tex
shallow total iteration

@@
 The research will be done in a python-databricks environment, which uses spark, a library that offers tools to work with big-data.
-\citet{armburst2015} state that Spark SQL lest programmers leverage the benefits of relational processing and lets SQL users call complex analytix libraries in Spark.
+\citet{armbrust2015spark} state that Spark SQL lest programmers leverage the benefits of relational processing and lets SQL users call complex analytix libraries in Spark.
 This allows for much tighter intergration between relational and procedural processing.

### 2018-06-20 Thesis/Parts/Conclusion/Conclusion.tex
shallow total iteration

@@
 The TF-IDF alternatives give better results than the embeddings based on abstracts.
-The performance of the embeddings have been improved by weighting them with the TF-IDF values on word level.
-This improved embedding results in a median rank decrease of 8 on title and an median rank increase of 8 on title, compared to the best performing TF-IDF alternative.
-The embedding also results in a memory decrease of 73.04\% making it more viable to keep it in memory.
-We have furthermore shown that limiting vocabulary size to exclude rare words or common words decreases the performance of the embeddings. We thus come to the following conclusions:
+The performance of the embeddings have been improved by weighting them with the TF-IDF values on word level, although this improvement cannot be seen as significant on our dataset.
+This improved embedding results in a median rank decrease of 8 on the titles and an median rank increase of 8 on the abstract, compared to the best performing TF-IDF alternative.
+The embedding also results in a memory decrease of 73.04\% compared to the best performing TF-IDF alternative, making it more viable to keep it in memory.
+We thus come to the following conclusions:
 \begin{enumerate}

### 2018-06-20 Thesis/Parts/Data/Data.tex
shallow total iteration

@@
 \header{Corpus}
-The dataset we used for this research consists of all articles\footnote{From Elseviers corpus} published in 2017 which have been published in a journal that has, in 2017, atleast 150 publications.
+The dataset we used for this research consists of articles published in 2017 which have been published in a journal that has, in 2017, atleast 150 publications.
 This results in a total dataset of $1.391.543$ articles from $3.759$ journals.
+Details about the corpus can be found in table~\ref{table:corpusSize}.
 \begin{table}[hbt]
 \begin{center}
-\begin{tabular}{|l|c|c|c|c|}
+\begin{tabular}{|l|c|c|c|}
 \hline
- & Total word count & Unique word count & Total token count & Unique token count \\
+ & Total count & Unique count & Average length \\
+\hline\hline
+Title words & $18.822.399$ & $939.665$ & 13,53  \\
 \hline
-Title & $18.822.399$ & $939.665$ & $14.742.192$ & $230.805$ \\
+Title tokens & $14.742.192$ & $230.805$ & 10,64 \\
+\hline\hline
+Abstract words & $264.653.020$ & $5.853.077$  & 190,19  \\
 \hline
-Abstract & $264.653.020$ & $5.853.077$ & $171.474.473$ & $738.961$ \\
+Abstract tokens & $171.474.473$ & $738.961$ & 123,71 \\
+\hline\hline
+Total words & $283.475.419$ & $6.209.769$  & 203,71 \\
 \hline
-Total & $283.475.419$ & $6.209.769$ & $186.962.354$ & $763.475$ \\
+Total tokens & $186.962.354$ & $763.475$ & 134,36 \\
 \hline
@@
 The word occurrences follow the pattern of a pareto distribution as described by~\citet{wiegand2018word}.
-This distribution is visualized in XXXXXX, which displays the occurrences of the first 500 tokens of the corpus.
-\includegraphics[width=6.5in]{Plots/word_occurrences}\\
+This distribution is visualized in figure~\ref{figure:wordTokenOccurrence}, which displays the occurrences of the first 500 tokens of the corpus.
+\begin{figure}[hbt]
+\includegraphics[width=6.5in]{Plots/word_occurrences}
+\caption{Word and token occurrences}\label{figure:wordTokenOccurrence}
+\end{figure}
 
@@
 Furthermore, we denote 1.000 as 1K, since we deal with chosen values which can be exactly noted given this notation.\\
-\includegraphics[width=6in]{Plots/tfidf_selection_plot}\\
-The graph XXX shows the performance and storage size\footnote{in gigabyte, 1024 based} of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations.
+\begin{figure}
+\includegraphics[width=6in]{Plots/tfidf_selection_plot}
+\caption{TF-IDF performance and memory usage}\label{figure:tfidfPerformance}
+\end{figure}
+
+Figure~\ref{figure:tfidfPerformance} shows the performance and storage size\footnote{in gigabyte, 1024 based} of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations.
 This plot shows that, while the required storage size keeps rising, the performance on title quickly stagnates, and the performance on abstract follows too.
@@
 \subheader{Create journal embeddings}
-From our training set we create the journal embeddings, which are created for most sets\footnote{see XXXXX} by averaging the article embeddings or feature vectors.
+From our training set we create the journal embeddings, which are created for most sets\footnote{see paragraph datasets} by averaging the article embeddings or feature vectors.
 \subheader{Categorize validation articles}
@@
 \subsubheader{Distance metrics}
-To calculate the distance between to vectors, cosine similarity is commonly used CITATIONS NEEDED.
+To calculate the distance between to vectors, cosine similarity is commonly used.
 We validated the quality of cosine similarity as a distance metrics by comparing it to all other similarity matrices available in the SciPy library, which we used to calculate the distances.
 We calculate the similarities based on the normalized embeddings, and compared the distance metrics based on the default embedding set.
-XXXX shows the results of this validation.\\
-\begin{minipage}{6.5in}
+Table~\ref{table:distanceMetrics} shows the results of this validation.\\
+\begin{table}[hbt]
 \begin{tabular}{|l|l|l|l|l|}
@@
 \end{tabular}
-\end{minipage}\\
-These results show high similarity between cosine-based metrics (Cosine \& Correlation) and euclidean based metrics (Euclidean, Seuclidean \& sqeuclidean).
+\caption{Distance metric performance for word embeddings on the categorization of academic texts}\label{table:distanceMetrics}
+\end{table}
+These results show high similarity between cosine-based metrics (Cosine \& Correlation) and euclidean based metrics (Euclidean, Seuclidean \& Sqeuclidean).
 This similarity is expected, since the cosine and euclidean distances should yield the same results on normalized sets.
-The results show that some enhancement on the euclidean algorithm result in slightly improved results, although not significant XXX EXPLAIN?
-XXX.
+The results show that some enhancement on the euclidean algorithm result in slightly improved results, although not significant.
 Also the Cityblock metric yields results close to the Cosine metric, it has a slightly worse performance, which is also not significant.

### 2018-06-20 Thesis/Parts/Discussion/Discussion.tex
shallow total iteration

@@
 \documentclass[../../Thesis.tex]{subfiles}
+\externaldocument{../Research_results/Research_results}
+\externaldocument{../Data/Data}
 \begin{document}
 \header{Discussion}
+\subheader{Best performers}
+The data, as presented in figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank on abstract and 3 median ranks on title.
+For the embeddings the TF-IDF weighted embedding works better than the others, although it is has is not a significant improvement compared to the default embeddings, which 1 median rank higher on abstract, and equal on title.
 \subheader{Sets}
-\subheader{Best performers}
-The data shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank (7.14\%) on abstract and 3 median ranks (8.57\%) on title.
-For the embeddings the TF-IDF weighted embedding works better than the others, although it is has is not a significant improvement compared to the default embeddings, which 1 median rank higher on abstract, and equal on title.
 \subsubheader{TF-IDF}
-The TF-IDF feature vectors outperform the embeddings on the abstract, while the embeddings ourperform the TF-IDF feature vectors on the title.
-The main difference between the abstract \& title is that the title contains less unique tokens (see XXXXX), this means that the titles contain less unique information, making them more generic.
-Due to this, the TF-IDF method, which is purely based on word-occurrences \& counts cannot differentiate between the highly similar titles.
-The TF-IDF method works better on the abstract, which contain more unique words, which help in differentiating the different texts.
-Furthermore, increasing the vocabulary size increases the performance of the TF-IDF, since the vocabulary size is cut-off at word occurrences, which reduces the amount of unique words.
+The TF-IDF feature vectors outperform the embeddings on the abstract, while the embeddings outperform the TF-IDF feature vectors on the title.
+The main difference between the abstract \& title is that the title contains less tokens (see table~\ref{table:corpusSize}), this means that the titles contain less information.
+Due to this, the TF-IDF method, which is purely based on word-occurrences \& counts has less information on the titles.
+The TF-IDF method works better on the abstract, which contain more tokens, which improves the differentiating the different abstract.
+The data furthermore shows that increasing the vocabulary size increases the performance of the TF-IDF, this means that none of the created cut-off's resulted in cutting off noise, the increasing size of the vocabulary only improved the performance in this case.
+It could be possible that at higher vocabulary sizes the cut-off would result in a sharper signal, we did not looked into this further due to our findings that the TF-IDF performance stagnates (presented in figure~\ref{figure:tfidfPerformance}).
 \subsubheader{Embedding}
@@
 However, the rank lowers, indicating the reduction in embedding quality due to missing words.
-However, graphs XXX and XXX show that their rank distribution is different from the other embeddings.
+This is in line with what we found with the TF-IDF results, higher vocabulary sizes give better performance.
+However, figures~\ref{figure:titleDistribution} \&~\ref{figure:abstractDistribution} show that their rank distribution is different from the other embeddings.
 Their pattern show a decent performance indicates the following pattern: a high/average performance on the top-rankings, an under performance on the middle rankings and  a resulting stack-up of articles with a high-ranking.
-This is further supported by the TF-IDF score on titles (Graph XXX), on which the limited TF-IDF embeddings are the top performance.
+This is further supported by the TF-IDF score on titles (figure~\ref{figure:titleRanks}), on which the limited TF-IDF embeddings are the top performance.
 Indicating a better performance on the top-1 articles compared to the other sets.\\This leads us to believe that the cut-off was effective, but that is did not suit our purpose.
@@
 \subsubheader{TF-IDF \& embeddings}
-The difference between the TFIDF weighted embedding and the default embedding can be explained as follows:
+Our hypothesis on the difference between the TF-IDF and the standard embedding is as follows:\\
 The embeddings seem to outperform the TF-IDF in situation when there is little information available, the titles in our case.
@@
 Our data seems to indicate that the amount of information available in the abstracts enable the TF-IDF to cope with the lack of embedded information.
-If this is the case, we could expect that there would little performance increase on the title, since the TF-IDF lacks the information to perform well.
+If this is the case, we could expect that there would little performance increase on the title when we compare the embeddings to the weighted TF-IDF embeddings, since the TF-IDF lacks the information to perform well.
 This can be seen in our data, only the average rank increased by 3, indicating that there is a difference between the two embeddings, but not a major one.
-We could expect on the abstract an increase in performance, since the TF-IDF has more information in this context.
+We would also expect on the abstract an increase in performance, since the TF-IDF has more information in this context.
 We would expect that the weighting applied by the TF-IDF improves the performance of the embedding by indicating word importance.
-Our data shows a minor improvement in performance of 1(4.35\%) median rank and 10(6.41\%) average ranks.
+Our data shows a minor improvement in performance of 1 median rank and 10 average ranks while these improvements cannot be seen as significant, our data at least indicates that weighting the embeddings with TF-IDF values has a positive effect on the embeddings.
 
@@
 The top-performing embedding, TF-IDF weighted embedding, uses 3.13 GB, the top performing TF-IDF, 10K/10K uses 11.61 GB, which is 270.93\% of the storage size needed for the embedding.
-The closest TF-IDF configuration we used was 1K/1K, which uses 5.13 GB (SEE GRAPH XXX).
+The closest TF-IDF configuration we used was 1K/1K, which uses 5.13 GB (as displayed in figure~\ref{figure:tfidfPerformance}).
 This TF-IDF set has a median title rank of 183 and a median abstract rank of 44.
-Which is worse than the embedding, which also uses less memory.
+Which is significantly worse than the embedding, which also uses less memory.
 \end{document}

### 2018-06-20 Thesis/Parts/Future_work/Future_work.tex
shallow total iteration

@@
 \header{Future work}
-- How do unique token count, token count and vocabulary size relate for TF-IDF?
-- Can high quality word similarity sets be created from embedding for future benchmarking?
-- Can embeddings give a visual representation of the evolution of scientific research over time?
-- Does TF-IDF improve when top-occurring words are cut-off?
+- Does the performance of embeddings and TF-IDF improve when embeddings and feature vectors are generated over the combination of title and abstract as one text?\\
+	- this helps when dealing with articles that do not have a title or an abstract.\\
+- How do unique token count, token count and vocabulary size relate for TF-IDF?\\
+- Can high quality word similarity sets be created from embedding for future benchmarking?\\
+- Can embeddings give a visual representation of the evolution of scientific research over time?\\
+- Does TF-IDF improve when top-occurring words are cut-off?\\
 \end{document}

### 2018-06-20 Thesis/Parts/Motivation/Motivation.tex
shallow total iteration

@@
 \subheader{In-domain embeddings and validation}
-Earlier research, concerning domain specific articles, by \citet{Truong2017Thesis}, found that in-domain training of the word embeddings can  improve the process of document clustering.
+In earlier research concerning domain specific articles,  \citet{Truong2017Thesis}, found that in-domain training of the word embeddings can  improve the process of document clustering.
 This effect is even stronger than the number of training examples and the model architecture.
@@
 state that the embeddings show high error rates on the validation scores.
-This seems to indicate that the word-vectors are of good quality, but that the available validation metrics cannot confirm this.
+This seems to indicate that the word-vectors are of good quality, but that the available validation metrics fail to confirm this.
 \citet{Truong2017Thesis} used multiple word similarity validations to asses the quality of the word embeddings.
@@
 \begin{jumpin}
-	\textbf{RQ.1} Have word-embeddings a higher accuracy for academic texts than TF-IDF for article classification?\\
-	\textbf{RQ.2} Which metric can be used to measure the accuracy of word embeddings for scientific articles?
+	\textbf{RQ. 1} Have word-embeddings a higher accuracy for academic texts than TF-IDF for article classification?\\
+	\begin{adjustwidth}{0.3in}{}
+		\textbf{RQ. 1.1} Does TF-IDF weighting increase the performance of word embedding on academic texts for article classification?\\
+		\textbf{RQ. 1.2} Can the usage of alternative distance metrics improve the performance of word embedding on academic articles for article classification?
+	\end{adjustwidth}
+	\vspace{0.1in}\textbf{RQ. 2} Can word embeddings, combined with pca\footnote{principal component analysis}-based TSNE, create a two-dimensional plot that preserves the journal relatedness?
 \end{jumpin}
 \subsubheader{Embedding and TF-IDF}
-Research question one focusses on the classification results of both embedding-based techniques and TF-IDF.
+RQ.
+1 focusses on the classification results of both embedding-based techniques and TF-IDF.
 To measure classification task we use the rank of the class to which the item belongs.
 Transforming the classification task from a binary metric to a ranking metric.
-For this task, we will use different versions of embeddings, and different TF-IDF versions to not only compare the two techniques, but also look for the optimal results of both techniques.
+For this task, we will use different versions of embeddings, to answer RQ 1.1, and different TF-IDF versions to not only compare the two techniques, but also look for the optimal results of both techniques.
+To achieve the optimal results, we compare 20 distance metrics from the SciPy library on ranking performance on the standard embeddings.
 For this part of the research, we will use the following hypothesis:
-\begin{center}
-\textit{Embedding based techniques give lower rankings than the TF-IDF based techniques}
-\end{center}
-By validating our invalidating  this hypothesis we get an indication of the performance of the embeddings compare to older techniques, and get insight into possible performance and resource trade-off's and if the computational power and AI expertise needed for the creation of embeddings is worth the investment .
+\begin{jumpin}
+\textit{\textbf{H. 1} Embedding based techniques give lower rankings than the TF-IDF based techniques.}
+\begin{jumpin}
+\textit{\textbf{H. 1.1} TF-IDF weighted document embeddings outperform standard embeddings on the classification of academic articles.}\\
+\textit{\textbf{H. 1.2} Cosine similarity based ranking results in the best performance for the classification of academic articles.}\\
+\textit{\textbf{H. 1.3} Word embeddings use less memory while giving better ranking results than TF-IDF on the classification of academic articles.}
+\end{jumpin}
+\end{jumpin}
+By validating our invalidating  these hypotheses we get an indication of the performance of the embeddings compare to older techniques,  get insight into possible performance and resource trade-off's and get insight into the performance of different distance calculation metrics.
+RQ. 2 concerns the visualization of word embeddings and the accuracy of this visualization. To answer this research question, we will use the following hypothesis:
+\begin{jumpin}
+\textit{\textbf{H. 2} Word embeddings, combined with pca-based TSNE can preserve the journal relatedness on a two dimensional plot.}
+\end{jumpin}
+The validation of this hypothesis will be visual, this serves as a supporting insight in the relatedness of journals.
 

### 2018-06-20 Thesis/Parts/Research_results/Research_results.tex
shallow total iteration

--- 2018-06-11 Thesis/Parts/Research_results/Research_results.tex
@@
 \subheader{Ranking}
-\includegraphics[width=6in]{Plots/Abstract_rankings}\\
-\\
-\includegraphics[width=6in]{Plots/Title_rankings}\\
+The figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} show the result of the categorization task as ranking results.
+The rank indicates the position of the correct journal in the sorted list of matched journals.
+Figure~\ref{figure:titleRanks} shows the ranking results for the different sets based on the title.
+Figure~\ref{figure:abstractRanks} displays the ranking results based on the abstract.
+Both graphs show both average and median ranks, based on the cosine-similarity between the article and journal embeddings or feature vectors.\\
+\begin{figure}[hbt]
+\includegraphics[width=6.5in]{Plots/Title_rankings}
+\caption{Median and average title rankings}\label{figure:titleRanks}
+\end{figure}
+\begin{figure}[hbt]
+\includegraphics[width=6.5in]{Plots/Abstract_rankings}
+\caption{Median and average abstract rankings}\label{figure:abstractRanks}
+\end{figure}
+\clearpage
 \subheader{Rank distribution}
-\includegraphics[width=6in]{Plots/Abstract_rank_distribution}\\
-\\
-\includegraphics[width=6in]{Plots/Title_rank_distribution}\\
+Figures~\ref{figure:titleDistribution} \&~\ref{figure:abstractDistribution} show the distributions of the ranks for each set.
+The figures plot the summed amount of articles against the ranks on a logarithmic scale.
+Figure~\ref{figure:titleDistribution} shows the rank distribution for the titles, figure~\ref{figure:abstractDistribution} shows this for the ranks based on the abstract.
+These graphs give a detailed view of the ranks presented in their respective figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks}.
+\begin{figure}[hbt]
+\includegraphics[width=6.5in]{Plots/Title_rank_distribution}
+\caption{Title rank distribution per set}\label{figure:titleDistribution}
+\end{figure}
+\begin{figure}[hbt]
+\includegraphics[width=6.5in]{Plots/Abstract_rank_distribution}
+\caption{Abstract rank distribution per set}\label{figure:abstractDistribution}
+\end{figure}
+
+\clearpage
 \subheader{F1-Score}
-d
+Figures~\ref{figure:f1Title} \&~\ref{figure:f1Abstract} show the precision, recall and f1 scores.
+These scores are calculated on journal level, and are averaged per set.
+Figure~\ref{figure:f1Title} shows the F1 score for the title and figure~\ref{figure:f1Abstract} shows the scores for the abstract.
+These scores indicate the performance of the sets on absolute hits/top-1.
+\begin{figure}[hbt]
+\includegraphics[width=6.5in]{Plots/Title_avg_f1}
+\caption{Precision, recall and F1 scores based on title}\label{figure:f1Title}
+\end{figure}
+\begin{figure}[htb]
+\includegraphics[width=6.5in]{Plots/Abstract_avg_f1}
+\caption{Precision, recall and F1 scores based on abstract}\label{figure:f1Abstract}
+\end{figure}
+\clearpage
+\subheader{Memory usage}
+Table~\ref{table:memoryUsage} shows the total memory usage of each set for the \textit{Validation set}, indicating their storage costs in gigabytes\footnote{1024 based}.\\
+\begin{table}[hbt]
+\begin{center}
+\begin{tabular}{|l|l|l|l|l|}
+\hline
+Set & Size in GB & Absolute hit percentage & Median title rank & Median abstract rank\\
+&&\begin{tabular}{p{0.5in}|p{0.5in}}Title & Abstract\end{tabular}&&\\
+\hline
+tfidf 5k 5K & $9.82$ & \begin{tabular}{p{0.5in}|p{0.5in}}5.42\% & 10.18\%\end{tabular} & 50 & 27\\
+\hline
+tfidf 5K 10K & $11.47$ & \begin{tabular}{p{0.5in}|p{0.5in}}6.49\% & 11.08\%\end{tabular} & 38 & 15\\
+\hline
+\textbf{tfidf 10K 10K} &\textbf{11.61}& \begin{tabular}{p{0.5in}|p{0.5in}}\textbf{6.79\%} & \textbf{11.32\%}\end{tabular} & \textbf{35} & \textbf{14}\\
+\hline
+embedding & $3.13$ & \begin{tabular}{p{0.5in}|p{0.5in}}7.92\% & 9.24\%\end{tabular} & 27 & 23\\
+\hline
+5k embedding & $3.13$ & \begin{tabular}{p{0.5in}|p{0.5in}}6.34\% & 8.36\%\end{tabular} & 42 & 27\\
+\hline
+10k embedding & $3.13$ & \begin{tabular}{p{0.5in}|p{0.5in}}7.03\% & 8.76\%\end{tabular} & 34 & 25\\
+\hline
+\textbf{tfidf embedding} & \textbf{3.13} & \begin{tabular}{p{0.5in}|p{0.5in}}\textbf{7.89\%} & \textbf{9.33\%}\end{tabular} & \textbf{27} & \textbf{22}\\
+\hline
+1k 6k embedding & $3.06$ & \begin{tabular}{p{0.5in}|p{0.5in}}5.16\% & 7.86\%\end{tabular} & 64 &31 \\
+\hline
+\end{tabular}
+\end{center}
+\caption{Memory usage and performance for each set}\label{table:memoryUsage}
+\end{table}
+
 \end{document}
+
+%1k_6k_embedding
+%  7.85534550616
+
+%tfidf_embedding
+%  9.33435128732
+
+%tfidf_5k_5K
+%  10.1820853794
+
+%embedding
+%  9.24083300477
+
+%tfidf_5K_10K
+%  11.0842682533
+
+%tfidf_10K_10K
+%  11.3222696154
+
+%10k_embedding
+%  8.75583800194
+
+%5k_embedding
+%  8.36120161582

### 2018-06-21 Thesis/Parts/Abstract/Abstract.tex

@@
 This research focusses on the usefulness of word embeddings on domain specific texts, concerning $1.391.543$ scientific articles which have been published in 2017.
-The data shows that the word embeddings only perform better than TF-IDF, which was chosen as a traditional alternative, when the ranking is done on titles.
-The best ranking result is obtained through a TF-IDF with a vocabulary size of 10.000 applied on the abstracts, resulting in a median rank of 14, while the pure word embeddings result in a median rank of 23.
-This shows that word embeddings, although useful, are not unchallenged by older techniques.
 \end{document}

### 2018-06-21 Thesis/Parts/Data/Data.tex
2d plot explanation added

@@
 To limit the computational and storage expenses and to reduce noise by rare words, we limit our vocabulary size.
-We denote the TF-IDF configurations as follows: $vocabulary size/hashbucket size$.
-Furthermore, we denote 1.000 as 1K, since we deal with chosen values which can be exactly noted given this notation.\\
+We denote the TF-IDF configurations as follows: $vocabulary size/hashbucket size$. Furthermore, we denote 1.000 as 1K, since we deal with chosen values which can be exactly noted given this notation.
 \begin{figure}
@@
 \end{figure}
-
-Figure~\ref{figure:tfidfPerformance} shows the performance and storage size\footnote{in gigabyte, 1024 based} of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations.
+\FloatBarrier
+Figure~\ref{figure:tfidfPerformance} shows the performance, as median rank, and storage size, in gigabyte, of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations.
 This plot shows that, while the required storage size keeps rising, the performance on title quickly stagnates, and the performance on abstract follows too.
@@
 \header{Pipeline}
-We procesessed the TF-IDF sets an the embedding sets via the same pipeline, based on vector calculations. This ensures comparable results. The pipeline is setup as follows:
+We procesessed the TF-IDF sets and the embedding sets via the same pipeline, using their common vector properties. This ensures comparable results, the pipeline is set-up as follows:
 \begin{enumerate}
@@
 To further analyse the ranking results, we plot the rank distribution to get an indication of the ranking-landscape.
+
+\header{Two dimensional plot}
+To create a plot, we transformed the 300-dimensional journal vectors into 2-dimensional vectors using TSNE based on pca\footnote{Principal component analysis}.
+These 2-dimensional vectors, representing the x \& y coordinate, can then be drawn in a plot.
+To visualize the preservation of journal-relatedness while converting the 300 dimensions to 2 dimension, we create groupings using k-means.
+These groupings are created on the 300-dimensional vectors, and are visualized in the plot using colors.
 \end{document}

### 2018-06-21 Thesis/Parts/Research_results/Research_results.tex
journal plots embedded in thesis

@@
 \end{table}
+\subheader{Journal relatedness plot}
+Figure~\ref{figure:journalPlotNormal} is the two dimensional plot of the journal embeddings.
+The journals are color-marked by publisher.
+Red is Wiley, lime is Elsevier and blue is Springer Nature.
+The grey points are other or not-specified.
+Figure~\ref{figure:journalPlotGroups} shows the journals, grouped by a k-means algorithm, creating 8 groups.
+The bottom right shows the names of the journals closest to the center of the group.
+The k-means algorithm ran on the 300-dimensional set, while the plot shows the 2-dimensional set.
+\begin{landscape}
+\begin{figure}
+\includegraphics[height=6.5in]{Plots/journal_plot_normal}
+\caption{Journal plot grouped by publisher}\label{figure:journalPlotNormal}
+\end{figure}
+\end{landscape}
 
+\begin{landscape}
+\begin{figure}
+\includegraphics[height=6.5in]{Plots/journal_plot_grouped}
+\caption{Journal plot grouped k-means grouped}\label{figure:journalPlotGroups}
+\end{figure}
+\end{landscape}
 \end{document}
-
-%1k_6k_embedding
-%  7.85534550616
-
-%tfidf_embedding
-%  9.33435128732
-
-%tfidf_5k_5K
-%  10.1820853794
-
-%embedding
-%  9.24083300477
-
-%tfidf_5K_10K
-%  11.0842682533
-
-%tfidf_10K_10K
-%  11.3222696154
-
-%10k_embedding
-%  8.75583800194
-
-%5k_embedding
-%  8.36120161582

### 2018-06-21 Thesis/Parts/Discussion/Discussion.tex
Journal plot

@@
 Which is significantly worse than the embedding, which also uses less memory.
+
+\subheader{Journal plots}
+Figure~\ref{figure:journalPlotNormal} show the journals in the, what we will refer to as "subject spectrum".
+We do this because the journal embeddings capture journal-relatedness, which leads to the clustering of related articles, which share, in varying degree, the common subject.
+In this figure, we can see that the publisher Wiley is more active in the right part of the spectrum than the left.
+We can further see that Nature is far to the center, as we would expect a generic journal to be, but it is on the biology/medicine side of the center (indicated by the position of Cell and Pharmaceutical Research).\\
+Figure~\ref{figure:journalPlotGroups} shows the journals, grouped with k-means on the original 300-dimensional embedding vector.
+On the bottom right hand side, the journals closest to the center point of the k-means algorithm are displayed.
+In this plot we can see that the original embedding-clustering is relatively well preserved, most groups stay clustered together.
+The central journals belong to mainly mixed groups, which is likely caused by either their general nature, or due to a collection of articles on the opposing ends of the spectrum.\\
+The interactive version shows that the clusterings, as seen on both figure~\ref{figure:journalPlotNormal} \&~\ref{figure:journalPlotGroups} are subject based.
+Journals concerning the same subjects are correctly clustered together, and the journals in between topic clusters are also positioned at logical positions.
+It furthermore shows that the k-means groupings create an insight in research fields, although it is limited by the amount of groups the k-means algorithm creates.
 \end{document}

### 2018-06-22 Thesis/Parts/Future_work/Future_work.tex
Future work

--- 2018-06-18 Thesis/Parts/Future_work/Future_work.tex
@@
 \header{Future work}
-- How do unique token count, token count and vocabulary size relate for TF-IDF?
-- Can high quality word similarity sets be created from embedding for future benchmarking?
-- Can embeddings give a visual representation of the evolution of scientific research over time?
-- Does TF-IDF improve when top-occurring words are cut-off?
+This research focussed on the quality of word embeddings on academic texts.
+To do this we used both a comparison to TF-IDF and a visualization of the word embeddings.
+Future works may seek to further improve the quality of the word embeddings.
+\subheader{Smarter cutting}
+An interesting improvement to enhance the word embeddings with could be a smarter way to remove noise, based on word embeddings.
+This might be achieved by analysing the word embedding spectrum before normalization, and to then cut the center of the vector space out.
+This must be applied before normalization, since normalization causes all embeddings to have a distance of 1 to the center point.
+All words which are generic are in the center of the spectrum.
+Removing these words prevents the larger texts to be pulled towards the middle, where they lose the parts of their meaning which sets them apart from the other journals.
+We expect that this way of cutting, instead of word-occurrence cutting, will improve the quality of the word embeddings.
+
+\subheader{Text combination}
+To cope with the problem of articles that do have an abstract but no title, or vice versa, it would be interesting to see what the quality of the embeddings would be if both texts were combined into one text.
+This should be possible since title and abstract per article share a common topic.
+We would expect that the common text would have the quality of the abstract, which is according to our findings the part that is best usable for the embeddings and TF-IDF.
+
+\subheader{TF-IDFs performance point}
+In our research, TF-IDF performed better on the abstracts than on the titles, which, according to us, is caused by the text size of the two texts.
+This leads to the question, how do unique token count, token count and vocabulary size relate for TF-IDF?
+Is there a point in at which we can expect that TF-IDF will be able to rank items in the top-10?
+If this is the case, we can skip the TF-IDF calculations in certain situations, saving time and costs.
+
+\subheader{Reversed word pairs}
+At this point in time, there are no domain specific word pair sets available.
+However, as we demonstrated, we can still test the quality of word embeddings.
+Once we established that we have word vectors of high quality, could we create word pairs from the embeddings?
+If this is the case, we could reverse-engineer domain specific word pair sets for future use.
+These word pairs should most likely still be validated by humans, but the automatic generation of word pairs should already reduce the effort needed for this process.
+
+\subheader{Historical overview}
+We have shown that the word embeddings can be used to create a subject spectrum, in which we plotted all the articles of one year.
+This gives insight into the currently popular research field, indicated by dense areas on the plot.
+If we would create this plot over multiple years, and then show these years in chronological order, we should be able to see the evaluation of research fields in time, giving more insight in shifting interests and the development of new research areas.
+
+\subheader{TF-IDF top-cutoff}
+In our research we used a dataset from which we removed the top 1k words, together with everything beyond 6k.
+This dataset did not perform well in our research, future work could look into this by validating if the top-words cut-off decreases the TF-IDF performance.
+Our findings on this topic are minimal, although we can say that we would not expect that the top-cutoff improves the performance, since a set with the top 5k words performed better than the 1k till 6k words set.
 \end{document}

### 2018-06-22 Thesis/Parts/Conclusion/Conclusion.tex
Journal plot
discussion & presentation

@@
 \header{Conclusion}
-This research shows that the article embeddings, created with word embeddings, perform better than the reasonable TF-IDF alternatives for our categorization task, based on article titles.
+This research shows that the article embeddings, created with word embeddings, perform better than the reasonable TF-IDF alternatives on our categorization task, based on article titles.
 The TF-IDF alternatives give better results than the embeddings based on abstracts.
 The performance of the embeddings have been improved by weighting them with the TF-IDF values on word level, although this improvement cannot be seen as significant on our dataset.
-This improved embedding results in a median rank decrease of 8 on the titles and an median rank increase of 8 on the abstract, compared to the best performing TF-IDF alternative.
+This improved embedding set results in a median rank decrease of 8 on the titles and an median rank increase of 8 on the abstract, compared to the best performing TF-IDF alternative.
 The embedding also results in a memory decrease of 73.04\% compared to the best performing TF-IDF alternative, making it more viable to keep it in memory.
+The visualization of the journal embedding show that similar journals are grouped together, indicating a preservation of relatedness between the journal embeddings.
 We thus come to the following conclusions:
@@
 \item{Embeddings give a significant decrease in memory usage compared to TF-IDF}
+\item{Visualization of the journal embeddings show that the embeddings capture and preserve subject relatedness when they are combined to create embeddings for larger texts}
+
 \end{enumerate}

### 2018-06-22 Thesis/Parts/Discussion/Discussion.tex
discussion & presentation

@@
 \header{Discussion}
-\subheader{Best performers}
+
+\subheader{Result analysis}
+\subsubheader{Best performers}
 The data, as presented in figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank on abstract and 3 median ranks on title.
 For the embeddings the TF-IDF weighted embedding works better than the others, although it is has is not a significant improvement compared to the default embeddings, which 1 median rank higher on abstract, and equal on title.
-\subheader{Sets}
+
 \subsubheader{TF-IDF}
@@
 It could be possible that at higher vocabulary sizes the cut-off would result in a sharper signal, we did not looked into this further due to our findings that the TF-IDF performance stagnates (presented in figure~\ref{figure:tfidfPerformance}).
-\subsubheader{Embedding}
-\subsubsubheader{Limited tfidf embeddings}
+
+\subsubheader{Limited tfidf embeddings}
 The limited TF-IDF embeddings all under perform, compared to the non-limited TF-IDF embedding, on the median and average ranking.
@@
 
-\subheader{Memory usage}
+\subsubheader{Memory usage}
 Although the TF-IDF outperforms the embeddings on the abstracts, the memory usage of the TF-IDF is higher than the memory usage of the embeddings.
@@
 
-\subheader{Journal plots}
+\subsubheader{Journal plots}
 Figure~\ref{figure:journalPlotNormal} show the journals in the, what we will refer to as "subject spectrum".
@@
 On the bottom right hand side, the journals closest to the center point of the k-means algorithm are displayed.
-In this plot we can see that the original embedding-clustering is relatively well preserved, most groups stay clustered together.
+While most journal titles clearly state the research field, some do not.
+SAGE opens research area is social and behavioural sciences and humanities, RSC Advances' research area is chemical sciences and Orvosi hetilaps research area is experimental and clinical medicine.
+In the plot we can see that the original embedding-clustering is relatively well preserved, most groups stay clustered together.
 The central journals belong to mainly mixed groups, which is likely caused by either their general nature, or due to a collection of articles on the opposing ends of the spectrum.\\
@@
 It furthermore shows that the k-means groupings create an insight in research fields, although it is limited by the amount of groups the k-means algorithm creates.
+We found that our findings on the 2-dimensional representation of embeddings are simmilar to those of \citet{dai2015document}, who plotted 4.4 million Wikipedia articles.
+
+\subheader{Improvements}
+This research shows that, even tough the embeddings are able to capture and preserve relatedness, TF-IDF is able outperform the embeddings.
+Earlier research already proposed improvements to the word embeddings.
+\citet{dai2015document} show that the usage of paragraph vectors improve the accuracy of word embeddings with 4.4\% on triplet creation with the wikipedia corpus, and a 3.9\% improvement on the same task based on the arXiv articles.
+Furthermore, \citet{le2014distributed} show that the usage of paragraph vectors decrease the error rate (positive/negative) with 7.7\% compared to averaging the word embeddings on categorizing text as either positive or negative.
+While this looks promising, we have to keep in min that our task differs from earlier tasks, since we do not categorize on 2 categories, but on more than 3k.
+Still, we would expect an improvement by using paragraph vectors since the classification task if fundamentally the same, only on a much larger scale.
+
 \end{document}

### 2018-06-22 Thesis/Parts/Future_work/Future_work.tex
discussion & presentation

@@
 Future works may seek to further improve the quality of the word embeddings.
-\subheader{Smarter cutting}
+
+\subheader{Intelligent cutting}
 An interesting improvement to enhance the word embeddings with could be a smarter way to remove noise, based on word embeddings.

### 2018-06-22 Thesis/Parts/Discussion/Discussion.tex
Discussion p2

@@
 \subheader{Result analysis}
+\begin{jumpin}
 \subsubheader{Best performers}
@@
 We found that our findings on the 2-dimensional representation of embeddings are simmilar to those of \citet{dai2015document}, who plotted 4.4 million Wikipedia articles.
-
+\end{jumpin}
 \subheader{Improvements}
@@
 Still, we would expect an improvement by using paragraph vectors since the classification task if fundamentally the same, only on a much larger scale.
+\citet{pennington2014glove} showed that the GloVe model  outperforms the CBOW model, used in this research on a word analogy task.
+While using other methods may look promising, \citet{levy2015improving} observed that there were no major differences between the various method.
+They state that the difference in performance is manly caused by the global/hyper parameters.
+In this research,  we have not looked at comparison between various models and/or (hyper) parameters.
+We instead used a standard configuration, to focus more on the actual performance of the embeddings, instead of the best-possible performance.
 

### 2018-06-22 Thesis/Parts/Abstract/Abstract.tex
minor changes

@@
 Giving promising results, the word embeddings have been studied and improved over recent years.
-However, these studies have been focused on generic text, which do not contain the characteristics of in-domain knowledge, such as rare domain specific words.
+However, these studies have been focused on, or in combination with, generic texts, which are not limited the characteristics of in-domain texts, such as rare domain specific words.
 This research focusses on the usefulness of word embeddings on domain specific texts, concerning $1.391.543$ scientific articles which have been published in 2017.

### 2018-06-22 Thesis/Parts/Background/Background.tex
minor changes

@@
 \subheader{Neural Network}
-Neural Networks are computational structures, based on vector and/or matrix calculations.
-They can be applied to many different tasks, but need to be trained for each task.
+A complete in-depth background into neural networks is beyond the scope of this thesis, therefore we will only describe the simplified basic application of the neural networks in IR.
+Neural Networks are multi-layered computational software, based on vector and/or matrix calculations, which tries to map input values to output values.
+This mapping uses a pre-defined amount of layers that modify the values through matrix calculations.
+Neural networks rely on training to create optimal values for these layers, these values are only changed at training time, high quality training data is therefore essential for neural networks.
+Neural networks can be applied to many different tasks, as long as there is sufficient training data available.
 This training is the process of iteratively adjusting multiplication matrices or vectors to achieve the optimal result.
 Which is the result that is as close as possible to the given output for different input and output sets.
-In some IR techniques, Neural Networks are used to either predict words that may occur around a given word, or predict a word given words that surround it. For example, given the sentence\\
+To create word embeddings, Neural Networks are used to either predict words that may occur around a given word, or predict a word given words that surround it.
+For example, given the sentence\\
 \begin{center}
@@
 The results produced by the techniques have to be validated to determine their quality (in usage).
-The quality of the results can be validated through, among others the F1 score, which combines the precision score and the recall score in a single metric, and, for classification tasks, the rank of the correct category.
+The quality of the results can be validated through, among others the F1 score, which combines the precision score and the recall score in a single metric, and, for classification tasks, the rank of the correct class, which is for this research a journal.
 The embeddings can furthermore be validated through their performance on tasks such as word analogies, word similarities, categorization and position visualization.

### 2018-06-22 Thesis/Parts/Discussion/Discussion.tex
minor changes

@@
 Furthermore, \citet{le2014distributed} show that the usage of paragraph vectors decrease the error rate (positive/negative) with 7.7\% compared to averaging the word embeddings on categorizing text as either positive or negative.
-While this looks promising, we have to keep in min that our task differs from earlier tasks, since we do not categorize on 2 categories, but on more than 3k.
+While this looks promising, we have to keep in mind that our task differs from earlier tasks, since we do not categorize on 2 categories, but on more than 3k.
 Still, we would expect an improvement by using paragraph vectors since the classification task if fundamentally the same, only on a much larger scale.
@@
 While using other methods may look promising, \citet{levy2015improving} observed that there were no major differences between the various method.
-They state that the difference in performance is manly caused by the global/hyper parameters.
+They state that the difference in performance is mainly caused by the global/hyper parameters.
 In this research,  we have not looked at comparison between various models and/or (hyper) parameters.

### 2018-06-22 Thesis/Parts/Motivation/Motivation.tex
minor changes

@@
 \subheader{In-domain embeddings and validation}
-In earlier research concerning domain specific articles,  \citet{Truong2017Thesis}, found that in-domain training of the word embeddings can  improve the process of document clustering.
-This effect is even stronger than the number of training examples and the model architecture.
+In earlier research concerning domain specific articles,  \citet{Truong2017Thesis} found that in-domain training of the word embeddings can  improve the process of document clustering.
+The usage of in-domain data is more important than the number of training examples and the model architecture.
 \citet{lai2016generate} found that the corpus domain is more important than the corpus size.
@@
 \end{jumpin}
-The validation of this hypothesis will be visual, this serves as a supporting insight in the relatedness of journals.
-
+The validation of this hypothesis will rely on visual conformation.
+We expect to see clustering of journals in certain areas, which indicates a research subject.
+We also expect that articles which are visually close together are closely related by subject.
 \end{document}

### 2018-06-25 Thesis/Parts/Background/Background.tex
re-read background & presentation rename

@@
 \subheader{Neural Network}
-A complete in-depth background into neural networks is beyond the scope of this thesis, therefore we will only describe the simplified basic application of the neural networks in IR.
+A complete in-depth background into neural networks is beyond the scope of this thesis, therefore we will only describe the simplified woking of a neural network, and its basic application in IR.
 Neural Networks are multi-layered computational software, based on vector and/or matrix calculations, which tries to map input values to output values.
@@
 This training is the process of iteratively adjusting multiplication matrices or vectors to achieve the optimal result.
-Which is the result that is as close as possible to the given output for different input and output sets.
-To create word embeddings, Neural Networks are used to either predict words that may occur around a given word, or predict a word given words that surround it.
+Which is the result that is as close as possible to the given output for all input and output sets.\\To create word embeddings, Neural Networks are used to either predict words that may occur around a given word, or predict a word given words that surround it.
 For example, given the sentence\\
@@
 the Neural Network can be trained to either predict the words around "searches" (the, search, engine, for, relevant, information) or to predict the word "searches", given the surrounding (the, search, engine, for, relevant, information).
-This trained matrix, a vector per word which is referred to as a word embedding, now indicates "word relatedness" which, as mentioned earlier enables association (thus retrieval) with related(relevant) texts.
+This result in a matrix, a vector per word which is referred to as a word embedding.
+This embedding indicates "word relatedness" which, as mentioned earlier enables association (thus retrieval) with related(relevant) texts.
+It is to be noted that the word embeddings are only able to represent word relatedness to the other words trained in the same run.
+Due to the random initialization of the initial values of the layers in the neural networks, neural networks do not produce every run the same results.
+Therefore, word embeddings from different runs of the same neural network cannot be compared.
 Neural networks are also used for other tasks such as video recommendation on Google's YouTube, as described by \citet{covington2016deep}.
@@
 \subheader{Embedding}
-An embedding is a distributed, numerical representation of a text in a vector space\footnote{The vector space of separately trained word embeddings are not shared, since the trained vector dimensions are not fixed.
-This means that two separately trained word embeddings which have the same dimension do not share the same vector space.} which can capture both the semantic and syntactic information\cite{mikolov2013distributed}.
+An embedding is a distributed, numerical representation of a text in a vector space\footnote{The vector spaces of separately trained word embeddings differ, since each run the initial values of the neural network are randomly initialized.
+This means that the same word trained in two seperate runs do not have to have the same embedding.
+However, they will have the same relationship to other words trained in their respective runs.} which can capture both the semantic and syntactic information\cite{mikolov2013distributed}.
 In the case of a word embedding, the embedding represents the word.
@@
 \subheader{Text analysis techniques}
-To enable a computer to process text, for embedding creation or for tasks, the text has to be processed by an algorithm.
+To enable a computer to process text, for embedding creation or for other tasks, the text has to be processed by an algorithm.
 In this research we used embeddings created by Word2Vec and TF-IDF feature vectors.
@@
 The Paragraph Vector framework is based on the word vectors framework.
-The difference between the frameworks is the calculation of the probability, the Paragraph Vector framework uses an matrix D, which consists of every paragraph.
+The difference between the frameworks is the calculation of the probability, the Paragraph Vector framework uses an matrix, which consists of every paragraph.
 This matrix is used to replace a concatenation or average of word vectors.
 An advantage of the paragraph vector model is that it takes the word order into consideration, atleast in a small context \cite{le2014distributed}.
-\citet{dai2015document} state in their paper "Document embedding with paragraph vectors" that the Paragraph Vectors model performs significantly better than other models on grouping, triplet finding and related object/article finding tasks on the Wikipeida and arXiv texts.
+\citet{dai2015document} state that the Paragraph Vectors model performs significantly better than other models on grouping, triplet finding and related object/article finding tasks on Wikipeida and arXiv texts.
 
@@
 The model transforms the word co-occurrences of all words in the corpus to chances, it excludes all the zero values and uses that as initial input for the neural network.
-This model out performs other models on three specific tasks, word analogy, word similarity and entity recognition.\\
+This model out performs other models on three specific tasks, word analogy, word similarity and entity recognition according to the findings by \citet{pennington2014glove}.\\
 
@@
 \end{jumpin}
-As \citet{lai2016generate} state in their paper "How to generate a good word embedding?", all embedding methods rely on the same hypothesis, words that occur in similar contexts have similar meanings.
+As \citet{lai2016generate} state in their paper "How to generate a good word embedding?", that all embedding methods rely on the same hypothesis, \textit{words that occur in similar contexts have similar meanings}.
 They furthermore found that larger corpus' lead to better quality embeddings, but that the domain in which the embeddings are trained is dominant over the corpus size.
@@
 The results produced by the techniques have to be validated to determine their quality (in usage).
-The quality of the results can be validated through, among others the F1 score, which combines the precision score and the recall score in a single metric, and, for classification tasks, the rank of the correct class, which is for this research a journal.
+The quality of the results can be validated through, among others the F1 score\footnote{The F1 score combines the precision score and the recall score in a single metric} and, for classification tasks, the rank of the correct class, which is for this research a journal.
 The embeddings can furthermore be validated through their performance on tasks such as word analogies, word similarities, categorization and position visualization.
@@
 This means that the resulting vector of embedding of "Man" minus the embedding of "King" is approximately the embedding of "Woman" minus the embedding of "Queen".
-This resulting vector may be close to a vector "monarch" for example.
+This resulting vector may, for example, be close to the vector representing "monarch".
 \subsubheader{Word Similarity}

### 2018-06-25 Thesis/Parts/Abstract/Abstract.tex
added references

@@
 \begin{document}
-\header{Abstract}
+\fakeheader{Abstract}
 Over the last few years, word embeddings have taken a dominant position in the Information Retrieval domain.
@@
 However, these studies have been focused on, or in combination with, generic texts, which are not limited the characteristics of in-domain texts, such as rare domain specific words.
-This research focusses on the usefulness of word embeddings on domain specific texts, concerning $1.391.543$ scientific articles which have been published in 2017.
+This research focusses on the usefulness of word embeddings on domain specific texts, concerning 1.391.543 scientific articles which have been published in 2017.
 \end{document}

### 2018-06-25 Thesis/Parts/Discussion/Discussion.tex
added references

--- 2018-06-22 Thesis/Parts/Discussion/Discussion.tex
@@
 Figure~\ref{figure:journalPlotGroups} shows the journals, grouped with k-means on the original 300-dimensional embedding vector.
-On the bottom right hand side, the journals closest to the center point of the k-means algorithm are displayed.
-While most journal titles clearly state the research field, some do not.
-SAGE opens research area is social and behavioural sciences and humanities, RSC Advances' research area is chemical sciences and Orvosi hetilaps research area is experimental and clinical medicine.
-In the plot we can see that the original embedding-clustering is relatively well preserved, most groups stay clustered together.
-The central journals belong to mainly mixed groups, which is likely caused by either their general nature, or due to a collection of articles on the opposing ends of the spectrum.\\
+In the plot we can see that the original embedding-clustering, as provided by the k-means algorithm, is relatively well preserved, most groups stay clustered together.
+The journals in the center of the plot belong mainly to mixed groups, which is caused by the separation of the medicine field into two groups, with as center journals \textit{Orvosi hetilap} and \textit{Journal of Clinical and Diagnostic Research}.\\
 The interactive version shows that the clusterings, as seen on both figure~\ref{figure:journalPlotNormal} \&~\ref{figure:journalPlotGroups} are subject based.
@@
 It furthermore shows that the k-means groupings create an insight in research fields, although it is limited by the amount of groups the k-means algorithm creates.
-We found that our findings on the 2-dimensional representation of embeddings are simmilar to those of \citet{dai2015document}, who plotted 4.4 million Wikipedia articles.
-
+This problem is already visible in figure~\ref{figure:journalPlotGroups} where, as discussed earlier, the k-means algorithm divided one field into multiple groups.
+We found that our findings on the 2-dimensional representation of embeddings are similar to those of \citet{dai2015document}, who plotted 4.4 million Wikipedia articles.
+The mayor difference between our plot and their plot is that they focus on just a view subjects in an entire plot, and have access to (human made) partitioning data.
+They have therefore a more reliable grouping metric.
+\end{jumpin}
 \subheader{Improvements}
@@
 Furthermore, \citet{le2014distributed} show that the usage of paragraph vectors decrease the error rate (positive/negative) with 7.7\% compared to averaging the word embeddings on categorizing text as either positive or negative.
-While this looks promising, we have to keep in min that our task differs from earlier tasks, since we do not categorize on 2 categories, but on more than 3k.
-Still, we would expect an improvement by using paragraph vectors since the classification task if fundamentally the same, only on a much larger scale.
+While this looks promising, we have to keep in mind that our task differs from earlier tasks, since we do not categorize on 2 categories, but on more than 3k.
+Still, we would expect an improvement by using paragraph vectors since the classification task if fundamentally the same, only on a much larger scale., which complicates the task due to the "grey areas"  between categories, which increases given more categories.
+\citet{pennington2014glove} showed that the GloVe model outperforms the CBOW model, which is used in this research, on a word analogy task.
+\citet{wang2016linked} introduced the Linked Document Embedding method (LDE) method, which makes use of additional information about a document, such as citations.
+Their research specifically focused on categorizing documents, showed a 5.89\% increase of the micro-F1 score on LDE compared to CBOW, and a 9.11\% increase of the macro-F1 score.
+We would expect that applying this technique on our dataset would improve our scores, given earlier results on comparable tasks.\\
+Even though  much research has been done, we have not been able to find published results which are directly comparable to our results.
+This is likely due to our high amount of categorization groups, which enabled us to handle our results as a ranking problem, instead of a absolute hit, which has been used in earlier researches\cite{wang2016linked}.
+Even though we have a F1 score, which indicates performance on the absolute hits, our results are not comparable to other works due to the amount of categories, and their overlapping subjects\footnote{As visualized in the journal embedding plots and discussed earlier}.
 

### 2018-06-25 Thesis/Parts/Future_work/Future_work.tex
added references

@@
 Future works may seek to further improve the quality of the word embeddings.
+
+\subheader{Method differences}
+\citet{levy2015improving} observed that there were no major differences between the various embedding creation methods.
+They state that the difference in performance is mainly caused by the global/hyper parameters.
+In this research, we have not looked at comparison between various models and/or (hyper) parameters.
+We instead used a standard configuration, to focus more on the actual performance of the embeddings, instead of the best-possible performance.
+Future work could seek to validate the results of \citet{levy2015improving} by expanding our research with multiple metrics.
+It should be noted however that Levy et al.
+base their conclusions on word similarity and word analogy tasks, and not on categorization.
+This is the reason why we did not take this research into account in our discussion, since their experiments are not comparable to ours.
 

### 2018-06-25 Thesis/Parts/Research_results/Research_results.tex
Future work
discussion & presentation
added references

@@
 The bottom right shows the names of the journals closest to the center of the group.
+While most names state the topic of the research field, some do not.
+These are  \textit{SAGE Open}: social and behavioural sciences and humanities, \textit{RSC Advances}: chemical sciences, and \textit{Orvosi hetilap}: experimental and clinical medicine.
 The k-means algorithm ran on the 300-dimensional set, while the plot shows the 2-dimensional set.
+A digital version of this plot can be found at:~\url{https://goo.gl/tdHGnD}.
+The usage of this digital version is advised, since this interactive plot enables zooming and adjusting plot settings, which can give a better insight into the results than the presented figures.
 \begin{landscape}
 \begin{figure}
+\begin{center}
 \includegraphics[height=6.5in]{Plots/journal_plot_normal}
+\end{center}
 \caption{Journal plot grouped by publisher}\label{figure:journalPlotNormal}
@@
 \begin{figure}
+\begin{center}
 \includegraphics[height=6.5in]{Plots/journal_plot_grouped}
+\end{center}
 \caption{Journal plot grouped k-means grouped}\label{figure:journalPlotGroups}

### 2018-06-25 Thesis/Parts/Abstract/Abstract.tex
thesis, version 1.0

@@
 Giving promising results, the word embeddings have been studied and improved over recent years.
-However, these studies have been focused on, or in combination with, generic texts, which are not limited the characteristics of in-domain texts, such as rare domain specific words.
+However, these studies have been focused generic texts, which are not limited the characteristics of in-domain texts such as rare domain specific words, or have focussed on small sets academic texts.
 This research focusses on the usefulness of word embeddings on domain specific texts, concerning 1.391.543 scientific articles which have been published in 2017.

### 2018-06-26 Thesis/Parts/Research_results/Research_results.tex
url update

@@
 \subheader{Journal relatedness plot}
-Figure~\ref{figure:journalPlotNormal} is the two dimensional plot of the journal embeddings.
+We created two seperate journal plot, figures~\ref{figure:titlePlotNormal} \&~\ref{figure:titlePlotGrouped} show the title based embeddings, and figures~\ref{figure:abstractPlotNormal} \&~\ref{figure:abstractPlotGrouped} show the abstract based embeddings.
+Figures~\ref{figure:titlePlotNormal} \&~\ref{figure:abstractPlotNormal} are the two dimensional plot of the journal embeddings.
 The journals are color-marked by publisher.
 Red is Wiley, lime is Elsevier and blue is Springer Nature.
-The grey points are other or not-specified.
-Figure~\ref{figure:journalPlotGroups} shows the journals, grouped by a k-means algorithm, creating 8 groups.
+The grey points are other or not-specified publishers.
+Figures~\ref{figure:titlePlotGrouped} \&~\ref{figure:abstractPlotGrouped} show the journals, grouped by a k-means algorithm, creating 8 groups.
 The bottom right shows the names of the journals closest to the center of the group.
 While most names state the topic of the research field, some do not.
-These are  \textit{SAGE Open}: social and behavioural sciences and humanities, \textit{RSC Advances}: chemical sciences, and \textit{Orvosi hetilap}: experimental and clinical medicine.
+These are \textit{RSC Advances}: chemical sciences, and \textit{Symmetry}:  research on symmetry phenomena wherever they occur in mathematical or scientific studies.
 The k-means algorithm ran on the 300-dimensional set, while the plot shows the 2-dimensional set.
-A digital version of this plot can be found at:~\url{https://goo.gl/tdHGnD}.
+A digital version of this plot can be found at:~\url{https://goo.gl/nCGMcu} (title-based) and~\url{https://goo.gl/LwYP6k}.
 The usage of this digital version is advised, since this interactive plot enables zooming and adjusting plot settings, which can give a better insight into the results than the presented figures.
@@
 \begin{center}
-\includegraphics[height=6.5in]{Plots/journal_plot_normal}
+\includegraphics[height=6.5in]{Plots/Journal_Plots/Title_normal}
 \end{center}
-\caption{Journal plot grouped by publisher}\label{figure:journalPlotNormal}
+\caption{Journal plot grouped k-means grouped}\label{figure:titlePlotNormal}
 \end{figure}
@@
 \begin{center}
-\includegraphics[height=6.5in]{Plots/journal_plot_grouped}
+\includegraphics[height=6.5in]{Plots/Journal_Plots/Abstract_normal}
 \end{center}
-\caption{Journal plot grouped k-means grouped}\label{figure:journalPlotGroups}
+\caption{Journal plot grouped by publisher}\label{figure:abstractPlotNormal}
+\end{figure}
+\end{landscape}
+
+\begin{landscape}
+\begin{figure}
+\begin{center}
+\includegraphics[height=6.5in]{Plots/Journal_Plots/Title_grouped}
+\end{center}
+\caption{Journal plot grouped k-means grouped}\label{figure:titlePlotGrouped}
+\end{figure}
+\end{landscape}
+
+\begin{landscape}
+\begin{figure}
+\begin{center}
+\includegraphics[height=6.5in]{Plots/Journal_Plots/Abstract_grouped}
+\end{center}
+\caption{Journal plot grouped k-means grouped}\label{figure:abstractPlotGrouped}
 \end{figure}

### 2018-06-26 Thesis/Parts/Discussion/Discussion.tex
Updated ev/mv

@@
 \subsubheader{Journal plots}
-Figure~\ref{figure:journalPlotNormal} show the journals in the, what we will refer to as "subject spectrum".
+Figures~\ref{figure:titlePlotNormal} \&~\ref{figure:abstractPlotNormal} show the journals in the, what we will refer to as "subject spectrum".
 We do this because the journal embeddings capture journal-relatedness, which leads to the clustering of related articles, which share, in varying degree, the common subject.
@@
 We can further see that Nature is far to the center, as we would expect a generic journal to be, but it is on the biology/medicine side of the center (indicated by the position of Cell and Pharmaceutical Research).\\
-Figure~\ref{figure:journalPlotGroups} shows the journals, grouped with k-means on the original 300-dimensional embedding vector.
+Figures~\ref{figure:titlePlotGrouped} \&~\ref{figure:abstractPlotGrouped} show the journals, grouped with k-means on the original 300-dimensional embedding vector.
 In the plot we can see that the original embedding-clustering, as provided by the k-means algorithm, is relatively well preserved, most groups stay clustered together.
-The journals in the center of the plot belong mainly to mixed groups, which is caused by the separation of the medicine field into two groups, with as center journals \textit{Orvosi hetilap} and \textit{Journal of Clinical and Diagnostic Research}.\\
-The interactive version shows that the clusterings, as seen on both figure~\ref{figure:journalPlotNormal} \&~\ref{figure:journalPlotGroups} are subject based.
+The interactive version shows that the clusterings, as seen on all four figures, are subject based.
 Journals concerning the same subjects are correctly clustered together, and the journals in between topic clusters are also positioned at logical positions.
 It furthermore shows that the k-means groupings create an insight in research fields, although it is limited by the amount of groups the k-means algorithm creates.
-This problem is already visible in figure~\ref{figure:journalPlotGroups} where, as discussed earlier, the k-means algorithm divided one field into multiple groups.
-We found that our findings on the 2-dimensional representation of embeddings are similar to those of \citet{dai2015document}, who plotted 4.4 million Wikipedia articles.
-The mayor difference between our plot and their plot is that they focus on just a view subjects in an entire plot, and have access to (human made) partitioning data.
+Our findings on the 2-dimensional representation of embeddings are similar to those of \citet{dai2015document}, who plotted 4.4 million Wikipedia articles.
+The major difference between our plot and their plot is that they focus on just a view subjects in an entire plot, and have access to (human made) partitioning data.
 They have therefore a more reliable grouping metric.

### 2018-06-26 Thesis/Parts/Research_results/Research_results.tex
Updated ev/mv

--- 2018-06-21 Thesis/Parts/Research_results/Research_results.tex
@@
 \subheader{Journal relatedness plot}
-Figure~\ref{figure:journalPlotNormal} is the two dimensional plot of the journal embeddings.
+We created two seperate journal plot, figures~\ref{figure:titlePlotNormal} \&~\ref{figure:titlePlotGrouped} show the title based embeddings, and figures~\ref{figure:abstractPlotNormal} \&~\ref{figure:abstractPlotGrouped} show the abstract based embeddings.
+Figures~\ref{figure:titlePlotNormal} \&~\ref{figure:abstractPlotNormal} show the two dimensional plots of the journal embeddings.
 The journals are color-marked by publisher.
 Red is Wiley, lime is Elsevier and blue is Springer Nature.
-The grey points are other or not-specified.
-Figure~\ref{figure:journalPlotGroups} shows the journals, grouped by a k-means algorithm, creating 8 groups.
+The grey points are other or not-specified publishers.
+Figures~\ref{figure:titlePlotGrouped} \&~\ref{figure:abstractPlotGrouped} show the journal embeddings grouped by a k-means algorithm, creating 8 groups.
 The bottom right shows the names of the journals closest to the center of the group.
-The k-means algorithm ran on the 300-dimensional set, while the plot shows the 2-dimensional set.
+While most names state the topic of the research field, some do not.
+These are \textit{RSC Advances}: chemical sciences, and \textit{Symmetry}:  research on symmetry phenomena wherever they occur in mathematical or scientific studies.
+The k-means algorithm ran on the 300-dimensional vectors, while the plot shows the 2-dimensional vectors.
+In the title-based figures (\ref{figure:titlePlotNormal} \&~\ref{figure:titlePlotGrouped}) the journals \textit{PNAS} and \textit{Cell} overlap each others labels on the bottom right side of the graph.
+In the abstract-based figures (\ref{figure:abstractPlotNormal} \&~\ref{figure:abstractPlotGrouped}) the journals \textit{PNAS} and \textit{Nature} overlap each others label on the bottom right side of the graph.
+The digital versions of these plots can be found at:~\url{https://goo.gl/nCGMcu} (title-based) and~\url{https://goo.gl/LwYP6k}.
+The usage of this digital version is advised, since this interactive plot enables zooming and adjusting plot settings, which can give a broader insight into the results than the presented figures.
+Although the presented figures give sufficient for the purpose of this thesis.
 \begin{landscape}
 \begin{figure}
-\includegraphics[height=6.5in]{Plots/journal_plot_normal}
-\caption{Journal plot grouped by publisher}\label{figure:journalPlotNormal}
+\begin{center}
+\includegraphics[height=6.5in]{Plots/Journal_Plots/Title_normal}
+\end{center}
+\caption{Journal plot of title embeddings, grouped by publisher}\label{figure:titlePlotNormal}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[height=6.5in]{Plots/journal_plot_grouped}
-\caption{Journal plot grouped k-means grouped}\label{figure:journalPlotGroups}
+\begin{center}
+\includegraphics[height=6.5in]{Plots/Journal_Plots/Abstract_normal}
+\end{center}
+\caption{Journal plot of abstract embeddings, grouped by publisher}\label{figure:abstractPlotNormal}
+\end{figure}
+\end{landscape}
+
+\begin{landscape}
+\begin{figure}
+\begin{center}
+\includegraphics[height=6.5in]{Plots/Journal_Plots/Title_grouped}
+\end{center}
+\caption{Journal plot of title embeddings, k-means grouped}\label{figure:titlePlotGrouped}
+\end{figure}
+\end{landscape}
+
+\begin{landscape}
+\begin{figure}
+\begin{center}
+\includegraphics[height=6.5in]{Plots/Journal_Plots/Abstract_grouped}
+\end{center}
+\caption{Journal plot of abstract embeddings, k-means grouped}\label{figure:abstractPlotGrouped}
 \end{figure}

### 2018-06-26 Thesis/Parts/Future_work/Future_work.tex
Future work addition

@@
 In our research, TF-IDF performed better on the abstracts than on the titles, which, according to us, is caused by the text size of the two texts.
-This leads to the question, how do unique token count, token count and vocabulary size relate for TF-IDF?
-Is there a point in at which we can expect that TF-IDF will be able to rank items in the top-10?
-If this is the case, we can skip the TF-IDF calculations in certain situations, saving time and costs.
+This leads to the question, how do token count and unique token count relate for TF-IDF?
+Is there a point at which the TF-IDF outperforms the embeddings, and will continue to outperform?
+If this relation is found,  we could skip the TF-IDF calculations in certain situations, and skip the embedding training in other scenario's, saving time and costs.
 
@@
 Our findings on this topic are minimal, although we can say that we would not expect that the top-cutoff improves the performance, since a set with the top 5k words performed better than the 1k till 6k words set.
+
+\subheader{Collecting a set of terms}
+Our results show that, for larger texts, TF-IDF outperforms the embeddings.
+Given this, it would be logical to use TF-IDF for search tasks on sets with many tokens.
+However, the search term itself will contain a small amount of tokens, as our research showed, embeddings perform better in this situation.
+Future work could try to combine these findings, by collecting a large amount of words, resembling the meaning (captured by the embeddings), and transforming this into a large collection of words (mimicking word occurrence, captured by the TF-IDF).
+If this could be done effectively, the power of the TF-IDF method could be applied to smaller texts.
+This process could be seen as a translation from word-embedding space into TF-IDF space.
+Further more, it would be interesting to see which words would be selected, and if these words represent the given sentence as an "extracted version" which would still be interpretable by humans.
 \end{document}

### 2018-06-27 Thesis/Parts/Abstract/Abstract.tex
Spelling check

--- 2018-06-25 Thesis/Parts/Abstract/Abstract.tex
@@
 Over the last few years, word embeddings have taken a dominant position in the Information Retrieval domain.
-Many studies have been done concerning the quality of word embeddings on general texts, such as the Wikipedia corpus and comments on review websites.
+Many studies have been done concerning the quality and application of word embeddings on general texts, such as the Wikipedia corpus and comments on review websites.
 Giving promising results, the word embeddings have been studied and improved over recent years.
-However, these studies have been focused on, or in combination with, generic texts, which are not limited the characteristics of in-domain texts, such as rare domain specific words.
-This research focusses on the usefulness of word embeddings on domain specific texts, concerning 1.391.543 scientific articles which have been published in 2017.
+However, these studies have been focused on generic texts, which are not limited to the characteristics of in-domain texts such as rare domain-specific words or have been focussed on small sets of academic texts.
+This research focusses on the quality and application of word embeddings on domain-specific texts, concerning a large corpus of 1.391.543 scientific articles which have been published in 2017.
 \end{document}

### 2018-06-27 Thesis/Parts/Background/Background.tex
Spelling check

@@
 To be able to do this, the search engine must know which texts are related.
-This can be achieved with and without neural networks, a traditional technique which does not use a neural network is TF-IDF, shot for Term Frequency - Inverted Document Frequency.
+This can be achieved with, and without neural networks, a traditional technique which does not use a neural network is TF-IDF, shot for Term Frequency - Inverted Document Frequency.
 Techniques that use a neural network are newer, these are (among others) Word2Vec, Paragraph Vectors and GloVe.
@@
 \subheader{Neural Network}
-A complete in-depth background into neural networks is beyond the scope of this thesis, therefore we will only describe the simplified woking of a neural network, and its basic application in IR.
-Neural Networks are multi-layered computational software, based on vector and/or matrix calculations, which tries to map input values to output values.
+A complete in-depth background into neural networks is beyond the scope of this thesis, therefore we will only describe the simplified working of a neural network and its basic application in IR.
+Neural Networks are multi-layered computational software, based on matrix calculations, which tries to map input values to output values.
 This mapping uses a pre-defined amount of layers that modify the values through matrix calculations.
-Neural networks rely on training to create optimal values for these layers, these values are only changed at training time, high quality training data is therefore essential for neural networks.
+Neural networks rely on training to create optimal values for these layers.
+The values in the layers are only changed at training time; high-quality training data is therefore essential for neural networks.
 Neural networks can be applied to many different tasks, as long as there is sufficient training data available.
-This training is the process of iteratively adjusting multiplication matrices or vectors to achieve the optimal result.
-Which is the result that is as close as possible to the given output for all input and output sets.\\To create word embeddings, Neural Networks are used to either predict words that may occur around a given word, or predict a word given words that surround it.
+The training is the process of iteratively adjusting multiplication matrices or vectors to achieve the optimal result.
+Which is the result that is as close as possible to the given output for all input and output sets.\\Neural Networks are used, in the creation of word embeddings, to either predict words that may occur around a given word or predict a word given words that surround it.
 For example, given the sentence\\
@@
 Neural networks are also used for other tasks such as video recommendation on Google's YouTube, as described by \citet{covington2016deep}.
-%The basic theory of word embedding can be explained by the following quote of J.R. Firth: "You shall know a word by the company it keeps". 
+
 \subheader{Embedding}
-An embedding is a distributed, numerical representation of a text in a vector space\footnote{The vector spaces of separately trained word embeddings differ, since each run the initial values of the neural network are randomly initialized.
-This means that the same word trained in two seperate runs do not have to have the same embedding.
+An embedding is a distributed, numerical representation of text in a vector space\footnote{The vector spaces of separately trained word embeddings differ, since each run the initial values of the neural network are randomly initialized.
+This means that the same word trained in two separate runs do not have to have the same embedding.
 However, they will have the same relationship to other words trained in their respective runs.} which can capture both the semantic and syntactic information\cite{mikolov2013distributed}.
 In the case of a word embedding, the embedding represents the word.
-These embeddings are created using by machine learning models.
-These models create the embeddings without the need for human interaction~\cite{lai2016generate}, they are so called \textit{unsupervised learning algorithms}.
+These embeddings are created using machine learning models, which create the embeddings without the need for human interaction~\cite{lai2016generate}, they are so-called \textit{unsupervised learning algorithms}.
 Once trained, the embeddings can be used to construct embeddings for collections of texts.
-For example, a word embedding can be used to create a sentence, paragraph, document or corpus embedding.
-The usage of word embeddings have improved various Natural Language Processing areas such as named entity recognition, part-of-speech tagging, parsing, and semantic role labelling~\citet{luong2013better}.
+For example, a word embedding can be used to create a sentence, paragraph, document or corpus embeddings.
+The usage of word embeddings has improved various Natural Language Processing areas such as named entity recognition, part-of-speech tagging, parsing, and semantic role labelling~\citet{luong2013better}.
 
 \subheader{Text analysis techniques}
-To enable a computer to process text, for embedding creation or for other tasks, the text has to be processed by an algorithm.
-In this research we used embeddings created by Word2Vec and TF-IDF feature vectors.
+To enable a computer to process text, for embedding creation or other tasks, the text has to be processed by an algorithm.
+In this research, we used embeddings created by Word2Vec and TF-IDF feature vectors.
 \begin{jumpin}
 \subsubheader{Word2Vec}
-Word2vec word embeddings are created using neural network, Word2vec learns word embeddings via maximizing the log conditional probability of the word given the context word(s) occurring within a fixed-sized window.
-Therefore the learnt embeddings contain useful knowledge about word co-occurrence\cite{nalisnick2016improving}.
+Word2vec word embeddings are created using a neural network, Word2vec learns word embeddings via maximizing the log conditional probability of the word given the context word(s) occurring within a fixed-sized window.
+Therefore the learned embeddings contain useful knowledge about word co-occurrence\cite{nalisnick2016improving}.
 There are multiple input/output possibilities for the neural network, best known are Skip-gram and the Continuous Bag-of-Words model (CBOW).
@@
 \subsubheader{Paragraph vectors}
-Variations on the word2vec model have also been proposed,~\citet{le2014distributed} introduced the paragraph vector based in their paper "Distributed representations of sentences and documents".
+Variations on the word2vec model have also been proposed,~\citet{le2014distributed} introduced the paragraph vector in their paper "Distributed representations of sentences and documents".
 The Paragraph Vector framework is based on the word vectors framework.
-The difference between the frameworks is the calculation of the probability, the Paragraph Vector framework uses an matrix, which consists of every paragraph.
+The difference between the frameworks is the calculation of the probability, the Paragraph Vector framework uses a matrix, which consists of every paragraph.
 This matrix is used to replace a concatenation or average of word vectors.
-An advantage of the paragraph vector model is that it takes the word order into consideration, atleast in a small context \cite{le2014distributed}.
-\citet{dai2015document} state that the Paragraph Vectors model performs significantly better than other models on grouping, triplet finding and related object/article finding tasks on Wikipeida and arXiv texts.
+An advantage of the paragraph vector model is that it takes the word order into consideration, at least in a small context \cite{le2014distributed}.
+\citet{dai2015document} state that the Paragraph Vectors model performs significantly better than other models on grouping, triplet finding and related object/article finding tasks on Wikipedia and arXiv texts.
 
 \subsubheader{GloVe}
-\citet{pennington2014glove} introduced the GloVe (Global Vectors) model.
+\citet{pennington2014glove} introduced the Global Vectors (GloVe) model.
 This model captures the global corpus statistics.
 The model transforms the word co-occurrences of all words in the corpus to chances, it excludes all the zero values and uses that as initial input for the neural network.
-This model out performs other models on three specific tasks, word analogy, word similarity and entity recognition according to the findings by \citet{pennington2014glove}.\\
+This model out-performs other models on word analogy, word similarity and entity recognition according to the findings by~\citet{pennington2014glove}.\\
 
@@
 The feature vectors produced by TF-IDF do not capture syntactic or semantic information about words, but capture information about word occurrences.
-These features are created by supplying the algorithm with the text it needs to "know".
-This text is then analysed on word occurrences on corpus and document and level, this results in a score per-word.
-This score can be converted to a feature vector, in which the indexes of these vector represent the words and the value is the TF-IDF score.
+The text, provided to the algorithm, is analyzed on word occurrences on corpus and document level, this results in a score per word.
+This score can be converted to a feature vector, in which the indexes of this vector represent the words and the value is the TF-IDF score.
 The size of this feature vector can optionally be controlled by hashing the words in the text, which can then be reduced to a given size.
-If this is not applied, the size of the feature vector is equal to the amount of unique words in the corpus, also known as the (corpus) vocabulary.
-Some applications of this technique limit the amount of unique words in the text supplied to the TF-IDF algorithm, they do this by taking only a certain amount of top words, ordered on their occurrence.
+If this is not applied, the size of the feature vector is equal to the number of unique words in the corpus, also known as the (corpus) vocabulary.
+Some applications of this technique limit the number of unique words in the text supplied to the TF-IDF algorithm, they do this by taking only a certain amount of top words, ordered on their occurrence.
 This reduces the amount of storage needed when hashing is not applied.
-It furthermore reduces the amount of words which occur rarely.
-Due to the nature of TF-IDF these rare words have a high score, cancelling out other more frequent words, while rarely occurring in the corpus.
+It furthermore reduces the number of words which occur rarely.
+Due to the nature of TF-IDF, these rare words have a high score, canceling out other more frequent words, while rarely occurring in the corpus.
+\end{jumpin}
 
-\end{jumpin}
 As \citet{lai2016generate} state in their paper "How to generate a good word embedding?", that all embedding methods rely on the same hypothesis, \textit{words that occur in similar contexts have similar meanings}.
-They furthermore found that larger corpus' lead to better quality embeddings, but that the domain in which the embeddings are trained is dominant over the corpus size.
+They furthermore found that larger corpus' lead to better quality embeddings, but that the domain in which the embeddings are trained has more influence on this than the corpus size.
 
 \subheader{Validation methods}
-The results produced by the techniques have to be validated to determine their quality (in usage).
-The quality of the results can be validated through, among others the F1 score\footnote{The F1 score combines the precision score and the recall score in a single metric} and, for classification tasks, the rank of the correct class, which is for this research a journal.
-The embeddings can furthermore be validated through their performance on tasks such as word analogies, word similarities, categorization and position visualization.
-These tasks can be designed to produce a score that gives an indication of the performance on a specific task.
+The results produced by the previously mentioned techniques have to be validated to determine their quality (in usage).
+The quality of the results can be validated through, among others the F1 score\footnote{The F1 score combines the precision score and the recall score in a single metric} and, for classification tasks, the rank of the correct class, which is in this research a journal.
+The embeddings can furthermore be validated through their performance on tasks such as word analogy, word similarity, categorization and embedding visualization.
+These tasks can be designed to produce a score that indicates the performance on a specific task.
 \citet{schnabel2015evaluation} found that a single validation metric cannot produce a representative result for other tasks.
 Embeddings that perform well on one task do not have to perform well on another task.
-As a result, the findings about performance of an embedding method are limited to the task on which they are tested, their results cannot be generalized to state that the embedding are overall "performing well".
-Validation tasks use either labelled or unlabelled data.
-Labelled data is data that is in some way marked, so that the correct answer can be derived from it, while this is not possible with unlabelled data.
-Labelled data enables the usage of unsupervised learning models, since  \textit{a system or model which is not involved in the actual learning} can automatically validate the given results and use it as feedback for the next learning iteration.
-Unlabelled data on the other hand requires human interaction to give a score for the produced result.
-The validation tasks can also be divided into two groups, extrinsic evaluation, ones that use word embeddings as input for a downstream task.
-And Intrinsic evaluation, which directly test the relationships of the word embedding themselves.
-\citet{schnabel2015evaluation} note that the extrinsic evaluation may not be consistent with intrinsic evaluations, since the performance on downstream tasks is not consistent across tasks.
+As a result, findings about the performance of an embedding method are limited to the task on which they are tested.
+Their results cannot be generalized to state that the embeddings are overall "performing well".
+Validation tasks use either labeled or unlabeled data.
+Labeled data is data that is in some way marked so that the correct answer can be derived from it, while this is not possible with unlabelled data.
+Labeled data enables the use of unsupervised learning models since  \textit{a system or model which is not involved in the actual learning} can automatically validate the given results and use it as feedback for the next learning iteration.
+Unlabelled data, on the other hand, requires human interaction to give a score for the produced result.
+The validation tasks can also be divided into two groups, extrinsic evaluation, ones that use word embeddings as input for a downstream task and Intrinsic evaluation, which directly tests the relationships of the word embedding themselves.
+\citet{schnabel2015evaluation} note that the extrinsic evaluation may not be consistent with intrinsic evaluations since the performance on downstream tasks is not consistent across tasks.
 
@@
 \subsubheader{Word Analogy}
-Word analogy validation is based on a labelled validation set, containing, commonly, word pairs of four, that can be logically divided into two parts.
+Word analogy validation is based on a labelled validation set, containing word pairs of four that can be logically divided into two parts.
 As Table~\ref{table:wordAnalogies} shows, each last word can be derived from the three words before.
@@
 \begin{displayquote}
-	X\textsubscript{Man} - X\textsubscript{King} $\approx$  X\textsubscript{Women} - X\textsubscript{Queen}
+    X\textsubscript{King} - X\textsubscript{Man} $\approx$  X\textsubscript{Queen} - X\textsubscript{Women}
 \end{displayquote}
-This means that the resulting vector of embedding of "Man" minus the embedding of "King" is approximately the embedding of "Woman" minus the embedding of "Queen".
-This resulting vector may, for example, be close to the vector representing "monarch".
+This means that the resulting vector of embedding of "King" minus the embedding of "Men" is approximately the embedding of "Queen" minus the embedding of "Women".
+This resulting vector may, for example, be close to the vector representing "Monarch".
 \subsubheader{Word Similarity}
@@
 For these test, the distance between the word embeddings (vectors) is measured and compared to similarity scores defined by humans.
-Multiple non domain specific validation sets are publicly available including: the Rare-word dataset introduced in the paper "Better Word Representations with Recursive Neural Networks for Morphology" by \citet{luong2013better},
+Multiple non-domain specific validation sets are publicly available including the Rare-word dataset introduced in the paper "Better Word Representations with Recursive Neural Networks for Morphology" by \citet{luong2013better},
 the MEN test collection by \citet{EBruniMENCollection} and the WordSimilarity-353 test collection by \citet{EGabrilovichWScollection}.
-These sets, among others, have been used in multiple studies of word embeddings\cite{pennington2014glove, mikolov2013efficient}. This validation metric also relies on labelled data.
+These sets, among others, have been used in multiple studies of word embeddings\cite{pennington2014glove, mikolov2013efficient}.
+This validation method is limited by the availability of word similarity sets that share the same domain as the trained embeddings.
 \subsubheader{Classification}
@@
 In their setup, the text was a pair of texts, and their categories were duplicate and non-duplicate.
-\citet{le2014distributed} used for their research a dataset of IMDB with 100,000 movie review.
+\citet{le2014distributed} used for their research a dataset of IMDB with 100,000 movie reviews.
 They validated their proposed paragraph vector model by determining whether a review was positive or negative.
 \subsubheader{Position Visualization}
-\citet{dai2015document} and \citet{hinton2003stochastic} mapped their word embeddings from a high dimensional vector to a two dimensional vector to be able to display them in a scatter plot and applied colors to various categories.
-These categories can be created with labelled or unlabelled data.
-The advantage of this is that a human can directly see the word distributions, and see if it is distributed in a way that seems logical.
-It gives furthermore insight in the overall spectrum of the words.
-However, this representation does not give a score, since it is not a evaluation of the data, but an alternative representation.
+\citet{dai2015document} and \citet{hinton2003stochastic} mapped their word embeddings from a high dimensional vector to a two-dimensional vector to be able to display them in a scatter plot and applied colors to various categories.
+The advantage of this visualization is that a human can directly see the embedding distribution, and see if it is distributed in a way that seems logical.
+It gives furthermore insight in the overall spectrum of the embedding.
+However, this representation does not give an empirical score, since it is not an evaluation of the data, but an alternative representation.
 \end{jumpin}
@@
 All meaning embedded in the word embedding is derived from the original text.
-Because of this, embeddings can be "Domain specific" meaning that it only knows words (or a specific word) in a certain context.
+Because of this, embeddings can be "Domain-specific" meaning that it only knows words (or a specific word) in a certain context.
 This becomes most clear when faced with words that can have different meanings in different contexts.
-For this research we categorize the embedding in two categories, general embeddings and domain specific embeddings.
-The general embeddings are trained on a collection of texts that use common English and contains a wide variety of topics.
-The domain specific embeddings are trained on a collection of texts that uses uncommon English (i.e.
-domain specific terms) and/or is limited to a small amount of topics.
+For this research, we categorize the embeddings into two categories, generic embeddings and domain-specific embeddings.
+The generic embeddings are trained on a collection of texts that use common English and contains a wide variety of topics.
+The domain-specific embeddings are trained on a collection of texts that uses uncommon English (i.e., domain-specific terms) or is limited to a small number of topics.
 Given these terms, we regard the embeddings trained on the Wikipedia corpus\cite{lai2016generate, pennington2014glove, dai2015document, lau2016empirical, schnabel2015evaluation} as general, since Wikipedia uses common English and spans a wide range of topics.
-On the other hand we regard the embeddings created by \citet{Truong2017Thesis} as Domain specific, these embeddings were created on academic articles, which use domain-specific terms and notations and only consists of academic texts, which contains less general/generic words compared to the Wikipedia corpus.
-The domain specific texts can use the same word for unrelated topics, like clouds in computer science and meteorology.
+On the other hand, we regard the embeddings created by \citet{Truong2017Thesis} as Domain specific; these embeddings were created on academic articles, which use domain-specific terms and notations and only consists of academic texts, which contains less general/generic words compared to the Wikipedia corpus.
 \subheader{Research environment}
 The research will be done in a python-databricks environment, which uses spark, a library that offers tools to work with big-data.
-\citet{armbrust2015spark} state that Spark SQL lest programmers leverage the benefits of relational processing and lets SQL users call complex analytix libraries in Spark.
-This allows for much tighter intergration between relational and procedural processing.
-The paper further states that Spark SQL makes it significanly simpler and more efficient to write data piplines that mix relational and procedural processing, while offering substantial speedups over previous SQL-on-Spark engines.
+\citet{armbrust2015spark} state that Spark SQL lets programmers leverage the benefits of relational processing and lets SQL users call complex analytic libraries in Spark.
+This allows for much tighter integration between relational and procedural processing.
+The paper further states that Spark SQL makes it significantly simpler and more efficient to write data pipelines that mix relational and procedural processing while offering substantial speedups over previous SQL-on-Spark engines.
 \subheader{Text properties}
-\citet{wiegand2018word} state that the pareto distribution offers a good fit to the word occurrences in natural language.
-Their models show that, due to the additional parameters in the pareto-III, the tail of the data fits better to the model than the Zipf model.
-This shows the relation between the word occurrences rank, and the actual occurrences.
+\citet{wiegand2018word} state that the Pareto distribution offers a good fit to the word occurrences in natural language.
+Their models show that, due to the additional parameters in the Pareto-III, the tail of the data fits better with the model than the Zipf model.
+This shows the relation between the word occurrences rank and the actual occurrences.
 This kind of word-occurrences distribution holds for many texts, including the writings of William Shakespeare and scientific texts and novels\cite{thurner2015understanding}.

### 2018-06-27 Thesis/Parts/Data/Data.tex
discussion & presentation
minor changes
Spelling check

@@
 \item{Removed punctuation}
-\item{Removed all non-ascii characters}
+\item{Removed all non-ASCII characters}
 \item{Transformed all characters to lower-case}
@@
 \subheader{Embedding}
-For this research we reused the word embeddings created by \citet{Truong2017Thesis}.
+For this research, we reused the word embeddings created by \citet{Truong2017Thesis}.
 These embeddings have a vector size of 300, which is an industry default.
 They have been trained on the entire Elsevier corpus, not limited to the subset we used for this research.
-To construct article embeddings we take the average of all normalized word embeddings for that article.
-Journal embeddings are constructed in the same way, we averaged all the normalized article embeddings to create the journal embeddings.
+To create article embeddings, we take the average of all normalized word embeddings for that article.
+Journal embeddings are created in the same way.
+We averaged all the normalized article embeddings to create the journal embeddings.
 We have used multiple embedding configurations for this research
 \subsubheader{Default embedding}
-The default embedding is created form the pre-trained word embeddings, no modifications have been applied to this set.
+The default embedding is created form the pre-trained word embeddings; no modifications have been applied to this set.
 \subsubheader{TF-IDF embedding}
@@
 \subsubheader{10K TF-IDF embedding}
-The 10K embedding set is generated similarity to the TF-IDF embedding, this version only uses the 10.000 most common tokens, reducing the amount of tokens it uses.
-This set was created to see if the limitation to 10.000 tokens reduces the amount of noise, and with that increasing the performance.
+The 10K embedding set is generated similarity to the TF-IDF embedding, this version only uses the 10.000 most common tokens, reducing the number of tokens it uses.
+This set was created to see if the limitation to 10.000 tokens reduces the amount of noise, increasing the performance.
 \subsubheader{5K TF-IDF embedding}
-The 5K TF-IDF embedding is the TF-IDF embedding set, limited to the 5.000 most common words. This set was created to more aggressively limit the amount of tokens, and with that, cancel out more noise.
+The 5K TF-IDF embedding is the TF-IDF embedding set, limited to the 5.000 most common words. This set was created to limit the number of tokens more aggressively, and with that, cancel out more noise.
 \subsubheader{1K-6K TF-IDF embedding}
 The 1K-6K TF-IDF embedding is the TF-IDF embedding limited to the top 6.000 most common words, without the top 1.000 most common words.
-The rationale for this is that common words will occur in many articles, creating noise, by cutting of the top 1.000 and cutting of everything below 6.000 we tried to reduce the noise by filtering common words.
+The rationale for this is that common words will occur in many articles, creating noise, by cutting off the top 1.000 and cutting off everything below 6.000 we tried to reduce the noise by filtering common words.
 This cut results in a set of 5.000 tokens, which allows us to compare it to the 5K TF-IDF set.
@@
 \subheader{TF-IDF}
-To create the TF-IDF feature vectors, we used the TF-IDF model and a hasher from pysparks the MlLib library.
+To create the TF-IDF feature vectors, we used the TF-IDF model and a hasher from PySparks MlLib library.
 The TF-IDF feature vectors are created by hashing the tokens with the hasher, which has a set hash bucket size.
-These hashed values are passed on to the TF-IDF model, resulting in a feature vector which vector dimensions equals the amount of hash buckets.
+These hashed values are passed on to the TF-IDF model, resulting in a feature vector which vector dimensions equal the number of hash buckets.
 To limit the computational and storage expenses and to reduce noise by rare words, we limit our vocabulary size.
-We denote the TF-IDF configurations as follows: $vocabulary size/hashbucket size$. Furthermore, we denote 1.000 as 1K, since we deal with chosen values which can be exactly noted given this notation.
+We denote the TF-IDF configurations as follows: $vocabulary size/hash bucket number$.
+Furthermore, we denote 1.000 as 1K, since we deal with chosen values which can be exactly noted given this notation.
 \begin{figure}
@@
 \subheader{Create training and validation set}
-We split our initial set  $80\%$ - $20\%$,.
+We split our initial set  $80\%$ - $20\%$.
 We use the $80\%$ set as the training set for the journal representations, and the $20\%$ set as the validation set for the journal representations.
@@
 \subsubheader{Median \& average rank}
-We use the median rank to indicate around which rank the 'standard' article would be ranked, based on its title or abstract.
+We use the median rank to indicate at which rank the 'standard' article would be ranked, based on its title or abstract.
 We do this by taking the median of the respective rank from each article.
-This gives us an indication of the behaviour of most articles in our validation set.
+This gives us an indication of the behaviour of the articles in our validation set.
 This median rank (mostly) ignores the outliers, we therefore also use the average rank, which gives a more global indication, although this rank may be over-influenced by some outliers.
@@
 
-\header{Two dimensional plot}
+\header{ Two-dimensional plot}
 To create a plot, we transformed the 300-dimensional journal vectors into 2-dimensional vectors using TSNE based on pca\footnote{Principal component analysis}.
 These 2-dimensional vectors, representing the x \& y coordinate, can then be drawn in a plot.
-To visualize the preservation of journal-relatedness while converting the 300 dimensions to 2 dimension, we create groupings using k-means.
-These groupings are created on the 300-dimensional vectors, and are visualized in the plot using colors.
+To visualize the preservation of journal-relatedness while converting the 300 dimensions to 2 dimensions, we create groupings using k-means.
+These groupings are created on the 300-dimensional vectors and are visualized in the plot using colors.
+We use the k-means groupings due to the lack of subject-based grouping values in our dataset.
 \end{document}
-
-% RAW DATA:
-% 1,391,543 articles
-% 14 811 433 title tokens			230805 unique		18.822.399			939.665
-% 172 150 921 abstract tokens		738961 unique		264.653.020			5.853.077
-% 186 962 354 total tokens			763475 unique		283.475.419			6.209.769
-% 3,759 journals
-
-% split = 79.9509609117 - 20.0490390883
-
-% training numbers
-% 10K = percentage?}

### 2018-06-27 Thesis/Parts/Future_work/Future_work.tex
Spelling check

@@
 This research focussed on the quality of word embeddings on academic texts.
-To do this we used both a comparison to TF-IDF and a visualization of the word embeddings.
-Future works may seek to further improve the quality of the word embeddings.
+To do this, we used both a comparison to TF-IDF and a visualization of the word embeddings.
+Future works may seek to improve the quality of the embeddings further or determine the limit of the capabilities of the embedding technique.
 
 \subheader{Method differences}
-\citet{levy2015improving} observed that there were no major differences between the various embedding creation methods.
-They state that the difference in performance is mainly caused by the global/hyper parameters.
-In this research, we have not looked at comparison between various models and/or (hyper) parameters.
-We instead used a standard configuration, to focus more on the actual performance of the embeddings, instead of the best-possible performance.
+\citet{levy2015improving} observed that there were no significant differences between the various embedding creation methods.
+They state that the global/hyperparameters mainly cause the difference in performance.
+In this research, we have not looked at the comparison between various models and (hyper) parameters.
+We instead used a standard configuration, to focus more on the actual performance of the embeddings, instead of the best possible performance.
 Future work could seek to validate the results of \citet{levy2015improving} by expanding our research with multiple metrics.
@@
 base their conclusions on word similarity and word analogy tasks, and not on categorization.
-This is the reason why we did not take this research into account in our discussion, since their experiments are not comparable to ours.
+This is the reason why we did not take this research into account in our discussion since their experiments are not comparable to ours.
 
@@
 An interesting improvement to enhance the word embeddings with could be a smarter way to remove noise, based on word embeddings.
-This might be achieved by analysing the word embedding spectrum before normalization, and to then cut the center of the vector space out.
-This must be applied before normalization, since normalization causes all embeddings to have a distance of 1 to the center point.
+This might be achieved by analyzing the word embedding spectrum before normalization, and to then cut the center of the vector space out.
+This must be applied before normalization since normalization causes all embeddings to have a distance of 1 to the center point.
 All words which are generic are in the center of the spectrum.
@@
 This should be possible since title and abstract per article share a common topic.
-We would expect that the common text would have the quality of the abstract, which is according to our findings the part that is best usable for the embeddings and TF-IDF.
+We would expect that the common text would have the quality of the abstract, which is according to our findings the part that is best used for the embeddings and TF-IDF.
 
@@
 \subheader{Reversed word pairs}
-At this point in time, there are no domain specific word pair sets available.
+At this point, there are no domain-specific word pair sets available.
 However, as we demonstrated, we can still test the quality of word embeddings.
@@
 \subheader{Historical overview}
-We have shown that the word embeddings can be used to create a subject spectrum, in which we plotted all the articles of one year.
+We have shown that the word embeddings can be used to create a subject spectrum, in which we plotted all the articles for one year.
 This gives insight into the currently popular research field, indicated by dense areas on the plot.
@@
 \subheader{TF-IDF top-cutoff}
-In our research we used a dataset from which we removed the top 1k words, together with everything beyond 6k.
-This dataset did not perform well in our research, future work could look into this by validating if the top-words cut-off decreases the TF-IDF performance.
-Our findings on this topic are minimal, although we can say that we would not expect that the top-cutoff improves the performance, since a set with the top 5k words performed better than the 1k till 6k words set.
+In our research, we used a dataset from which we removed the top 1k words, together with everything beyond 6k.
+This dataset did not perform well in our research; future work could look into this by validating if the top-words cut-off decreases the TF-IDF performance.
+Our findings on this topic are minimal, although we can say that we would not expect that the top-cutoff improves the performance since a set with the top 5k words performed better than the 1k till 6k words set.
 
@@
 Given this, it would be logical to use TF-IDF for search tasks on sets with many tokens.
-However, the search term itself will contain a small amount of tokens, as our research showed, embeddings perform better in this situation.
-Future work could try to combine these findings, by collecting a large amount of words, resembling the meaning (captured by the embeddings), and transforming this into a large collection of words (mimicking word occurrence, captured by the TF-IDF).
+However, the search term itself will contain a small number of tokens, as our research showed, embeddings perform better in this situation.
+Future work could try to combine these findings, by collecting a large number of words, resembling the meaning (captured by the embeddings), and transforming this into a (large) collection of words (mimicking word occurrence, captured by the TF-IDF).
 If this could be done effectively, the power of the TF-IDF method could be applied to smaller texts.
 This process could be seen as a translation from word-embedding space into TF-IDF space.
-Further more, it would be interesting to see which words would be selected, and if these words represent the given sentence as an "extracted version" which would still be interpretable by humans.
+Furthermore, it would be interesting to see which words would be selected and if these words represent the given sentence as an "extracted version" which would still be interpretable by humans.
 \end{document}

### 2018-06-27 Thesis/Parts/Motivation/Motivation.tex
Spelling check

@@
 encountered a problem in the validation of these in-domain embeddings.
-The word embedding produced correct document clustering results, leading to the conclusion that these embeddings are of good quality, since they capture the document relatedness needed to create correct clusterings.
+The word embedding produced correct document clustering results, leading to the conclusion that these embeddings are of good quality since they capture the document relatedness needed to create correct clusterings.
 However unpublished results by Truong et al.
@@
 \citet{Truong2017Thesis} used multiple word similarity validations to asses the quality of the word embeddings.
-However, these set are created to validate the generic embeddings, they fail to asses the quality of the domain specific embeddings.
+However, these sets are created to validate the generic embeddings; they fail to asses the quality of the domain-specific embeddings.
 
 \subheader{Research}
-To asses the problem of the limited availability of pre-labelled validation sets for domain specific articles, we compare the embeddings to  TF-IDF on a categorization task.
-This A) gives an indication of the embedding quality for categorization tasks and B) contrasts the performance of embeddings to the performance of the more traditional TF-IDF approach.
+To asses the problem of the limited availability of pre-labeled validation sets for domain-specific articles, we compare the embeddings to  TF-IDF on a categorization task.
+This A) indicates the embedding quality for categorization tasks and B) contrasts the performance of embeddings to the performance of the more traditional TF-IDF approach.
 To ensure the quality of the embeddings for our research, we reuse the embeddings created in the research of \citet{Truong2017Thesis}.
@@
 1 focusses on the classification results of both embedding-based techniques and TF-IDF.
-To measure classification task we use the rank of the class to which the item belongs.
-Transforming the classification task from a binary metric to a ranking metric.
-For this task, we will use different versions of embeddings, to answer RQ 1.1, and different TF-IDF versions to not only compare the two techniques, but also look for the optimal results of both techniques.
+To measure classification task, we use the rank of the class to which the item belongs.
+This transforms the classification task from a binary metric to a ranking metric.
+For this task, we will use different versions of embeddings, to answer RQ 1.1, and different TF-IDF versions to not only compare the two techniques but also look for the optimal results of both techniques.
 To achieve the optimal results, we compare 20 distance metrics from the SciPy library on ranking performance on the standard embeddings.
@@
 \end{jumpin}
-By validating our invalidating  these hypotheses we get an indication of the performance of the embeddings compare to older techniques,  get insight into possible performance and resource trade-off's and get insight into the performance of different distance calculation metrics.
+By validating or invalidating these hypotheses, we get an indication of the performance of the embeddings compared to TF-IDF,  get insight into possible performance and resource trade-off's and get insight into the performance of different distance calculation metrics.
 RQ. 2 concerns the visualization of word embeddings and the accuracy of this visualization. To answer this research question, we will use the following hypothesis:
 \begin{jumpin}
-\textit{\textbf{H. 2} Word embeddings, combined with pca-based TSNE can preserve the journal relatedness on a two dimensional plot.}
+\textit{\textbf{H. 2} Word embeddings, combined with PCA-based TSNE can preserve the journal relatedness on a two-dimensional plot.}
 \end{jumpin}
-The validation of this hypothesis will rely on visual conformation.
+The validation of this hypothesis will rely on visual confirmation.
 We expect to see clustering of journals in certain areas, which indicates a research subject.

### 2018-06-28 Thesis/Parts/Conclusion/Conclusion.tex

@@
 The TF-IDF alternatives give better results than the embeddings based on abstracts.
-The performance of the embeddings have been improved by weighting them with the TF-IDF values on word level, although this improvement cannot be seen as significant on our dataset.
-This improved embedding set results in a median rank decrease of 8 on the titles and an median rank increase of 8 on the abstract, compared to the best performing TF-IDF alternative.
+The performance of the embeddings has been improved by weighting them with the TF-IDF values on the word level, although this improvement cannot be seen as significant on our dataset.
+This improved embedding set results in a median rank decrease of 8 on the titles and a median rank increase of 8 on the abstract, compared to the best performing TF-IDF alternative.
 The embedding also results in a memory decrease of 73.04\% compared to the best performing TF-IDF alternative, making it more viable to keep it in memory.
-The visualization of the journal embedding show that similar journals are grouped together, indicating a preservation of relatedness between the journal embeddings.
+The visualization of the journal embedding shows that similar journals are grouped together, indicating a preservation of relatedness between the journal embeddings.
 We thus come to the following conclusions:

### 2018-06-28 Thesis/Parts/Discussion/Discussion.tex
Future work addition

@@
 \header{Discussion}
-
 \subheader{Result analysis}
@@
 \subsubheader{Best performers}
-The data, as presented in figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank on abstract and 3 median ranks on title.
-For the embeddings the TF-IDF weighted embedding works better than the others, although it is has is not a significant improvement compared to the default embeddings, which 1 median rank higher on abstract, and equal on title.
+The data, as presented in figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank on abstract and 3 median ranks on the titles.
+For the embeddings, the TF-IDF weighted embedding works better than the others, although it is not a significant improvement compared to the default embeddings, which 1 median rank higher on the abstracts, and equal on the titles.
 
@@
 The TF-IDF feature vectors outperform the embeddings on the abstract, while the embeddings outperform the TF-IDF feature vectors on the title.
-The main difference between the abstract \& title is that the title contains less tokens (see table~\ref{table:corpusSize}), this means that the titles contain less information.
+The main difference between the abstract \& title is that the title contains fewer tokens compared to the abstract (see table~\ref{table:corpusSize}).
+This means that the titles contain less information than the abstracts.
 Due to this, the TF-IDF method, which is purely based on word-occurrences \& counts has less information on the titles.
@@
 The data furthermore shows that increasing the vocabulary size increases the performance of the TF-IDF, this means that none of the created cut-off's resulted in cutting off noise, the increasing size of the vocabulary only improved the performance in this case.
-It could be possible that at higher vocabulary sizes the cut-off would result in a sharper signal, we did not looked into this further due to our findings that the TF-IDF performance stagnates (presented in figure~\ref{figure:tfidfPerformance}).
+It could be possible that at higher vocabulary sizes the cut-off would result in a sharper signal, we did not look into this further due to our findings that the TF-IDF performance stagnates (presented in figure~\ref{figure:tfidfPerformance}).
 
-\subsubheader{Limited tfidf embeddings}
-The limited TF-IDF embeddings all under perform, compared to the non-limited TF-IDF embedding, on the median and average ranking.
+\subsubheader{Limited TF-IDF embeddings}
+The limited TF-IDF embeddings all underperform, compared to the non-limited TF-IDF embedding, on the median and average ranking.
 Indicating that the noise reduction is too much, and it removes meaningful words.
@@
 However, the rank lowers, indicating the reduction in embedding quality due to missing words.
-This is in line with what we found with the TF-IDF results, higher vocabulary sizes give better performance.
+This is in line with what we found with the TF-IDF results; higher vocabulary sizes give better performance.
 However, figures~\ref{figure:titleDistribution} \&~\ref{figure:abstractDistribution} show that their rank distribution is different from the other embeddings.
-Their pattern show a decent performance indicates the following pattern: a high/average performance on the top-rankings, an under performance on the middle rankings and  a resulting stack-up of articles with a high-ranking.
+Their pattern shows a decent performance indicates the following pattern: a high/average performance on the top-rankings, an underperformance on the middle rankings and a resulting stack-up of articles with a high-ranking.
 This is further supported by the TF-IDF score on titles (figure~\ref{figure:titleRanks}), on which the limited TF-IDF embeddings are the top performance.
-Indicating a better performance on the top-1 articles compared to the other sets.\\This leads us to believe that the cut-off was effective, but that is did not suit our purpose.
-The cut-off moved the "middle-ranked"  articles to either the high end of the rankings, or the lower end.
-Resulting in low median and average scores, but in (relatively) high accuracy scores.
+Indicating a better performance on the top-1 articles compared to the other sets.\\This leads us to believe that the cut-off was effective, but that it did not suit our purpose.
+The cut-off moved the "middle-ranked"  articles to either the higher end or the lower end of the rankings.
+Resulting in high median and average ranks, and in (relatively) high accuracy scores.
 The reduction in vocabulary size did not reduce the storage size for the embeddings, except for the 1K-6K embedding.
-This indicates that only the 1K-6K cut actually removes entire titles and/or abstracts, since all vectors are stored as dense-vectors\footnote{Dense vectors are bigger in memory, since they store all their values, including zeros.
-However they can be processed more efficiently during calculations}.
+This indicates that only the 1K-6K cut actually removes entire titles and abstracts, since all vectors are stored as dense-vectors\footnote{Dense vectors are bigger in memory, since they store all their values, including zeros.
+However, they can be processed more efficiently during calculations}.
 This results in a lower memory requirement.
@@
 Our hypothesis on the difference between the TF-IDF and the standard embedding is as follows:\\
-The embeddings seem to outperform the TF-IDF in situation when there is little information available, the titles in our case.
-This indicates that the embeddings store some kind of word meaning that enables them to perform relatively well on the titles.
-The abstracts on the other hand contain much more information.
+The embeddings seem to outperform the TF-IDF in situations when there is little information available, the titles in our case.
+This indicates that the embeddings store some word meaning that enables them to perform relatively well on the titles.
+The abstracts, on the other hand, contain much more information.
 Our data seems to indicate that the amount of information available in the abstracts enable the TF-IDF to cope with the lack of embedded information.
@@
 This can be seen in our data, only the average rank increased by 3, indicating that there is a difference between the two embeddings, but not a major one.
-We would also expect on the abstract an increase in performance, since the TF-IDF has more information in this context.
+We would also expect on the abstract an increase in performance since the TF-IDF has more information in this context.
 We would expect that the weighting applied by the TF-IDF improves the performance of the embedding by indicating word importance.
@@
 Journals concerning the same subjects are correctly clustered together, and the journals in between topic clusters are also positioned at logical positions.
-It furthermore shows that the k-means groupings create an insight in research fields, although it is limited by the amount of groups the k-means algorithm creates.
+It furthermore shows that the k-means groupings give insight in research fields, although it is limited by the number of groups the k-means algorithm creates.
 Our findings on the 2-dimensional representation of embeddings are similar to those of \citet{dai2015document}, who plotted 4.4 million Wikipedia articles.
-The major difference between our plot and their plot is that they focus on just a view subjects in an entire plot, and have access to (human made) partitioning data.
+The major difference between our plot and their plot is that they focus on just a view subjects in an entire plot, and have access to (human-made) partitioning data.
 They have therefore a more reliable grouping metric.
@@
 \subheader{Improvements}
-This research shows that, even tough the embeddings are able to capture and preserve relatedness, TF-IDF is able outperform the embeddings.
+This research shows that even tough the embeddings can capture and preserve relatedness, TF-IDF is able to outperform the embeddings.
 Earlier research already proposed improvements to the word embeddings.
-\citet{dai2015document} show that the usage of paragraph vectors improve the accuracy of word embeddings with 4.4\% on triplet creation with the wikipedia corpus, and a 3.9\% improvement on the same task based on the arXiv articles.
+\citet{dai2015document} show that the usage of paragraph vectors improve the accuracy of word embeddings with 4.4\% on triplet creation with the Wikipedia corpus and a 3.9\% improvement on the same task based on the arXiv articles.\\
 Furthermore, \citet{le2014distributed} show that the usage of paragraph vectors decrease the error rate (positive/negative) with 7.7\% compared to averaging the word embeddings on categorizing text as either positive or negative.
-While this looks promising, we have to keep in mind that our task differs from earlier tasks, since we do not categorize on 2 categories, but on more than 3k.
+While this looks promising, we have to keep in mind that our task differs from earlier tasks.
+We do not categorize on two categories but more than 3k.
 Still, we would expect an improvement by using paragraph vectors since the classification task if fundamentally the same, only on a much larger scale., which complicates the task due to the "grey areas"  between categories, which increases given more categories.
@@
 Their research specifically focused on categorizing documents, showed a 5.89\% increase of the micro-F1 score on LDE compared to CBOW, and a 9.11\% increase of the macro-F1 score.
-We would expect that applying this technique on our dataset would improve our scores, given earlier results on comparable tasks.\\
+We would expect that applying this technique to our dataset would improve our scores, given earlier results on comparable tasks.\\
 Even though much research has been done, we have not been able to find published results which are directly comparable to our results.
-This is likely due to our high amount of categorization groups, which enabled us to handle our results as a ranking problem, instead of a absolute hit, which has been used in earlier researches\cite{wang2016linked}.
-Even though we have a F1 score, which indicates performance on the absolute hits, our results are not comparable to other works due to the amount of categories, and their overlapping subjects\footnote{As visualized in the journal embedding plots and discussed earlier}.
+This is likely due to our high amount of categorization groups, which enabled us to handle our results as a ranking problem, instead of an absolute hit, which has been used in earlier researches\cite{wang2016linked}.
+Even though we have an F1 score, which indicates performance on the absolute hits, our results are not comparable to other works due to the number of categories, and their overlapping subjects\footnote{As visualized in the journal embedding plots and discussed earlier}.
 

### 2018-06-28 Thesis/Parts/Research_results/Research_results.tex

@@
 In the abstract-based figures (\ref{figure:abstractPlotNormal} \&~\ref{figure:abstractPlotGrouped}) the journals \textit{PNAS} and \textit{Nature} overlap each others label on the bottom right side of the graph.
-The digital versions of these plots can be found at:~\url{https://goo.gl/nCGMcu} (title-based) and~\url{https://goo.gl/LwYP6k}.
+The digital versions of these plots can be found at:~\url{https://goo.gl/nCGMcu} (title-based) and~\url{https://goo.gl/LwYP6k} (abstract-based).
 The usage of this digital version is advised, since this interactive plot enables zooming and adjusting plot settings, which can give a broader insight into the results than the presented figures.
-Although the presented figures give sufficient for the purpose of this thesis.
+Although the presented figures give sufficient insight for the purpose of this thesis.
 \begin{landscape}

### 2018-06-29 Thesis/Parts/Background/Background.tex
Feedback update

@@
 Information Retrieval(IR)is the activity of gathering relevant information, given another initial piece of information. 
-The most practical example of this is a search engine.
+\\\\The most practical example of this is a search engine.
 Given one or more search words the search engine will attempt to find relevant information.
@@
 To be able to do this, the search engine must know which texts are related.
-This can be achieved with, and without neural networks, a traditional technique which does not use a neural network is TF-IDF, shot for Term Frequency - Inverted Document Frequency.
+\\\\This can be achieved with, and without neural networks, a traditional technique which does not use a neural network is TF-IDF, shot for Term Frequency - Inverted Document Frequency.
 Techniques that use a neural network are newer, these are (among others) Word2Vec, Paragraph Vectors and GloVe.
@@
 A complete in-depth background into neural networks is beyond the scope of this thesis, therefore we will only describe the simplified working of a neural network and its basic application in IR.
-Neural Networks are multi-layered computational software, based on matrix calculations, which tries to map input values to output values.
-This mapping uses a pre-defined amount of layers that modify the values through matrix calculations.
+Neural Networks are multi-layered computational software, based on matrix transformations, which tries to map input values to output values.
+This mapping uses a pre-defined amount of layers that modify the values through matrix transformations.
 Neural networks rely on training to create optimal values for these layers.
@@
 The training is the process of iteratively adjusting multiplication matrices or vectors to achieve the optimal result.
-Which is the result that is as close as possible to the given output for all input and output sets.\\Neural Networks are used, in the creation of word embeddings, to either predict words that may occur around a given word or predict a word given words that surround it.
+Which is the result that is as close as possible to the given output for all input and output sets, without under performing on other sets\footnote{Having only good results for the training/validation set is know as overfitting.
+This means that the layer-values are fine-tuned to only perform (extremely) well on one set, while under performing on others}.\\Neural Networks are used, in the creation of word embeddings, to either predict words that may occur around a given word or predict a word given words that surround it.
 For example, given the sentence\\
 \begin{center}
-\textit{"The search engine searches for relevant information"}
+\textit{"The quick brown fox jumps over the lazy dog"}
 \end{center}
-the Neural Network can be trained to either predict the words around "searches" (the, search, engine, for, relevant, information) or to predict the word "searches", given the surrounding (the, search, engine, for, relevant, information).
+the Neural Network can be trained to either predict the words around "jumps", which we refer to as context words (the, quick, brown, fox, over, the, lazy, dog).
+It can also predict the word "jumps", given the context words (the, quick, brown, fox, over, the, lazy, dog).
 This result in a matrix, a vector per word which is referred to as a word embedding.
@@
 Therefore, word embeddings from different runs of the same neural network cannot be compared.
-Neural networks are also used for other tasks such as video recommendation on Google's YouTube, as described by \citet{covington2016deep}.
 
 \subheader{Embedding}
-An embedding is a distributed, numerical representation of text in a vector space\footnote{The vector spaces of separately trained word embeddings differ, since each run the initial values of the neural network are randomly initialized.
+An embedding is a distributed, numerical representation of text in a multi-dimensional vector space\footnote{The vector spaces of separately trained word embeddings differ, since each run the initial values of the neural network are randomly initialized.
 This means that the same word trained in two separate runs do not have to have the same embedding.
 However, they will have the same relationship to other words trained in their respective runs.} which can capture both the semantic and syntactic information\cite{mikolov2013distributed}.
-In the case of a word embedding, the embedding represents the word.
-These embeddings are created using machine learning models, which create the embeddings without the need for human interaction~\cite{lai2016generate}, they are so-called \textit{unsupervised learning algorithms}.
-Once trained, the embeddings can be used to construct embeddings for collections of texts.
+In the case of a word embeddings, the embeddings represent the words.
+These embeddings are created using machine learning models, which do not have the need for human interaction~\cite{lai2016generate}, they are so-called \textit{unsupervised learning algorithms}.
+Once trained, the embeddings can also be used to construct embeddings for collections of texts.
 For example, a word embedding can be used to create a sentence, paragraph, document or corpus embeddings.
@@
 The Skip-gram model takes a target word as input and outputs the predicted output words, while CBOW takes the context words as input and outputs the predicted target word\cite{nalisnick2016improving, pennington2014glove}.
+This is illustrated in figure~\ref{figure:word2vecModels}, in this figure, $v(w)$ represents the target word, and $v(w...)$ represent the context words.
 \citet{mikolov2013distributed}\cite{mikolov2013efficient} presented several extensions to the word2vec model that improve the quality of vector training and its speed, such as introducing Hierarchical Softmax, Negative Sampling and the subsampling of frequent words to the Skip-gram approach.
 Variations to the word2vec model have also been proposed, such as the doc2vec model described by \citet{lau2016empirical} which creates document embeddings instead of word embeddings.
-
+\begin{figure}[hbt]
+\includegraphics[width=4in]{Plots/Model-Architecture-of-CBOW-and-Skip-Gram.png}
+\caption{Illustration of the CBOW and Skip-Gram models, as presented by \citet{chen2017convolutional}}\label{figure:word2vecModels}
+\end{figure}
+\FloatBarrier
 \subsubheader{Paragraph vectors}
@@
 \subsubheader{TF-IDF}
-TF-IDF is an abbreviation for Term Frequency times Inverted Document Frequency.
-This method does not rely on a neural network and therefore does not require training.
+Term Frequency * Inverted Document Frequency (TF-IDF) is a method that does not rely on a neural network and, therefore, does not require training.
 The TF-IDF score is the product of the term frequency in a text and the inverted document frequency of the same term in a corpus of texts.
 Both of which can be calculated in a variety of ways.
-The feature vectors produced by TF-IDF do not capture syntactic or semantic information about words, but capture information about word occurrences.
+Figure~\ref{table:TFIDFScore} shows an example of the TF-IDF calculation.
+The multiplication of the TF and IDF is referred to as the TF-IDF score.
 The text, provided to the algorithm, is analyzed on word occurrences on corpus and document level, this results in a score per word.
@@
 If this is not applied, the size of the feature vector is equal to the number of unique words in the corpus, also known as the (corpus) vocabulary.
+The feature vectors produced by TF-IDF do not capture syntactic or semantic information about words, but capture information about word occurrences.
 Some applications of this technique limit the number of unique words in the text supplied to the TF-IDF algorithm, they do this by taking only a certain amount of top words, ordered on their occurrence.
@@
 It furthermore reduces the number of words which occur rarely.
-Due to the nature of TF-IDF, these rare words have a high score, canceling out other more frequent words, while rarely occurring in the corpus.
+Due to the nature of TF-IDF, these rare words have a high score, cancelling out other more frequent words, while rarely occurring in the corpus.
+\vspace{0.3in}\begin{table}[hbt]
+\begin{center}
+\begin{tabular}{|p{1in}|p{1in}|p{1in}|p{1.3in}|p{1in}|}
+\hline
+Term & Frequency (TF) & Document Frequency (DF) & Inverted Document Frequency (IDF) & TF-IDF score\\
+\hline
+Exponential & 4 & 15 & 0.824 & 3.296\\
+\hline
+Occurrence & 1 & 20 & 0.699 & 0.699\\
+\hline
+Multitude & 1 & 40 & 0.398 & 0.398\\
+\hline
+Abstract & 100 & 100 & 0 & 0\\
+\hline
+\end{tabular}
+\caption{Example of TF-IDF score calculation.}\label{table:TFIDFScore}
+\end{center}
+\end{table}
+\FloatBarrier
 \end{jumpin}
-
 As \citet{lai2016generate} state in their paper "How to generate a good word embedding?", that all embedding methods rely on the same hypothesis, \textit{words that occur in similar contexts have similar meanings}.
@@
 The results produced by the previously mentioned techniques have to be validated to determine their quality (in usage).
-The quality of the results can be validated through, among others the F1 score\footnote{The F1 score combines the precision score and the recall score in a single metric} and, for classification tasks, the rank of the correct class, which is in this research a journal.
+The quality of the results can be validated through various validation metrics, one of these is the F1 score\footnote{The F1 score combines the precision score and the recall score in a single metric}.
 The embeddings can furthermore be validated through their performance on tasks such as word analogy, word similarity, categorization and embedding visualization.
@@
 They validated their proposed paragraph vector model by determining whether a review was positive or negative.
+We will use the classification task for this research too, we will use journals (collection of articles) as classes, and the articles as items that need to be classified.
+We create a list, sorted on the similarity between article and journal, of journals for each article to get a measurable result from this.
+From this list we can extract, among other things, the position (rank) of the journal from which the article was taken.
 \subsubheader{Position Visualization}
@@
 On the other hand, we regard the embeddings created by \citet{Truong2017Thesis} as Domain specific; these embeddings were created on academic articles, which use domain-specific terms and notations and only consists of academic texts, which contains less general/generic words compared to the Wikipedia corpus.
-\subheader{Research environment}
-The research will be done in a python-databricks environment, which uses spark, a library that offers tools to work with big-data.
-\citet{armbrust2015spark} state that Spark SQL lets programmers leverage the benefits of relational processing and lets SQL users call complex analytic libraries in Spark.
-This allows for much tighter integration between relational and procedural processing.
-The paper further states that Spark SQL makes it significantly simpler and more efficient to write data pipelines that mix relational and procedural processing while offering substantial speedups over previous SQL-on-Spark engines.
-\subheader{Text properties}
-\citet{wiegand2018word} state that the Pareto distribution offers a good fit to the word occurrences in natural language.
-Their models show that, due to the additional parameters in the Pareto-III, the tail of the data fits better with the model than the Zipf model.
-This shows the relation between the word occurrences rank and the actual occurrences.
-This kind of word-occurrences distribution holds for many texts, including the writings of William Shakespeare and scientific texts and novels\cite{thurner2015understanding}.
+Figure~\ref{figure:domainPlot} illustrates our corpus, marked in green, in comparison to the Wikipedia corpus, marked in blue.
+Our corpus is a collection of domain specific texts, written in academic language.
+A set that would be more specific would only focus on the individual domains or sub-domains.
+\begin{figure}[hbt]
+\includegraphics[width=6.5in]{Plots/domain_specification_graph}
+\caption{Illustration of generic texts and domain specific texts. Our research focusses on the green-marked area.}\label{figure:domainPlot}
+\end{figure}
 \end{document}

### 2018-06-29 Thesis/Parts/Data/Data.tex
Feedback update

@@
 \end{table}\\
-The word occurrences follow the pattern of a pareto distribution as described by~\citet{wiegand2018word}.
-This distribution is visualized in figure~\ref{figure:wordTokenOccurrence}, which displays the occurrences of the first 500 tokens of the corpus.
+\subheader{Text properties}
+\citet{wiegand2018word} state that the Pareto distribution offers a good fit to the word occurrences in natural language.
+Their models show that, due to the additional parameters in the Pareto-III, the tail of the data fits better with the model than the Zipf model.
+This shows the relation between the word occurrences rank and the actual occurrences.
+This kind of word-occurrences distribution holds for many texts, including the writings of William Shakespeare and scientific texts and novels\cite{thurner2015understanding}.
+The word occurrences in our corpus also follow the pattern of a Pareto distribution as described by~\citet{wiegand2018word}.
+Our distribution is visualized in figure~\ref{figure:wordTokenOccurrence}, which displays the occurrences of the first 500 tokens of the corpus.
 \begin{figure}[hbt]
@@
 \header{Datasets}
-For this researched we used a (pre-made) tokenized dataset, which reduces the total amount of words by 34\%, from this tokenized set, we created the embeddings and the TF-IDF feature vectors.
+For this researched we used a (pre-made) tokenized dataset, created from the earlier described corpus, which reduces the total amount of words by 34\% (see table~\ref{table:corpusSize}).
+From this tokenized set, we created the embeddings and the TF-IDF feature vectors.
 \subheader{Tokenization}
@@
 \item{Transformed all characters to lower-case}
-\item{Removed stop-words, as provided by the NLTK library}
+\item{Removed stop-words, as provided by the NLTK\footnote{Natural Language ToolKit, \url{https://www.nltk.org/}} library}
 \item{Removed numbers}
@@
 For this research, we reused the word embeddings created by \citet{Truong2017Thesis}.
-These embeddings have a vector size of 300, which is an industry default.
+These embeddings have a vector dimension of 300, which is an industry default.
 They have been trained on the entire Elsevier corpus, not limited to the subset we used for this research.
-To create article embeddings, we take the average of all normalized word embeddings for that article.
-Journal embeddings are created in the same way.
-We averaged all the normalized article embeddings to create the journal embeddings.
-We have used multiple embedding configurations for this research
+To create higher-level embeddings, we average all component embeddings.
+Thus, to create article embeddings, we take the average of all normalized word embeddings for that article.
+Journal embeddings are created by taking the average of all normalized article embeddings.
+We use the average to combine multiple embeddings into one, because we determine the meaning of a larger text as the average meaning of all components.
+Since this meaning is represented as an embedding, we can average the embeddings to create the "average meaning".
+We have used multiple embedding optimizations for this research.
 \subsubheader{Default embedding}
-The default embedding is created form the pre-trained word embeddings; no modifications have been applied to this set.
-\subsubheader{TF-IDF embedding}
+The default embedding is created form the pre-trained word embeddings; no modifications have been applied to this set. We refer to this set in the figures as "embedding".
+\subsubheader{TF-IDF weighted embedding}
 The TF-IDF weighted embedding set, referred to as TF-IDF embedding, are the default word embeddings weighted with a TF-IDF score per word.\\
@@
 Where $|A|$ is the total count of articles and $|A_t|$ is the count of articles containing term t.
-The articles embeddings are a normalized summation of each word vector multiplied by it TF-IDF value. Since we take a sum of all words, the Term Frequency is embedded as the raw count of each word.
+The articles embeddings are a normalized summation of each word vector multiplied by it TF-IDF value.
+Since we take a sum of all words, the Term Frequency is embedded as the raw count of each word.
+We will refer to this embedding in the figures as "tfidf\_embedding".
 \subsubheader{10K TF-IDF embedding}
@@
 This set was created to see if the limitation to 10.000 tokens reduces the amount of noise, increasing the performance.
+We will refer to this embedding in the figures as the "10k\_embedding".
 \subsubheader{5K TF-IDF embedding}
-The 5K TF-IDF embedding is the TF-IDF embedding set, limited to the 5.000 most common words. This set was created to limit the number of tokens more aggressively, and with that, cancel out more noise.
+The 5K TF-IDF embedding is the TF-IDF embedding set, limited to the 5.000 most common words.
+This set was created to limit the number of tokens more aggressively, and with that, cancel out more noise.
+We will refer to this embedding in the figures as "5k\_embedding".
 \subsubheader{1K-6K TF-IDF embedding}
@@
 This cut results in a set of 5.000 tokens, which allows us to compare it to the 5K TF-IDF set.
-
+We will refer to this embedding in the figures as "1k\_6k\_embedding".
+We refer to the "10k\_embedding", "5k\_embedding" and the "1k\_6k\_embedding" as the limited TF-IDF embeddings, because these embedding use TF-IDF weighing, and have been limited in their vocabulary due to the cut-off's.
 \subheader{TF-IDF}
@@
 To limit the computational and storage expenses and to reduce noise by rare words, we limit our vocabulary size.
-We denote the TF-IDF configurations as follows: $vocabulary size/hash bucket number$.
+We label the TF-IDF configurations as follows: $vocabulary size/hash bucket size$.
 Furthermore, we denote 1.000 as 1K, since we deal with chosen values which can be exactly noted given this notation.
-\begin{figure}
-\includegraphics[width=6in]{Plots/tfidf_selection_plot}
-\caption{TF-IDF performance and memory usage}\label{figure:tfidfPerformance}
+This means that the set with a 10.000 vocabulary size and a 10.000 hash bucket size will be denoted as "10K/10K".
+We will refer to the TF-IDF configurations in our figures as "tfidf\_vocabulary size\_hash bucket size".
+\begin{figure}[hbt]
+\includegraphics[width=5in]{Plots/tfidf_selection_plot_performance}
+\caption{TF-IDF performance on title and abstract}\label{figure:tfidfPerformance}
+\end{figure}
+\begin{figure}[hbt]
+\includegraphics[width=5in]{Plots/tfidf_selection_plot_memory}
+\caption{TF-IDF performance on title and abstract}\label{figure:tfidfMemory}
 \end{figure}
 \FloatBarrier
-Figure~\ref{figure:tfidfPerformance} shows the performance, as median rank, and storage size, in gigabyte, of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations.
+Figure~\ref{figure:tfidfPerformance} shows the performance of title and abstract as median rank, and figure~\ref{figure:tfidfMemory} shows the storage size in gigabyte, of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations.
 This plot shows that, while the required storage size keeps rising, the performance on title quickly stagnates, and the performance on abstract follows too.
@@
 The TF-IDF features are created on article level.
-We average the set of article embeddings to create a journal embedding.
+We average the set of article feature vectors to create a journal feature vector, just as we did with the embeddings.
+
+\header{Research environment}
+The research will be done in a python-databricks environment, which uses spark, a library that offers tools to work with big-data.
+\citet{armbrust2015spark} state that Spark SQL lets programmers leverage the benefits of relational processing and lets SQL users call complex analytic libraries in Spark.
+This allows for much tighter integration between relational and procedural processing.
+The paper further states that Spark SQL makes it significantly simpler and more efficient to write data pipelines that mix relational and procedural processing while offering substantial speedups over previous SQL-on-Spark engines.
 
@@
 \subheader{Categorize validation articles}
-To categorize the articles, we calculate the distance between the title- and abstract embedding of each article, from the validation set, to the title- and abstract embedding of each journal, during this process we keep track of:
+To categorize the articles, we calculate the distance between the title of the article, and the title of each journal from the validation set.
+We also do this for the abstract of the article and the abstract of each journal.
+During this process we keep track of:
 \begin{itemize}
@@
 Also the Cityblock metric yields results close to the Cosine metric, it has a slightly worse performance, which is also not significant.
-Because of this, we will use the cosine-similarity as the distance matrix, which will make our results better comparable with other work.
+Because of this, we will use the cosine-similarity as the distance metric, which will make our results better comparable with other work.
 

### 2018-06-29 Thesis/Parts/Discussion/Discussion.tex
Feedback update

@@
 The data, as presented in figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank on abstract and 3 median ranks on the titles.
-For the embeddings, the TF-IDF weighted embedding works better than the others, although it is not a significant improvement compared to the default embeddings, which 1 median rank higher on the abstracts, and equal on the titles.
+For the embeddings, the TF-IDF weighted embedding works better than the others, although it is not a significant improvement (1 rank on a set of more than 3.000) compared to the default embeddings, which 1 median rank higher on the abstracts, and equal on the titles.
 
@@
 \subsubheader{Limited TF-IDF embeddings}
-The limited TF-IDF embeddings all underperform, compared to the non-limited TF-IDF embedding, on the median and average ranking.
+The limited TF-IDF embeddings all underperform, compared to the TF-IDF embedding (which does not have a limited vocabulary), on the median and average ranking.
 Indicating that the noise reduction is too much, and it removes meaningful words.
@@
 This is further supported by the TF-IDF score on titles (figure~\ref{figure:titleRanks}), on which the limited TF-IDF embeddings are the top performance.
-Indicating a better performance on the top-1 articles compared to the other sets.\\This leads us to believe that the cut-off was effective, but that it did not suit our purpose.
+Indicating a better performance on the top-1 articles compared to the other sets.\\This seems to indicate that the cut-off was effective, but that it did not suit our purpose.
 The cut-off moved the "middle-ranked"  articles to either the higher end or the lower end of the rankings.
@@
 If this is the case, we could expect that there would little performance increase on the title when we compare the embeddings to the weighted TF-IDF embeddings, since the TF-IDF lacks the information to perform well.
-This can be seen in our data, only the average rank increased by 3, indicating that there is a difference between the two embeddings, but not a major one.
+This can be seen in our data, only the average rank increased by 3, indicating that there is a difference between the two embeddings, but not a significant one.
 We would also expect on the abstract an increase in performance since the TF-IDF has more information in this context.
@@
 Which is significantly worse than the embedding, which also uses less memory.
+This indicates that the embeddings are able to store the relatedness information more densely than the TF-IDF feature vectors can store the worod occurrence information.
 
@@
 \subheader{Improvements}
-This research shows that even tough the embeddings can capture and preserve relatedness, TF-IDF is able to outperform the embeddings.
+This research shows that even tough the embeddings can capture and preserve relatedness, TF-IDF is able to outperform the embeddings on the abstracts.
 Earlier research already proposed improvements to the word embeddings.
@@
 We do not categorize on two categories but more than 3k.
-Still, we would expect an improvement by using paragraph vectors since the classification task if fundamentally the same, only on a much larger scale., which complicates the task due to the "grey areas"  between categories, which increases given more categories.
+Still, we would expect an improvement by using paragraph vectors since the classification task if fundamentally the same, only on a much larger scale, which complicates the task due to the "grey areas"  between categories.
+These are the area's in which the classification algorithm is "in doubt" and could reasonably assing the article to both journals.
+The number of these grey areas increases given more categories.
 \citet{pennington2014glove} showed that the GloVe model outperforms the CBOW model, which is used in this research, on a word analogy task.

### 2018-06-29 Thesis/Parts/Future_work/Future_work.tex
Feedback update

@@
 \citet{levy2015improving} observed that there were no significant differences between the various embedding creation methods.
-They state that the global/hyperparameters mainly cause the difference in performance.
+They state that the global/hyperparameters of the various methods mainly cause the difference in performance.
 In this research, we have not looked at the comparison between various models and (hyper) parameters.
@@
 All words which are generic are in the center of the spectrum.
-Removing these words prevents the larger texts to be pulled towards the middle, where they lose the parts of their meaning which sets them apart from the other journals.
+Removing these words prevents the larger texts to be pulled towards the middle of the vector space, where they lose the parts of their meaning which sets them apart from the other journals.
 We expect that this way of cutting, instead of word-occurrence cutting, will improve the quality of the word embeddings.

### 2018-06-29 Thesis/Parts/Motivation/Motivation.tex
Feedback update

@@
 \begin{jumpin}
-    \textbf{RQ. 1} Have word-embeddings a higher accuracy for academic texts than TF-IDF for article classification?\\
+    \textbf{RQ. 1} Have classical word-embeddings a higher accuracy for academic texts than TF-IDF for article classification?\\
     \begin{adjustwidth}{0.3in}{}
-        \textbf{RQ. 1.1} Does TF-IDF weighting increase the performance of word embedding on academic texts for article classification?\\
+        \textbf{RQ. 1.1} Do embedding optimizations increase the performance of word embedding on academic texts for article classification?\\
         \textbf{RQ. 1.2} Can the usage of alternative distance metrics improve the performance of word embedding on academic articles for article classification?
@@
 \end{jumpin}
-\subsubheader{Embedding and TF-IDF}
+\subsubheader{Methodology}
 RQ.
@@
 For this task, we will use different versions of embeddings, to answer RQ 1.1, and different TF-IDF versions to not only compare the two techniques but also look for the optimal results of both techniques.
-To achieve the optimal results, we compare 20 distance metrics from the SciPy library on ranking performance on the standard embeddings.
+To achieve the optimal results, we compare 20 distance metrics on ranking performance on the classical embeddings.
 For this part of the research, we will use the following hypothesis:

### 2018-06-29 Thesis/Parts/Research_results/Research_results.tex
Feedback update

@@
 These graphs give a detailed view of the ranks presented in their respective figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks}.
+The Y-axis of the two figures show the fraction of the total number of articles.
+The X-axis plots the ranks of the articles.
+These ranks are the ranks of each individual article in our validation set, in contrast to figure~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} which show average and median ranks.
 \begin{figure}[hbt]
@@
 These scores indicate the performance of the sets on absolute hits/top-1.
+We show the precision and recall scores since they vary between sets that have similar F1-scores (i.e.
+figure~\ref{figure:f1Title}, tfidf\_5k\_5k \& tfidf\_embedding
 \begin{figure}[hbt]
@@
 \subheader{Memory usage}
-Table~\ref{table:memoryUsage} shows the total memory usage of each set for the \textit{Validation set}, indicating their storage costs in gigabytes\footnote{1024 based}.\\
+Table~\ref{table:memoryUsage} shows the total memory usage of each set for the \textit{Validation set}, indicating their storage costs in gigabytes\footnote{1024 based}.
+It furthermore shows the absolute hit percentage of the title and the abstracts, this is the percentage of articles that have the journals from which they were taken at rank 0, meaning that the journal has the closest embedding.
+The table furthermore shows the median rank and the median abstract rank, as visualized in figures \ref{figure:titleRanks} \&~\ref{figure:abstractRanks}.\\
 \begin{table}[hbt]

### 2018-06-29 Thesis/Parts/Data/Data.tex
Updated thesis

@@
 \caption{Corpus size}\label{table:corpusSize}
-\end{table}\\
+\end{table}
+\clearpage
 \subheader{Text properties}
@@
 Our distribution is visualized in figure~\ref{figure:wordTokenOccurrence}, which displays the occurrences of the first 500 tokens of the corpus.
+\FloatBarrier
 \begin{figure}[hbt]
@@
 \end{figure}
-
+\FloatBarrier
 \header{Datasets}
@@
 We refer to the "10k\_embedding", "5k\_embedding" and the "1k\_6k\_embedding" as the limited TF-IDF embeddings, because these embedding use TF-IDF weighing, and have been limited in their vocabulary due to the cut-off's.
+\clearpage
 \subheader{TF-IDF}
@@
 We average the set of article feature vectors to create a journal feature vector, just as we did with the embeddings.
-
-\header{Research environment}
+\header{Pipeline}
+\subheader{Research environment}
 The research will be done in a python-databricks environment, which uses spark, a library that offers tools to work with big-data.
@@
 This allows for much tighter integration between relational and procedural processing.
-The paper further states that Spark SQL makes it significantly simpler and more efficient to write data pipelines that mix relational and procedural processing while offering substantial speedups over previous SQL-on-Spark engines.
-
-\header{Pipeline}
+The paper further states that Spark SQL makes it significantly simpler and more efficient to write data pipelines that mix relational and procedural processing while offering substantial speedups over previous SQL-on-Spark engines.\\
 We procesessed the TF-IDF sets and the embedding sets via the same pipeline, using their common vector properties. This ensures comparable results, the pipeline is set-up as follows:
@@
 To calculate the distance between to vectors, cosine similarity is commonly used.
-We validated the quality of cosine similarity as a distance metrics by comparing it to all other similarity matrices available in the SciPy library, which we used to calculate the distances.
+We validated the quality of cosine similarity as a distance metrics by comparing it to other similarity matrices available in the SciPy\footnote{\url{https://www.scipy.org/}} library, which we used to calculate the distances.
 We calculate the similarities based on the normalized embeddings, and compared the distance metrics based on the default embedding set.
@@
 Because of this, we will use the cosine-similarity as the distance metric, which will make our results better comparable with other work.
-
+\clearpage
 \subheader{Performance measurement}
@@
 To further analyse the ranking results, we plot the rank distribution to get an indication of the ranking-landscape.
-
-\header{ Two-dimensional plot}
+\subsubheader{Two-dimensional plot}
 To create a plot, we transformed the 300-dimensional journal vectors into 2-dimensional vectors using TSNE based on pca\footnote{Principal component analysis}.

### 2018-06-29 Thesis/Parts/Data/Data.tex
Update

@@
 Figure~\ref{figure:tfidfPerformance} shows the performance of title and abstract as median rank, and figure~\ref{figure:tfidfMemory} shows the storage size in gigabyte, of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations.
-This plot shows that, while the required storage size keeps rising, the performance on title quickly stagnates, and the performance on abstract follows too.
+This plot shows that, while the required storage size stagnate, the performance on title also quickly stagnates, together with the performance on the abstracts.
 Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to.
+Since these configurations can be kept in memory (storage size) while it is not likely that larger sets will give much improvement.
 The TF-IDF features are created on article level.

### 2018-07-02 Thesis/Parts/Abstract/Abstract.tex
UVA_template
Updated pdfs
Auto stash before merge of "master" and "origin/master"

@@
 \begin{document}
-\fakeheader{Abstract}
 Over the last few years, word embeddings have taken a dominant position in the Information Retrieval domain.
@@
 However, these studies have been focused on generic texts, which are not limited to the characteristics of in-domain texts such as rare domain-specific words or have been focussed on small sets of academic texts.
-This research focusses on the quality and application of word embeddings on domain-specific texts, concerning a large corpus of 1.391.543 scientific articles which have been published in 2017.
+This research focusses on the quality and application of word embeddings on domain-specific texts, concerning a large corpus of 1.391.543 scientific articles which have been published in 2017.\\
+\vspace*{\fill}
+\\
+We aim to have this thesis published in the proceedings of the 14th Asia Information Retrieval Societies (AIRS) Conference (\url{http://airs2018.org/site/page.aspx?pid=901&sid=1221&lang=en}).
+\textit{Paper submission deadline: 23 July 2018; Notification of acceptance: 27 August 2018}
 \end{document}

### 2018-07-02 Thesis/Parts/Background/Background.tex
Auto stash before merge of "master" and "origin/master"

@@
 Neural networks rely on training to create optimal values for these layers.
+Finding these optimal values is done iteratively, via a process known as "back-propogation".
+Back-propogation is done by starting at the output layer of the Neural Network and tracing error in the output back through the layers.
+This error information is used to improve the values of the layers.
 The values in the layers are only changed at training time; high-quality training data is therefore essential for neural networks.
@@
 The Skip-gram model takes a target word as input and outputs the predicted output words, while CBOW takes the context words as input and outputs the predicted target word\cite{nalisnick2016improving, pennington2014glove}.
-This is illustrated in figure~\ref{figure:word2vecModels}, in this figure, $v(w)$ represents the target word, and $v(w...)$ represent the context words.
+This is illustrated in Figure~\ref{figure:word2vecModels}, in this figure, $v(w)$ represents the target word, and $v(w...)$ represent the context words.
 \citet{mikolov2013distributed}\cite{mikolov2013efficient} presented several extensions to the word2vec model that improve the quality of vector training and its speed, such as introducing Hierarchical Softmax, Negative Sampling and the subsampling of frequent words to the Skip-gram approach.
 Variations to the word2vec model have also been proposed, such as the doc2vec model described by \citet{lau2016empirical} which creates document embeddings instead of word embeddings.
+\begin{center}
 \begin{figure}[hbt]
 \includegraphics[width=4in]{Plots/Model-Architecture-of-CBOW-and-Skip-Gram.png}
-\caption{Illustration of the CBOW and Skip-Gram models, as presented by \citet{chen2017convolutional}}\label{figure:word2vecModels}
+\caption{Illustration of the CBOW and Skip-Gram models, as presented by \citet{chen2017convolutional}.
+Left part of the Figure illustrates the CBOW model, context words are represented at the left side (input) and the center word (output) is represented as $v(w)$ as output.
+The right side of the Figure illustrates the Skip-Gram Model, which takes the center word as input (left) and outputs the context words (right).}\label{figure:word2vecModels}
 \end{figure}
 \FloatBarrier
+\end{center}
 \subsubheader{Paragraph vectors}
@@
 Both of which can be calculated in a variety of ways.
-Figure~\ref{table:TFIDFScore} shows an example of the TF-IDF calculation.
+Table~\ref{table:TFIDFScore} shows an example of the TF-IDF calculation.
 The multiplication of the TF and IDF is referred to as the TF-IDF score.
@@
 Labeled data is data that is in some way marked so that the correct answer can be derived from it, while this is not possible with unlabelled data.
-Labeled data enables the use of unsupervised learning models since  \textit{a system or model which is not involved in the actual learning} can automatically validate the given results and use it as feedback for the next learning iteration.
-Unlabelled data, on the other hand, requires human interaction to give a score for the produced result.
-The validation tasks can also be divided into two groups, extrinsic evaluation, ones that use word embeddings as input for a downstream task and Intrinsic evaluation, which directly tests the relationships of the word embedding themselves.
+The validation tasks can be divided into two groups, extrinsic evaluation, ones that use word embeddings as input for a downstream task and Intrinsic evaluation, which directly tests the relationships of the word embedding themselves.
 \citet{schnabel2015evaluation} note that the extrinsic evaluation may not be consistent with intrinsic evaluations since the performance on downstream tasks is not consistent across tasks.
@@
 The generic embeddings are trained on a collection of texts that use common English and contains a wide variety of topics.
-The domain-specific embeddings are trained on a collection of texts that uses uncommon English (i.e., domain-specific terms) or is limited to a small number of topics.
+The domain-specific embeddings are trained on a collection of texts that uses jargon English (i.e., domain-specific terms) or is limited to a small number of topics.
 Given these terms, we regard the embeddings trained on the Wikipedia corpus\cite{lai2016generate, pennington2014glove, dai2015document, lau2016empirical, schnabel2015evaluation} as general, since Wikipedia uses common English and spans a wide range of topics.

### 2018-07-02 Thesis/Parts/Data/Data.tex
Auto stash before merge of "master" and "origin/master"

@@
 \subsubheader{Median \& average rank}
-We use the median rank to indicate at which rank the 'standard' article would be ranked, based on its title or abstract.
+The median rank of a journal indicates the point where 50\% of all articles are to the left of a virtual line and 50\% are to the right of this line.
+The median rank therefore indicates the position of the "normal/typical"  article.
+This median rank differs from the average, since the median is not influenced by a single value.
+If the median is 20, it does not matter if an article is 25 of 250, it does matter however if an articles is 19 or 21.
+For the average this is not the case, the average is influenced by single articles.
+Therefore it does not represents the "normal/typical" article but it represents the exact average of all articles in the validation set, which is changed when an article changed from 25 to 250.\\
+We use the median rank to indicate at which rank the typical article would be ranked, based on its title and abstract.
 We do this by taking the median of the respective rank from each article.
 This gives us an indication of the behaviour of the articles in our validation set.
-This median rank (mostly) ignores the outliers, we therefore also use the average rank, which gives a more global indication, although this rank may be over-influenced by some outliers.
+We also calculate the average score for the title and abstract of all articles.
+This gives us four scores: median title rank, median abstract rank, average title rank \& average abstract rank.\\
 \subsubheader{Rank distribution}

### 2018-07-02 Thesis/Parts/Discussion/Discussion.tex
Auto stash before merge of "master" and "origin/master"

@@
 \header{Discussion}
+In this chapter, the results presented in Chapter 6: Results will be discussed. No additional results will be presented in this chapter.
 \subheader{Result analysis}
-\begin{jumpin}
+
 \subsubheader{Best performers}
-The data, as presented in figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank on abstract and 3 median ranks on the titles.
+The data, as presented in Figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank on abstract and 3 median ranks on the titles.
 For the embeddings, the TF-IDF weighted embedding works better than the others, although it is not a significant improvement (1 rank on a set of more than 3.000) compared to the default embeddings, which 1 median rank higher on the abstracts, and equal on the titles.
@@
 The TF-IDF feature vectors outperform the embeddings on the abstract, while the embeddings outperform the TF-IDF feature vectors on the title.
-The main difference between the abstract \& title is that the title contains fewer tokens compared to the abstract (see table~\ref{table:corpusSize}).
+The main difference between the abstract \& title is that the title contains fewer tokens compared to the abstract (see Table~\ref{table:corpusSize}).
 This means that the titles contain less information than the abstracts.
@@
 The data furthermore shows that increasing the vocabulary size increases the performance of the TF-IDF, this means that none of the created cut-off's resulted in cutting off noise, the increasing size of the vocabulary only improved the performance in this case.
-It could be possible that at higher vocabulary sizes the cut-off would result in a sharper signal, we did not look into this further due to our findings that the TF-IDF performance stagnates (presented in figure~\ref{figure:tfidfPerformance}).
-
+It could be possible that at higher vocabulary sizes the cut-off would result in a sharper signal, we did not look into this further due to our findings that the TF-IDF performance stagnates (presented in Figure~\ref{figure:tfidfPerformance}).
+\clearpage
 \subsubheader{Limited TF-IDF embeddings}
@@
 This is in line with what we found with the TF-IDF results; higher vocabulary sizes give better performance.
-However, figures~\ref{figure:titleDistribution} \&~\ref{figure:abstractDistribution} show that their rank distribution is different from the other embeddings.
+\begin{jumpin}
+\subsubsubheader{Rank distribution}
+However, Figures~\ref{figure:titleDistribution} \&~\ref{figure:abstractDistribution} show that their rank distribution is different from the other embeddings.
 Their pattern shows a decent performance indicates the following pattern: a high/average performance on the top-rankings, an underperformance on the middle rankings and a resulting stack-up of articles with a high-ranking.
-This is further supported by the TF-IDF score on titles (figure~\ref{figure:titleRanks}), on which the limited TF-IDF embeddings are the top performance.
-Indicating a better performance on the top-1 articles compared to the other sets.\\This seems to indicate that the cut-off was effective, but that it did not suit our purpose.
+This is further supported by the TF-IDF score on titles (Figure~\ref{figure:titleRanks}), on which the limited TF-IDF embeddings are the top performance.
+Indicating a better performance on the top-1 articles compared to the other sets.
+\end{jumpin}This seems to indicate that the cut-off was effective, but that it did not suit our purpose.
 The cut-off moved the "middle-ranked"  articles to either the higher end or the lower end of the rankings.
@@
 The top-performing embedding, TF-IDF weighted embedding, uses 3.13 GB, the top performing TF-IDF, 10K/10K uses 11.61 GB, which is 270.93\% of the storage size needed for the embedding.
-The closest TF-IDF configuration we used was 1K/1K, which uses 5.13 GB (as displayed in figure~\ref{figure:tfidfPerformance}).
+The closest TF-IDF configuration we used was 1K/1K, which uses 5.13 GB (as displayed in Figure~\ref{figure:tfidfPerformance}).
 This TF-IDF set has a median title rank of 183 and a median abstract rank of 44.
@@
 They have therefore a more reliable grouping metric.
-\end{jumpin}
+
 \subheader{Improvements}

### 2018-07-02 Thesis/Parts/Future_work/Future_work.tex
Auto stash before merge of "master" and "origin/master"

@@
 Furthermore, it would be interesting to see which words would be selected and if these words represent the given sentence as an "extracted version" which would still be interpretable by humans.
+
+\subheader{Pre-categorization}
+Our results show that the embeddings can indicate the domains of the given articles, as visualized in the journal embedding plots (Figure~\ref{figure:titlePlotNormal}-\ref{figure:abstractPlotGrouped}).
+This knowledge could be used to pre-process given texts, creating a two-step search.
+This method would first categorize the given article into a field, and then search in the limited set of journals for the best fit.
+This has two advantages: A) we predict the field of the article, giving additional information to a user and B) once an article is inside a certain domain, ambiguous words between domains (i.e.
+cloud for computer science and meteorology) are eliminated, since these embeddings do not have to be trained with the other embeddings, which create ambiguity.
+A possible downside of this approach is the need for data within each domain, since the embeddings are created on two levels, cross-domain for domain categorization and in-domain for journal categorization.
+The lack of articles within one domain could hurt the embeddings since they need training data to make accurate predictions.
+In a situation were there is no categorization data available, like in our research, a k-means algorithm should suffice for categorization.
+The goal is to have multiple separate vector spaces, for this is does not matter if the "domains" are well-interpretable or make sense to humans.
 \end{document}

### 2018-07-02 Thesis/Parts/Research_results/Research_results.tex
Updated thesis
Auto stash before merge of "master" and "origin/master"

@@
 \header{Research results}
+In this chapter the results of our research will be presented with only the required explanation of the results. These results will be discussed in Chapter 7: Discussion.
 \subheader{Ranking}
-The figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} show the result of the categorization task as ranking results.
+The Figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} show the result of the categorization task as ranking results.
 The rank indicates the position of the correct journal in the sorted list of matched journals.
@@
 Figure~\ref{figure:abstractRanks} displays the ranking results based on the abstract.
-Both graphs show both average and median ranks, based on the cosine-similarity between the article and journal embeddings or feature vectors.\\
+Both graphs show both average and median ranks, based on the cosine-similarity between the article and journal embeddings or feature vectors.
+\clearpage
 \begin{figure}[hbt]
@@
 The figures plot the summed amount of articles against the ranks on a logarithmic scale.
-Figure~\ref{figure:titleDistribution} shows the rank distribution for the titles, figure~\ref{figure:abstractDistribution} shows this for the ranks based on the abstract.
+Figure~\ref{figure:titleDistribution} shows the rank distribution for the titles, Figure~\ref{figure:abstractDistribution} shows this for the ranks based on the abstract.
 These graphs give a detailed view of the ranks presented in their respective figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks}.
 The Y-axis of the two figures show the fraction of the total number of articles.
+Due to this, all sets will move towards one.
+When one is hit, the graph stagnates since there are no more articles that can be added once the value reaches one.
 The X-axis plots the ranks of the articles.

### 2018-07-03 Thesis/Parts/Abstract/Abstract.tex
new thesis version

@@
 \\
-We aim to have this thesis published in the proceedings of the 14th Asia Information Retrieval Societies (AIRS) Conference (\url{http://airs2018.org/site/page.aspx?pid=901&sid=1221&lang=en}).
-\textit{Paper submission deadline: 23 July 2018; Notification of acceptance: 27 August 2018}
+We aim to have this thesis published in the proceedings of the --- \textit{Paper submission deadline: xx XXXX 2018; Notification of acceptance: xx XXXX 2018}
 \end{document}

### 2018-07-03 Thesis/Parts/Background/Background.tex
new thesis version

@@
 The Skip-gram model takes a target word as input and outputs the predicted output words, while CBOW takes the context words as input and outputs the predicted target word\cite{nalisnick2016improving, pennington2014glove}.
-This is illustrated in Figure~\ref{figure:word2vecModels}, in this figure, $v(w)$ represents the target word, and $v(w...)$ represent the context words.
+This is illustrated in Figure~\ref{figure:word2vecModels}, in this Figure, $v(w)$ represents the target word, and $v(w...)$ represent the context words.
 \citet{mikolov2013distributed}\cite{mikolov2013efficient} presented several extensions to the word2vec model that improve the quality of vector training and its speed, such as introducing Hierarchical Softmax, Negative Sampling and the subsampling of frequent words to the Skip-gram approach.

### 2018-07-03 Thesis/Parts/Data/Data.tex
new thesis version

@@
 \begin{document}
-\header{Corpus}
+\header{Research Data}
+\subheader{Corpus}
 The dataset we used for this research consists of articles published in 2017 which have been published in a journal that has, in 2017, atleast 150 publications.
@@
 \clearpage
-\subheader{Text properties}
+\subsubheader{Text properties}
 \citet{wiegand2018word} state that the Pareto distribution offers a good fit to the word occurrences in natural language.
-Their models show that, due to the additional parameters in the Pareto-III, the tail of the data fits better with the model than the Zipf model.
+Their models show that, due to the additional parameters in the Pareto-III\footnote{The pareto distribution is a distribution in which recognizable by a long "tail" of low values and a quick and short ascend to the top values.
+More information: \url{https://en.wikipedia.org/wiki/Pareto_distribution}.}, the tail of the data fits better with the model than the Zipf\footnote{Distribution similar to the Pareto distribution, see: \url{https://en.wikipedia.org/wiki/Zipf\%27s_law}} model.
 This shows the relation between the word occurrences rank and the actual occurrences.
@@
 The word occurrences in our corpus also follow the pattern of a Pareto distribution as described by~\citet{wiegand2018word}.
-Our distribution is visualized in figure~\ref{figure:wordTokenOccurrence}, which displays the occurrences of the first 500 tokens of the corpus.
+Our distribution is visualized in Figure~\ref{figure:wordTokenOccurrence}, which displays the occurrences of the first 500 tokens of the corpus.
 \FloatBarrier
@@
 \includegraphics[width=6.5in]{Plots/word_occurrences}
-\caption{Word and token occurrences}\label{figure:wordTokenOccurrence}
+\caption{Word and token occurrences. The word counts pattern resembles a Pareto distribution, the tokenization reduced the amount of high frequency words.}\label{figure:wordTokenOccurrence}
 \end{figure}
 \FloatBarrier
-\header{Datasets}
+\subheader{Datasets}
 For this researched we used a (pre-made) tokenized dataset, created from the earlier described corpus, which reduces the total amount of words by 34\% (see table~\ref{table:corpusSize}).
 From this tokenized set, we created the embeddings and the TF-IDF feature vectors.
-\subheader{Tokenization}
+\subsubheader{Tokenization}
 The following steps have been applied to the words to create a tokenized set:
@@
 These transformations reduced our dataset by 34\%, resulting in a tokenized set of $186.962.354$ tokens.
-
-\subheader{Embedding}
+\subsubheader{Embedding}
 For this research, we reused the word embeddings created by \citet{Truong2017Thesis}.
@@
 We have used multiple embedding optimizations for this research.
-\subsubheader{Default embedding}
-The default embedding is created form the pre-trained word embeddings; no modifications have been applied to this set. We refer to this set in the figures as "embedding".
-\subsubheader{TF-IDF weighted embedding}
+\subsubsubheader{Default embedding}
+The default embedding is created form the pre-trained word embeddings; no modifications have been applied to this set. We refer to this set in the Figures as \textbf{embedding}.
+\subsubsubheader{TF-IDF weighted embedding}
 The TF-IDF weighted embedding set, referred to as TF-IDF embedding, are the default word embeddings weighted with a TF-IDF score per word.\\
@@
 Since we take a sum of all words, the Term Frequency is embedded as the raw count of each word.
-We will refer to this embedding in the figures as "tfidf\_embedding".
-\subsubheader{10K TF-IDF embedding}
+We will refer to this embedding in the Figures as \textbf{tfidf\_embedding}.
+\subsubsubheader{10K TF-IDF embedding}
 The 10K embedding set is generated similarity to the TF-IDF embedding, this version only uses the 10.000 most common tokens, reducing the number of tokens it uses.
 This set was created to see if the limitation to 10.000 tokens reduces the amount of noise, increasing the performance.
-We will refer to this embedding in the figures as the "10k\_embedding".
-\subsubheader{5K TF-IDF embedding}
+We will refer to this embedding in the Figures as the \textbf{10k\_embedding}.
+\subsubsubheader{5K TF-IDF embedding}
 The 5K TF-IDF embedding is the TF-IDF embedding set, limited to the 5.000 most common words.
 This set was created to limit the number of tokens more aggressively, and with that, cancel out more noise.
-We will refer to this embedding in the figures as "5k\_embedding".
-\subsubheader{1K-6K TF-IDF embedding}
+We will refer to this embedding in the Figures as \textbf{5k\_embedding}.
+\subsubsubheader{1K-6K TF-IDF embedding}
 The 1K-6K TF-IDF embedding is the TF-IDF embedding limited to the top 6.000 most common words, without the top 1.000 most common words.
@@
 This cut results in a set of 5.000 tokens, which allows us to compare it to the 5K TF-IDF set.
-We will refer to this embedding in the figures as "1k\_6k\_embedding".
-We refer to the "10k\_embedding", "5k\_embedding" and the "1k\_6k\_embedding" as the limited TF-IDF embeddings, because these embedding use TF-IDF weighing, and have been limited in their vocabulary due to the cut-off's.
+We will refer to this embedding in the Figures as \textbf{1k\_6k\_embedding}.
+We refer to the \textbf{10k\_embedding}, \textbf{5k\_embedding} and the \textbf{1k\_6k\_embedding} as the \textbf{limited TF-IDF embeddings}, because these embedding use TF-IDF weighing, and have been limited in their vocabulary due to the cut-off's.
 \clearpage
-\subheader{TF-IDF}
+\subsubheader{TF-IDF}
 To create the TF-IDF feature vectors, we used the TF-IDF model and a hasher from PySparks MlLib library.
@@
 This means that the set with a 10.000 vocabulary size and a 10.000 hash bucket size will be denoted as "10K/10K".
-We will refer to the TF-IDF configurations in our figures as "tfidf\_vocabulary size\_hash bucket size".
+We will refer to the TF-IDF configurations in our Figures as "tfidf\_vocabulary size\_hash bucket size".
 \begin{figure}[hbt]
@@
 \includegraphics[width=5in]{Plots/tfidf_selection_plot_memory}
-\caption{TF-IDF performance on title and abstract}\label{figure:tfidfMemory}
+\caption{TF-IDF memory usage for title and abstract combined}\label{figure:tfidfMemory}
 \end{figure}
 \FloatBarrier
-Figure~\ref{figure:tfidfPerformance} shows the performance of title and abstract as median rank, and figure~\ref{figure:tfidfMemory} shows the storage size in gigabyte, of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations.
+Figure~\ref{figure:tfidfPerformance} shows the performance of title and abstract as median rank, and Figure~\ref{figure:tfidfMemory} shows the storage size in gigabyte, of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations.
 This plot shows that, while the required storage size stagnate, the performance on title also quickly stagnates, together with the performance on the abstracts.

### 2018-07-03 Thesis/Parts/Discussion/Discussion.tex
new thesis version

@@
 This is further supported by the TF-IDF score on titles (Figure~\ref{figure:titleRanks}), on which the limited TF-IDF embeddings are the top performance.
-Indicating a better performance on the top-1 articles compared to the other sets.
-\end{jumpin}This seems to indicate that the cut-off was effective, but that it did not suit our purpose.
+Indicating a better performance on the top-1 articles compared to the other sets.\vspace{0.3in}
+\end{jumpin}
+The rank distribution seems to indicate that the cut-off was effective, but also that it did not suit our purpose.
 The cut-off moved the "middle-ranked"  articles to either the higher end or the lower end of the rankings.
@@
 We do this because the journal embeddings capture journal-relatedness, which leads to the clustering of related articles, which share, in varying degree, the common subject.
-In this figure, we can see that the publisher Wiley is more active in the right part of the spectrum than the left.
+In this Figure, we can see that the publisher Wiley is more active in the right part of the spectrum than the left.
 We can further see that Nature is far to the center, as we would expect a generic journal to be, but it is on the biology/medicine side of the center (indicated by the position of Cell and Pharmaceutical Research).\\
@@
 In the plot we can see that the original embedding-clustering, as provided by the k-means algorithm, is relatively well preserved, most groups stay clustered together.
-The interactive version shows that the clusterings, as seen on all four figures, are subject based.
+The interactive version shows that the clusterings, as seen on all four Figures, are subject based.
 Journals concerning the same subjects are correctly clustered together, and the journals in between topic clusters are also positioned at logical positions.

### 2018-07-03 Thesis/Parts/Research_results/Research_results.tex
new thesis version

@@
 Figures~\ref{figure:titleDistribution} \&~\ref{figure:abstractDistribution} show the distributions of the ranks for each set.
-The figures plot the summed amount of articles against the ranks on a logarithmic scale.
+The Figures plot the summed amount of articles against the ranks on a logarithmic scale.
 Figure~\ref{figure:titleDistribution} shows the rank distribution for the titles, Figure~\ref{figure:abstractDistribution} shows this for the ranks based on the abstract.
-These graphs give a detailed view of the ranks presented in their respective figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks}.
-The Y-axis of the two figures show the fraction of the total number of articles.
+These graphs give a detailed view of the ranks presented in their respective Figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks}.
+The Y-axis of the two Figures show the fraction of the total number of articles.
 Due to this, all sets will move towards one.
@@
 The X-axis plots the ranks of the articles.
-These ranks are the ranks of each individual article in our validation set, in contrast to figure~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} which show average and median ranks.
+These ranks are the ranks of each individual article in our validation set, in contrast to Figure~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} which show average and median ranks.
 \begin{figure}[hbt]
@@
 These scores are calculated on journal level, and are averaged per set.
-Figure~\ref{figure:f1Title} shows the F1 score for the title and figure~\ref{figure:f1Abstract} shows the scores for the abstract.
+Figure~\ref{figure:f1Title} shows the F1 score for the title and Figure~\ref{figure:f1Abstract} shows the scores for the abstract.
 These scores indicate the performance of the sets on absolute hits/top-1.
 We show the precision and recall scores since they vary between sets that have similar F1-scores (i.e.
-figure~\ref{figure:f1Title}, tfidf\_5k\_5k \& tfidf\_embedding
+Figure~\ref{figure:f1Title}, tfidf\_5k\_5k \& tfidf\_embedding
 \begin{figure}[hbt]
@@
 It furthermore shows the absolute hit percentage of the title and the abstracts, this is the percentage of articles that have the journals from which they were taken at rank 0, meaning that the journal has the closest embedding.
-The table furthermore shows the median rank and the median abstract rank, as visualized in figures \ref{figure:titleRanks} \&~\ref{figure:abstractRanks}.\\
+The table furthermore shows the median rank and the median abstract rank, as visualized in Figures \ref{figure:titleRanks} \&~\ref{figure:abstractRanks}.\\
 \begin{table}[hbt]
@@
 \subheader{Journal relatedness plot}
-We created two seperate journal plot, figures~\ref{figure:titlePlotNormal} \&~\ref{figure:titlePlotGrouped} show the title based embeddings, and figures~\ref{figure:abstractPlotNormal} \&~\ref{figure:abstractPlotGrouped} show the abstract based embeddings.
+We created two seperate journal plot, Figures~\ref{figure:titlePlotNormal} \&~\ref{figure:titlePlotGrouped} show the title based embeddings, and Figures~\ref{figure:abstractPlotNormal} \&~\ref{figure:abstractPlotGrouped} show the abstract based embeddings.
 Figures~\ref{figure:titlePlotNormal} \&~\ref{figure:abstractPlotNormal} show the two dimensional plots of the journal embeddings.
@@
 The k-means algorithm ran on the 300-dimensional vectors, while the plot shows the 2-dimensional vectors.
-In the title-based figures (\ref{figure:titlePlotNormal} \&~\ref{figure:titlePlotGrouped}) the journals \textit{PNAS} and \textit{Cell} overlap each others labels on the bottom right side of the graph.
-In the abstract-based figures (\ref{figure:abstractPlotNormal} \&~\ref{figure:abstractPlotGrouped}) the journals \textit{PNAS} and \textit{Nature} overlap each others label on the bottom right side of the graph.
+In the title-based Figures (\ref{figure:titlePlotNormal} \&~\ref{figure:titlePlotGrouped}) the journals \textit{PNAS} and \textit{Cell} overlap each others labels on the bottom right side of the graph.
+In the abstract-based Figures (\ref{figure:abstractPlotNormal} \&~\ref{figure:abstractPlotGrouped}) the journals \textit{PNAS} and \textit{Nature} overlap each others label on the bottom right side of the graph.
 The digital versions of these plots can be found at:~\url{https://goo.gl/nCGMcu} (title-based) and~\url{https://goo.gl/LwYP6k} (abstract-based).
-The usage of this digital version is advised, since this interactive plot enables zooming and adjusting plot settings, which can give a broader insight into the results than the presented figures.
-Although the presented figures give sufficient insight for the purpose of this thesis.
+The usage of this digital version is advised, since this interactive plot enables zooming and adjusting plot settings, which can give a broader insight into the results than the presented Figures.
+Although the presented Figures give sufficient insight for the purpose of this thesis.
 \begin{landscape}

### 2018-07-03 Thesis/Parts/Background/Background.tex
fb niels

@@
 To be able to do this, the search engine must know which texts are related.
-\\\\This can be achieved with, and without neural networks, a traditional technique which does not use a neural network is TF-IDF, shot for Term Frequency - Inverted Document Frequency.
+\\\\Interpreting which texts are related can be achieved with, and without neural networks, a traditional technique which does not use a neural network is TF-IDF, shot for Term Frequency - Inverted Document Frequency.
 Techniques that use a neural network are newer, these are (among others) Word2Vec, Paragraph Vectors and GloVe.
@@
 This error information is used to improve the values of the layers.
-The values in the layers are only changed at training time; high-quality training data is therefore essential for neural networks.
-Neural networks can be applied to many different tasks, as long as there is sufficient training data available.
+The values in the layers are only changed at training time; high-quality (training) data is therefore essential for neural networks.
+Neural networks can be applied to many different tasks, as long as there is sufficient data available to create a training and validation set.
 The training is the process of iteratively adjusting multiplication matrices or vectors to achieve the optimal result.
@@
 \subsubheader{Word2Vec}
-Word2vec word embeddings are created using a neural network, Word2vec learns word embeddings via maximizing the log conditional probability of the word given the context word(s) occurring within a fixed-sized window.
+Word2vec word embeddings are created using a neural network, Word2Vec learns word embeddings via maximizing the log conditional probability of the word given the context word(s) occurring within a fixed-sized window.
 Therefore the learned embeddings contain useful knowledge about word co-occurrence\cite{nalisnick2016improving}.
@@
 \subheader{General and Domain specific}
-Since the word embeddings are created form a given text, these embeddings are bound to the text.
+Since the word embeddings are created from a given text, these embeddings are bound to the text.
 All meaning embedded in the word embedding is derived from the original text.
@@
 \caption{Illustration of generic texts and domain specific texts. Our research focusses on the green-marked area.}\label{figure:domainPlot}
+\subheader{Domain-specific \& in-domain}
+We defined domain specific earlier, a related term to this is "in-domain".
+The term domain-specific refers to a specific domain, I.E.
+biology or chemistry.
+In-domain refers to a relation between texts, this means that an article on biology is an in-domain text of another article on biology, but not on an article on chemistry.
+This means that two domain-specific texts do not necessarily share their domain, while an text A which is an in-domain text for text B means that text A and B share the same domain.
 \end{figure}

### 2018-07-03 Thesis/Parts/Data/Data.tex
fb niels

@@
 This shows the relation between the word occurrences rank and the actual occurrences.
-This kind of word-occurrences distribution holds for many texts, including the writings of William Shakespeare and scientific texts and novels\cite{thurner2015understanding}.
+This kind of word-occurrences distribution holds for many texts, including the writings of William Shakespeare, scientific texts and novels\cite{thurner2015understanding}.
 The word occurrences in our corpus also follow the pattern of a Pareto distribution as described by~\citet{wiegand2018word}.
@@
 We use the $80\%$ set as the training set for the journal representations, and the $20\%$ set as the validation set for the journal representations.
-This split is based on a random number given to article each record, ensuring that all set have the same (random) training and validation set.
+This split is based on a random number given to each article, ensuring that all set have the same (random) training and validation set.
 \subheader{Create journal embeddings}

### 2018-07-03 Thesis/Parts/Discussion/Discussion.tex
fb niels

@@
 The top-performing embedding, TF-IDF weighted embedding, uses 3.13 GB, the top performing TF-IDF, 10K/10K uses 11.61 GB, which is 270.93\% of the storage size needed for the embedding.
-The closest TF-IDF configuration we used was 1K/1K, which uses 5.13 GB (as displayed in Figure~\ref{figure:tfidfPerformance}).
+The closest TF-IDF configuration (based on memory usage) we used was 1K/1K, which uses 5.13 GB (as displayed in Figure~\ref{figure:tfidfPerformance}).
 This TF-IDF set has a median title rank of 183 and a median abstract rank of 44.
@@
 \subheader{Improvements}
-This research shows that even tough the embeddings can capture and preserve relatedness, TF-IDF is able to outperform the embeddings on the abstracts.
+This research shows that even though the embeddings can capture and preserve relatedness, TF-IDF is able to outperform the embeddings on the abstracts.
 Earlier research already proposed improvements to the word embeddings.

### 2018-07-03 Thesis/Parts/Future_work/Future_work.tex
fb niels

@@
 \subheader{Intelligent cutting}
-An interesting improvement to enhance the word embeddings with could be a smarter way to remove noise, based on word embeddings.
+An interesting improvement to enhance the word embeddings with, could be a smarter way to remove noise, based on word embeddings.
 This might be achieved by analyzing the word embedding spectrum before normalization, and to then cut the center of the vector space out.

### 2018-07-03 Thesis/Parts/Motivation/Motivation.tex
fb niels

@@
 \subheader{In-domain embeddings and validation}
-In earlier research concerning domain specific articles,  \citet{Truong2017Thesis} found that in-domain training of the word embeddings can improve the process of document clustering.
+In earlier research concerning domain specific articles,~\citet{Truong2017Thesis} found that in-domain training of the word embeddings can improve the process of document clustering.
 The usage of in-domain data is more important than the number of training examples and the model architecture.

### 2018-07-04 Thesis/Parts/Data/Data.tex
File cleanup

@@
 \hline
-Metric\footnote{As defined and provided by the SciPy library} & Median title rank & Average title rank & Median abstract rank & Average abstract rank  \\
+Metric\footnotemark & Median title rank & Average title rank & Median abstract rank & Average abstract rank  \\
 \hline
@@
 \end{table}
+\footnotetext{As defined and provided by the SciPy library} 
 These results show high similarity between cosine-based metrics (Cosine \& Correlation) and euclidean based metrics (Euclidean, Seuclidean \& Sqeuclidean).

### 2018-07-05 Thesis/Parts/Background/Background.tex
temp_update

@@
 It is to be noted that the word embeddings are only able to represent word relatedness to the other words trained in the same run.
-Due to the random initialization of the initial values of the layers in the neural networks, neural networks do not produce every run the same results.
+Due to the random initialization of the initial values of the layers in the neural networks, they do not produce the same result every run.
 Therefore, word embeddings from different runs of the same neural network cannot be compared.
@@
 However, they will have the same relationship to other words trained in their respective runs.} which can capture both the semantic and syntactic information\cite{mikolov2013distributed}.
-In the case of a word embeddings, the embeddings represent the words.
+In the case of word embeddings, the embeddings represent the words.
 These embeddings are created using machine learning models, which do not have the need for human interaction~\cite{lai2016generate}, they are so-called \textit{unsupervised learning algorithms}.
 Once trained, the embeddings can also be used to construct embeddings for collections of texts.
-For example, a word embedding can be used to create a sentence, paragraph, document or corpus embeddings.
+For example, word embeddings can be used to create sentence, paragraph, document or corpus embeddings.
 The usage of word embeddings has improved various Natural Language Processing areas such as named entity recognition, part-of-speech tagging, parsing, and semantic role labelling~\citet{luong2013better}.
@@
 Labeled data is data that is in some way marked so that the correct answer can be derived from it, while this is not possible with unlabelled data.
-The validation tasks can be divided into two groups, extrinsic evaluation, ones that use word embeddings as input for a downstream task and Intrinsic evaluation, which directly tests the relationships of the word embedding themselves.
+The validation tasks can be divided into two groups, Extrinsic evaluation; these are the ones that use word embeddings as input for a downstream task; and Intrinsic evaluation; which directly tests the relationships of the word embeddings themselves.
 \citet{schnabel2015evaluation} note that the extrinsic evaluation may not be consistent with intrinsic evaluations since the performance on downstream tasks is not consistent across tasks.
@@
 Because of this, embeddings can be "Domain-specific" meaning that it only knows words (or a specific word) in a certain context.
-This becomes most clear when faced with words that can have different meanings in different contexts.
+This becomes most clear when faced with words that can have different a meaning in different contexts.
 For this research, we categorize the embeddings into two categories, generic embeddings and domain-specific embeddings.
@@
 We defined domain specific earlier, a related term to this is "in-domain".
-The term domain-specific refers to a specific domain, I.E.
+The term domain-specific refers to a specific domain, i.e.
 biology or chemistry.

### 2018-07-05 Thesis/Parts/Data/Data.tex
temp_update

@@
 \subheader{Corpus}
-The dataset we used for this research consists of articles published in 2017 which have been published in a journal that has, in 2017, atleast 150 publications.
+The dataset we used for this research consists of articles published in 2017 which have been published in journals that have, in 2017, atleast 150 publications.
 This results in a total dataset of $1.391.543$ articles from $3.759$ journals.
@@
 \hline
- & Total count & Unique count & Average length \\
+ & Total count & Unique count & Average length\footnotemark \\
 \hline\hline
-Title words & $18.822.399$ & $939.665$ & 13,53  \\
+Title words & $18.822.399$ & $939.665$ & 14  \\
 \hline
-Title tokens & $14.742.192$ & $230.805$ & 10,64 \\
+Title tokens & $14.742.192$ & $230.805$ & 11 \\
 \hline\hline
-Abstract words & $264.653.020$ & $5.853.077$  & 190,19  \\
+Abstract words & $264.653.020$ & $5.853.077$  & 190  \\
 \hline
-Abstract tokens & $171.474.473$ & $738.961$ & 123,71 \\
+Abstract tokens & $171.474.473$ & $738.961$ & 124 \\
 \hline\hline
-Total words & $283.475.419$ & $6.209.769$  & 203,71 \\
+Total words & $283.475.419$ & $6.209.769$  & 204 \\
 \hline
-Total tokens & $186.962.354$ & $763.475$ & 134,36 \\
+Total tokens & $186.962.354$ & $763.475$ & 134 \\
 \hline
@@
 \end{table}
+\footnotetext{Rounded}
 \clearpage

### 2018-07-05 Thesis/Parts/Data/Data.tex
updates

--- 2018-07-04 Thesis/Parts/Data/Data.tex
@@
 \subsubsubheader{Default embedding}
-The default embedding is created form the pre-trained word embeddings; no modifications have been applied to this set. We refer to this set in the Figures as \textbf{embedding}.
+The default embedding is created form the pre-trained word embeddings; no modifications have been applied to this set. We refer to this set in the figures as \textbf{embedding}.
 \subsubsubheader{TF-IDF weighted embedding}
@@
 Since we take a sum of all words, the Term Frequency is embedded as the raw count of each word.
-We will refer to this embedding in the Figures as \textbf{tfidf\_embedding}.
+We will refer to this embedding in the figures as \textbf{tfidf\_embedding}.
 \subsubsubheader{10K TF-IDF embedding}
@@
 This set was created to see if the limitation to 10.000 tokens reduces the amount of noise, increasing the performance.
-We will refer to this embedding in the Figures as the \textbf{10k\_embedding}.
+We will refer to this embedding in the figures as the \textbf{10k\_embedding}.
 \subsubsubheader{5K TF-IDF embedding}
@@
 This set was created to limit the number of tokens more aggressively, and with that, cancel out more noise.
-We will refer to this embedding in the Figures as \textbf{5k\_embedding}.
+We will refer to this embedding in the figures as \textbf{5k\_embedding}.
 \subsubsubheader{1K-6K TF-IDF embedding}
@@
 This cut results in a set of 5.000 tokens, which allows us to compare it to the 5K TF-IDF set.
-We will refer to this embedding in the Figures as \textbf{1k\_6k\_embedding}.
+We will refer to this embedding in the figures as \textbf{1k\_6k\_embedding}.
 We refer to the \textbf{10k\_embedding}, \textbf{5k\_embedding} and the \textbf{1k\_6k\_embedding} as the \textbf{limited TF-IDF embeddings}, because these embedding use TF-IDF weighing, and have been limited in their vocabulary due to the cut-off's.
@@
 This means that the set with a 10.000 vocabulary size and a 10.000 hash bucket size will be denoted as "10K/10K".
-We will refer to the TF-IDF configurations in our Figures as "tfidf\_vocabulary size\_hash bucket size".
+We will refer to the TF-IDF configurations in our figures as "tfidf\_vocabulary size\_hash bucket size".
 \begin{figure}[hbt]
@@
 This plot shows that, while the required storage size stagnate, the performance on title also quickly stagnates, together with the performance on the abstracts.
-Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to.
+The stagnation of the storage size is likely due to the fact that the terms which are added to the higher vocabulary sets occur less often than the other words (the cut-off is based on word occurrence, descending).Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to.
 Since these configurations can be kept in memory (storage size) while it is not likely that larger sets will give much improvement.
@@
 \subheader{Research environment}
-The research will be done in a python-databricks environment, which uses spark, a library that offers tools to work with big-data.
+The research has been done in a python-databricks environment, which used Spark, a library that offers tools to work with big-data.
 \citet{armbrust2015spark} state that Spark SQL lets programmers leverage the benefits of relational processing and lets SQL users call complex analytic libraries in Spark.
@@
 \subsubheader{Distance metrics}
-To calculate the distance between to vectors, cosine similarity is commonly used.
-We validated the quality of cosine similarity as a distance metrics by comparing it to other similarity matrices available in the SciPy\footnote{\url{https://www.scipy.org/}} library, which we used to calculate the distances.
+To calculate the distance between two vectors, cosine similarity is commonly used.
+We validated the quality of cosine similarity as a distance metric by comparing it to other similarity matrices available in the SciPy\footnote{\url{https://www.scipy.org/}} library, which we used to calculate the distances.
 We calculate the similarities based on the normalized embeddings, and compared the distance metrics based on the default embedding set.
@@
 This median rank differs from the average, since the median is not influenced by a single value.
-If the median is 20, it does not matter if an article is 25 of 250, it does matter however if an articles is 19 or 21.
+If the median is 20, it does not matter if an article rank is 25 of 250, it does matter however if an articles is 19 or 21.
 For the average this is not the case, the average is influenced by single articles.
-Therefore it does not represents the "normal/typical" article but it represents the exact average of all articles in the validation set, which is changed when an article changed from 25 to 250.\\
+Therefore, it does not represents the "normal/typical" article but it represents the exact average of all articles in the validation set, which is changed when an article changed from 25 to 250.\\
 We use the median rank to indicate at which rank the typical article would be ranked, based on its title and abstract.
@@
 We also calculate the average score for the title and abstract of all articles.
-This gives us four scores: median title rank, median abstract rank, average title rank \& average abstract rank.\\
+This gives us four scores: \textbf{median title rank, median abstract rank, average title rank \& average abstract rank.}\\
 \subsubheader{Rank distribution}

### 2018-07-05 Thesis/Parts/Future_work/Future_work.tex

@@
 \header{Future work}
-This research focussed on the quality of word embeddings on academic texts.
+This research focused on the quality of word embeddings on academic texts.
 To do this, we used both a comparison to TF-IDF and a visualization of the word embeddings.
@@
 In a situation were there is no categorization data available, like in our research, a k-means algorithm should suffice for categorization.
-The goal is to have multiple separate vector spaces, for this is does not matter if the "domains" are well-interpretable or make sense to humans.
+The goal is to have multiple separate vector spaces, for this it does not matter if the "domains" are well-interpretable or make sense to humans.
 \end{document}

### 2018-07-05 Thesis/Parts/Research_results/Research_results.tex

@@
 \header{Research results}
-In this chapter the results of our research will be presented with only the required explanation of the results. These results will be discussed in Chapter 7: Discussion.
+In this chapter the results of our research will be presented with only the required explanation of the results. These results will be discussed in Chapter 6: Discussion.
 \subheader{Ranking}
@@
 \subheader{F1-Score}
-Figures~\ref{figure:f1Title} \&~\ref{figure:f1Abstract} show the precision, recall and f1 scores.
+Figures~\ref{figure:f1Title} \&~\ref{figure:f1Abstract} show the precision, recall and F1 scores.
 These scores are calculated on journal level, and are averaged per set.
@@
 Table~\ref{table:memoryUsage} shows the total memory usage of each set for the \textit{Validation set}, indicating their storage costs in gigabytes\footnote{1024 based}.
-It furthermore shows the absolute hit percentage of the title and the abstracts, this is the percentage of articles that have the journals from which they were taken at rank 0, meaning that the journal has the closest embedding.
-The table furthermore shows the median rank and the median abstract rank, as visualized in Figures \ref{figure:titleRanks} \&~\ref{figure:abstractRanks}.\\
+It furthermore shows the absolute hit percentage of the title and the abstracts, this is the percentage of articles that their source\footnote{Journal from which the article was taken} journal as first result in the ranking.
+The table furthermore shows the median rank and the median abstract rank, as visualized in Figures \ref{figure:titleRanks} \&~\ref{figure:abstractRanks}.
+Thus, this table gives an overview of the memory usage of the sets, combined with their performance on the ranking task.\\
 \begin{table}[hbt]

### 2018-07-05 Thesis/Parts/Conclusion/Conclusion.tex
re-read updates

@@
 The TF-IDF alternatives give better results than the embeddings based on abstracts.
-The performance of the embeddings has been improved by weighting them with the TF-IDF values on the word level, although this improvement cannot be seen as significant on our dataset.
+The performance of the embeddings has been improved by weighing them with the TF-IDF values on the word level, although this improvement cannot be seen as significant on our dataset.
 This improved embedding set results in a median rank decrease of 8 on the titles and a median rank increase of 8 on the abstract, compared to the best performing TF-IDF alternative.

### 2018-07-05 Thesis/Parts/Data/Data.tex
re-read updates

@@
 This plot shows that, while the required storage size stagnate, the performance on title also quickly stagnates, together with the performance on the abstracts.
-The stagnation of the storage size is likely due to the fact that the terms which are added to the higher vocabulary sets occur less often than the other words (the cut-off is based on word occurrence, descending).Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to.
+The stagnation of the storage size is likely due to the fact that the terms which are added to the higher vocabulary sets occur less often than the other words (the cut-off is based on word occurrence, descending).
+Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to.
 Since these configurations can be kept in memory (storage size) while it is not likely that larger sets will give much improvement.
@@
 To calculate the distance between two vectors, cosine similarity is commonly used.
-We validated the quality of cosine similarity as a distance metric by comparing it to other similarity matrices available in the SciPy\footnote{\url{https://www.scipy.org/}} library, which we used to calculate the distances.
+We validated the quality of cosine similarity as a distance metric by comparing it to other similarity matrices available in the SciPy library\footnote{\url{https://www.scipy.org/}}, which we used to calculate the distances.
 We calculate the similarities based on the normalized embeddings, and compared the distance metrics based on the default embedding set.
@@
 This median rank differs from the average, since the median is not influenced by a single value.
-If the median is 20, it does not matter if an article rank is 25 of 250, it does matter however if an articles is 19 or 21.
+If the median is 20, it does not matter if an article rank is 25 of 250, it does matter however if an article rank is 19 or 21.
 For the average this is not the case, the average is influenced by single articles.
-Therefore, it does not represents the "normal/typical" article but it represents the exact average of all articles in the validation set, which is changed when an article changed from 25 to 250.\\
+Therefore, it does not represents the "normal/typical" article but it represents the exact average of all articles in the validation set, which is changed when an article rank is changed from 25 to 250.\\
 We use the median rank to indicate at which rank the typical article would be ranked, based on its title and abstract.
@@
 These groupings are created on the 300-dimensional vectors and are visualized in the plot using colors.
-We use the k-means groupings due to the lack of subject-based grouping values in our dataset.
+We use the k-means groupings due to the lack of subject-based grouping values in our dataset, for this research we used 8 groups.
 \end{document}

### 2018-07-05 Thesis/Parts/Background/Background.tex
updates
pc-re-read

--- 2018-07-03 Thesis/Parts/Background/Background.tex
@@
 Neural networks rely on training to create optimal values for these layers.
-Finding these optimal values is done iteratively, via a process known as "back-propogation".
-Back-propogation is done by starting at the output layer of the Neural Network and tracing error in the output back through the layers.
+Finding these optimal values is done iteratively, via a process known as "back-propagation".
+Back-propagation is done by starting at the output layer of the Neural Network and tracking error in the output back through the layers.
 This error information is used to improve the values of the layers.
-The values in the layers are only changed at training time; high-quality (training) data is therefore essential for neural networks.
+The values in the layers are only changed at training time; high-quality (training) data is, therefore, essential for neural networks.
 Neural networks can be applied to many different tasks, as long as there is sufficient data available to create a training and validation set.
-The training is the process of iteratively adjusting multiplication matrices or vectors to achieve the optimal result.
-Which is the result that is as close as possible to the given output for all input and output sets, without under performing on other sets\footnote{Having only good results for the training/validation set is know as overfitting.
-This means that the layer-values are fine-tuned to only perform (extremely) well on one set, while under performing on others}.\\Neural Networks are used, in the creation of word embeddings, to either predict words that may occur around a given word or predict a word given words that surround it.
+The training is the process of iteratively adjusting multiplication matrices or vectors values to achieve the optimal result.
+Which is the result that is as close as possible to the given output for all input and output sets, without underperforming on other sets\footnote{Having only good results for the training/validation set is known as overfitting.
+This means that the layer-values are fine-tuned to only perform (extremely) well on one set while underperforming on others}.\\Neural Networks are used, in the creation of word embeddings, to either predict words that may occur around a given word or predict a word given words that surround it.
 For example, given the sentence\\
@@
 In the case of a word embeddings, the embeddings represent the words.
-These embeddings are created using machine learning models, which do not have the need for human interaction~\cite{lai2016generate}, they are so-called \textit{unsupervised learning algorithms}.
+These embeddings are created using machine learning models, which do not need human interaction~\cite{lai2016generate}, they are so-called \textit{unsupervised learning algorithms}.
 Once trained, the embeddings can also be used to construct embeddings for collections of texts.
@@
 It furthermore reduces the number of words which occur rarely.
-Due to the nature of TF-IDF, these rare words have a high score, cancelling out other more frequent words, while rarely occurring in the corpus.
+Due to the nature of TF-IDF, these rare words have a high score, canceling out other more frequent words, while rarely occurring in the corpus.
 \vspace{0.3in}\begin{table}[hbt]
@@
 Embeddings that perform well on one task do not have to perform well on another task.
-As a result, findings about the performance of an embedding method are limited to the task on which they are tested.
+As a result, the findings of the performance of an embedding method are limited to the task on which they are tested.
 Their results cannot be generalized to state that the embeddings are overall "performing well".
@@
 Figure~\ref{figure:domainPlot} illustrates our corpus, marked in green, in comparison to the Wikipedia corpus, marked in blue.
-Our corpus is a collection of domain specific texts, written in academic language.
+Our corpus is a collection of domain-specific texts, written in academic language.
 A set that would be more specific would only focus on the individual domains or sub-domains.
@@
 \includegraphics[width=6.5in]{Plots/domain_specification_graph}
-\caption{Illustration of generic texts and domain specific texts. Our research focusses on the green-marked area.}\label{figure:domainPlot}
+\caption{Illustration of generic texts and domain-specific texts. Our research focusses on the green-marked area.}\label{figure:domainPlot}
 \subheader{Domain-specific \& in-domain}
-We defined domain specific earlier, a related term to this is "in-domain".
+We defined domain-specific earlier, a related term to this is "in-domain".
 The term domain-specific refers to a specific domain, I.E.
@@
 In-domain refers to a relation between texts, this means that an article on biology is an in-domain text of another article on biology, but not on an article on chemistry.
-This means that two domain-specific texts do not necessarily share their domain, while an text A which is an in-domain text for text B means that text A and B share the same domain.
+This means that two domain-specific texts do not necessarily share their domain, while a text A which is an in-domain text for text B means that text A and B share the same domain.
 \end{figure}

### 2018-07-05 Thesis/Parts/Data/Data.tex
pc-re-read

--- 2018-07-05 Thesis/Parts/Data/Data.tex
@@
 \includegraphics[width=6.5in]{Plots/word_occurrences}
-\caption{Word and token occurrences. The word counts pattern resembles a Pareto distribution, the tokenization reduced the amount of high frequency words.}\label{figure:wordTokenOccurrence}
+\caption{Word and token occurrences. The word counts pattern resembles a Pareto distribution; the tokenization reduced the number of high-frequency words.}\label{figure:wordTokenOccurrence}
 \end{figure}
@@
 \subheader{Datasets}
-For this researched we used a (pre-made) tokenized dataset, created from the earlier described corpus, which reduces the total amount of words by 34\% (see table~\ref{table:corpusSize}).
+For this research we used a (pre-made) tokenized dataset, created from the earlier described corpus, which reduces the total amount of words by 34\% (see table~\ref{table:corpusSize}).
 From this tokenized set, we created the embeddings and the TF-IDF feature vectors.
@@
 Journal embeddings are created by taking the average of all normalized article embeddings.
-We use the average to combine multiple embeddings into one, because we determine the meaning of a larger text as the average meaning of all components.
+We use the average to combine multiple embeddings into one because we determine the meaning of a larger text as the average meaning of all components.
 Since this meaning is represented as an embedding, we can average the embeddings to create the "average meaning".
@@
 Figure~\ref{figure:tfidfPerformance} shows the performance of title and abstract as median rank, and Figure~\ref{figure:tfidfMemory} shows the storage size in gigabyte, of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations.
-This plot shows that, while the required storage size stagnate, the performance on title also quickly stagnates, together with the performance on the abstracts.
-The stagnation of the storage size is likely due to the fact that the terms which are added to the higher vocabulary sets occur less often than the other words (the cut-off is based on word occurrence, descending).Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to.
+This plot shows that, while the required storage size stagnates, the performance on title also quickly stagnates, together with the performance on the abstracts.
+The stagnation of the storage size is likely due to the fact that the terms which are added to the higher vocabulary sets occur less often than the other words (the cut-off is based on word occurrence, descending).
+Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to.
 Since these configurations can be kept in memory (storage size) while it is not likely that larger sets will give much improvement.
@@
 The paper further states that Spark SQL makes it significantly simpler and more efficient to write data pipelines that mix relational and procedural processing while offering substantial speedups over previous SQL-on-Spark engines.\\
-We procesessed the TF-IDF sets and the embedding sets via the same pipeline, using their common vector properties. This ensures comparable results, the pipeline is set-up as follows:
+We processed the TF-IDF sets and the embedding sets via the same pipeline, using their common vector properties. This ensures comparable results, the pipeline is set-up as follows:
 \begin{enumerate}

### 2018-07-05 Thesis/Parts/Data/Data.tex

--- 2018-07-05 Thesis/Parts/Data/Data.tex
@@
 Figure~\ref{figure:tfidfPerformance} shows the performance of title and abstract as median rank, and Figure~\ref{figure:tfidfMemory} shows the storage size in gigabyte, of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations.
-This plot shows that, while the required storage size stagnate, the performance on title also quickly stagnates, together with the performance on the abstracts.
+This plot shows that, while the required storage size stagnates, the performance on title also quickly stagnates, together with the performance on the abstracts.
 The stagnation of the storage size is likely due to the fact that the terms which are added to the higher vocabulary sets occur less often than the other words (the cut-off is based on word occurrence, descending).

### 2018-07-05 Thesis/Parts/Discussion/Discussion.tex
Publishing note updates, all_latex added for Jenny
pc-re-read

@@
 \header{Discussion}
-In this chapter, the results presented in Chapter 6: Results will be discussed. No additional results will be presented in this chapter.
+In this chapter, we discuss the results presented in Chapter 5: Results. No additional results will be presented in this chapter.
 \subheader{Result analysis}
@@
 Which is significantly worse than the embedding, which also uses less memory.
-This indicates that the embeddings are able to store the relatedness information more densely than the TF-IDF feature vectors can store the worod occurrence information.
+This indicates that the embeddings are able to store the relatedness information more densely than the TF-IDF feature vectors can store the word occurrence information.
 
@@
 Still, we would expect an improvement by using paragraph vectors since the classification task if fundamentally the same, only on a much larger scale, which complicates the task due to the "grey areas"  between categories.
-These are the area's in which the classification algorithm is "in doubt" and could reasonably assing the article to both journals.
-The number of these grey areas increases given more categories.
+These are the area's in which the classification algorithm is "in doubt" and could reasonably assign the article to both journals.
+The number of these grey areas increase given more categories.
 \citet{pennington2014glove} showed that the GloVe model outperforms the CBOW model, which is used in this research, on a word analogy task.
@@
 Even though we have an F1 score, which indicates performance on the absolute hits, our results are not comparable to other works due to the number of categories, and their overlapping subjects\footnote{As visualized in the journal embedding plots and discussed earlier}.
-
 \end{document}

### 2018-07-05 Thesis/Parts/Research_results/Research_results.tex

@@
 Table~\ref{table:memoryUsage} shows the total memory usage of each set for the \textit{Validation set}, indicating their storage costs in gigabytes\footnote{1024 based}.
-It furthermore shows the absolute hit percentage of the title and the abstracts, this is the percentage of articles that their source\footnote{Journal from which the article was taken} journal as first result in the ranking.
+It furthermore shows the absolute hit percentage of the title and the abstracts, this is the percentage of articles that have their source\footnote{Journal from which the article was taken} journal as the first result in the ranking.
 The table furthermore shows the median rank and the median abstract rank, as visualized in Figures \ref{figure:titleRanks} \&~\ref{figure:abstractRanks}.

### 2018-07-05 Thesis/Parts/Background/Background.tex
Final thesis Version

@@
 \\\\The most practical example of this is a search engine.
-Given one or more search words the search engine will attempt to find relevant information.
+Given one or more search words (a query) the search engine will attempt to find relevant information.
 For example, an online search for "Information Retrieval" (initial piece of information) will give you a list of results (relevant information).
@@
 \\\\Interpreting which texts are related can be achieved with, and without neural networks, a traditional technique which does not use a neural network is TF-IDF, shot for Term Frequency - Inverted Document Frequency.
-Techniques that use a neural network are newer, these are (among others) Word2Vec, Paragraph Vectors and GloVe.
+Techniques that use a neural network are (among others) Word2Vec, Paragraph Vectors and GloVe.
 
@@
 It can also predict the word "jumps", given the context words (the, quick, brown, fox, over, the, lazy, dog).
-This result in a matrix, a vector per word which is referred to as a word embedding.
+This results in a matrix, a vector per word which is referred to as a word embedding.
 This embedding indicates "word relatedness" which, as mentioned earlier enables association (thus retrieval) with related(relevant) texts.
 It is to be noted that the word embeddings are only able to represent word relatedness to the other words trained in the same run.
-Due to the random initialization of the initial values of the layers in the neural networks, neural networks do not produce every run the same results.
+Due to the random initialization of the initial values of the layers in the neural networks, they do not produce the same result every run.
 Therefore, word embeddings from different runs of the same neural network cannot be compared.
@@
 There are multiple input/output possibilities for the neural network, best known are Skip-gram and the Continuous Bag-of-Words model (CBOW).
-The Skip-gram model takes a target word as input and outputs the predicted output words, while CBOW takes the context words as input and outputs the predicted target word\cite{nalisnick2016improving, pennington2014glove}.
+The Skip-gram model takes a target word as input and outputs the predicted context words, while CBOW takes the context words as input and outputs the predicted target word\cite{nalisnick2016improving, pennington2014glove}.
 This is illustrated in Figure~\ref{figure:word2vecModels}, in this Figure, $v(w)$ represents the target word, and $v(w...)$ represent the context words.
@@
 They furthermore found that larger corpus' lead to better quality embeddings, but that the domain in which the embeddings are trained has more influence on this than the corpus size.
-
 \subheader{Validation methods}
@@
 \citet{schnabel2015evaluation} note that the extrinsic evaluation may not be consistent with intrinsic evaluations since the performance on downstream tasks is not consistent across tasks.
-
+\clearpage
 \begin{jumpin}
@@
 \end{jumpin}
+\clearpage
 \subheader{General and Domain specific}
@@
 All meaning embedded in the word embedding is derived from the original text.
-Because of this, embeddings can be "Domain-specific" meaning that it only knows words (or a specific word) in a certain context.
+Because of this, embeddings can be "domain-specific" meaning that it only knows words (or a specific word) in a certain context.
 This becomes most clear when faced with words that can have different meanings in different contexts.
@@
 The generic embeddings are trained on a collection of texts that use common English and contains a wide variety of topics.
-The domain-specific embeddings are trained on a collection of texts that uses jargon English (i.e., domain-specific terms) or is limited to a small number of topics.
+The domain-specific embeddings are trained on a collection of texts that uses jargon English (i.e., domain-specific terminology) or is limited to a small number of topics.
 Given these terms, we regard the embeddings trained on the Wikipedia corpus\cite{lai2016generate, pennington2014glove, dai2015document, lau2016empirical, schnabel2015evaluation} as general, since Wikipedia uses common English and spans a wide range of topics.

### 2018-07-05 Thesis/Parts/Data/Data.tex
Final thesis Version

@@
 \subheader{Corpus}
-The dataset we used for this research consists of articles published in 2017 which have been published in journals that have, in 2017, atleast 150 publications.
+The dataset we used for this research consists of articles published in 2017 which have been published in journals that have, in 2017, at least 150 publications.
 This results in a total dataset of $1.391.543$ articles from $3.759$ journals.
@@
 These transformations reduced our dataset by 34\%, resulting in a tokenized set of $186.962.354$ tokens.
+\clearpage
 \subsubheader{Embedding}
@@
 These embeddings have a vector dimension of 300, which is an industry default.
-They have been trained on the entire Elsevier corpus, not limited to the subset we used for this research.
+They have been trained on the entire Elsevier corpus (titles and abstracts respectively), not limited to the subset we used for this research.
 To create higher-level embeddings, we average all component embeddings.
@@
 From our training set we create the journal embeddings, which are created for most sets\footnote{see paragraph datasets} by averaging the article embeddings or feature vectors.
+\clearpage
 \subheader{Categorize validation articles}
@@
 Because of this, we will use the cosine-similarity as the distance metric, which will make our results better comparable with other work.
-\clearpage
 \subheader{Performance measurement}
@@
 We also calculate the average score for the title and abstract of all articles.
-This gives us four scores: \textbf{median title rank, median abstract rank, average title rank \& average abstract rank.}\\
+This gives us four scores: \textbf{median title rank, median abstract rank, average title rank \& average abstract rank.}
+\clearpage
 \subsubheader{Rank distribution}

### 2018-07-05 Thesis/Parts/Future_work/Future_work.tex
re-read updates
Final thesis Version

@@
 They state that the global/hyperparameters of the various methods mainly cause the difference in performance.
-In this research, we have not looked at the comparison between various models and (hyper) parameters.
+In this research, we did not look at the comparison between various models and (hyper) parameters.
 We instead used a standard configuration, to focus more on the actual performance of the embeddings, instead of the best possible performance.
@@
 \subheader{Intelligent cutting}
-An interesting improvement to enhance the word embeddings with, could be a smarter way to remove noise, based on word embeddings.
+An interesting improvement to enhance the word embeddings with, what could be a smarter way to remove noise, based on word embeddings.
 This might be achieved by analyzing the word embedding spectrum before normalization, and to then cut the center of the vector space out.
@@
 To cope with the problem of articles that do have an abstract but no title, or vice versa, it would be interesting to see what the quality of the embeddings would be if both texts were combined into one text.
-This should be possible since title and abstract per article share a common topic.
+This should be possible since the title and the abstract per article share a common topic.
 We would expect that the common text would have the quality of the abstract, which is according to our findings the part that is best used for the embeddings and TF-IDF.
@@
 Furthermore, it would be interesting to see which words would be selected and if these words represent the given sentence as an "extracted version" which would still be interpretable by humans.
-
+\clearpage
 \subheader{Pre-categorization}
@@
 This knowledge could be used to pre-process given texts, creating a two-step search.
-This method would first categorize the given article into a field, and then search in the limited set of journals for the best fit.
+This method would first categorize the given article into a field and then search in the limited set of journals for the best fit.
 This has two advantages: A) we predict the field of the article, giving additional information to a user and B) once an article is inside a certain domain, ambiguous words between domains (i.e.
 cloud for computer science and meteorology) are eliminated, since these embeddings do not have to be trained with the other embeddings, which create ambiguity.
-A possible downside of this approach is the need for data within each domain, since the embeddings are created on two levels, cross-domain for domain categorization and in-domain for journal categorization.
+A possible downside of this approach is the need for data within each domain since the embeddings are created on two levels, cross-domain for domain categorization and in-domain for journal categorization.
 The lack of articles within one domain could hurt the embeddings since they need training data to make accurate predictions.
-In a situation were there is no categorization data available, like in our research, a k-means algorithm should suffice for categorization.
-The goal is to have multiple separate vector spaces, for this it does not matter if the "domains" are well-interpretable or make sense to humans.
+In a situation where there is no categorization data available, like in our research, a k-means algorithm should suffice for categorization.
+The goal is to have multiple separate vector spaces, for this, it does not matter if the "domains" are well-interpretable or make sense to humans.
 \end{document}

### 2018-07-05 Thesis/Parts/Motivation/Motivation.tex
Final thesis Version

@@
 This A) indicates the embedding quality for categorization tasks and B) contrasts the performance of embeddings to the performance of the more traditional TF-IDF approach.
-To ensure the quality of the embeddings for our research, we reuse the embeddings created in the research of \citet{Truong2017Thesis}.
+To ensure the quality of the embeddings for our research, we reuse the embeddings created in the research of~\citet{Truong2017Thesis}.
 \begin{jumpin}
-    \textbf{RQ. 1} Have classical word-embeddings a higher accuracy for academic texts than TF-IDF for article classification?\\
+    \textbf{RQ. 1} Have word-embeddings a higher accuracy for academic texts than TF-IDF for article classification?\\
     \begin{adjustwidth}{0.3in}{}
@@
 \end{jumpin}
+\clearpage
 \subsubheader{Methodology}

### 2018-07-17 Thesis/Parts/Research_results/Research_results.tex
defence feedback

--- 2018-07-05 Thesis/Parts/Research_results/Research_results.tex
@@
 \header{Research results}
-In this chapter the results of our research will be presented with only the required explanation of the results. These results will be discussed in Chapter 6: Discussion.
+In this chapter the results of our research are presented; the detailed discussion on the meaning and implications of these results is presented in Chapter 6: Discussion.
 \subheader{Ranking}
@@
 \subheader{Rank distribution}
-Figures~\ref{figure:titleDistribution} \&~\ref{figure:abstractDistribution} show the distributions of the ranks for each set.
+Figures~\ref{figure:titleDistribution} and~\ref{figure:abstractDistribution} show the distributions of the ranks for each set.
 The Figures plot the summed amount of articles against the ranks on a logarithmic scale.
 Figure~\ref{figure:titleDistribution} shows the rank distribution for the titles, Figure~\ref{figure:abstractDistribution} shows this for the ranks based on the abstract.
-These graphs give a detailed view of the ranks presented in their respective Figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks}.
-The Y-axis of the two Figures show the fraction of the total number of articles.
-Due to this, all sets will move towards one.
-When one is hit, the graph stagnates since there are no more articles that can be added once the value reaches one.
+These graphs give a detailed view of the ranks presented in their respective Figures~\ref{figure:titleRanks} and~\ref{figure:abstractRanks}.
+The Y-axis of the two Figures shows the fraction of the total number of articles.
+Due to this, all sets will have a maximum of 1.
+When 1 is hit, the graph stagnates since the dataset has reached the maximum fraction.
 The X-axis plots the ranks of the articles.
-These ranks are the ranks of each individual article in our validation set, in contrast to Figure~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} which show average and median ranks.
+These ranks are the ranks of each individual article in our validation set, in contrast to Figure~\ref{figure:titleRanks} and~\ref{figure:abstractRanks} which show average and median ranks.
 \begin{figure}[hbt]
@@
 \subheader{F1-Score}
-Figures~\ref{figure:f1Title} \&~\ref{figure:f1Abstract} show the precision, recall and F1 scores.
+Figures~\ref{figure:f1Title} and~\ref{figure:f1Abstract} show the precision, recall and F1 scores.
 These scores are calculated on journal level, and are averaged per set.
@@
 We show the precision and recall scores since they vary between sets that have similar F1-scores (i.e.
-Figure~\ref{figure:f1Title}, tfidf\_5k\_5k \& tfidf\_embedding
+Figure~\ref{figure:f1Title}, tfidf\_5k\_5k and tfidf\_embedding
 \begin{figure}[hbt]
@@
 Table~\ref{table:memoryUsage} shows the total memory usage of each set for the \textit{Validation set}, indicating their storage costs in gigabytes\footnote{1024 based}.
-It furthermore shows the absolute hit percentage of the title and the abstracts, this is the percentage of articles that their source\footnote{Journal from which the article was taken} journal as first result in the ranking.
-The table furthermore shows the median rank and the median abstract rank, as visualized in Figures \ref{figure:titleRanks} \&~\ref{figure:abstractRanks}.
+It furthermore shows the absolute hit percentage of the title and the abstracts, i.e.
+the percentage of articles that have their source\footnote{Journal from which the article was taken} journal as the first result in the ranking.
+The table furthermore shows the median rank and the median abstract rank, as visualized in Figures \ref{figure:titleRanks} and~\ref{figure:abstractRanks}.
 Thus, this table gives an overview of the memory usage of the sets, combined with their performance on the ranking task.\\
@@
 \begin{center}
-\begin{tabular}{|l|l|l|l|l|}
+\begin{tabular}{|l|r|r|r|r|}
 \hline
@@
 \subheader{Journal relatedness plot}
-We created two seperate journal plot, Figures~\ref{figure:titlePlotNormal} \&~\ref{figure:titlePlotGrouped} show the title based embeddings, and Figures~\ref{figure:abstractPlotNormal} \&~\ref{figure:abstractPlotGrouped} show the abstract based embeddings.
-Figures~\ref{figure:titlePlotNormal} \&~\ref{figure:abstractPlotNormal} show the two dimensional plots of the journal embeddings.
+We created four seperate journal plots, Figures~\ref{figure:titlePlotNormal} and~\ref{figure:titlePlotGrouped} show the title based embeddings, and Figures~\ref{figure:abstractPlotNormal} and~\ref{figure:abstractPlotGrouped} show the abstract based embeddings.
+Figures~\ref{figure:titlePlotNormal} and~\ref{figure:abstractPlotNormal} show the two dimensional plots of the journal embeddings.
 The journals are color-marked by publisher.
@@
 The grey points are other or not-specified publishers.
-Figures~\ref{figure:titlePlotGrouped} \&~\ref{figure:abstractPlotGrouped} show the journal embeddings grouped by a k-means algorithm, creating 8 groups.
-The bottom right shows the names of the journals closest to the center of the group.
-While most names state the topic of the research field, some do not.
+Figures~\ref{figure:titlePlotGrouped} and~\ref{figure:abstractPlotGrouped} show the journal embeddings grouped by a k-means algorithm, creating 8 groups.
+The bottom right of the plot shows the names of the journals closest to the center of the group.
+While most names state the topic of the research field, two do not.
 These are \textit{RSC Advances}: chemical sciences, and \textit{Symmetry}:  research on symmetry phenomena wherever they occur in mathematical or scientific studies.
@@
 The digital versions of these plots can be found at:~\url{https://goo.gl/nCGMcu} (title-based) and~\url{https://goo.gl/LwYP6k} (abstract-based).
-The usage of this digital version is advised, since this interactive plot enables zooming and adjusting plot settings, which can give a broader insight into the results than the presented Figures.
-Although the presented Figures give sufficient insight for the purpose of this thesis.
+The usage of this digital version is advised, since this interactive plot enables zooming and adjusting plot settings, which can give a broader insight into the results than the presented figures.
+Although the presented figures give sufficient insight for the purpose of this thesis.
 \begin{landscape}

### 2018-07-17 Thesis/Parts/Abstract/Abstract.tex
Publishing note updates, all_latex added for Jenny
updates

--- 2018-06-27 Thesis/Parts/Abstract/Abstract.tex
@@
 This research focusses on the quality and application of word embeddings on domain-specific texts, concerning a large corpus of 1.391.543 scientific articles which have been published in 2017.
+We validate the word embeddings using a categorization task to match articles to journals.
+We furthermore create a 2-dimensional visualization of the word embeddings on journal level, to visualize journal relatedness.\\
+\vspace*{\fill}
+\\
+We aim to have this thesis published in the proceedings of the \textit{ECIR} (\url{http://ecir2019.org/}). \textit{Submission deadline: 9-10-2018}.
 \end{document}

### 2018-07-17 Thesis/Parts/Data/Data.tex

@@
 \subheader{Corpus}
-The dataset we used for this research consists of articles published in 2017 which have been published in journals that have, in 2017, at least 150 publications.
-This results in a total dataset of $1.391.543$ articles from $3.759$ journals.
+The dataset we used for this research consists of articles published in 2017 which have been published in journals that have (in 2017) at least 150 publications.
+This selection leads to a dataset of $1.391.543$ articles from $3.759$ journals.
 Details about the corpus can be found in table~\ref{table:corpusSize}.
@@
 \begin{center}
-\begin{tabular}{|l|c|c|c|}
+\begin{tabular}{|l|r|r|r|}
 \hline
@@
 \hline
-Total tokens & $186.962.354$ & $763.475$ & 134 \\
+Total tokens & $186.962.354$ & $763.475$ & 135 \\
 \hline
@@
 \citet{wiegand2018word} state that the Pareto distribution offers a good fit to the word occurrences in natural language.
-Their models show that, due to the additional parameters in the Pareto-III\footnote{The pareto distribution is a distribution in which recognizable by a long "tail" of low values and a quick and short ascend to the top values.
+Their work shows that, due to the additional parameters in the Pareto-III\footnote{The pareto distribution is a distribution in which recognizable by a long "tail" of low values and a quick and short ascend to the top values.
 More information: \url{https://en.wikipedia.org/wiki/Pareto_distribution}.}, the tail of the data fits better with the model than the Zipf\footnote{Distribution similar to the Pareto distribution, see: \url{https://en.wikipedia.org/wiki/Zipf\%27s_law}} model.
-This shows the relation between the word occurrences rank and the actual occurrences.
+The fit to the Pareto distribution shows the relation between the word occurrences rank and the actual occurrences.
 This kind of word-occurrences distribution holds for many texts, including the writings of William Shakespeare, scientific texts and novels\cite{thurner2015understanding}.
 The word occurrences in our corpus also follow the pattern of a Pareto distribution as described by~\citet{wiegand2018word}.
-Our distribution is visualized in Figure~\ref{figure:wordTokenOccurrence}, which displays the occurrences of the first 500 tokens of the corpus.
+Our word and token distribution is visualized in Figure~\ref{figure:wordTokenOccurrence}, which displays the occurrences of the first 500 tokens of the corpus.
 \FloatBarrier
@@
 \includegraphics[width=6.5in]{Plots/word_occurrences}
-\caption{Word and token occurrences. The word counts pattern resembles a Pareto distribution; the tokenization reduced the number of high-frequency words.}\label{figure:wordTokenOccurrence}
+\caption{Word and token occurrences.
+The word counts pattern resembles a Pareto distribution; the tokenization reduced the number of high-frequency words.
+The y-axis shows the number of occurances for each word, the x-axis shows the occurence rank of the word, meaning the position of the word in a list sorted on word occurance.}\label{figure:wordTokenOccurrence}
 \end{figure}
@@
 \subsubheader{Tokenization}
-The following steps have been applied to the words to create a tokenized set:
+The following steps have been applied to the words from the text to create a tokenized set:
 \begin{enumerate}
@@
 To create higher-level embeddings, we average all component embeddings.
-Thus, to create article embeddings, we take the average of all normalized word embeddings for that article.
+Thus, to create article embeddings (higher level), we take the average of all normalized word embeddings (component) for that article.
 Journal embeddings are created by taking the average of all normalized article embeddings.
-We use the average to combine multiple embeddings into one because we determine the meaning of a larger text as the average meaning of all components.
-Since this meaning is represented as an embedding, we can average the embeddings to create the "average meaning".
+We use the average to combine multiple embeddings into one because we determine the meaning of a larger text as the "average meaning" of all components.
+Since this meaning is represented as an embedding, we can average the embeddings to create the average meaning.
 We have used multiple embedding optimizations for this research.
 \subsubsubheader{Default embedding}
-The default embedding is created form the pre-trained word embeddings; no modifications have been applied to this set. We refer to this set in the figures as \textbf{embedding}.
+The default embedding is created from the pre-trained word embeddings; no modifications have been applied to this set. We refer to this set in the figures as \textbf{embedding}.
 \subsubsubheader{TF-IDF weighted embedding}
-The TF-IDF weighted embedding set, referred to as TF-IDF embedding, are the default word embeddings weighted with a TF-IDF score per word.\\
+The TF-IDF weighted embedding sets, referred to as TF-IDF embedding, are the default word embeddings weighted with a TF-IDF score per word.\\
 The TF-IDF is calculated with a raw token count, and a smoothed inverted document frequency, calculated as follows:\\
@@
 Where $|A|$ is the total count of articles and $|A_t|$ is the count of articles containing term t.
-The articles embeddings are a normalized summation of each word vector multiplied by it TF-IDF value.
+The article embeddings are a normalized summation of each word vector multiplied by it TF-IDF value.
 Since we take a sum of all words, the Term Frequency is embedded as the raw count of each word.
@@
 The 10K embedding set is generated similarity to the TF-IDF embedding, this version only uses the 10.000 most common tokens, reducing the number of tokens it uses.
-This set was created to see if the limitation to 10.000 tokens reduces the amount of noise, increasing the performance.
+This set was created to see if the limitation to 10.000 tokens reduces the amount of noise\footnote{Noise in this context are rare word}, increasing the performance.
 We will refer to this embedding in the figures as the \textbf{10k\_embedding}.
@@
 The 1K-6K TF-IDF embedding is the TF-IDF embedding limited to the top 6.000 most common words, without the top 1.000 most common words.
-The rationale for this is that common words will occur in many articles, creating noise, by cutting off the top 1.000 and cutting off everything below 6.000 we tried to reduce the noise by filtering common words.
+The rationale for this cutting is that common words will occur in many articles, creating noise, by cutting off the top 1.000 and cutting off everything below 6.000 we tried to reduce the noise by filtering common words.
 This cut results in a set of 5.000 tokens, which allows us to compare it to the 5K TF-IDF set.
@@
 \subsubheader{TF-IDF}
-To create the TF-IDF feature vectors, we used the TF-IDF model and a hasher from PySparks MlLib library.
+To create the TF-IDF feature vectors, we used the TF-IDF model and a hasher from PySparks MlLib library\footnote{\url{http://spark.apache.org/docs/2.0.0/api/python/pyspark.mllib.html}.}.
 The TF-IDF feature vectors are created by hashing the tokens with the hasher, which has a set hash bucket size.
-These hashed values are passed on to the TF-IDF model, resulting in a feature vector which vector dimensions equal the number of hash buckets.
+These hashed values are passed on to the TF-IDF model, resulting in a feature vector.
+The vector dimensions of the feature vector equal the number of hash buckets.
 To limit the computational and storage expenses and to reduce noise by rare words, we limit our vocabulary size.
@@
 \includegraphics[width=5in]{Plots/tfidf_selection_plot_performance}
-\caption{TF-IDF performance on title and abstract}\label{figure:tfidfPerformance}
+\caption{TF-IDF performance on title and abstract.}\label{figure:tfidfPerformance}
 \end{figure}
@@
 \includegraphics[width=5in]{Plots/tfidf_selection_plot_memory}
-\caption{TF-IDF memory usage for title and abstract combined}\label{figure:tfidfMemory}
+\caption{TF-IDF memory usage for title and abstract combined.}\footnote{We combined the memory usage of the titles and abstracts since the titles and abstract are created together and share their feature vector size.}\label{figure:tfidfMemory}
 \end{figure}
 \FloatBarrier
-Figure~\ref{figure:tfidfPerformance} shows the performance of title and abstract as median rank, and Figure~\ref{figure:tfidfMemory} shows the storage size in gigabyte, of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations.
-This plot shows that, while the required storage size stagnates, the performance on title also quickly stagnates, together with the performance on the abstracts.
-The stagnation of the storage size is likely due to the fact that the terms which are added to the higher vocabulary sets occur less often than the other words (the cut-off is based on word occurrence, descending).
-Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to.
-Since these configurations can be kept in memory (storage size) while it is not likely that larger sets will give much improvement.
+Figure~\ref{figure:tfidfPerformance} shows the performance of TF-IDF on title and abstract as median rank, and Figure~\ref{figure:tfidfMemory} shows the storage size in gigabyte, of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations.
+This plot shows that, while the required storage size stagnates, the performance on title also quickly stagnates; the performance of the abstracts show similar behaviour.
+The stagnation of the storage size is likely due to the fact that the terms which are added to the larger vocabulary sets occur less often than the other words (the cut-off is based on word occurrence, descending).
+Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to because these configurations can be kept in memory (storage size) while it is not likely that larger sets will give much improvement.
 The TF-IDF features are created on article level.
@@
 \subheader{Research environment}
-The research has been done in a python-databricks environment, which used Spark, a library that offers tools to work with big-data.
+The research has been done in a python-databricks environment, which used Spark SQL, a library that offers tools to work with big-data.
 \citet{armbrust2015spark} state that Spark SQL lets programmers leverage the benefits of relational processing and lets SQL users call complex analytic libraries in Spark.
-This allows for much tighter integration between relational and procedural processing.
+This allows for much tighter integration of relational and procedural processing.
 The paper further states that Spark SQL makes it significantly simpler and more efficient to write data pipelines that mix relational and procedural processing while offering substantial speedups over previous SQL-on-Spark engines.\\
-We processed the TF-IDF sets and the embedding sets via the same pipeline, using their common vector properties. This ensures comparable results, the pipeline is set-up as follows:
+\subheader{Data processing}
+We processed the TF-IDF sets and the embedding sets \footnote{See Chapter 3.2 Datasets.} via the same pipeline, using their common vector properties.
+Using the same pipeline ensures comparable results.
+The pipeline is set-up as follows:
 \begin{enumerate}
@@
 \end{enumerate}
-
 \subheader{Create training and validation set}
@@
 We use the $80\%$ set as the training set for the journal representations, and the $20\%$ set as the validation set for the journal representations.
-This split is based on a random number given to each article, ensuring that all set have the same (random) training and validation set.
+This split is based on a random number given to each article, ensuring that all datasets (i.e.
+tfidf\_10k\_10k, embedding) have the same (random) training and validation set.
 \subheader{Create journal embeddings}
-From our training set we create the journal embeddings, which are created for most sets\footnote{see paragraph datasets} by averaging the article embeddings or feature vectors.
+From our training set we create the journal embeddings, which are created for most sets\footnote{See chapter 3.2 Datasets.} by averaging the article embeddings or feature vectors.
 \clearpage
@@
 We also do this for the abstract of the article and the abstract of each journal.
-During this process we keep track of:
+During this process we record of:
 \begin{itemize}
@@
 To calculate the distance between two vectors, cosine similarity is commonly used.
-We validated the quality of cosine similarity as a distance metric by comparing it to other similarity matrices available in the SciPy library\footnote{\url{https://www.scipy.org/}}, which we used to calculate the distances.
+We validated the quality of cosine similarity as a distance metric by comparing it to other similarity metrics available in the SciPy library\footnote{\url{https://www.scipy.org/}}.
 We calculate the similarities based on the normalized embeddings, and compared the distance metrics based on the default embedding set.
@@
 \begin{table}[hbt]
-\begin{tabular}{|l|l|l|l|l|}
+\begin{tabular}{|l|r|r|r|r|}
 \hline
@@
 These results show high similarity between cosine-based metrics (Cosine \& Correlation) and euclidean based metrics (Euclidean, Seuclidean \& Sqeuclidean).
-This similarity is expected, since the cosine and euclidean distances should yield the same results on normalized sets.
-The results show that some enhancement on the euclidean algorithm result in slightly improved results, although not significant.
-Also the Cityblock metric yields results close to the Cosine metric, it has a slightly worse performance, which is also not significant.
-Because of this, we will use the cosine-similarity as the distance metric, which will make our results better comparable with other work.
+This similarity is expected, since the cosine and euclidean distances should yield the same results on normalized sets\footnote{See: \url{https://en.wikipedia.org/wiki/Cosine_similarity\#Properties}.}.
+The results show that some enhancement on the euclidean algorithm (Seuclidean) result in slightly improved results, although not significant.
+Also the Cityblock metric yields results close to the Cosine metric, only having a slightly worse performance, which is also not significant.
+Because of this, we will use the cosine-similarity as the distance metric, which will make our results easier to compare with other work, since the cosine-similarity is a commonly used similarity measure.
 \subheader{Performance measurement}
@@
 \subsubheader{F1-score}
-We define the positive \& negative metrics as follows:\\
+For our matching algorithm, we classify the results as follows:
 \begin{jumpin}
@@
 \end{jumpin}
-We used these metrics to calculate the Recall, Precision \& F1 as follows:\\
+With these definitions, we calculate the Recall, Precision \& F1 as follows:\\
 \begin{jumpin}
-$Recall = \dfrac{True Positive}{True Positive + False Negative}$\vspace{0.1in}\\
-$Precision = \dfrac{True Positive}{True Positive + False Positive}$\vspace{0.1in}\\
-$F1 = \dfrac{2 * Precision * Recall}{Precision + Recall}$
+$Recall = \dfrac{|True Positive|}{|True Positive| + |False Negative|}$\vspace{0.1in}\\
+$Precision = \dfrac{|True Positive|}{|True Positive| + |False Positive|}$\vspace{0.1in}\\
+$F1 = \dfrac{2 * Precision * Recall}{Precision + Recall|}$
 \end{jumpin}
+here we denote the amount of articles in a class as $|class|$.
 \subsubheader{Median \& average rank}
-The median rank of a journal indicates the point where 50\% of all articles are to the left of a virtual line and 50\% are to the right of this line.
+A dataset rank is calculated using the ranks of all article in that dataset.
+The median rank of a dataset indicates the point where 50\% of all articles are to the left of a virtual line and 50\% are to the right of this line.
 The median rank therefore indicates the position of the "normal/typical" article.
 This median rank differs from the average, since the median is not influenced by a single value.
-If the median is 20, it does not matter if an article rank is 25 of 250, it does matter however if an article rank is 19 or 21.
-For the average this is not the case, the average is influenced by single articles.
-Therefore, it does not represents the "normal/typical" article but it represents the exact average of all articles in the validation set, which is changed when an article rank is changed from 25 to 250.\\
+If the median is 20, it does not matter if an article rank is 25 or 250, it does matter however if an article rank is 19 or 21.
+For the average rank this is not the case, the average rank is influenced by single articles.
+Therefore, it does not represents the "normal/typical" article but it represents the exact average rank of all articles in the validation set, which is changed when an article rank is changed from 25 to 250.\\
 We use the median rank to indicate at which rank the typical article would be ranked, based on its title and abstract.
-We do this by taking the median of the respective rank from each article.
-This gives us an indication of the behaviour of the articles in our validation set.
 We also calculate the average score for the title and abstract of all articles.
@@
 \subsubheader{Rank distribution}
-To further analyse the ranking results, we plot the rank distribution to get an indication of the ranking-landscape.
+To further analyse the ranking results, we plot the article rank distribution to get an indication of the ranking-landscape.
 \subsubheader{Two-dimensional plot}
-To create a plot, we transformed the 300-dimensional journal vectors into 2-dimensional vectors using TSNE based on pca\footnote{Principal component analysis}.
+To create a plot, we transformed the 300-dimensional journal vectors into 2-dimensional vectors using TSNE based on PCA\footnote{Principal component analysis}.
 These 2-dimensional vectors, representing the x \& y coordinate, can then be drawn in a plot.
@@
 These groupings are created on the 300-dimensional vectors and are visualized in the plot using colors.
-We use the k-means groupings due to the lack of subject-based grouping values in our dataset, for this research we used 8 groups.
+We use the k-means groupings due to the lack of subject-based grouping values in our dataset, for this research we used 2, 5, 8, 10, 20, 25, 30, 35 and 40 as the amount of groups.
+We included only the plots of 8 groups, because we find this plot the most informative.
+All group amounts can be seen in the digital version of the plots.
 \end{document}

### 2018-07-20 Paper/Parts/Abstract/Abstract.tex
paper setup

--- 2018-07-17 Thesis/Parts/Abstract/Abstract.tex
@@
 We validate the word embeddings using a categorization task to match articles to journals.
-We furthermore create a 2-dimensional visualization of the word embeddings on journal level, to visualize journal relatedness.\\
-\vspace*{\fill}
-\\
-We aim to have this thesis published in the proceedings of the \textit{ECIR} (\url{http://ecir2019.org/}). \textit{Submission deadline: 9-10-2018}.
+We furthermore create a 2-dimensional visualization of the word embeddings on journal level, to visualize journal relatedness.
 \end{document}

### 2018-07-20 Paper/Parts/Background/Background.tex
paper setup

--- 2018-07-05 Thesis/Parts/Background/Background.tex
@@
 \header{Introduction and Background}
+\subheader{Academic texts}
+Academic texts are, among others, academic articles.
+These articles are focussed on specific domains, such as biology, economy and computer science, because of this, we call the articles "domain-specific" meaning that they give information about a topic in a domain (i.e.
+biology).
+Articles are published in journals, which are collections of articles which share a common topic, i.e.
+a specific field inside the biology domain.
+Our research focusses on the academic articles and journals not limited to a specific domain.
 \subheader{Information retrieval}
-Information Retrieval(IR)is the activity of gathering relevant information, given another initial piece of information. 
-\\\\The most practical example of this is a search engine.
+Information Retrieval (IR) is the activity of gathering relevant information, starting from an initial piece of information. 
+\\\\The most practical example of IR is a search engine.
 Given one or more search words (a query) the search engine will attempt to find relevant information.
-For example, an online search for "Information Retrieval" (initial piece of information) will give you a list of results (relevant information).
-To be able to do this, the search engine must know which texts are related.
+For example, an online search for "Information Retrieval" (initial piece of information) will return a list of results (relevant information).
+To be able to do return a list of results, the search engine must know which texts are related.
 \\\\Interpreting which texts are related can be achieved with, and without neural networks, a traditional technique which does not use a neural network is TF-IDF, shot for Term Frequency - Inverted Document Frequency.
@@
 
-\subheader{Neural Network}
-A complete in-depth background into neural networks is beyond the scope of this thesis, therefore we will only describe the simplified working of a neural network and its basic application in IR.
-Neural Networks are multi-layered computational software, based on matrix transformations, which tries to map input values to output values.
+\subheader{Neural Networks}
+A complete in-depth background into neural networks is beyond the scope of this thesis, therefore we will only describe the simplified working of neural networks and their basic application in IR.
+Neural Networks are mathematical modesl\cite{funahashi1989approximate}, which use matrix transformations, to map input values to output values.
 This mapping uses a pre-defined amount of layers that modify the values through matrix transformations.
@@
 Finding these optimal values is done iteratively, via a process known as "back-propagation".
-Back-propagation is done by starting at the output layer of the Neural Network and tracking error in the output back through the layers.
+Back-propagation is done by starting at the output layer of the neural network and tracking the error in the output back through the layers.
 This error information is used to improve the values of the layers.
-The values in the layers are only changed at training time; high-quality (training) data is, therefore, essential for neural networks.
-Neural networks can be applied to many different tasks, as long as there is sufficient data available to create a training and validation set.
-The training is the process of iteratively adjusting multiplication matrices or vectors values to achieve the optimal result.
-Which is the result that is as close as possible to the given output for all input and output sets, without underperforming on other sets\footnote{Having only good results for the training/validation set is known as overfitting.
-This means that the layer-values are fine-tuned to only perform (extremely) well on one set while underperforming on others}.\\Neural Networks are used, in the creation of word embeddings, to either predict words that may occur around a given word or predict a word given words that surround it.
+The values of the layers are only changed at training time; high-quality (training) data is, therefore, essential for neural networks\cite{Truong2017Thesis, lai2016generate}.
+Neural networks can be applied to many different tasks, as long as there is sufficient data available to create a training and validation sets.
+During the training process, one seeks to achieve the optimal results, i.e.
+the result that is as close as possible to the given output for all input and output sets, without underperforming on other sets\footnote{Having only good results for the training/validation set is known as overfitting.
+This means that the layer-values are fine-tuned to only perform (extremely) well on one set while underperforming on others.}.\\Neural Networks are used, in the creation of word embeddings, to either predict words that may occur around a given word or predict a word given words that surround it.
 For example, given the sentence\\
@@
 \end{center}
-the Neural Network can be trained to either predict the words around "jumps", which we refer to as context words (the, quick, brown, fox, over, the, lazy, dog).
-It can also predict the word "jumps", given the context words (the, quick, brown, fox, over, the, lazy, dog).
-This results in a matrix, a vector per word which is referred to as a word embedding.
+a neural network can be trained to either predict the words around "jumps", which we refer to as context words (the, quick, brown, fox, over, the, lazy, dog), or to predict the word "jumps", given the context words (the, quick, brown, fox, over, the, lazy, dog).
+The training process results in a matrix, which is transformed to a collection of vectors, each vector is associated to a word, these vectors are referred to as word embeddings.
 This embedding indicates "word relatedness" which, as mentioned earlier enables association (thus retrieval) with related(relevant) texts.
 It is to be noted that the word embeddings are only able to represent word relatedness to the other words trained in the same run.
-Due to the random initialization of the initial values of the layers in the neural networks, they do not produce the same result every run.
+Due to the random initialization of the initial values of the layers in  neural networks, the neural networks do not produce the same result every run.
 Therefore, word embeddings from different runs of the same neural network cannot be compared.
@@
 This means that the same word trained in two separate runs do not have to have the same embedding.
-However, they will have the same relationship to other words trained in their respective runs.} which can capture both the semantic and syntactic information\cite{mikolov2013distributed}.
-In the case of a word embeddings, the embeddings represent the words.
-These embeddings are created using machine learning models, which do not need human interaction~\cite{lai2016generate}, they are so-called \textit{unsupervised learning algorithms}.
+However, they will have the same relationship to other words trained in their respective runs.} which can capture both semantic and syntactic information\cite{mikolov2013distributed}.
+In the case of word embeddings, the embeddings represent the words.
+These embeddings can be\footnote{This depends on the method used to create the word embeddings, for this research, we used word embeddings trained by an unsupervised learing algorithm.} created using machine learning models, which do not need human interaction~\cite{lai2016generate}, they are so-called \textit{unsupervised learning algorithms}.
 Once trained, the embeddings can also be used to construct embeddings for collections of texts.
-For example, a word embedding can be used to create a sentence, paragraph, document or corpus embeddings.
-The usage of word embeddings has improved various Natural Language Processing areas such as named entity recognition, part-of-speech tagging, parsing, and semantic role labelling~\citet{luong2013better}.
+For example, a word embedding can be used to create sentence, paragraph, document or corpus embeddings.
+The usage of word embeddings has improved various Natural Language Processing areas such as named entity recognition, part-of-speech tagging, parsing, and semantic role labelling~\cite{luong2013better}.
+Embeddings can furthermore be used in search and recommendation.
+Potential application of the embeddings in the academic domain could be the improvement of search engines, text analysis to improve NLP tasks for academic texts, and journal recommendation for article publishing.
+The embeddings can furthermore be used to help researchers which are new to a field to explore the field by finding related articles or articles that are related to the field of expertise of the researcher and the new research field.
+Embeddings can also be visualized (see paragraph 1.6), this can give insight into the topics of popular journals, and can be used to indicate research subjects where there are few publications or journals.
 
@@
 To enable a computer to process text, for embedding creation or other tasks, the text has to be processed by an algorithm.
-In this research, we used embeddings created by Word2Vec and TF-IDF feature vectors.
+In this research, we used embeddings created by Word2Vec and feature vectors\footnote{Which do not require training (see subparagraph TF-IDF).} created using TF-IDF.
 \begin{jumpin}
 \subsubheader{Word2Vec}
-Word2vec word embeddings are created using a neural network, Word2Vec learns word embeddings via maximizing the log conditional probability of the word given the context word(s) occurring within a fixed-sized window.
-Therefore the learned embeddings contain useful knowledge about word co-occurrence\cite{nalisnick2016improving}.
-There are multiple input/output possibilities for the neural network, best known are Skip-gram and the Continuous Bag-of-Words model (CBOW).
+Word2vec word embeddings are created using a neural network, Word2Vec learns word embeddings via maximizing the probability of the word given the context word(s) occurring within a fixed-sized window, therefore the learned embeddings contain useful knowledge about word co-occurrence\cite{nalisnick2016improving} which indicates relatedness\cite{lai2016generate}.
+There are multiple input/output possibilities for the neural network.
+The best known are Skip-gram and the Continuous Bag-of-Words model (CBOW).
 The Skip-gram model takes a target word as input and outputs the predicted context words, while CBOW takes the context words as input and outputs the predicted target word\cite{nalisnick2016improving, pennington2014glove}.
-This is illustrated in Figure~\ref{figure:word2vecModels}, in this Figure, $v(w)$ represents the target word, and $v(w...)$ represent the context words.
-\citet{mikolov2013distributed}\cite{mikolov2013efficient} presented several extensions to the word2vec model that improve the quality of vector training and its speed, such as introducing Hierarchical Softmax, Negative Sampling and the subsampling of frequent words to the Skip-gram approach.
-Variations to the word2vec model have also been proposed, such as the doc2vec model described by \citet{lau2016empirical} which creates document embeddings instead of word embeddings.
+This is illustrated in Figure~\ref{figure:word2vecModels}, where, $v(w)$ represents the target word, and $v(w...)$ represent the context words.
+\citet{mikolov2013distributed}\cite{mikolov2013efficient} presented several extensions to the word2vec model that improve the quality of the embeddings and the training speed, such as introducing Hierarchical Softmax, Negative Sampling and the subsampling of frequent words to the Skip-gram approach.
+Variations to the word2vec model have also been proposed, such as the doc2vec model described by \citet{lau2016empirical} which creates document embeddings\footnote{Document embeddings are embeddings which capture the relatedness between documents.} instead of word embeddings.
+
+\begin{figure}[hbt]
 \begin{center}
-\begin{figure}[hbt]
 \includegraphics[width=4in]{Plots/Model-Architecture-of-CBOW-and-Skip-Gram.png}
@@
 The right side of the Figure illustrates the Skip-Gram Model, which takes the center word as input (left) and outputs the context words (right).}\label{figure:word2vecModels}
+\end{center}
+\end{figure}
+\begin{figure}[hbt]
+\begin{center}
+\includegraphics[width=4in]{Plots/training_window.png}
+\caption{Illustration of the training windows. Illustration created by \citet{trainingWindow}.}
+\end{center}
 \end{figure}
 \FloatBarrier
-\end{center}
 \subsubheader{Paragraph vectors}
@@
 This model captures the global corpus statistics.
-The model transforms the word co-occurrences of all words in the corpus to chances, it excludes all the zero values and uses that as initial input for the neural network.
-This model out-performs other models on word analogy, word similarity and entity recognition according to the findings by~\citet{pennington2014glove}.\\
+The model transforms the word co-occurrences of all words in the corpus to probabilities, it excludes all the zero probabilities and uses that as initial input for the neural network.
+This model outperforms other models on word analogy, word similarity and entity recognition according to the findings by~\citet{pennington2014glove}.\\
 
 \subsubheader{TF-IDF}
-Term Frequency * Inverted Document Frequency (TF-IDF) is a method that does not rely on a neural network and, therefore, does not require training.
+Term Frequency * Inverted Document Frequency (TF-IDF) is a method that does not rely on a neural network and does not require training.
 The TF-IDF score is the product of the term frequency in a text and the inverted document frequency of the same term in a corpus of texts.
-Both of which can be calculated in a variety of ways.
+Both of metrics, TF and IDF, can be calculated in a variety of ways.
 Table~\ref{table:TFIDFScore} shows an example of the TF-IDF calculation.
 The multiplication of the TF and IDF is referred to as the TF-IDF score.
-The text, provided to the algorithm, is analyzed on word occurrences on corpus and document level, this results in a score per word.
-This score can be converted to a feature vector, in which the indexes of this vector represent the words and the value is the TF-IDF score.
-The size of this feature vector can optionally be controlled by hashing the words in the text, which can then be reduced to a given size.
-If this is not applied, the size of the feature vector is equal to the number of unique words in the corpus, also known as the (corpus) vocabulary.
+The text, provided to the algorithm, is analyzed on word occurrences on corpus and document level, resulting in one score per word.
+These scores (the scores of all words) can be converted to a feature vector, in which the indexes represent the words and the value is the TF-IDF score for the word.
+The size of this feature vector can optionally be controlled by hashing the words in the text.
+If hashing is not applied, the size of the feature vector is equal to the number of unique words in the corpus, also known as the (corpus) vocabulary.
 The feature vectors produced by TF-IDF do not capture syntactic or semantic information about words, but capture information about word occurrences.
@@
 \begin{center}
-\begin{tabular}{|p{1in}|p{1in}|p{1in}|p{1.3in}|p{1in}|}
+\begin{tabular}{|p{1in}|R{1in}|R{1in}|R{1.3in}|R{1in}|}
 \hline
@@
 \end{jumpin}
-As \citet{lai2016generate} state in their paper "How to generate a good word embedding?", that all embedding methods rely on the same hypothesis, \textit{words that occur in similar contexts have similar meanings}.
-They furthermore found that larger corpus' lead to better quality embeddings, but that the domain in which the embeddings are trained has more influence on this than the corpus size.
+As \citet{lai2016generate} state in their paper "How to generate a good word embedding?", all embedding methods rely on the same hypothesis, \textit{words that occur in similar contexts have similar meanings}.
+They furthermore found that larger corpus lead to better quality embeddings, but that the domain in which the embeddings are trained has more influence on this than the corpus size.
 \subheader{Validation methods}
-The results produced by the previously mentioned techniques have to be validated to determine their quality (in usage).
-The quality of the results can be validated through various validation metrics, one of these is the F1 score\footnote{The F1 score combines the precision score and the recall score in a single metric}.
+The results produced by the previously mentioned techniques have to be validated to determine their quality (in use).
+The quality of the results can be validated through various metrics.
+One of these is the F1 score\footnote{The F1 score combines the precision score and the recall score in a single metric.}.
 The embeddings can furthermore be validated through their performance on tasks such as word analogy, word similarity, categorization and embedding visualization.
@@
 Labeled data is data that is in some way marked so that the correct answer can be derived from it, while this is not possible with unlabelled data.
-The validation tasks can be divided into two groups, extrinsic evaluation, ones that use word embeddings as input for a downstream task and Intrinsic evaluation, which directly tests the relationships of the word embedding themselves.
+The validation tasks can be divided into two groups: extrinsic evaluation, i.e.
+tasks that use word embeddings as input for a downstream task, and Intrinsic evaluation, which directly tests the relationships of the word embeddings.
 \citet{schnabel2015evaluation} note that the extrinsic evaluation may not be consistent with intrinsic evaluations since the performance on downstream tasks is not consistent across tasks.
@@
 \subsubheader{Word Analogy}
-Word analogy validation is based on a labelled validation set, containing word pairs of four that can be logically divided into two parts.
+Word analogy validation is based on a labelled validation set, containing word groups of four that can be logically divided into two parts.
 As Table~\ref{table:wordAnalogies} shows, each last word can be derived from the three words before.
@@
 \begin{center}
-\begin{tabular}{l l l l}
-Man & Women & King & Queen \\
+\begin{tabular}{|l|l||l|l|}
+\hline
+\textbf{Word 1} & \textbf{Word 2} & \textbf{Word 3} & \textbf{Word 4}\\
+\hline
+\hline
+Man & Woman & King & Queen \\
+\hline
 Athens & Greece & Oslo & Norway\\
-great & greater & tough & tougher
+\hline
+Great & Greater & Tough & Tougher\\
+\hline
 \end{tabular}
@@
 \end{table}\\
-Both this validation technique and the Word Similarity technique use vector distance calculations to validate the embeddings, this can therefore also be written as:
+Both this validation technique and the Word Similarity technique use vector distance calculations to validate the embeddings, the word group can therefore also be written as:
 \begin{displayquote}
-    X\textsubscript{King} - X\textsubscript{Man} $\approx$  X\textsubscript{Queen} - X\textsubscript{Women}
+    X\textsubscript{King} - X\textsubscript{Man} $\approx$  X\textsubscript{Queen} - X\textsubscript{Woman}
 \end{displayquote}
-This means that the resulting vector of embedding of "King" minus the embedding of "Men" is approximately the embedding of "Queen" minus the embedding of "Women".
-This resulting vector may, for example, be close to the vector representing "Monarch".
+This means that the resulting vector of embedding of "King" minus the embedding of "Men" is approximately the embedding of "Queen" minus the embedding of "Woman".
+The resulting vector of the subtraction may, for example, be close to the vector of the embedding for "Monarch".
 \subsubheader{Word Similarity}
 A method to test the quality of word embeddings is the word similarity test.
-For these test, the distance between the word embeddings (vectors) is measured and compared to similarity scores defined by humans.
+For this test, the distance between the word embeddings (vectors) is measured and compared to similarity scores defined by humans.
 Multiple non-domain specific validation sets are publicly available including the Rare-word dataset introduced in the paper "Better Word Representations with Recursive Neural Networks for Morphology" by \citet{luong2013better},
@@
 A classification validation method is a simple task which assigns a label to a text.
-\citet{lau2016empirical} used data from StackExchange and tried to determine if a pair was a duplicate.
-In their setup, the text was a pair of texts, and their categories were duplicate and non-duplicate.
+\citet{lau2016empirical} used text pairs from StackExchange and tried to determine if a pair was a duplicate.
+In their setup the categories were duplicate and non-duplicate.
 \citet{le2014distributed} used for their research a dataset of IMDB with 100,000 movie reviews.
 They validated their proposed paragraph vector model by determining whether a review was positive or negative.
-We will use the classification task for this research too, we will use journals (collection of articles) as classes, and the articles as items that need to be classified.
-We create a list, sorted on the similarity between article and journal, of journals for each article to get a measurable result from this.
-From this list we can extract, among other things, the position (rank) of the journal from which the article was taken.
+We will use the classification task for our research too, we will use journals (collection of articles) as classes, and the articles as items that need to be classified.
+We create a list, sorted on the similarity between article and journal, of journals for each article to get a measurable ranking result.
+From the resulting list we can extract, among other things, the position (rank) of the journal from which the article was taken.
 \subsubheader{Position Visualization}
-\citet{dai2015document} and \citet{hinton2003stochastic} mapped their word embeddings from a high dimensional vector to a two-dimensional vector to be able to display them in a scatter plot and applied colors to various categories.
+\citet{dai2015document} and \citet{hinton2003stochastic} mapped their word embeddings from a high dimensional vector to a two-dimensional vector to be able to display them in a scatter plot and apply colors to various categories.
 The advantage of this visualization is that a human can directly see the embedding distribution, and see if it is distributed in a way that seems logical.
@@
 Since the word embeddings are created from a given text, these embeddings are bound to the text.
-All meaning embedded in the word embedding is derived from the original text.
-Because of this, embeddings can be "domain-specific" meaning that it only knows words (or a specific word) in a certain context.
+All meaning embedded in the word embedding is derived from the original text, therefore embeddings can be "domain-specific" meaning that some words are only known in a certain context.
 This becomes most clear when faced with words that can have different meanings in different contexts.
@@
 \begin{figure}[hbt]
-\includegraphics[width=6.5in]{Plots/domain_specification_graph}
+\begin{center}
+\includegraphics[width=4.5in]{Plots/domain_specification_graph}
 \caption{Illustration of generic texts and domain-specific texts. Our research focusses on the green-marked area.}\label{figure:domainPlot}
+\end{center}
+\end{figure}
 \subheader{Domain-specific \& in-domain}
-We defined domain-specific earlier, a related term to this is "in-domain".
-The term domain-specific refers to a specific domain, I.E.
+In this paragraph, we will explain the meaning of the term "in-domain".
+The term domain-specific refers to a specific domain, i.e.
 biology or chemistry.
-In-domain refers to a relation between texts, this means that an article on biology is an in-domain text of another article on biology, but not on an article on chemistry.
+In-domain refers to a relation between texts, meaning that an article on biology is an in-domain text of another article on biology, but not on an article on chemistry.
 This means that two domain-specific texts do not necessarily share their domain, while a text A which is an in-domain text for text B means that text A and B share the same domain.
-\end{figure}
 \end{document}

### 2018-07-20 Paper/Parts/Conclusion/Conclusion.tex
paper setup

--- 2018-07-05 Thesis/Parts/Conclusion/Conclusion.tex
@@
 The TF-IDF alternatives give better results than the embeddings based on abstracts.
-The performance of the embeddings has been improved by weighing them with the TF-IDF values on the word level, although this improvement cannot be seen as significant on our dataset.
+The performance of the embeddings have been improved by weighing them with the TF-IDF values on the word level, although this improvement cannot be seen as significant on our dataset.
 This improved embedding set results in a median rank decrease of 8 on the titles and a median rank increase of 8 on the abstract, compared to the best performing TF-IDF alternative.
@@
 \begin{enumerate}
-\item{Article based embeddings perform better than TF-IDF on titles, small texts, which contain limited information}
-\item{TF-IDF performs better than article based embeddings on abstracts, larger texts, which contain more information}
+\item{Article based embeddings perform better than TF-IDF on titles, i.e. small texts which contain limited information}
+\item{TF-IDF performs better than article based embeddings on abstracts, i.e. larger texts which contain more information}
 \item{Embeddings give a significant decrease in memory usage compared to TF-IDF}

### 2018-07-20 Paper/Parts/Discussion/Discussion.tex
paper setup

--- 2018-07-05 Thesis/Parts/Discussion/Discussion.tex
@@
 \header{Discussion}
-In this chapter, we discuss the results presented in Chapter 5: Results. No additional results will be presented in this chapter.
-\subheader{Result analysis}
+\subheader{Results analysis}
 
 \subsubheader{Best performers}
-The data, as presented in Figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank on abstract and 3 median ranks on the titles.
-For the embeddings, the TF-IDF weighted embedding works better than the others, although it is not a significant improvement (1 rank on a set of more than 3.000) compared to the default embeddings, which 1 median rank higher on the abstracts, and equal on the titles.
+The data, as presented in Figures~\ref{figure:titleRanks} and~\ref{figure:abstractRanks} shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank on abstract and 3 median ranks on the titles.
+For the embeddings, the TF-IDF weighted embedding works better than the others, although it is not a significant improvement (1 rank on a set of more than 3.000) compared to the default embeddings, which is 1 median rank higher on the abstracts, and equal on the titles.
 
 \subsubheader{TF-IDF}
-The TF-IDF feature vectors outperform the embeddings on the abstract, while the embeddings outperform the TF-IDF feature vectors on the title.
-The main difference between the abstract \& title is that the title contains fewer tokens compared to the abstract (see Table~\ref{table:corpusSize}).
+The TF-IDF feature vectors outperform the embeddings on the abstracts, while the embeddings outperform the TF-IDF feature vectors on the titles.
+The main difference between the abstract and title is that the title contains fewer tokens compared to the abstract (see Table~\ref{table:corpusSize}).
 This means that the titles contain less information than the abstracts.
 Due to this, the TF-IDF method, which is purely based on word-occurrences \& counts has less information on the titles.
-The TF-IDF method works better on the abstract, which contain more tokens, which improves the differentiating the different abstract.
-The data furthermore shows that increasing the vocabulary size increases the performance of the TF-IDF, this means that none of the created cut-off's resulted in cutting off noise, the increasing size of the vocabulary only improved the performance in this case.
-It could be possible that at higher vocabulary sizes the cut-off would result in a sharper signal, we did not look into this further due to our findings that the TF-IDF performance stagnates (presented in Figure~\ref{figure:tfidfPerformance}).
+The TF-IDF method works better on the abstract, containing more tokens than the tile, thus improving the differentiating the different abstract.
+The data furthermore shows that increasing the vocabulary size increases the performance of the TF-IDF, meaning that none of the created cut-off's resulted in cutting off noise, the increasing size of the vocabulary only improved the performance on our data.
+It could be possible that at higher vocabulary sizes the cut-off would result in a sharper signal, but we did not investigate this further due to our findings that the TF-IDF performance stagnates (presented in Figure~\ref{figure:tfidfPerformance}).
 \clearpage
@@
 The limited TF-IDF embeddings all underperform, compared to the TF-IDF embedding (which does not have a limited vocabulary), on the median and average ranking.
-Indicating that the noise reduction is too much, and it removes meaningful words.
-If the noise reduction would be too low, we would only see a slight increase or none at all.
-However, the rank lowers, indicating the reduction in embedding quality due to missing words.
-This is in line with what we found with the TF-IDF results; higher vocabulary sizes give better performance.
+This result indicates that the noise reduction is too much, and it removes meaningful words.
+If the noise reduction would be too low, we would only see a slight increase of performance compared to the TF-IDF embedding, or none at all.
+However, the rank increases, indicating the reduction in embedding quality due to missing words.
+This is in line with what we found with the TF-IDF results: higher vocabulary sizes give better performance.
 \begin{jumpin}
 \subsubsubheader{Rank distribution}
-However, Figures~\ref{figure:titleDistribution} \&~\ref{figure:abstractDistribution} show that their rank distribution is different from the other embeddings.
-Their pattern shows a decent performance indicates the following pattern: a high/average performance on the top-rankings, an underperformance on the middle rankings and a resulting stack-up of articles with a high-ranking.
-This is further supported by the TF-IDF score on titles (Figure~\ref{figure:titleRanks}), on which the limited TF-IDF embeddings are the top performance.
-Indicating a better performance on the top-1 articles compared to the other sets.\vspace{0.3in}
+However, Figures~\ref{figure:titleDistribution} and~\ref{figure:abstractDistribution} show that their rank distribution is different from the other embeddings.
+The rank distribution of the limited TF-IDF embeddings show the following pattern: a high/average performance on the top-rankings, an underperformance on the middle rankings and a resulting stack-up of articles with a high-ranking.
+This is further supported by the TF-IDF score on titles (Figure~\ref{figure:titleRanks}), on which the limited TF-IDF embeddings are the top performers, indicating a better performance on the top-1 articles compared to the other sets.\vspace{0.3in}
 \end{jumpin}
 The rank distribution seems to indicate that the cut-off was effective, but also that it did not suit our purpose.
-The cut-off moved the "middle-ranked"  articles to either the higher end or the lower end of the rankings.
-Resulting in high median and average ranks, and in (relatively) high accuracy scores.
+The cut-off moved the "middle-ranked"  articles to either the higher end or the lower end of the rankings, resulting in high median and average ranks, and in (relatively) high accuracy scores.
 The reduction in vocabulary size did not reduce the storage size for the embeddings, except for the 1K-6K embedding.
@@
 However, they can be processed more efficiently during calculations}.
-This results in a lower memory requirement.
+The removal of titles and abstracts results in a lower memory requirement.
 
@@
 Our hypothesis on the difference between the TF-IDF and the standard embedding is as follows:\\
-The embeddings seem to outperform the TF-IDF in situations when there is little information available, the titles in our case.
+The embeddings seem to outperform the TF-IDF feature vectors in situations where there is little information available (titles).
 This indicates that the embeddings store some word meaning that enables them to perform relatively well on the titles.
@@
 Our data seems to indicate that the amount of information available in the abstracts enable the TF-IDF to cope with the lack of embedded information.
-If this is the case, we could expect that there would little performance increase on the title when we compare the embeddings to the weighted TF-IDF embeddings, since the TF-IDF lacks the information to perform well.
+If this is the case, we could expect that there would little performance increase on the title when we compare the embeddings to the weighted TF-IDF embeddings, because the TF-IDF lacks the information to perform well.
 This can be seen in our data, only the average rank increased by 3, indicating that there is a difference between the two embeddings, but not a significant one.
@@
 \subsubheader{Memory usage}
-Although the TF-IDF outperforms the embeddings on the abstracts, the memory usage of the TF-IDF is higher than the memory usage of the embeddings.
+Although the TF-IDF outperforms the embeddings on the abstracts, its memory usage is higher than the memory usage of the embeddings.
 The top-performing embedding, TF-IDF weighted embedding, uses 3.13 GB, the top performing TF-IDF, 10K/10K uses 11.61 GB, which is 270.93\% of the storage size needed for the embedding.
@@
 \subsubheader{Journal plots}
-Figures~\ref{figure:titlePlotNormal} \&~\ref{figure:abstractPlotNormal} show the journals in the, what we will refer to as "subject spectrum".
+Figures~\ref{figure:titlePlotNormal} and~\ref{figure:abstractPlotNormal} show the journals in the so-called "subject spectrum".
 We do this because the journal embeddings capture journal-relatedness, which leads to the clustering of related articles, which share, in varying degree, the common subject.
@@
 We can further see that Nature is far to the center, as we would expect a generic journal to be, but it is on the biology/medicine side of the center (indicated by the position of Cell and Pharmaceutical Research).\\
-Figures~\ref{figure:titlePlotGrouped} \&~\ref{figure:abstractPlotGrouped} show the journals, grouped with k-means on the original 300-dimensional embedding vector.
+Figures~\ref{figure:titlePlotGrouped} and~\ref{figure:abstractPlotGrouped} show the journals, grouped with k-means on the original 300-dimensional embedding vector.
 In the plot we can see that the original embedding-clustering, as provided by the k-means algorithm, is relatively well preserved, most groups stay clustered together.
@@
 Journals concerning the same subjects are correctly clustered together, and the journals in between topic clusters are also positioned at logical positions.
-It furthermore shows that the k-means groupings give insight in research fields, although it is limited by the number of groups the k-means algorithm creates.
+The interactive version furthermore shows that the k-means groupings give insight in research fields, although it is limited by the number of groups the k-means algorithm creates.
 Our findings on the 2-dimensional representation of embeddings are similar to those of \citet{dai2015document}, who plotted 4.4 million Wikipedia articles.
 The major difference between our plot and their plot is that they focus on just a view subjects in an entire plot, and have access to (human-made) partitioning data.
-They have therefore a more reliable grouping metric.
+They can therefore show human defined/understandable groups in their plot, while we use the k-means algorithm to create the groupings based on the embeddings.
 
@@
 Earlier research already proposed improvements to the word embeddings.
-\citet{dai2015document} show that the usage of paragraph vectors improve the accuracy of word embeddings with 4.4\% on triplet creation with the Wikipedia corpus and a 3.9\% improvement on the same task based on the arXiv articles.\\
+\citet{dai2015document} show that using paragraph vectors improves the accuracy of word embeddings with 4.4\% on triplet creation with the Wikipedia corpus and a 3.9\% improvement on the same task based on the arXiv articles.\\
 Furthermore, \citet{le2014distributed} show that the usage of paragraph vectors decrease the error rate (positive/negative) with 7.7\% compared to averaging the word embeddings on categorizing text as either positive or negative.
-While this looks promising, we have to keep in mind that our task differs from earlier tasks.
+While the improvement looks promising, we have to keep in mind that our task differs from earlier tasks.
 We do not categorize on two categories but more than 3k.
@@
 Even though much research has been done, we have not been able to find published results which are directly comparable to our results.
-This is likely due to our high amount of categorization groups, which enabled us to handle our results as a ranking problem, instead of an absolute hit, which has been used in earlier researches\cite{wang2016linked}.
+This is likely due to our high amount of categorization groups, which enabled us to handle our results as a ranking problem, instead of an absolute hit, which has been used in earlier work\cite{wang2016linked}.
 Even though we have an F1 score, which indicates performance on the absolute hits, our results are not comparable to other works due to the number of categories, and their overlapping subjects\footnote{As visualized in the journal embedding plots and discussed earlier}.

### 2018-07-20 Paper/Parts/Future_work/Future_work.tex
paper setup

--- 2018-07-05 Thesis/Parts/Future_work/Future_work.tex
@@
 To do this, we used both a comparison to TF-IDF and a visualization of the word embeddings.
-Future works may seek to improve the quality of the embeddings further or determine the limit of the capabilities of the embedding technique.
+Future work may seek to improve the quality of the embeddings further or determine the limit of the capabilities of the embedding technique.
 
@@
 \subheader{Intelligent cutting}
-An interesting improvement to enhance the word embeddings with, what could be a smarter way to remove noise, based on word embeddings.
-This might be achieved by analyzing the word embedding spectrum before normalization, and to then cut the center of the vector space out.
+A better way of cutting could improve the quality of the embeddings.
+This improvement might be achieved by cutting the center of the vector space out before normalization.
 This must be applied before normalization since normalization causes all embeddings to have a distance of 1 to the center point.
-All words which are generic are in the center of the spectrum.
-Removing these words prevents the larger texts to be pulled towards the middle of the vector space, where they lose the parts of their meaning which sets them apart from the other journals.
+All words which are generic are in the center of the spectrum before normalization.
+Removing these words prevents the larger texts to be pulled towards the middle of the vector space, where they lose the parts of their meaning which set them apart from the other journals.
 We expect that this way of cutting, instead of word-occurrence cutting, will improve the quality of the word embeddings.
@@
 Once we established that we have word vectors of high quality, could we create word pairs from the embeddings?
-If this is the case, we could reverse-engineer domain specific word pair sets for future use.
+If this is the case, we could create word pair sets using the embeddings, reverse-engineering the domain specific word pair sets for future use.
 These word pairs should most likely still be validated by humans, but the automatic generation of word pairs should already reduce the effort needed for this process.
@@
 
-\subheader{TF-IDF top-cutoff}
+\subheader{TF-IDF top cut-off}
 In our research, we used a dataset from which we removed the top 1k words, together with everything beyond 6k.
@@
 Given this, it would be logical to use TF-IDF for search tasks on sets with many tokens.
-However, the search term itself will contain a small number of tokens, as our research showed, embeddings perform better in this situation.
+However, the search queries consist of a small number of tokens (the average google query size was 4 in 2008\footnote{According to Brian Ussery (01/02/2008): \url{https://www.beussery.com/blog/index.php/2008/02/google-average-number-of-words-per-query-have-increased/}.}).
+Our research showed that embeddings perform better in a situation with a low amount of tokens.
 Future work could try to combine these findings, by collecting a large number of words, resembling the meaning (captured by the embeddings), and transforming this into a (large) collection of words (mimicking word occurrence, captured by the TF-IDF).
 If this could be done effectively, the power of the TF-IDF method could be applied to smaller texts.
-This process could be seen as a translation from word-embedding space into TF-IDF space.
+This process could be seen as a translation from the word-embedding space into the TF-IDF space.
 Furthermore, it would be interesting to see which words would be selected and if these words represent the given sentence as an "extracted version" which would still be interpretable by humans.
@@
 \subheader{Pre-categorization}
-Our results show that the embeddings can indicate the domains of the given articles, as visualized in the journal embedding plots (Figure~\ref{figure:titlePlotNormal}-\ref{figure:abstractPlotGrouped}).
+Our results show that the embeddings can indicate the domains of the given articles, as visualized in the journal embedding plots (Figures~\ref{figure:titlePlotNormal}-\ref{figure:abstractPlotGrouped}).
 This knowledge could be used to pre-process given texts, creating a two-step search.
 This method would first categorize the given article into a field and then search in the limited set of journals for the best fit.
-This has two advantages: A) we predict the field of the article, giving additional information to a user and B) once an article is inside a certain domain, ambiguous words between domains (i.e.
-cloud for computer science and meteorology) are eliminated, since these embeddings do not have to be trained with the other embeddings, which create ambiguity.
-A possible downside of this approach is the need for data within each domain since the embeddings are created on two levels, cross-domain for domain categorization and in-domain for journal categorization.
+This has two advantages: (a) we predict the field of the article, giving additional information to a user and (b) once an article is inside a certain domain, ambiguous words between domains (i.e.
+cloud for computer science and meteorology) are eliminated.
+The domain specific embeddings have not been trained with the other embeddings, thus they do not contain (cross-domain) ambiguity.
+A possible downside of this approach is the need for data within each domain, because the embeddings are created on two levels: cross-domain for domain categorization and in-domain for journal categorization.
 The lack of articles within one domain could hurt the embeddings since they need training data to make accurate predictions.

### 2018-07-20 Paper/Parts/Motivation/Motivation.tex
paper setup

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Motivation}
\subheader{In-domain embeddings and validation}
In previous research concerning domain specific articles,~\citet{Truong2017Thesis} found that in-domain training of the word embeddings can improve the process of document clustering\footnote{Document clustering aims to discover underlying structures in texts\citet{Truong2017Thesis}.}. The usage of in-domain data is more important than the number of training examples and the model architecture\cite{Truong2017Thesis}. \citet{lai2016generate} found that the corpus domain is more important than the corpus size. Using an in-domain corpus significantly improves the performance for a given task, whereas using a corpus in an unsuitable domain may decrease performance.
Truong et al. encountered a problem in the validation of these in-domain embeddings. The word embedding produced correct document clustering results, leading to the conclusion that these embeddings are of good quality since they capture the document relatedness needed to create correct clustering. However unpublished results\footnote{Obtained from author.} by Truong et al. state that the embeddings show high error rates on the word-relatedness validation scores. This seems to indicate that the word-vectors are of good quality due to the correct results on document clustering, but that the word-relatedness validation task has been unable to confirm this due to the domain-specific nature of the texts used by Truong. \citet{Truong2017Thesis} used multiple word similarity validations to asses the quality of the word embeddings. However, these sets are created to validate the generic embeddings; they fail to asses the quality of the domain-specific embeddings.

\subheader{Research}
To solve the problem of the limited availability of pre-labeled validation sets for domain-specific articles, we compare the embeddings to  TF-IDF on a categorization task. This (a) indicates the embedding quality for categorization tasks and (b) contrasts the performance of embeddings to the performance of the more traditional TF-IDF approach. To ensure the quality of the embeddings for our research, we reuse the embeddings created in the research of~\citet{Truong2017Thesis}.
\begin{jumpin}
    \textbf{RQ. 1} Have word embeddings a higher accuracy than TF-IDF for academic texts on the task of article classification?\\
    \begin{adjustwidth}{0.3in}{}
        \textbf{RQ. 1.1} Do embedding optimizations increase the performance of word embedding on academic texts for article classification?\\
        \textbf{RQ. 1.2} Can the usage of alternative distance metrics improve the performance of word embedding on academic texts for article classification?
    \end{adjustwidth}
    \vspace{0.1in}\textbf{RQ. 2} Can word embeddings, combined with PCA\footnote{PCA is the abbeviation for principal component analysis}-based TSNE\footnote{TSNE (t-Stochastic Neighbor Embedding) was introduced by \citet{maaten2008visualizing}. The technique is used to reduce the dimensions of a vector}, create a two-dimensional plot that preserves the relatedness between journals?
\end{jumpin}
\clearpage
\subsubheader{Methodology}
RQ. 1 focusses on the classification results of both embedding-based techniques and TF-IDF.  To asses the classification task, we use the rank of the class to which the item belongs. This transforms the classification task from a binary metric to a ranking metric. For this task, we will use different versions of embeddings, to answer RQ 1.1, and different TF-IDF versions to not only compare the two techniques but also look for the optimal ranking results of both techniques. To achieve optimal results, we also validate distance metrics, we compare 20 distance metrics on ranking performance on the embeddings. For this part of the research, we will use the following hypothesis:
\begin{jumpin}
\textit{\textbf{H. 1} Embedding based techniques give lower rankings (i.e. better performance) than the TF-IDF based techniques.}
\begin{jumpin}
\textit{\textbf{H. 1.1} TF-IDF weighted document embeddings outperform standard embeddings on the classification of academic articles.}\\
\textit{\textbf{H. 1.2} The cosine similarity metric produces the has performance (i.e. lowest ranks) for the classification of academic articles.}\\
\textit{\textbf{H. 1.3} Word embeddings use less memory while giving better ranking results than TF-IDF on the classification of academic articles.}
\end{jumpin}
\end{jumpin}
By validating or invalidating these hypotheses, we get an indication of the performance of the embeddings compared to TF-IDF,  get insight into possible performance and resource trade-offs and get insight into the performance of different distance calculation metrics.\\ 
RQ. 2 concerns the visualization of word embeddings and the accuracy of this visualization. To answer this research question, we will use the following hypothesis:
\begin{jumpin}
\textit{\textbf{H. 2} Word embeddings, combined with PCA-based TSNE can preserve the journal relatedness on a two-dimensional plot.}
\end{jumpin}
The validation of this hypothesis will rely on visual confirmation. We expect to see clustering of journals in certain areas, which indicates a research subject. We also expect that journals which are visually close together are closely related by subject. 
\end{document}

### 2018-07-20 Paper/paper.tex
paper setup

\documentclass[runningheads]{llncs}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{subfiles}
\usepackage{amssymb}
\usepackage{csquotes}
\usepackage[numbers, sort, comma, square]{natbib}
\usepackage{changepage}
\usepackage{graphicx}
\usepackage{placeins}
\usepackage{xr}
\usepackage{tabularx}
\usepackage{lscape}
\usepackage{hyperref}
\usepackage{tablefootnote}
\usepackage{fancyhdr}
\usepackage{hyperref}
%\renewcommand\UrlFont{\color{blue}\rmfamily}

\newenvironment{jumpin}{\begin{adjustwidth}{0.3in}{}}{\end{adjustwidth}}

\begin{document}
\title{Document Embedding for Scientific Articles:\newline A validation of word embeddings}
\titlerunning{Document embedding for Scientific Articles}

\author{H.J. Meijer\inst{1,2}\orcidID{0000-1111-2222-3333} \and
R. Karimi\inst{2}\orcidID{1111-2222-3333-4444}}
\authorrunning{H.J. Meijer et al.}

\institute{University of Amsterdam, Science park 904, 1012WX Amsterdam, The Netherlands \and
Elsevier, Radarweg 29, 1043 NX Amsterdam, The Neterlands
\email{meijerarjan@live.nl, r.karimi@elsevier.com}}
\maketitle

\begin{abstract}
\subfile{Parts/Abstract/Abstract.tex}

\keywords{Word Embedding  \and Document Embedding \and Article Embedding \and Journal Embedding \and Embedding Visualization \and Embedding Validation.}
\end{abstract}

\subfile{Parts/Data/Data.tex}
%\subfile{Parts/Research_results/Research_results.tex}
%\subfile{Parts/Discussion/Discussion.tex}
%\subfile{Parts/Conclusion/Conclusion.tex}
%\subfile{Parts/Future_work/Future_work.tex}

%\begin{theorem}
%This is a sample theorem. The run-in heading is set in bold, while
%the following text appears in italics. Definitions, lemmas,
%propositions, and corollaries are styled the same way.
%\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
%\begin{proof}
%Proofs, examples, and remarks have the initial word in italics,
%while the following text appears in normal font.
%\end{proof}
\cite{Truong2017Thesis}
\bibliographystyle{splncs04}
\bibliography{Bibliography.bib}
\end{document}

### 2018-07-24 Paper/Parts/Appendix/appendix.tex
new paper start

--- 2018-07-17 Thesis/Parts/Research_results/Research_results.tex
@@
-\documentclass[../../Thesis.tex]{subfiles}
+\documentclass[../../paper.tex]{subfiles}
 \begin{document}
-\header{Research results}
-In this chapter the results of our research are presented; the detailed discussion on the meaning and implications of these results is presented in Chapter 6: Discussion.
-\subheader{Ranking}
-The Figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} show the result of the categorization task as ranking results.
-The rank indicates the position of the correct journal in the sorted list of matched journals.
-Figure~\ref{figure:titleRanks} shows the ranking results for the different sets based on the title.
-Figure~\ref{figure:abstractRanks} displays the ranking results based on the abstract.
-Both graphs show both average and median ranks, based on the cosine-similarity between the article and journal embeddings or feature vectors.
-\clearpage
-\begin{figure}[hbt]
-\includegraphics[width=6.5in]{Plots/Title_rankings}
-\caption{Median and average title rankings}\label{figure:titleRanks}
-\end{figure}
-\begin{figure}[hbt]
-\includegraphics[width=6.5in]{Plots/Abstract_rankings}
-\caption{Median and average abstract rankings}\label{figure:abstractRanks}
-\end{figure}
-\clearpage
-\subheader{Rank distribution}
-Figures~\ref{figure:titleDistribution} and~\ref{figure:abstractDistribution} show the distributions of the ranks for each set.
-The Figures plot the summed amount of articles against the ranks on a logarithmic scale.
-Figure~\ref{figure:titleDistribution} shows the rank distribution for the titles, Figure~\ref{figure:abstractDistribution} shows this for the ranks based on the abstract.
-These graphs give a detailed view of the ranks presented in their respective Figures~\ref{figure:titleRanks} and~\ref{figure:abstractRanks}.
-The Y-axis of the two Figures shows the fraction of the total number of articles.
-Due to this, all sets will have a maximum of 1.
-When 1 is hit, the graph stagnates since the dataset has reached the maximum fraction.
-The X-axis plots the ranks of the articles.
-These ranks are the ranks of each individual article in our validation set, in contrast to Figure~\ref{figure:titleRanks} and~\ref{figure:abstractRanks} which show average and median ranks.
-\begin{figure}[hbt]
-\includegraphics[width=6.5in]{Plots/Title_rank_distribution}
-\caption{Title rank distribution per set}\label{figure:titleDistribution}
-\end{figure}
-\begin{figure}[hbt]
-\includegraphics[width=6.5in]{Plots/Abstract_rank_distribution}
-\caption{Abstract rank distribution per set}\label{figure:abstractDistribution}
-\end{figure}
-
-\clearpage
-\subheader{F1-Score}
-Figures~\ref{figure:f1Title} and~\ref{figure:f1Abstract} show the precision, recall and F1 scores.
-These scores are calculated on journal level, and are averaged per set.
-Figure~\ref{figure:f1Title} shows the F1 score for the title and Figure~\ref{figure:f1Abstract} shows the scores for the abstract.
-These scores indicate the performance of the sets on absolute hits/top-1.
-We show the precision and recall scores since they vary between sets that have similar F1-scores (i.e.
-Figure~\ref{figure:f1Title}, tfidf\_5k\_5k and tfidf\_embedding
-\begin{figure}[hbt]
-\includegraphics[width=6.5in]{Plots/Title_avg_f1}
-\caption{Precision, recall and F1 scores based on title}\label{figure:f1Title}
-\end{figure}
-\begin{figure}[htb]
-\includegraphics[width=6.5in]{Plots/Abstract_avg_f1}
-\caption{Precision, recall and F1 scores based on abstract}\label{figure:f1Abstract}
-\end{figure}
-\clearpage
-\subheader{Memory usage}
-Table~\ref{table:memoryUsage} shows the total memory usage of each set for the \textit{Validation set}, indicating their storage costs in gigabytes\footnote{1024 based}.
-It furthermore shows the absolute hit percentage of the title and the abstracts, i.e.
-the percentage of articles that have their source\footnote{Journal from which the article was taken} journal as the first result in the ranking.
-The table furthermore shows the median rank and the median abstract rank, as visualized in Figures \ref{figure:titleRanks} and~\ref{figure:abstractRanks}.
-Thus, this table gives an overview of the memory usage of the sets, combined with their performance on the ranking task.\\
-\begin{table}[hbt]
-\begin{center}
-\begin{tabular}{|l|r|r|r|r|}
-\hline
-Set & Size in GB & Absolute hit percentage & Median title rank & Median abstract rank\\
-&&\begin{tabular}{p{0.5in}|p{0.5in}}Title & Abstract\end{tabular}&&\\
-\hline
-tfidf 5k 5K & $9.82$ & \begin{tabular}{p{0.5in}|p{0.5in}}5.42\% & 10.18\%\end{tabular} & 50 & 27\\
-\hline
-tfidf 5K 10K & $11.47$ & \begin{tabular}{p{0.5in}|p{0.5in}}6.49\% & 11.08\%\end{tabular} & 38 & 15\\
-\hline
-\textbf{tfidf 10K 10K} &\textbf{11.61}& \begin{tabular}{p{0.5in}|p{0.5in}}\textbf{6.79\%} & \textbf{11.32\%}\end{tabular} & \textbf{35} & \textbf{14}\\
-\hline
-embedding & $3.13$ & \begin{tabular}{p{0.5in}|p{0.5in}}7.92\% & 9.24\%\end{tabular} & 27 & 23\\
-\hline
-5k embedding & $3.13$ & \begin{tabular}{p{0.5in}|p{0.5in}}6.34\% & 8.36\%\end{tabular} & 42 & 27\\
-\hline
-10k embedding & $3.13$ & \begin{tabular}{p{0.5in}|p{0.5in}}7.03\% & 8.76\%\end{tabular} & 34 & 25\\
-\hline
-\textbf{tfidf embedding} & \textbf{3.13} & \begin{tabular}{p{0.5in}|p{0.5in}}\textbf{7.89\%} & \textbf{9.33\%}\end{tabular} & \textbf{27} & \textbf{22}\\
-\hline
-1k 6k embedding & $3.06$ & \begin{tabular}{p{0.5in}|p{0.5in}}5.16\% & 7.86\%\end{tabular} & 64 &31 \\
-\hline
-\end{tabular}
-\end{center}
-\caption{Memory usage and performance for each set}\label{table:memoryUsage}
-\end{table}
-\subheader{Journal relatedness plot}
+\section{Appendix}
+\subsection{Journal Plots}
 We created four seperate journal plots, Figures~\ref{figure:titlePlotNormal} and~\ref{figure:titlePlotGrouped} show the title based embeddings, and Figures~\ref{figure:abstractPlotNormal} and~\ref{figure:abstractPlotGrouped} show the abstract based embeddings.

### 2018-07-24 Paper/Parts/Conclusion/Conclusion.tex
new paper start

@@
 \begin{document}
-\header{Conclusion}
+\section{Conclusion}
 This research shows that the article embeddings, created with word embeddings, perform better than the reasonable TF-IDF alternatives on our categorization task, based on article titles.

### 2018-07-24 Paper/Parts/Data/Data.tex
paper setup
new paper start

--- 2018-07-17 Thesis/Parts/Data/Data.tex
@@
-\documentclass[../../Thesis.tex]{subfiles}
+\documentclass[../../paper.tex]{subfiles}
 \begin{document}
-\header{Research Data}
-\subheader{Corpus}
-The dataset we used for this research consists of articles published in 2017 which have been published in journals that have (in 2017) at least 150 publications.
-This selection leads to a dataset of $1.391.543$ articles from $3.759$ journals.
+\section{Research Data}
+\subsection{Corpus}
+The dataset we used for this research consists of $1.391.543$ articles from $3.759$ journals, all articles have been published in journals in 2017, that have (in 2017) at least 150 publications.
 Details about the corpus can be found in table~\ref{table:corpusSize}.
+The distribution of the text in our dataset follows a Pareto-like distribution, which is a common property of texts (\citet{wiegand2018word}).
+Our word and token distribution is visualized in Figure~\ref{figure:wordTokenOccurrence}, which displays the occurrences of the first 500 tokens and words of the corpus, ordered on occurrences.
+\FloatBarrier
 \begin{table}[hbt]
@@
 \end{table}
+\FloatBarrier
 \footnotetext{Rounded}
-\clearpage
-\subsubheader{Text properties}
-\citet{wiegand2018word} state that the Pareto distribution offers a good fit to the word occurrences in natural language.
-Their work shows that, due to the additional parameters in the Pareto-III\footnote{The pareto distribution is a distribution in which recognizable by a long "tail" of low values and a quick and short ascend to the top values.
-More information: \url{https://en.wikipedia.org/wiki/Pareto_distribution}.}, the tail of the data fits better with the model than the Zipf\footnote{Distribution similar to the Pareto distribution, see: \url{https://en.wikipedia.org/wiki/Zipf\%27s_law}} model.
-The fit to the Pareto distribution shows the relation between the word occurrences rank and the actual occurrences.
-This kind of word-occurrences distribution holds for many texts, including the writings of William Shakespeare, scientific texts and novels\cite{thurner2015understanding}.
-The word occurrences in our corpus also follow the pattern of a Pareto distribution as described by~\citet{wiegand2018word}.
-Our word and token distribution is visualized in Figure~\ref{figure:wordTokenOccurrence}, which displays the occurrences of the first 500 tokens of the corpus.
 \FloatBarrier
 \begin{figure}[hbt]
-\includegraphics[width=6.5in]{Plots/word_occurrences}
+\includegraphics[width=4.5in]{Plots/word_occurrences}
 \caption{Word and token occurrences.
-The word counts pattern resembles a Pareto distribution; the tokenization reduced the number of high-frequency words.
-The y-axis shows the number of occurances for each word, the x-axis shows the occurence rank of the word, meaning the position of the word in a list sorted on word occurance.}\label{figure:wordTokenOccurrence}
+The y-axis shows the number of occurances for each word/token, the x-axis shows the occurence rank of the word/token; the position of the word/token in a list sorted on occurance.}\label{figure:wordTokenOccurrence}
 \end{figure}
 \FloatBarrier
-\subheader{Datasets}
-For this research we used a (pre-made) tokenized dataset, created from the earlier described corpus, which reduces the total amount of words by 34\% (see table~\ref{table:corpusSize}).
+\subsection{Datasets}
+For this research we used a tokenized dataset, created from the earlier described corpus (see table~\ref{table:corpusSize}).
 From this tokenized set, we created the embeddings and the TF-IDF feature vectors.
-\subsubheader{Tokenization}
-The following steps have been applied to the words from the text to create a tokenized set:
-\begin{enumerate}
-\item{Removed punctuation}
-\item{Removed all non-ASCII characters}
-\item{Transformed all characters to lower-case}
-\item{Removed stop-words, as provided by the NLTK\footnote{Natural Language ToolKit, \url{https://www.nltk.org/}} library}
-\item{Removed numbers}
-\item{Stemmed all words, using the stemmer provided by the NLTK library}
-\end{enumerate}
-These transformations reduced our dataset by 34\%, resulting in a tokenized set of $186.962.354$ tokens.
-\clearpage
-\subsubheader{Embedding}
+The following steps have been applied to convert the words from the text to tokens: removing punctuation, non-ascii characters, number \& stop-words, transforming all characters to lower-case and by stemming all remaining tokens using the NLTK stemmer\footnote{Natural Language ToolKit library, \url{https://www.nltk.org/}.}.
+These steps reduced our dataset by 34\% (words to tokens), resulting in a set of $186.962.354$ tokens.
+\subsubsection{Embedding}
 For this research, we reused the word embeddings created by \citet{Truong2017Thesis}.
-These embeddings have a vector dimension of 300, which is an industry default.
-They have been trained on the entire Elsevier corpus (titles and abstracts respectively), not limited to the subset we used for this research.
+These embeddings have a vector dimension of 300, and have been trained on the entire Elsevier corpus (titles and abstracts respectively), not limited to the subset we used for this research.
 To create higher-level embeddings, we average all component embeddings.
@@
 Journal embeddings are created by taking the average of all normalized article embeddings.
-We use the average to combine multiple embeddings into one because we determine the meaning of a larger text as the "average meaning" of all components.
-Since this meaning is represented as an embedding, we can average the embeddings to create the average meaning.
-We have used multiple embedding optimizations for this research.
-\subsubsubheader{Default embedding}
-The default embedding is created from the pre-trained word embeddings; no modifications have been applied to this set. We refer to this set in the figures as \textbf{embedding}.
-\subsubsubheader{TF-IDF weighted embedding}
-The TF-IDF weighted embedding sets, referred to as TF-IDF embedding, are the default word embeddings weighted with a TF-IDF score per word.\\
-The TF-IDF is calculated with a raw token count, and a smoothed inverted document frequency, calculated as follows:\\
-\begin{equation}
-IDF = \log_{10}(\dfrac{|A|}{|A_t|})
-\end{equation}
-Where $|A|$ is the total count of articles and $|A_t|$ is the count of articles containing term t.
-The article embeddings are a normalized summation of each word vector multiplied by it TF-IDF value.
-Since we take a sum of all words, the Term Frequency is embedded as the raw count of each word.
-We will refer to this embedding in the figures as \textbf{tfidf\_embedding}.
-\subsubsubheader{10K TF-IDF embedding}
-The 10K embedding set is generated similarity to the TF-IDF embedding, this version only uses the 10.000 most common tokens, reducing the number of tokens it uses.
-This set was created to see if the limitation to 10.000 tokens reduces the amount of noise\footnote{Noise in this context are rare word}, increasing the performance.
-We will refer to this embedding in the figures as the \textbf{10k\_embedding}.
-\subsubsubheader{5K TF-IDF embedding}
-The 5K TF-IDF embedding is the TF-IDF embedding set, limited to the 5.000 most common words.
-This set was created to limit the number of tokens more aggressively, and with that, cancel out more noise.
-We will refer to this embedding in the figures as \textbf{5k\_embedding}.
-\subsubsubheader{1K-6K TF-IDF embedding}
-The 1K-6K TF-IDF embedding is the TF-IDF embedding limited to the top 6.000 most common words, without the top 1.000 most common words.
-The rationale for this cutting is that common words will occur in many articles, creating noise, by cutting off the top 1.000 and cutting off everything below 6.000 we tried to reduce the noise by filtering common words.
-This cut results in a set of 5.000 tokens, which allows us to compare it to the 5K TF-IDF set.
-We will refer to this embedding in the figures as \textbf{1k\_6k\_embedding}.
-We refer to the \textbf{10k\_embedding}, \textbf{5k\_embedding} and the \textbf{1k\_6k\_embedding} as the \textbf{limited TF-IDF embeddings}, because these embedding use TF-IDF weighing, and have been limited in their vocabulary due to the cut-off's.
-\clearpage
-\subsubheader{TF-IDF}
-To create the TF-IDF feature vectors, we used the TF-IDF model and a hasher from PySparks MlLib library\footnote{\url{http://spark.apache.org/docs/2.0.0/api/python/pyspark.mllib.html}.}.
-The TF-IDF feature vectors are created by hashing the tokens with the hasher, which has a set hash bucket size.
-These hashed values are passed on to the TF-IDF model, resulting in a feature vector.
-The vector dimensions of the feature vector equal the number of hash buckets.
+We use the average to combine multiple embeddings into one because we determine the meaning of a larger text for this research as the "average meaning" of all components.
+We have used multiple embedding variations for this research.
+\textbf{Default embedding}; the embeddings  obtained from the word embeddings are referred to as the default embedding, \textit{embedding} in figures.
+A variation on this embedding is the \textbf{TF-IDF weighted embedding}.
+The word embeddings in this set have been weighted with the TF-IDF value for each word, we refer to this set as TF-IDF embedding, \}.{tfidf\_embedding} in figures.
+The TF-IDF score is calculated using the raw token count and the smoothed inverted document frequency.
+The \textbf{10K TF-IDF embedding} uses the TF-IDF embedding as basis, The 10K TF-IDF embedding set has been weighted with the same TF-IDF, but is limited to the top 10.000 most occurring tokens.
+This set is referred to as 10K TF-IDF embedding, \textit{10K\_embedding} in the figures.
+Another variation on the TF-IDF set is the \textbf{5K TF-IDF embedding}.
+The 5K TF-IDF embedding has also been weighted with the TF-IDF values, but has been limited to the top 5.000 most occurring tokens.
+This set is referred to as 5K TF-IDF embedding, \textit{5K\_embedding} in the figures.
+The \textbf{1K-6K TF-IDF embedding} set weights the word embeddings with the TF-IDF values and is limited to the tokens between the top 1.000 and top 6.000 based on their occurrence.
+Creating a set of 5.000 tokens, without using the top 1.000 tokens.
+We refer to this set as \textit{1k\_6k\_embedding} in the figures.
+\subsubsection{TF-IDF}
+The TF-IDF feature vectors are created using the TF-IDF model and a hasher from the PySpark MlLib\footnote{\url{http://spark.apache.org/docs/2.0.0/api/python/pyspark.mllib.html}.}.The TF-IDF feature vectors are created by hashing the tokens with the hasher, which has a set hash bucket size.
+These hashed values are passed on to the TF-IDF model, resulting in a feature vector with a dimension equal to the amount of hash buckets.
 To limit the computational and storage expenses and to reduce noise by rare words, we limit our vocabulary size.
@@
 We will refer to the TF-IDF configurations in our figures as "tfidf\_vocabulary size\_hash bucket size".
+Figure~\ref{figure:tfidfPerformance} shows the performance of TF-IDF on title and abstract as median rank, and Figure~\ref{figure:tfidfMemory} shows the storage size in gigabyte, of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations.
+These figures show that, while the required storage size stagnates, the performance on title also quickly stagnates; the performance of the abstracts show similar behaviour.
+The stagnation of the storage size is likely due to the fact that the terms which are added to the larger vocabulary sets occur less often than the other words (the cut-off is based on word occurrence, descending).
+Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to because these configurations can be kept in memory (storage size) while it is not likely that larger sets will give much improvement.
+The TF-IDF feature vectors are created on article level and we average the set of article feature vectors to create a journal feature vector, just as we did with the embeddings.
+\section{Pipeline}
+\textbf{Data processing;} The research has been done in a python-databricks environment, which used Spark SQL, a library that offers tools to work with big-data.
+We processed the TF-IDF sets and the embedding sets \footnote{See Chapter 3.2 Datasets.} via the same pipeline, using their common vector properties.
+The pipeline contains the following steps: creating a training and validation set, creating the journal embeddings from the training set, categorizing the validation set articles using the journal embeddings and calculating the performance metrics.
 \begin{figure}[hbt]
@@
 \caption{TF-IDF performance on title and abstract.}\label{figure:tfidfPerformance}
-\end{figure}
-\begin{figure}[hbt]
 \includegraphics[width=5in]{Plots/tfidf_selection_plot_memory}
@@
 \end{figure}
-\FloatBarrier
-Figure~\ref{figure:tfidfPerformance} shows the performance of TF-IDF on title and abstract as median rank, and Figure~\ref{figure:tfidfMemory} shows the storage size in gigabyte, of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations.
-This plot shows that, while the required storage size stagnates, the performance on title also quickly stagnates; the performance of the abstracts show similar behaviour.
-The stagnation of the storage size is likely due to the fact that the terms which are added to the larger vocabulary sets occur less often than the other words (the cut-off is based on word occurrence, descending).
-Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to because these configurations can be kept in memory (storage size) while it is not likely that larger sets will give much improvement.
-The TF-IDF features are created on article level.
-We average the set of article feature vectors to create a journal feature vector, just as we did with the embeddings.
-\header{Pipeline}
-\subheader{Research environment}
-The research has been done in a python-databricks environment, which used Spark SQL, a library that offers tools to work with big-data.
-\citet{armbrust2015spark} state that Spark SQL lets programmers leverage the benefits of relational processing and lets SQL users call complex analytic libraries in Spark.
-This allows for much tighter integration of relational and procedural processing.
-The paper further states that Spark SQL makes it significantly simpler and more efficient to write data pipelines that mix relational and procedural processing while offering substantial speedups over previous SQL-on-Spark engines.\\
-\subheader{Data processing}
-We processed the TF-IDF sets and the embedding sets \footnote{See Chapter 3.2 Datasets.} via the same pipeline, using their common vector properties.
-Using the same pipeline ensures comparable results.
-The pipeline is set-up as follows:
-\begin{enumerate}
-\item{Create training and validation set}
-\item{Create journal embeddings}
-\item{Categorize validation articles}
-\item{Calculate performance metrics}
-\end{enumerate}
-\subheader{Create training and validation set}
-We split our initial set  $80\%$ - $20\%$.
-We use the $80\%$ set as the training set for the journal representations, and the $20\%$ set as the validation set for the journal representations.
-This split is based on a random number given to each article, ensuring that all datasets (i.e.
-tfidf\_10k\_10k, embedding) have the same (random) training and validation set.
-\subheader{Create journal embeddings}
-From our training set we create the journal embeddings, which are created for most sets\footnote{See chapter 3.2 Datasets.} by averaging the article embeddings or feature vectors.
-\clearpage
-\subheader{Categorize validation articles}
-To categorize the articles, we calculate the distance between the title of the article, and the title of each journal from the validation set.
+\begin{itemize}
+\item{Create training and validation set;
+We split our initial set in a training set ($80\%$) and a validation set ($20\%$).
+This split of the data is based on a random number given to each article, ensuring that all datasets (i.e.
+tfidf\_10k\_10k, embedding) have the same (random) training and validation set.}
+\item{Create journal embeddings;
+From our training set we create the journal embeddings, which are created for most sets\footnote{See chapter 3.2 Datasets.} by averaging the article embeddings or feature vectors.}
+\item{Categorize validation articles;
+To categorize the articles, we calculate the distance between the title of the article (validation set), and the title of each journal (training set).
 We also do this for the abstract of the article and the abstract of each journal.
-During this process we record of:
-\begin{itemize}
-\item{Title-based-rank of the actual journal}
-\item{Abstract-based-rank of the actual journal}
-\item{Best scored journal on the abstract similarity}
-\item{Best scored journal on the title similarity}
-\item{Abstract similarity between the actual journal and the article}
-\item{Title similarity between the actual journal and the article}
-\end{itemize}
-\subsubheader{Distance metrics}
+During this process we record of the title-based-rank and abstract-based-rank of the source journal, best scored journal on abstract and title and the similarity between the source journal and article for both abstract and title.}
+\item{Distance metrics;
 To calculate the distance between two vectors, cosine similarity is commonly used.
@@
 We calculate the similarities based on the normalized embeddings, and compared the distance metrics based on the default embedding set.
-Table~\ref{table:distanceMetrics} shows the results of this validation.\\
+Table~\ref{table:distanceMetrics} shows the results of this validation.}
+\end{itemize} 
 \begin{table}[hbt]
@@
 \hline
-Dice & 1995 & 1929 & 1995 & 1929  \\
-\hline
 \textit{Euclidean} & \textit{27} & \textit{127} & \textit{23} & \textit{122}  \\
-\hline
-Hamming & 1995 & 1929 & 1995 & 1929  \\
-\hline
-Jaccard & 1995 & 1929 & 1995 & 1929  \\
-\hline
-Kulsinski & 1995 & 1929 & 1995 & 1929  \\
 \hline
@@
 \hline
-Matching & 1995 & 1929 & 1995 & 1929  \\
-\hline
-Rogerstanimoto & 1995 & 1929 & 1995 & 1929  \\
-\hline
-Russellrao & 1995 & 1929 & 1995 & 1929  \\
-\hline
 \textit{Seuclidean} & \textit{27} & \textit{124} & \textit{22} & \textit{115}  \\
-\hline
-Sokalmichener & 1995 & 1929 & 1995 & 1929  \\
-\hline
-Sokalsneath & 1995 & 1929 & 1995 & 1929  \\
 \hline
@@
 \hline
-Yule & 1995 & 1929 & 1995 & 1929  \\
-\hline
 \end{tabular}
-\caption{Distance metric performance for word embeddings on the categorization of academic texts}\label{table:distanceMetrics}
+\begin{center}
+\caption{Distance metric performance for word embeddings on the categorization of academic texts, only showing relevant results.}\label{table:distanceMetrics}
+\end{center}
 \end{table}
 \footnotetext{As defined and provided by the SciPy library} 
-These results show high similarity between cosine-based metrics (Cosine \& Correlation) and euclidean based metrics (Euclidean, Seuclidean \& Sqeuclidean).
+The results in Table~\ref{table:distanceMetrics} show high similarity between cosine-based metrics (Cosine \& Correlation) and euclidean based metrics (Euclidean, Seuclidean \& Sqeuclidean).
 This similarity is expected, since the cosine and euclidean distances should yield the same results on normalized sets\footnote{See: \url{https://en.wikipedia.org/wiki/Cosine_similarity\#Properties}.}.
@@
 Because of this, we will use the cosine-similarity as the distance metric, which will make our results easier to compare with other work, since the cosine-similarity is a commonly used similarity measure.
-\subheader{Performance measurement}
-We use multiple metrics to validate the performance of the embedding sets and TF-IDF sets on the categorization task. These metrics are:
-\begin{enumerate}
-\item{F1-score}
-\item{Median \& average rank}
-\item{Rank distribution}
-\end{enumerate}
-\subsubheader{F1-score}
+\subsection{Performance measurement}
+We use multiple metrics to validate the performance of the embedding sets and TF-IDF sets on the categorization task.
+These metrics are: the F1-score, the Median \& average rank and the Rank distribution.
+\begin{itemize}
+\item{F1-score;
 For our matching algorithm, we classify the results as follows:
-\begin{jumpin}
-$True Positive = $ Articles that are correctly matched to the current journal\\
-$False Positive = $ Articles that are incorrectly matched to other journals\\
-$False Negative = $ Articles that are incorrectly matched to the current journal\\
-\end{jumpin}
-With these definitions, we calculate the Recall, Precision \& F1 as follows:\\
-\begin{jumpin}
-$Recall = \dfrac{|True Positive|}{|True Positive| + |False Negative|}$\vspace{0.1in}\\
-$Precision = \dfrac{|True Positive|}{|True Positive| + |False Positive|}$\vspace{0.1in}\\
-$F1 = \dfrac{2 * Precision * Recall}{Precision + Recall|}$
-\end{jumpin}
-here we denote the amount of articles in a class as $|class|$.
-\subsubheader{Median \& average rank}
-A dataset rank is calculated using the ranks of all article in that dataset.
-The median rank of a dataset indicates the point where 50\% of all articles are to the left of a virtual line and 50\% are to the right of this line.
-The median rank therefore indicates the position of the "normal/typical" article.
-This median rank differs from the average, since the median is not influenced by a single value.
-If the median is 20, it does not matter if an article rank is 25 or 250, it does matter however if an article rank is 19 or 21.
-For the average rank this is not the case, the average rank is influenced by single articles.
-Therefore, it does not represents the "normal/typical" article but it represents the exact average rank of all articles in the validation set, which is changed when an article rank is changed from 25 to 250.\\
-We use the median rank to indicate at which rank the typical article would be ranked, based on its title and abstract.
-We also calculate the average score for the title and abstract of all articles.
-This gives us four scores: \textbf{median title rank, median abstract rank, average title rank \& average abstract rank.}
-\clearpage
-\subsubheader{Rank distribution}
-To further analyse the ranking results, we plot the article rank distribution to get an indication of the ranking-landscape.
-\subsubheader{Two-dimensional plot}
-To create a plot, we transformed the 300-dimensional journal vectors into 2-dimensional vectors using TSNE based on PCA\footnote{Principal component analysis}.
-These 2-dimensional vectors, representing the x \& y coordinate, can then be drawn in a plot.
-To visualize the preservation of journal-relatedness while converting the 300 dimensions to 2 dimensions, we create groupings using k-means.
-These groupings are created on the 300-dimensional vectors and are visualized in the plot using colors.
-We use the k-means groupings due to the lack of subject-based grouping values in our dataset, for this research we used 2, 5, 8, 10, 20, 25, 30, 35 and 40 as the amount of groups.
-We included only the plots of 8 groups, because we find this plot the most informative.
-All group amounts can be seen in the digital version of the plots.
+$True Positive = $ Articles correctly matched to the current journal\\
+$False Positive = $ Articles incorrectly matched to other journals\\
+$False Negative = $ Articles incorrectly matched to the current journal\\
+With these definitions, we calculate the Recall, Precision \& F1 using the standard formulas.}
+\item{Median \& average rank;
+We use both average and median ranks as rank-indication for a journal.
+The median rank indicates at which point 50\% of all values is larger and 50\% of all values is smaller, indicating the "typical article".
+While the average indicates the exact average of all articles in the set.
+We used both measures for our research.}
+\item{Rank distribution;
+To further analyse the ranking results, we plot the article rank distribution to get an indication of the ranking-landscape.}
+\end{itemize}
 \end{document}

### 2018-07-24 Paper/Parts/Discussion/Discussion.tex
new paper start

@@
 \begin{document}
-\header{Discussion}
-\subheader{Results analysis}
-
-\subsubheader{Best performers}
-The data, as presented in Figures~\ref{figure:titleRanks} and~\ref{figure:abstractRanks} shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank on abstract and 3 median ranks on the titles.
-For the embeddings, the TF-IDF weighted embedding works better than the others, although it is not a significant improvement (1 rank on a set of more than 3.000) compared to the default embeddings, which is 1 median rank higher on the abstracts, and equal on the titles.
-
-\subsubheader{TF-IDF}
+\section{Discussion}
+\subsection{Results analysis}
+\subsubsection{Best performers}
+The data, as presented in Figures~\ref{figure:titleRanks} and~\ref{figure:abstractRanks} shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low (1 median rank on abstract and 3 median ranks on the titles).
+For the embeddings, the TF-IDF weighted embedding works better than the others, although it is not a significant improvement (1 rank on a set of more than 3.000) compared to the default embeddings.
+\subsubsection{TF-IDF}
 The TF-IDF feature vectors outperform the embeddings on the abstracts, while the embeddings outperform the TF-IDF feature vectors on the titles.
@@
 The TF-IDF method works better on the abstract, containing more tokens than the tile, thus improving the differentiating the different abstract.
-The data furthermore shows that increasing the vocabulary size increases the performance of the TF-IDF, meaning that none of the created cut-off's resulted in cutting off noise, the increasing size of the vocabulary only improved the performance on our data.
-It could be possible that at higher vocabulary sizes the cut-off would result in a sharper signal, but we did not investigate this further due to our findings that the TF-IDF performance stagnates (presented in Figure~\ref{figure:tfidfPerformance}).
-\clearpage
-\subsubheader{Limited TF-IDF embeddings}
-The limited TF-IDF embeddings all underperform, compared to the TF-IDF embedding (which does not have a limited vocabulary), on the median and average ranking.
-This result indicates that the noise reduction is too much, and it removes meaningful words.
+The data furthermore shows that increasing the vocabulary size increases the performance of the TF-IDF, meaning that none of the created cut-off's resulted in cutting off noise.
+\subsubsection{Limited TF-IDF embeddings}
+The limited TF-IDF embeddings all underperform, compared to the TF-IDF embedding on median and average ranking.
+This result indicates that the noise reduction is too much, it removes meaningful words.
 If the noise reduction would be too low, we would only see a slight increase of performance compared to the TF-IDF embedding, or none at all.
@@
 \begin{jumpin}
-\subsubsubheader{Rank distribution}
+\textit{Rank distribution}.
 However, Figures~\ref{figure:titleDistribution} and~\ref{figure:abstractDistribution} show that their rank distribution is different from the other embeddings.
 The rank distribution of the limited TF-IDF embeddings show the following pattern: a high/average performance on the top-rankings, an underperformance on the middle rankings and a resulting stack-up of articles with a high-ranking.
-This is further supported by the TF-IDF score on titles (Figure~\ref{figure:titleRanks}), on which the limited TF-IDF embeddings are the top performers, indicating a better performance on the top-1 articles compared to the other sets.\vspace{0.3in}
+This is further supported by the TF-IDF score on titles (Figure~\ref{figure:titleRanks}), on which the limited TF-IDF embeddings are the top performers, indicating a better performance on the top-1 articles compared to the other sets.
 \end{jumpin}
-The rank distribution seems to indicate that the cut-off was effective, but also that it did not suit our purpose.
-The cut-off moved the "middle-ranked"  articles to either the higher end or the lower end of the rankings, resulting in high median and average ranks, and in (relatively) high accuracy scores.
-The reduction in vocabulary size did not reduce the storage size for the embeddings, except for the 1K-6K embedding.
-This indicates that only the 1K-6K cut actually removes entire titles and abstracts, since all vectors are stored as dense-vectors\footnote{Dense vectors are bigger in memory, since they store all their values, including zeros.
-However, they can be processed more efficiently during calculations}.
-The removal of titles and abstracts results in a lower memory requirement.
-
-\subsubheader{TF-IDF \& embeddings}
-Our hypothesis on the difference between the TF-IDF and the standard embedding is as follows:\\
-The embeddings seem to outperform the TF-IDF feature vectors in situations where there is little information available (titles).
+The rank distribution seems to indicate that the cut-off was effective, but not for our purpose.
+The cut-off moved the "middle-ranked"  articles to either the higher end or the lower end of the rankings, resulting in high median and average ranks.
+The reduction in vocabulary size did not reduce the storage size for the embeddings, except for the 1K-6K embedding\footnote{This indicates that he 1K-6K embedding removed some articles entirely from the dataset.}.
+\subsubsection{TF-IDF \& embeddings}
+Our hypothesis on the difference between the TF-IDF and the standard embedding is as follows: The embeddings seem to outperform the TF-IDF feature vectors in situations where there is little information available (titles).
 This indicates that the embeddings store some word meaning that enables them to perform relatively well on the titles.
@@
 Our data seems to indicate that the amount of information available in the abstracts enable the TF-IDF to cope with the lack of embedded information.
-If this is the case, we could expect that there would little performance increase on the title when we compare the embeddings to the weighted TF-IDF embeddings, because the TF-IDF lacks the information to perform well.
-This can be seen in our data, only the average rank increased by 3, indicating that there is a difference between the two embeddings, but not a significant one.
+\\
+If this is the case, we could expect that there would little performance increase on the title when we compare the embeddings to the weighted TF-IDF embeddings, because the TF-IDF lacks the information to perform well, this can be seen in our data.
 We would also expect on the abstract an increase in performance since the TF-IDF has more information in this context.
@@
 Our data shows a minor improvement in performance of 1 median rank and 10 average ranks while these improvements cannot be seen as significant, our data at least indicates that weighting the embeddings with TF-IDF values has a positive effect on the embeddings.
-
-\subsubheader{Memory usage}
+\subsubsection{Memory usage}
 Although the TF-IDF outperforms the embeddings on the abstracts, its memory usage is higher than the memory usage of the embeddings.
 The top-performing embedding, TF-IDF weighted embedding, uses 3.13 GB, the top performing TF-IDF, 10K/10K uses 11.61 GB, which is 270.93\% of the storage size needed for the embedding.
-The closest TF-IDF configuration (based on memory usage) we used was 1K/1K, which uses 5.13 GB (as displayed in Figure~\ref{figure:tfidfPerformance}).
-This TF-IDF set has a median title rank of 183 and a median abstract rank of 44.
-Which is significantly worse than the embedding, which also uses less memory.
-This indicates that the embeddings are able to store the relatedness information more densely than the TF-IDF feature vectors can store the word occurrence information.
-
-\subsubheader{Journal plots}
-Figures~\ref{figure:titlePlotNormal} and~\ref{figure:abstractPlotNormal} show the journals in the so-called "subject spectrum".
-We do this because the journal embeddings capture journal-relatedness, which leads to the clustering of related articles, which share, in varying degree, the common subject.
-In this Figure, we can see that the publisher Wiley is more active in the right part of the spectrum than the left.
-We can further see that Nature is far to the center, as we would expect a generic journal to be, but it is on the biology/medicine side of the center (indicated by the position of Cell and Pharmaceutical Research).\\
-Figures~\ref{figure:titlePlotGrouped} and~\ref{figure:abstractPlotGrouped} show the journals, grouped with k-means on the original 300-dimensional embedding vector.
-In the plot we can see that the original embedding-clustering, as provided by the k-means algorithm, is relatively well preserved, most groups stay clustered together.
-The interactive version shows that the clusterings, as seen on all four Figures, are subject based.
-Journals concerning the same subjects are correctly clustered together, and the journals in between topic clusters are also positioned at logical positions.
-The interactive version furthermore shows that the k-means groupings give insight in research fields, although it is limited by the number of groups the k-means algorithm creates.
-Our findings on the 2-dimensional representation of embeddings are similar to those of \citet{dai2015document}, who plotted 4.4 million Wikipedia articles.
-The major difference between our plot and their plot is that they focus on just a view subjects in an entire plot, and have access to (human-made) partitioning data.
-They can therefore show human defined/understandable groups in their plot, while we use the k-means algorithm to create the groupings based on the embeddings.
-
-\subheader{Improvements}
-This research shows that even though the embeddings can capture and preserve relatedness, TF-IDF is able to outperform the embeddings on the abstracts.
-Earlier research already proposed improvements to the word embeddings.
-\citet{dai2015document} show that using paragraph vectors improves the accuracy of word embeddings with 4.4\% on triplet creation with the Wikipedia corpus and a 3.9\% improvement on the same task based on the arXiv articles.\\
-Furthermore, \citet{le2014distributed} show that the usage of paragraph vectors decrease the error rate (positive/negative) with 7.7\% compared to averaging the word embeddings on categorizing text as either positive or negative.
-While the improvement looks promising, we have to keep in mind that our task differs from earlier tasks.
-We do not categorize on two categories but more than 3k.
-Still, we would expect an improvement by using paragraph vectors since the classification task if fundamentally the same, only on a much larger scale, which complicates the task due to the "grey areas"  between categories.
-These are the area's in which the classification algorithm is "in doubt" and could reasonably assign the article to both journals.
-The number of these grey areas increase given more categories.
-\citet{pennington2014glove} showed that the GloVe model outperforms the CBOW model, which is used in this research, on a word analogy task.
-\citet{wang2016linked} introduced the Linked Document Embedding method (LDE) method, which makes use of additional information about a document, such as citations.
-Their research specifically focused on categorizing documents, showed a 5.89\% increase of the micro-F1 score on LDE compared to CBOW, and a 9.11\% increase of the macro-F1 score.
-We would expect that applying this technique to our dataset would improve our scores, given earlier results on comparable tasks.\\
-Even though much research has been done, we have not been able to find published results which are directly comparable to our results.
-This is likely due to our high amount of categorization groups, which enabled us to handle our results as a ranking problem, instead of an absolute hit, which has been used in earlier work\cite{wang2016linked}.
-Even though we have an F1 score, which indicates performance on the absolute hits, our results are not comparable to other works due to the number of categories, and their overlapping subjects\footnote{As visualized in the journal embedding plots and discussed earlier}.
 \end{document}

### 2018-07-24 Paper/Parts/Future_work/Future_work.tex
new paper start

@@
 \begin{document}
-\header{Future work}
-This research focused on the quality of word embeddings on academic texts.
-To do this, we used both a comparison to TF-IDF and a visualization of the word embeddings.
-Future work may seek to improve the quality of the embeddings further or determine the limit of the capabilities of the embedding technique.
-
-\subheader{Method differences}
-\citet{levy2015improving} observed that there were no significant differences between the various embedding creation methods.
-They state that the global/hyperparameters of the various methods mainly cause the difference in performance.
-In this research, we did not look at the comparison between various models and (hyper) parameters.
-We instead used a standard configuration, to focus more on the actual performance of the embeddings, instead of the best possible performance.
-Future work could seek to validate the results of \citet{levy2015improving} by expanding our research with multiple metrics.
-It should be noted however that Levy et al.
-base their conclusions on word similarity and word analogy tasks, and not on categorization.
-This is the reason why we did not take this research into account in our discussion since their experiments are not comparable to ours.
-
-\subheader{Intelligent cutting}
+\section{Future work}
+\subsection{Intelligent cutting}
 A better way of cutting could improve the quality of the embeddings.
 This improvement might be achieved by cutting the center of the vector space out before normalization.
-This must be applied before normalization since normalization causes all embeddings to have a distance of 1 to the center point.
-All words which are generic are in the center of the spectrum before normalization.
-Removing these words prevents the larger texts to be pulled towards the middle of the vector space, where they lose the parts of their meaning which set them apart from the other journals.
+All words which are generic are in the center of the spectrum, removing these words prevents the larger texts to be pulled towards the middle of the vector space, where they lose the parts of their meaning which set them apart from the other texts.
 We expect that this way of cutting, instead of word-occurrence cutting, will improve the quality of the word embeddings.
-
-\subheader{Text combination}
-To cope with the problem of articles that do have an abstract but no title, or vice versa, it would be interesting to see what the quality of the embeddings would be if both texts were combined into one text.
-This should be possible since the title and the abstract per article share a common topic.
-We would expect that the common text would have the quality of the abstract, which is according to our findings the part that is best used for the embeddings and TF-IDF.
-
-\subheader{TF-IDFs performance point}
+\subsection{TF-IDFs performance point}
 In our research, TF-IDF performed better on the abstracts than on the titles, which, according to us, is caused by the text size of the two texts.
@@
 Is there a point at which the TF-IDF outperforms the embeddings, and will continue to outperform?
-If this relation is found,  we could skip the TF-IDF calculations in certain situations, and skip the embedding training in other scenario's, saving time and costs.
-
-\subheader{Reversed word pairs}
+If this relation is found, one could skip the TF-IDF calculations in certain situations, and skip the embedding training in other scenario's, reducing costs.
+\subsection{Reversed word pairs}
 At this point, there are no domain-specific word pair sets available.
 However, as we demonstrated, we can still test the quality of word embeddings.
-Once we established that we have word vectors of high quality, could we create word pairs from the embeddings?
+Once one has established that the word vectors are of high quality, could one create word pairs from the embeddings?
 If this is the case, we could create word pair sets using the embeddings, reverse-engineering the domain specific word pair sets for future use.
-These word pairs should most likely still be validated by humans, but the automatic generation of word pairs should already reduce the effort needed for this process.
-
-\subheader{Historical overview}
-We have shown that the word embeddings can be used to create a subject spectrum, in which we plotted all the articles for one year.
-This gives insight into the currently popular research field, indicated by dense areas on the plot.
-If we would create this plot over multiple years, and then show these years in chronological order, we should be able to see the evaluation of research fields in time, giving more insight in shifting interests and the development of new research areas.
-
-\subheader{TF-IDF top cut-off}
-In our research, we used a dataset from which we removed the top 1k words, together with everything beyond 6k.
-This dataset did not perform well in our research; future work could look into this by validating if the top-words cut-off decreases the TF-IDF performance.
-Our findings on this topic are minimal, although we can say that we would not expect that the top-cutoff improves the performance since a set with the top 5k words performed better than the 1k till 6k words set.
-
-\subheader{Collecting a set of terms}
-Our results show that, for larger texts, TF-IDF outperforms the embeddings.
-Given this, it would be logical to use TF-IDF for search tasks on sets with many tokens.
-However, the search queries consist of a small number of tokens (the average google query size was 4 in 2008\footnote{According to Brian Ussery (01/02/2008): \url{https://www.beussery.com/blog/index.php/2008/02/google-average-number-of-words-per-query-have-increased/}.}).
-Our research showed that embeddings perform better in a situation with a low amount of tokens.
-Future work could try to combine these findings, by collecting a large number of words, resembling the meaning (captured by the embeddings), and transforming this into a (large) collection of words (mimicking word occurrence, captured by the TF-IDF).
-If this could be done effectively, the power of the TF-IDF method could be applied to smaller texts.
-This process could be seen as a translation from the word-embedding space into the TF-IDF space.
-Furthermore, it would be interesting to see which words would be selected and if these words represent the given sentence as an "extracted version" which would still be interpretable by humans.
-\clearpage
-\subheader{Pre-categorization}
-Our results show that the embeddings can indicate the domains of the given articles, as visualized in the journal embedding plots (Figures~\ref{figure:titlePlotNormal}-\ref{figure:abstractPlotGrouped}).
-This knowledge could be used to pre-process given texts, creating a two-step search.
-This method would first categorize the given article into a field and then search in the limited set of journals for the best fit.
-This has two advantages: (a) we predict the field of the article, giving additional information to a user and (b) once an article is inside a certain domain, ambiguous words between domains (i.e.
-cloud for computer science and meteorology) are eliminated.
-The domain specific embeddings have not been trained with the other embeddings, thus they do not contain (cross-domain) ambiguity.
-A possible downside of this approach is the need for data within each domain, because the embeddings are created on two levels: cross-domain for domain categorization and in-domain for journal categorization.
-The lack of articles within one domain could hurt the embeddings since they need training data to make accurate predictions.
-In a situation where there is no categorization data available, like in our research, a k-means algorithm should suffice for categorization.
-The goal is to have multiple separate vector spaces, for this, it does not matter if the "domains" are well-interpretable or make sense to humans.
 \end{document}

### 2018-07-24 Paper/Parts/Research_results/Research_results.tex
new paper start

--- 2018-07-17 Thesis/Parts/Research_results/Research_results.tex
@@
-\documentclass[../../Thesis.tex]{subfiles}
+\documentclass[../../paper.tex]{subfiles}
 \begin{document}
-\header{Research results}
-In this chapter the results of our research are presented; the detailed discussion on the meaning and implications of these results is presented in Chapter 6: Discussion.
-\subheader{Ranking}
+\section{Research results}
+In this section the results of our research are presented; the detailed discussion on the meaning and implications of these results is presented in section 4: Discussion.
+\subsubsection{Ranking}
 The Figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} show the result of the categorization task as ranking results.
@@
 Both graphs show both average and median ranks, based on the cosine-similarity between the article and journal embeddings or feature vectors.
-\clearpage
-\begin{figure}[hbt]
-\includegraphics[width=6.5in]{Plots/Title_rankings}
-\caption{Median and average title rankings}\label{figure:titleRanks}
-\end{figure}
-\begin{figure}[hbt]
-\includegraphics[width=6.5in]{Plots/Abstract_rankings}
-\caption{Median and average abstract rankings}\label{figure:abstractRanks}
-\end{figure}
-\clearpage
-\subheader{Rank distribution}
+\subsubsection{Rank distribution}
 Figures~\ref{figure:titleDistribution} and~\ref{figure:abstractDistribution} show the distributions of the ranks for each set.
@@
 Figure~\ref{figure:titleDistribution} shows the rank distribution for the titles, Figure~\ref{figure:abstractDistribution} shows this for the ranks based on the abstract.
-These graphs give a detailed view of the ranks presented in their respective Figures~\ref{figure:titleRanks} and~\ref{figure:abstractRanks}.
-The Y-axis of the two Figures shows the fraction of the total number of articles.
-Due to this, all sets will have a maximum of 1.
-When 1 is hit, the graph stagnates since the dataset has reached the maximum fraction.
-The X-axis plots the ranks of the articles.
-These ranks are the ranks of each individual article in our validation set, in contrast to Figure~\ref{figure:titleRanks} and~\ref{figure:abstractRanks} which show average and median ranks.
-\begin{figure}[hbt]
-\includegraphics[width=6.5in]{Plots/Title_rank_distribution}
-\caption{Title rank distribution per set}\label{figure:titleDistribution}
-\end{figure}
-\begin{figure}[hbt]
-\includegraphics[width=6.5in]{Plots/Abstract_rank_distribution}
-\caption{Abstract rank distribution per set}\label{figure:abstractDistribution}
-\end{figure}
-
-\clearpage
-\subheader{F1-Score}
+These graphs give a detailed view of the ranks presented in their respective figures (Figures~\ref{figure:titleRanks} and~\ref{figure:abstractRanks}).
+\subsubsection{F1-Score}
 Figures~\ref{figure:f1Title} and~\ref{figure:f1Abstract} show the precision, recall and F1 scores.
@@
 These scores indicate the performance of the sets on absolute hits/top-1.
-We show the precision and recall scores since they vary between sets that have similar F1-scores (i.e.
-Figure~\ref{figure:f1Title}, tfidf\_5k\_5k and tfidf\_embedding
-\begin{figure}[hbt]
-\includegraphics[width=6.5in]{Plots/Title_avg_f1}
-\caption{Precision, recall and F1 scores based on title}\label{figure:f1Title}
-\end{figure}
-\begin{figure}[htb]
-\includegraphics[width=6.5in]{Plots/Abstract_avg_f1}
-\caption{Precision, recall and F1 scores based on abstract}\label{figure:f1Abstract}
-\end{figure}
-\clearpage
-\subheader{Memory usage}
+\subsubsection{Memory usage}
 Table~\ref{table:memoryUsage} shows the total memory usage of each set for the \textit{Validation set}, indicating their storage costs in gigabytes\footnote{1024 based}.
@@
 The table furthermore shows the median rank and the median abstract rank, as visualized in Figures \ref{figure:titleRanks} and~\ref{figure:abstractRanks}.
-Thus, this table gives an overview of the memory usage of the sets, combined with their performance on the ranking task.\\
-\begin{table}[hbt]
+Thus, this table gives an overview of the memory usage of the sets, combined with their performance on the ranking task.
+\FloatBarrier
+\begin{figure}
+\includegraphics[width=4.5in]{Plots/Title_rankings}
+\caption{Median and average title rankings}\label{figure:titleRanks}
+\end{figure}
+\begin{figure}
+\includegraphics[width=4.5in]{Plots/Abstract_rankings}
+\caption{Median and average abstract rankings}\label{figure:abstractRanks}
+\includegraphics[width=4.5in]{Plots/Title_rank_distribution}
+\caption{Title rank distribution per set, Y-axis shows the fraction of articles.}\label{figure:titleDistribution}
+\includegraphics[width=4.5in]{Plots/Abstract_rank_distribution}
+\caption{Abstract rank distribution per set, Y-axis shows the fraction of acticles.}\label{figure:abstractDistribution}
+\end{figure}
+\begin{figure}
+\includegraphics[width=4.5in]{Plots/Title_avg_f1}
+\caption{Precision, recall and F1 scores based on title}\label{figure:f1Title}
+\includegraphics[width=4.5in]{Plots/Abstract_avg_f1}
+\caption{Precision, recall and F1 scores based on abstract}\label{figure:f1Abstract}
+\end{figure}
+\FloatBarrier
+\begin{table}
 \begin{center}
@@
 \end{table}
-\subheader{Journal relatedness plot}
-We created four seperate journal plots, Figures~\ref{figure:titlePlotNormal} and~\ref{figure:titlePlotGrouped} show the title based embeddings, and Figures~\ref{figure:abstractPlotNormal} and~\ref{figure:abstractPlotGrouped} show the abstract based embeddings.
-Figures~\ref{figure:titlePlotNormal} and~\ref{figure:abstractPlotNormal} show the two dimensional plots of the journal embeddings.
-The journals are color-marked by publisher.
-Red is Wiley, lime is Elsevier and blue is Springer Nature.
-The grey points are other or not-specified publishers.
-Figures~\ref{figure:titlePlotGrouped} and~\ref{figure:abstractPlotGrouped} show the journal embeddings grouped by a k-means algorithm, creating 8 groups.
-The bottom right of the plot shows the names of the journals closest to the center of the group.
-While most names state the topic of the research field, two do not.
-These are \textit{RSC Advances}: chemical sciences, and \textit{Symmetry}:  research on symmetry phenomena wherever they occur in mathematical or scientific studies.
-The k-means algorithm ran on the 300-dimensional vectors, while the plot shows the 2-dimensional vectors.
-In the title-based Figures (\ref{figure:titlePlotNormal} \&~\ref{figure:titlePlotGrouped}) the journals \textit{PNAS} and \textit{Cell} overlap each others labels on the bottom right side of the graph.
-In the abstract-based Figures (\ref{figure:abstractPlotNormal} \&~\ref{figure:abstractPlotGrouped}) the journals \textit{PNAS} and \textit{Nature} overlap each others label on the bottom right side of the graph.
-The digital versions of these plots can be found at:~\url{https://goo.gl/nCGMcu} (title-based) and~\url{https://goo.gl/LwYP6k} (abstract-based).
-The usage of this digital version is advised, since this interactive plot enables zooming and adjusting plot settings, which can give a broader insight into the results than the presented figures.
-Although the presented figures give sufficient insight for the purpose of this thesis.
-\begin{landscape}
-\begin{figure}
-\begin{center}
-\includegraphics[height=6.5in]{Plots/Journal_Plots/Title_normal}
-\end{center}
-\caption{Journal plot of title embeddings, grouped by publisher}\label{figure:titlePlotNormal}
-\end{figure}
-\end{landscape}
-
-\begin{landscape}
-\begin{figure}
-\begin{center}
-\includegraphics[height=6.5in]{Plots/Journal_Plots/Abstract_normal}
-\end{center}
-\caption{Journal plot of abstract embeddings, grouped by publisher}\label{figure:abstractPlotNormal}
-\end{figure}
-\end{landscape}
-
-\begin{landscape}
-\begin{figure}
-\begin{center}
-\includegraphics[height=6.5in]{Plots/Journal_Plots/Title_grouped}
-\end{center}
-\caption{Journal plot of title embeddings, k-means grouped}\label{figure:titlePlotGrouped}
-\end{figure}
-\end{landscape}
-
-\begin{landscape}
-\begin{figure}
-\begin{center}
-\includegraphics[height=6.5in]{Plots/Journal_Plots/Abstract_grouped}
-\end{center}
-\caption{Journal plot of abstract embeddings, k-means grouped}\label{figure:abstractPlotGrouped}
-\end{figure}
-\end{landscape}
+\FloatBarrier
 \end{document}

### 2018-07-24 Paper/paper - Copy.tex
new paper start

\documentclass[runningheads]{llncs}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{subfiles}
\usepackage{amssymb}
\usepackage{csquotes}
\usepackage[numbers, sort, comma, square]{natbib}
\usepackage{changepage}
\usepackage{graphicx}
\usepackage{placeins}
\usepackage{xr}
\usepackage{tabularx}
\usepackage{lscape}
\usepackage{hyperref}
\usepackage{tablefootnote}
\usepackage{fancyhdr}
\usepackage{hyperref}
\newenvironment{jumpin}{\begin{adjustwidth}{0.3in}{}}{\end{adjustwidth}}

\begin{document}
\title{Document Embedding for Scientific Articles:\newline A validation of word embeddings}
\titlerunning{Document embedding for Scientific Articles}

\author{H.J. Meijer\inst{1,2}\orcidID{0000-1111-2222-3333} \and
R. Karimi\inst{2}\orcidID{1111-2222-3333-4444}}
\authorrunning{H.J. Meijer et al.}

\institute{University of Amsterdam, Science park 904, 1012WX Amsterdam, The Netherlands \and
Elsevier, Radarweg 29, 1043 NX Amsterdam, The Neterlands
\email{meijerarjan@live.nl, r.karimi@elsevier.com}}
\maketitle

\begin{abstract}
\subfile{Parts/Abstract/Abstract.tex}

\keywords{Word Embedding  \and Document Embedding \and Article Embedding \and Journal Embedding \and Embedding Visualization \and Embedding Validation.}
\end{abstract}
\section{Data}
For this research we used a dataset consisting of $186.962.354$ tokens. These tokens have been collected from $1.391.543$ articles which have been published in $3.759$ distinct journals. In our dataset, each article is represented with a title and an abstract.
\subsection{Sets}
\subsubsection{Embeddings}
For our research we used multiple embeddings (referred to as "sets"). These embedding sets are: the default embedding; as produced by the Word2Vec model and TF-IDF weighted embeddings (referred to in figures as \textit{embedding}). We used 4 variants of TF-IDF weighted embeddings: 
\begin{itemize}
\item{TF-IDF embedding (\textit{TFIDF\_embedding}); all words, weighted with the TF-IDF score, averaged to create an article embedding.}
\item{10K embedding (\textit{10K\_embedding}); TF-IDF weighting limited to the top 10.000 most occurring tokens.}
\item{5K embedding (\textit{5K\_embedding}); TF-IDF weighting limited to the top 5.000 most occurring tokens.}
\item{1K 6K embedding (\textit{1K\_6LK\_embedding}); TF-IDF weighting limited to the top 1.000 till 6.000 most occurring tokens.}
\end{itemize}
\subsubsection{TFIDF}
We furthermore used 3 TF-IDF sets, to create these sets we used the TF-IDF model and a hasher from the PySpark MlLib\footnote{\url{http://spark.apache.org/docs/2.0.0/api/python/pyspark.mllib.html}.}. We controlled these sets in two ways, (a) adjusting vocabulary size of the input and (b) adjusting the number of hashbuckets. We label the TF-IDF sets as follows: "vocabulary size / number of hash buckets", we furthermore indicate 1.000 as 1K. Thus, we label the TF-IDF configuration that has a vocabulary size of 10.000 and 10.000 hash buckets as TF-IDF 10K/10K. To select the TF-IDF sets, we measured and memory usage of multiple TF-IDF configurations. These results can be seen in Figures~\ref{figure:tfidfPerformance} and~\ref{figure:tfidfMemory}, in this figure we can see that the performance on both title and abstract stagnates; the same is true for the memory usage, although the memory usage does not stagnate as fast as the performance. Given these results, we selected the 10K/10K, 10K/5K and 5K/5K configurations for our research.
\begin{figure}[hbt]
\includegraphics[width=5in]{Plots/tfidf_selection_plot_performance}
\caption{TF-IDF performance on title and abstract.}\label{figure:tfidfPerformance}
\includegraphics[width=5in]{Plots/tfidf_selection_plot_memory}
\caption{TF-IDF memory usage for title and abstract combined.}\footnote{We combined the memory usage of the titles and abstracts since the titles and abstract are created together and share their feature vector size.}\label{figure:tfidfMemory}
\end{figure}
\section{Methodology}

%\begin{theorem}
%This is a sample theorem. The run-in heading is set in bold, while
%the following text appears in italics. Definitions, lemmas,
%propositions, and corollaries are styled the same way.
%\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
%\begin{proof}
%Proofs, examples, and remarks have the initial word in italics,
%while the following text appears in normal font.
%\end{proof}
\citep{EBruniMENCollection}
\bibliographystyle{splncs04}
\bibliography{Bibliography}
\end{document}

### 2018-07-25 Thesis/Parts/Abstract/Abstract.tex
update

@@
 \begin{document}
-Over the last few years, word embeddings have taken a dominant position in the Information Retrieval domain.
-Many studies have been done concerning the quality and application of word embeddings on general texts, such as the Wikipedia corpus and comments on review websites.
-Giving promising results, the word embeddings have been studied and improved over recent years.
-However, these studies have been focused on generic texts, which are not limited to the characteristics of in-domain texts such as rare domain-specific words or have been focussed on small sets of academic texts.
-This research focusses on the quality and application of word embeddings on domain-specific texts, concerning a large corpus of 1.391.543 scientific articles which have been published in 2017.
-We validate the word embeddings using a categorization task to match articles to journals.
-We furthermore create a 2-dimensional visualization of the word embeddings on journal level, to visualize journal relatedness.\\
+Over the last few years, word embeddings have taken a dominant position in the information retrieval research.
+Studies conducted have focused on the quality and application of word embeddings on corpuses such as Wikipedia or online comments/reviews/tweets.
+However, these studies are limited to generic texts and lack technical, scientific or domain specific nuances such as rare words, lots of abbreviations, or chemical/mathematical formulas commonly used in academic context.
+This research focusses on the quality and application of word embeddings on academic corpuses.
+Word embedding requires less memory and is processed faster than conventional alternatives such as TFIDF.
+Hence, we intend to use word embeddings as an efficient way to model the content for our recommendation/disambiguation/search engines.
+This study focuses on word embedding compared to TFIDF for modeling content in scientific articles.
+We use a word2vec model  trained on titles and abstracts of roughly 68 millions scientific articles.
+Word embedding are evaluated against existing benchmarks for generic texts from previous studies.
+Furthermore, we have developed a new benchmark to evaluate these embedding in the scientific context.
+We validate the word embeddings via a categorization task to match articles to journals for roughly 1.4 millions articles published in 2017.
+Our results show that word embedding is a better content model for titles (short text) while TFIDF is a better model for abstracts (longer text).
+Furthermore, we have created a 2-dimensional visualization of the journals modeled via embeddings to visualize their relatedness.
+This graphs can be used to find competitive journals or gaps to propose new journals.\\
 \vspace*{\fill}

### 2018-07-25 Thesis/Parts/Background/Background.tex
update

@@
 \header{Introduction and Background}
+\subheader{Academic articles}
+Academic articles are text, focussed on specific domains (i.e.
+biology, economy or computer science), that contain scientific or domain specific nuances such as: rare words, abbreviations, or mathematical formulas.
+Because these text contain information specific to a domain, we call the articles "domain-specific"; meaning that they give information about a topic in a domain (i.e.
+biology).
+Articles are published in journals, which are collections of articles which share a common topic, i.e.
+a specific field inside the biology domain.
+Our research focusses on the academic articles and journals that are not limited to a specific domain.
 \subheader{Information retrieval}
-Information Retrieval(IR)is the activity of gathering relevant information, given another initial piece of information. 
-\\\\The most practical example of this is a search engine.
+Information Retrieval (IR) is the activity of gathering relevant information, starting from an initial piece of information.
+The most practical example of IR is a search engine.
 Given one or more search words (a query) the search engine will attempt to find relevant information.
-For example, an online search for "Information Retrieval" (initial piece of information) will give you a list of results (relevant information).
-To be able to do this, the search engine must know which texts are related.
-\\\\Interpreting which texts are related can be achieved with, and without neural networks, a traditional technique which does not use a neural network is TF-IDF, shot for Term Frequency - Inverted Document Frequency.
-Techniques that use a neural network are (among others) Word2Vec, Paragraph Vectors and GloVe.
-
-\subheader{Neural Network}
-A complete in-depth background into neural networks is beyond the scope of this thesis, therefore we will only describe the simplified working of a neural network and its basic application in IR.
-Neural Networks are multi-layered computational software, based on matrix transformations, which tries to map input values to output values.
+For example, a search for "Information Retrieval" (initial piece of information) will return a list of results (relevant information).
+To be able to return a list of results, the search engine must know which texts are related.
+\\Interpreting which texts are related can be achieved with, and without neural networks, a traditional technique which does not use a neural network is TF-IDF, short for Term Frequency - Inverted Document Frequency.
+Techniques that use a neural network are Word2Vec, Paragraph Vectors and GloVe.
+\subheader{Neural Networks}
+A complete in-depth background into neural networks is beyond the scope of this thesis, therefore we will only describe the simplified working of neural networks and their basic application in IR.
+Neural Networks are mathematical models\cite{funahashi1989approximate}, which use matrix transformations, to map input values to output values.
 This mapping uses a pre-defined amount of layers that modify the values through matrix transformations.
@@
 Finding these optimal values is done iteratively, via a process known as "back-propagation".
-Back-propagation is done by starting at the output layer of the Neural Network and tracking error in the output back through the layers.
+Back-propagation is done by starting at the output layer of the neural network and tracking the error in the output back through the layers.
 This error information is used to improve the values of the layers.
-The values in the layers are only changed at training time; high-quality (training) data is, therefore, essential for neural networks.
-Neural networks can be applied to many different tasks, as long as there is sufficient data available to create a training and validation set.
-The training is the process of iteratively adjusting multiplication matrices or vectors values to achieve the optimal result.
-Which is the result that is as close as possible to the given output for all input and output sets, without underperforming on other sets\footnote{Having only good results for the training/validation set is known as overfitting.
-This means that the layer-values are fine-tuned to only perform (extremely) well on one set while underperforming on others}.\\Neural Networks are used, in the creation of word embeddings, to either predict words that may occur around a given word or predict a word given words that surround it.
-For example, given the sentence\\
+The values of the layers are only changed at training time; high-quality (training) data is, therefore, essential for neural networks\cite{Truong2017Thesis, lai2016generate}.
+Neural networks can be applied to many different tasks, as long as there is sufficient data available to create training and validation sets.
+During the training process, one seeks to achieve the optimal results, i.e.
+the result that is as close as possible to the given output for all input and output sets, without underperforming on other sets\footnote{Having only good results for the training/validation set is known as overfitting.
+This means that the layer-values are fine-tuned to only perform (extremely) well on one set while underperforming on others.}.\\Neural Networks are used, in the creation of word embeddings, to either predict words that may occur around a given word or predict a word given words that surround it.
+For example, given the sentence:\\
 \begin{center}
@@
 \end{center}
-the Neural Network can be trained to either predict the words around "jumps", which we refer to as context words (the, quick, brown, fox, over, the, lazy, dog).
-It can also predict the word "jumps", given the context words (the, quick, brown, fox, over, the, lazy, dog).
-This results in a matrix, a vector per word which is referred to as a word embedding.
-This embedding indicates "word relatedness" which, as mentioned earlier enables association (thus retrieval) with related(relevant) texts.
-It is to be noted that the word embeddings are only able to represent word relatedness to the other words trained in the same run.
-Due to the random initialization of the initial values of the layers in the neural networks, they do not produce the same result every run.
+a neural network can be trained to either predict the words around "jumps", which we refer to as context words (in this example, the context words are: the, quick, brown, fox, over, the, lazy, dog), or to predict the word "jumps", given the context words.
+The training process results in a matrix, which is transformed to a collection of vectors, each vector is associated to a word, these vectors are referred to as word embeddings.
+This embedding indicates "word relatedness" with other word embeddings (representing other words) which, as mentioned earlier, enables association (thus retrieval) with related (relevant) texts.
+It is to be noted that the word embeddings are only able to represent word relatedness to the other words trained in the same session.
+Due to the random initialization of the initial values of the layers in neural networks, the neural networks do not produce the same result every run.
 Therefore, word embeddings from different runs of the same neural network cannot be compared.
-
 \subheader{Embedding}
 An embedding is a distributed, numerical representation of text in a multi-dimensional vector space\footnote{The vector spaces of separately trained word embeddings differ, since each run the initial values of the neural network are randomly initialized.
-This means that the same word trained in two separate runs do not have to have the same embedding.
-However, they will have the same relationship to other words trained in their respective runs.} which can capture both the semantic and syntactic information\cite{mikolov2013distributed}.
-In the case of a word embeddings, the embeddings represent the words.
-These embeddings are created using machine learning models, which do not need human interaction~\cite{lai2016generate}, they are so-called \textit{unsupervised learning algorithms}.
+This means that the same word trained in two separate sessions may have two different embeddings.
+However, they will have the same relationship to other words trained in their respective sessions.} which can capture both semantic and syntactic information\cite{mikolov2013distributed}.
+In the case of word embeddings, the embeddings represent the words.
+These embeddings can be\footnote{This depends on the method used to create the word embeddings, for this research, we used word embeddings trained by an unsupervised learing algorithm.} created using machine learning models, which do not need human interaction~\cite{lai2016generate}, they are so-called \textit{unsupervised learning algorithms}.
 Once trained, the embeddings can also be used to construct embeddings for collections of texts.
-For example, a word embedding can be used to create a sentence, paragraph, document or corpus embeddings.
-The usage of word embeddings has improved various Natural Language Processing areas such as named entity recognition, part-of-speech tagging, parsing, and semantic role labelling~\citet{luong2013better}.
-
+For example, a word embedding can be used to create sentence, paragraph, document or corpus embeddings.
+The usage of word embeddings has improved various natural language processing (NLP) areas such as named entity recognition, part-of-speech tagging, parsing, and semantic role labelling~\cite{luong2013better}.
+Embeddings can furthermore be used in search and recommendation.
+Potential application of the embeddings in the academic domain could be the improvement of search engines, text analysis to improve NLP tasks for academic texts, and journal recommendation for publishing articles.
+The embeddings can furthermore be used to help researchers which are new to a field to explore the field by finding related articles or articles that are related to the field of expertise of the researcher and the new research field.
+Embeddings can also be visualized (see paragraph 1.6), this can give insight into the topics of popular journals, and can be used to indicate research subjects where there are few publications or journals.
 \subheader{Text analysis techniques}
 To enable a computer to process text, for embedding creation or other tasks, the text has to be processed by an algorithm.
-In this research, we used embeddings created by Word2Vec and TF-IDF feature vectors.
+In this research, we used embeddings created by Word2Vec, and feature vectors\footnote{Which do not require training (see subparagraph TF-IDF).} created using TF-IDF.
 \begin{jumpin}
 \subsubheader{Word2Vec}
-Word2vec word embeddings are created using a neural network, Word2Vec learns word embeddings via maximizing the log conditional probability of the word given the context word(s) occurring within a fixed-sized window.
-Therefore the learned embeddings contain useful knowledge about word co-occurrence\cite{nalisnick2016improving}.
-There are multiple input/output possibilities for the neural network, best known are Skip-gram and the Continuous Bag-of-Words model (CBOW).
-The Skip-gram model takes a target word as input and outputs the predicted context words, while CBOW takes the context words as input and outputs the predicted target word\cite{nalisnick2016improving, pennington2014glove}.
-This is illustrated in Figure~\ref{figure:word2vecModels}, in this Figure, $v(w)$ represents the target word, and $v(w...)$ represent the context words.
-\citet{mikolov2013distributed}\cite{mikolov2013efficient} presented several extensions to the word2vec model that improve the quality of vector training and its speed, such as introducing Hierarchical Softmax, Negative Sampling and the subsampling of frequent words to the Skip-gram approach.
-Variations to the word2vec model have also been proposed, such as the doc2vec model described by \citet{lau2016empirical} which creates document embeddings instead of word embeddings.
+Word2vec word embeddings are created using a neural network, Word2Vec learns word embeddings via maximizing the probability of the word given the context word(s) occurring within a fixed-sized window, therefore the learned embeddings contain useful knowledge about word co-occurrence\cite{nalisnick2016improving} which indicates relatedness\cite{lai2016generate}.
+There are multiple input/output possibilities for the neural network.
+The best known are Skip-gram and the Continuous Bag-of-Words model (CBOW).
+The Skip-gram model takes a target word as inp ut and outputs the predicted context words, while CBOW takes the context words as input and outputs the predicted target word\cite{nalisnick2016improving, pennington2014glove}.
+This is illustrated in Figure~\ref{figure:word2vecModels}, where, $v(w)$ represents the target word, and $v(w...)$ represent the context words.
+\citet{mikolov2013distributed}\cite{mikolov2013efficient} presented several extensions to the word2vec model that improve the quality of the embeddings and the training speed, such as Hierarchical Softmax, Negative Sampling and the subsampling of frequent words for the Skip-gram approach.
+Variations to the word2vec model have also been proposed, such as the doc2vec model described by \citet{lau2016empirical} which creates document embeddings\footnote{Document embeddings are embeddings which capture the relatedness between documents.} instead of word embeddings.
+\begin{figure}[hbt]
 \begin{center}
-\begin{figure}[hbt]
 \includegraphics[width=4in]{Plots/Model-Architecture-of-CBOW-and-Skip-Gram.png}

### 2018-07-25 Paper/paper.tex
new paper start
paper 2/2

@@
 \usepackage{hyperref}
-%\renewcommand\UrlFont{\color{blue}\rmfamily}
-
 \newenvironment{jumpin}{\begin{adjustwidth}{0.3in}{}}{\end{adjustwidth}}
+\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
 
@@
 \begin{abstract}
-\subfile{Parts/Abstract/Abstract.tex}
-
+Over the last few years, word embeddings have taken a dominant position in the information retrieval research.
+Studies conducted have focused on the quality and application of word embeddings on corpuses such as Wikipedia or online comments/reviews/tweets.
+However, these studies are limited to generic texts and lack technical, scientific or domain specific nuances such as rare words, lots of abbreviations, or chemical/mathematical formulas commonly used in academic context.
+This research focusses on the quality and application of word embeddings on academic corpuses.
+Word embedding requires less memory and is processed faster than conventional alternatives such as TFIDF.
+Hence, we intend to use word embeddings as an efficient way to model the content for our recommendation/disambiguation/search engines.
+This study focuses on word embedding compared to TFIDF for modeling content in scientific articles.
+We use a word2vec model  trained on titles and abstracts of roughly 68 millions scientific articles.
+Word embedding are evaluated against existing benchmarks for generic texts from previous studies.
+Furthermore, we have developed a new benchmark to evaluate these embedding in the scientific context.
+We validate the word embeddings via a categorization task to match articles to journals for roughly 1.4 millions articles published in 2017.
+Our results show that word embedding is a better content model for titles (short text) while TFIDF is a better model for abstracts (longer text).
 \keywords{Word Embedding  \and Document Embedding \and Article Embedding \and Journal Embedding \and Embedding Visualization \and Embedding Validation.}
 \end{abstract}
-
-\subfile{Parts/Data/Data.tex}
-%\subfile{Parts/Research_results/Research_results.tex}
-%\subfile{Parts/Discussion/Discussion.tex}
-%\subfile{Parts/Conclusion/Conclusion.tex}
-%\subfile{Parts/Future_work/Future_work.tex}
-
+\section{Introduction}
+Over the last few years word embeddings have proven to be powerful tools.
+Word embeddings, numerical representations of words, have atraccted the attention of many researchers over the last few years.
+Embeddings, created by (unsupervised) machine learning models\cite{lai2016generate} are able to capture semantic and syntactic information about words\cite{mikolov2013distributed}.
+The usage of word embeddings has improved various Natural Language Processing areas such as named entity recognition, part-of-speech tagging, parsing, and semantic role labelling~\cite{luong2013better}.
+Embeddings can furthermore be used in search and recommendation.
+Potential application of the embeddings in the academic domain could be the improvement of search engines, text analysis to improve NLP tasks for academic texts, and journal recommendation for publishing articles.
+Studies till this day have mostly focussed on generic texts like Wikipedia, or informal texts like reviews and tweets.
+We aim to validate the word embeddings for academic texts, containing technical, scientific or domain specific nuances such as rare words, lots of abbreviations, or chemical/mathematical formulas.
+We validate the embeddings by matching articles to journals, ranking them on cosine-similarity.
+\section{Data \& Environment}
+For this research we used a dataset consisting of $186.962.354$ tokens.
+These tokens have been collected from $1.391.543$ articles which have been published in $3.759$ distinct journals.
+In our dataset, each article is represented with a title and an abstract.
+The word occurrences in our dataset follow a Pareto-like distribution as described by \citet{wiegand2018word}, indicating that our original data has the same properties as standard English texts.
+We used Spark for this research, enabeling us to use its tools for big data processing\cite{armbrust2015spark}.
+\subsection{Sets}
+\subsubsection{Embeddings}
+We used 300-dimensional embeddings, created by \citet{Truong2017Thesis}, based on the Word2Vec model.
+From these embeddings we created multiple embedding sets.
+These sets are: the default embedding; as created by \citet{Truong2017Thesis} and TF-IDF weighted embeddings (referred to in figures as \textit{embedding}).
+We used 4 variants of TF-IDF weighted embeddings:
+\begin{itemize}
+\item{TF-IDF embedding (\textit{TFIDF\_embedding}); all words, weighted with the TF-IDF score, averaged to create an article embedding.}
+\item{10K embedding (\textit{10K\_embedding}); TF-IDF weighting limited to the top 10.000 most occurring tokens.}
+\item{5K embedding (\textit{5K\_embedding}); TF-IDF weighting limited to the top 5.000 most occurring tokens.}
+\item{1K 6K embedding (\textit{1K\_6LK\_embedding}); TF-IDF weighting limited to the top 1.000 till 6.000 most occurring tokens.}
+\end{itemize}
+\subsubsection{TFIDF}
+We furthermore used 3 TF-IDF sets, to create these sets we used the TF-IDF model and a hasher from the PySpark MlLib\footnote{\url{http://spark.apache.org/docs/2.0.0/api/python/pyspark.mllib.html}.}.
+We controlled these sets in two ways, (a) adjusting vocabulary size of the input and (b) adjusting the number of hashbuckets.
+We label the TF-IDF sets as follows: "vocabulary size / number of hash buckets", we furthermore indicate 1.000 as 1K.
+Thus, we label the TF-IDF configuration that has a vocabulary size of 10.000 and 10.000 hash buckets as TF-IDF 10K/10K.
+To select the TF-IDF sets, we measured and memory usage of multiple TF-IDF configurations.
+These results can be seen in Figures~\ref{figure:tfidfPerformance} and~\ref{figure:tfidfMemory}, in this figure we can see that the performance on both title and abstract stagnates; the same is true for the memory usage, although the memory usage does not stagnate as fast as the performance.
+Given these results, we selected the 10K/10K, 10K/5K and 5K/5K configurations for our research.
+\begin{figure}[hbt]
+\includegraphics[width=5in]{Plots/tfidf_selection_plot_performance}
+\caption{TF-IDF performance on title and abstract.}\label{figure:tfidfPerformance}
+\includegraphics[width=5in]{Plots/tfidf_selection_plot_memory}
+\caption{TF-IDF memory usage for title and abstract combined.}\footnote{We combined the memory usage of the titles and abstracts since the titles and abstract are created together and share their feature vector size.}\label{figure:tfidfMemory}
+\end{figure}
+\FloatBarrier
+\section{Methodology}
+We use a ranking task to validate the quality of the different sets.
+We calculate the distance from each article from our validation set to each journal embedding from our training set.
+We then order the journals (ascending) based on their similarity.
+We use as ranking the rank of the journal from which the article was taken (source journal) in the resulting list.
+We do this for both title and abstract separately.\\
+We calculate the performance per set, therefore we combine the ranking results of all articles for a set into one score.
+We use the median and average for that; where the average rank takes the total average of all ranks, the median is the point at which 50\% of all the ranks are greater and 50\% of all the ranks are lower than the point.
+We keep track of the following results when ranking: source journal rank and best match journal for both abstract and title.
+We furthermore monitor the memory usage and computation time.
+\section{Results}
+In this section the results of our research are presented; the detailed discussion on the meaning and implications of these results are presented in XXXXXXXXX discussion.
+\subsection{Ranking}
+The Figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} show the result of the categorization task as ranking results.
+The rank indicates the position of the correct journal in the sorted list of matched journals.
+Figure~\ref{figure:titleRanks} shows the ranking results for the different sets based on the title.
+Figure~\ref{figure:abstractRanks} displays the ranking results based on the abstract.
+Both graphs show both average and median ranks, based on the cosine-similarity between the article and journal embeddings or feature vectors.
+\subsection{Rank distribution}
+Figures~\ref{figure:titleDistribution} and~\ref{figure:abstractDistribution} show the distributions of the ranks for each set.
+The Figures plot the summed amount of articles against the ranks on a logarithmic scale.
+Figure~\ref{figure:titleDistribution} shows the rank distribution for the titles, Figure~\ref{figure:abstractDistribution} shows this for the ranks based on the abstract.
+These graphs give a detailed view of the ranks presented in their respective figures (Figures~\ref{figure:titleRanks} and~\ref{figure:abstractRanks}).
+\subsection{F1-Score}
+Figures~\ref{figure:f1Title} and~\ref{figure:f1Abstract} show the precision, recall and F1 scores.
+These scores are calculated on journal level, and are averaged per set.
+Figure~\ref{figure:f1Title} shows the F1 score for the title and Figure~\ref{figure:f1Abstract} shows the scores for the abstract.
+These scores indicate the performance of the sets on absolute hits/top-1.
+\subsection{Memory usage}
+Table~\ref{table:memoryUsage} shows the total memory usage of each set for the \textit{Validation set}, indicating their storage costs in gigabytes\footnote{1024 based}.
+It furthermore shows the absolute hit percentage of the title and the abstracts, i.e.
+the percentage of articles that have their source\footnote{Journal from which the article was taken} journal as the first result in the ranking.
+The table furthermore shows the median rank and the median abstract rank, as visualized in Figures \ref{figure:titleRanks} and~\ref{figure:abstractRanks}.
+Thus, this table gives an overview of the memory usage of the sets, combined with their performance on the ranking task.
+\subsection{Computation Time}
+Table~\ref{table:computationTimes} shows the computation time needed for 1.000 distance calculations, based on the cosine-similarity distance measurement.
+1.000 vectors (V) have been randomly selected and transformed into a matrix (M).
+We then calculate the distance between each vector from V to the matrix M; this results in the distance between the vector an all vectors (V) contained in the matrix (M).
+We do this for all vectors in V, for the 10K/10K TF-IDF set and the default embeddings.
+Because the embeddings are dense vectors, we also transformed the TF-IDF feature vectors to dense vectors for this comparison.
+Table~\ref{table:computationTimes} shows both computation time in seconds and the embedding fraction; meaning how many times faster the embedding is, based on time in seconds.
+\FloatBarrier
+\begin{figure}
+\includegraphics[width=4.5in]{Plots/Title_rankings}
+\caption{Median and average title rankings}\label{figure:titleRanks}
+\includegraphics[width=4.5in]{Plots/Abstract_rankings}
+\caption{Median and average abstract rankings}\label{figure:abstractRanks}
+\includegraphics[width=4.5in]{Plots/Title_rank_distribution}
+\caption{Title rank distribution per set, Y-axis shows the fraction of articles.}\label{figure:titleDistribution}
+\end{figure}
+\begin{figure}
+\includegraphics[width=4.5in]{Plots/Abstract_rank_distribution}
+\caption{Abstract rank distribution per set, Y-axis shows the fraction of acticles.}\label{figure:abstractDistribution}
+\includegraphics[width=4.5in]{Plots/Title_avg_f1}
+\caption{Precision, recall and F1 scores based on title}\label{figure:f1Title}
+\includegraphics[width=4.5in]{Plots/Abstract_avg_f1}
+\caption{Precision, recall and F1 scores based on abstract}\label{figure:f1Abstract}
+\end{figure}
+\FloatBarrier
+\begin{center}
+\begin{table}
+\begin{tabular}{|l|r|r|r|r|}
+\hline
+Set & Size in GB & Absolute hit percentage & Median title rank & Median abstract rank\\
+&&\begin{tabular}{p{0.5in}|p{0.5in}}Title & Abstract\end{tabular}&&\\
+\hline
+tfidf 5k 5K & $9.82$ & \begin{tabular}{R{0.5in}|R{0.5in}}5.42\% & 10.18\%\end{tabular} & 50 & 27\\
+\hline
+tfidf 5K 10K & $11.47$ & \begin{tabular}{R{0.5in}|R{0.5in}}6.49\% & 11.08\%\end{tabular} & 38 & 15\\
+\hline
+\textbf{tfidf 10K 10K} &\textbf{11.61}& \begin{tabular}{R{0.5in}|R{0.5in}}\textbf{6.79\%} & \textbf{11.32\%}\end{tabular} & \textbf{35} & \textbf{14}\\
+\hline
+embedding & $3.13$ & \begin{tabular}{R{0.5in}|R{0.5in}}7.92\% & 9.24\%\end{tabular} & 27 & 23\\
+\hline
+5k embedding & $3.13$ & \begin{tabular}{R{0.5in}|R{0.5in}}6.34\% & 8.36\%\end{tabular} & 42 & 27\\
+\hline
+10k embedding & $3.13$ & \begin{tabular}{R{0.5in}|R{0.5in}}7.03\% & 8.76\%\end{tabular} & 34 & 25\\
+\hline
+\textbf{tfidf embedding} & \textbf{3.13} & \begin{tabular}{R{0.5in}|R{0.5in}}\textbf{7.89\%} & \textbf{9.33\%}\end{tabular} & \textbf{27} & \textbf{22}\\
+\hline
+1k 6k embedding & $3.06$ & \begin{tabular}{R{0.5in}|R{0.5in}}5.16\% & 7.86\%\end{tabular} & 64 &31 \\
+\hline
+\end{tabular}
+\caption{Memory usage and performance for each set}\label{table:memoryUsage}
+%\end{table}
+%\begin{table}
+\begin{tabular}{|p{1.5in}|p{1.65in}|p{1.2in}|}
+\hline
+ & Computation time (seconds) & Embedding fraction\\
+ & \begin{tabular}{R{0.77in}|R{0.82in}}Title & Abstract\end{tabular} & \begin{tabular}{R{0.5in}|R{0.6in}}Title & Abstract\end{tabular} \\
+\hline
+TF-IDF (sparse vector) & \begin{tabular}{R{0.77in}|R{0.82in}} 154.95 & 169.89 \end{tabular}& \begin{tabular}{R{0.5in}|R{0.6in}} 231.25 & 184.36\end{tabular}\\
+\hline
+TF-IDF (dense vector) &\begin{tabular}{R{0.77in}|R{0.82in}} 35.67 & 35.18 \end{tabular} & \begin{tabular}{R{0.5in}|R{0.6in}} 53.23 & 39.59 \end{tabular} \\
+\hline
+Embedding & \begin{tabular}{R{0.77in}|R{0.82in}} 0.67&0.89 \end{tabular}& \begin{tabular}{R{0.5in}|R{0.6in}}1&1\end{tabular}\\
+\hline
+\end{tabular}
+\caption{Comparison of computation time in seconds, based on 1.000 distance calculations. Showing both absolute measurements and the fraction to the embedding time.} \label{table:computationTimes}
+\end{table}
+\end{center}
+\FloatBarrier
+\section{Discussion}
+\subsection{Results analysis}
+\subsubsection{Best performers}
+The data, as presented in Figures~\ref{figure:titleRanks} and~\ref{figure:abstractRanks} shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank on abstract and 3 median ranks on the titles.
+For the embeddings, the TF-IDF weighted embedding works better than the others, although it is not a significant improvement (1 rank on a set of more than 3.000) compared to the default embeddings, which is 1 median rank higher on the abstracts, and equal on the titles.
+\subsubsection{TF-IDF}
+The TF-IDF feature vectors outperform the embeddings on the abstracts, while the embeddings outperform the TF-IDF feature vectors on the titles.
+The main difference between the abstract and title is that the title contains fewer tokens compared to the abstract (see Table~\ref{table:corpusSize}).
+This means that the titles contain less information than the abstracts.
+Due to this, the TF-IDF method, which is purely based on word-occurrences \& counts has less information on the titles.
+The TF-IDF method works better on the abstract, containing more tokens than the tile, thus improving the differentiating the different abstract.
+The data furthermore shows that increasing the vocabulary size increases the performance of the TF-IDF, meaning that none of the created cut-off's resulted in cutting off noise, the increasing size of the vocabulary only improved the performance on our data.
+It could be possible that at higher vocabulary sizes the cut-off would result in a sharper signal, but we did not investigate this further due to our findings that the TF-IDF performance stagnates (presented in Figure~\ref{figure:tfidfPerformance}).
+\subsubsection{Limited TF-IDF embeddings}
+The limited TF-IDF embeddings all under perform, compared to the TF-IDF embedding (which does not have a limited vocabulary), on the median and average ranking.
+This result indicates that the noise reduction is too much, and it removes meaningful words.
+If the noise reduction would be too low, we would only see a slight increase of performance compared to the TF-IDF embedding, or none at all.
+However, the rank increases, indicating the reduction in embedding quality due to missing words.
+This is in line with what we found with the TF-IDF results: higher vocabulary sizes give better performance.
+\begin{itemize}
+\item{\textit{Rank distribution}; Although the limited TF-IDF embeddings under perform, Figures~\ref{figure:titleDistribution} and~\ref{figure:abstractDistribution} show that their rank distribution is different from the other embeddings.
+The rank distribution of the limited TF-IDF embeddings show the following pattern: a high/average performance on the top-rankings, a below average performance on the middle rankings and a resulting stack-up of articles with a high-ranking.
+This effect can be best seen in Figure~\ref{figure:titleDistribution} for the 1K\_6K\_embedding set.}
+\end{itemize}
+The rank distribution seems to indicate that the cut-off was effective, but also that it did not suit our purpose.
+The cut-off moved the "middle-ranked"  articles to either the higher end or the lower end of the rankings, resulting in high median and average ranks, and in (relatively) high accuracy scores.
+The reduction in vocabulary size did not reduce the storage size for the embeddings, except for the 1K-6K embedding.
+This indicates that only the 1K-6K cut actually removes entire titles and abstracts, since all vectors are stored as dense-vectors\footnote{Dense vectors are bigger in memory, since they store all their values, including zeros.
+However, they can be processed more efficiently during calculations}.
+The removal of titles and abstracts results in a lower memory requirement.
+\subsubsection{TF-IDF \& embeddings}
+Our hypothesis on the difference between the TF-IDF and the standard embedding is as follows:\\
+The embeddings seem to outperform the TF-IDF feature vectors in situations where there is little information available (titles).
+This indicates that the embeddings store some word meaning that enables them to perform relatively well on the titles.
+The abstracts, on the other hand, contain much more information.
+Our data seems to indicate that the amount of information available in the abstracts enable the TF-IDF to cope with the lack of embedded information.
+If this is the case, we could expect that there would little performance increase on the title when we compare the embeddings to the weighted TF-IDF embeddings, because the TF-IDF lacks the information to perform well.
+This can be seen in our data, only the average rank increased by 3, indicating that there is a difference between the two embeddings, but not a significant one.
+We would also expect on the abstract an increase in performance since the TF-IDF has more information in this context.
+We would expect that the weighting applied by the TF-IDF improves the performance of the embedding by indicating word importance.
+Our data shows a minor improvement in performance of 1 median rank and 10 average ranks while these improvements cannot be seen as significant, our data at least indicates that weighting the embeddings with TF-IDF values has a positive effect on the embeddings.
+\subsubsection{Memory usage}
+Although the TF-IDF outperforms the embeddings on the abstracts, its memory usage is higher than the memory usage of the embeddings.
+The top-performing embedding, TF-IDF weighted embedding, uses 3.13 GB, the top performing TF-IDF, 10K/10K uses 11.61 GB, which is 270.93\% of the storage size needed for the embedding.
+The closest TF-IDF configuration (based on memory usage) we used was 1K/1K, which uses 5.13 GB (as displayed in Figure~\ref{figure:tfidfPerformance}).
+This TF-IDF set has a median title rank of 183 and a median abstract rank of 44.
+Which is significantly worse than the embedding, which also uses less memory.
+This indicates that the embeddings are able to store the relatedness information more densely than the TF-IDF feature vectors can store the word occurrence information.
+\subsection{Improvements}
+This research shows that even though the embeddings can capture and preserve relatedness, TF-IDF is able to outperform the embeddings on the abstracts.
+Earlier research already proposed improvements to the word embeddings.
+\citet{dai2015document} show that using paragraph vectors improves the accuracy of word embeddings with 4.4\% on triplet creation with the Wikipedia corpus and a 3.9\% improvement on the same task based on the arXiv articles.\\
+Furthermore, \citet{le2014distributed} show that the usage of paragraph vectors decrease the error rate (positive/negative) with 7.7\% compared to averaging the word embeddings on categorizing text as either positive or negative.
+While the improvement looks promising, we have to keep in mind that our task differs from earlier tasks.
+We do not categorize on two categories but more than 3k.
+Still, we would expect an improvement by using paragraph vectors since the classification task if fundamentally the same, only on a much larger scale, which complicates the task due to the "grey areas"  between categories.
+These are the area's in which the classification algorithm is "in doubt" and could reasonably assign the article to both journals.
+The number of these grey areas increase given more categories.
+\citet{pennington2014glove} showed that the GloVe model outperforms the CBOW model, which is used in this research, on a word analogy task.
+\citet{wang2016linked} introduced the Linked Document Embedding method (LDE) method, which makes use of additional information about a document, such as citations.
+Their research specifically focused on categorizing documents, showed a 5.89\% increase of the micro-F1 score on LDE compared to CBOW, and a 9.11\% increase of the macro-F1 score.
+We would expect that applying this technique to our dataset would improve our scores, given earlier results on comparable tasks.\\
+Even though much research has been done, we have not been able to find published results which are directly comparable to our results.
+This is likely due to our high amount of categorization groups, which enabled us to handle our results as a ranking problem, instead of an absolute hit, which has been used in earlier work\cite{wang2016linked}.
+Even though we have an F1 score, which indicates performance on the absolute hits, our results are not comparable to other works due to the number of categories, and their overlapping subjects\footnote{As visualized in the journal embedding plots and discussed earlier}.
+\section{Conclusion}
+This research shows that the article embeddings, created with word embeddings, perform better than the reasonable TF-IDF alternatives on our categorization task, based on article titles.
+The TF-IDF alternatives give better results than the embeddings based on abstracts.
+The performance of the embeddings have been improved by weighing them with the TF-IDF values on the word level, although this improvement cannot be seen as significant on our dataset.
+This improved embedding set results in a median rank decrease of 8 on the titles and a median rank increase of 8 on the abstract, compared to the best performing TF-IDF alternative.
+The embedding also results in a memory decrease of 73.04\% compared to the best performing TF-IDF alternative, making it more viable to keep it in memory.
+The visualization of the journal embedding shows that similar journals are grouped together, indicating a preservation of relatedness between the journal embeddings.
+We thus come to the following conclusions:
+\begin{enumerate}
+\item{Article based embeddings perform better than TF-IDF on titles, i.e. small texts which contain limited information.}
+\item{TF-IDF performs better than article based embeddings on abstracts, i.e. larger texts which contain more information.}
+\item{Embeddings give a significant decrease in memory usage compared to TF-IDF.}
+\end{enumerate}
+\section{Future work}
+\subsection{Intelligent cutting}
+A better way of cutting could improve the quality of the embeddings.
+This improvement might be achieved by cutting the center of the vector space out before normalization.
+All words which are generic are in the center of the spectrum, removing these words prevents the larger texts to be pulled towards the middle of the vector space, where they lose the parts of their meaning which set them apart from the other texts.
+We expect that this way of cutting, instead of word-occurrence cutting, will improve the quality of the word embeddings which have been limited in their vocabulary.
+\subsection{TF-IDFs performance point}
+In our research, TF-IDF performed better on the abstracts than on the titles, which, according to us, is caused by the text size of the two texts.
+This leads to the question, how do token count and unique token count relate for TF-IDF?
+Is there a point at which the TF-IDF outperforms the embeddings, and will continue to outperform?
+If this relation is found, one could skip the TF-IDF calculations in certain situations, and skip the embedding training in other scenario's, reducing costs.
+\subsection{Reversed word pairs}
+At this point, there are no domain-specific word pair sets available.
+However, as we demonstrated, we can still test the quality of word embeddings.
+Once one has established that the word vectors are of high quality; could one create word pairs from these embeddings?
+If this is the case, we could create word pair sets using the embeddings, reverse-engineering the domain specific word pair sets for future use.
 %\begin{theorem}
@@
 %\end{proof}
-\cite{Truong2017Thesis}
 \bibliographystyle{splncs04}
-\bibliography{Bibliography.bib}
+\bibliography{Bibliography}
 \end{document}

### 2018-07-25 Paper/paper.tex
mac sync

@@
 Because the embeddings are dense vectors, we also transformed the TF-IDF feature vectors to dense vectors for this comparison.
-Table~\ref{table:computationTimes} shows both computation time in seconds and the embedding fraction; meaning how many times faster the embedding is, based on time in seconds.
+Table~\ref{table:computationTimes} shows both computation time in seconds and the embedding fraction; meaning how many times more efficient the embedding is for online similarity calculation, based on time in seconds.
 \FloatBarrier

### 2018-07-25 Paper/paper.tex
overleaf sync

--- 2018-07-25 Paper/paper.tex
@@
 \maketitle
-
 \begin{abstract}
@@
 In our dataset, each article is represented with a title and an abstract.
-The word occurrences in our dataset follow a Pareto-like distribution as described by \citet{wiegand2018word}, indicating that our original data has the same properties as standard English texts.
+The word occurrences in our dataset follow a Pareto-like distribution as described by Wiegand et al\cite{wiegand2018word}, indicating that our original data has the same properties as standard English texts.
 We used Spark for this research, enabeling us to use its tools for big data processing\cite{armbrust2015spark}.
@@
 \subsubsection{Embeddings}
-We used 300-dimensional embeddings, created by \citet{Truong2017Thesis}, based on the Word2Vec model.
+We used 300-dimensional embeddings, created by Truong\cite{Truong2017Thesis}, based on the Word2Vec model.
 From these embeddings we created multiple embedding sets.
-These sets are: the default embedding; as created by \citet{Truong2017Thesis} and TF-IDF weighted embeddings (referred to in figures as \textit{embedding}).
+These sets are: the default embedding; as created by Truong\cite{Truong2017Thesis} and TF-IDF weighted embeddings (referred to in figures as \textit{embedding}).
 We used 4 variants of TF-IDF weighted embeddings:
@@
 The TF-IDF feature vectors outperform the embeddings on the abstracts, while the embeddings outperform the TF-IDF feature vectors on the titles.
-The main difference between the abstract and title is that the title contains fewer tokens compared to the abstract (see Table~\ref{table:corpusSize}).
+The main difference between the abstract and title is that the title contains fewer tokens compared to the abstract.
 This means that the titles contain less information than the abstracts.
@@
 Earlier research already proposed improvements to the word embeddings.
-\citet{dai2015document} show that using paragraph vectors improves the accuracy of word embeddings with 4.4\% on triplet creation with the Wikipedia corpus and a 3.9\% improvement on the same task based on the arXiv articles.\\
-Furthermore, \citet{le2014distributed} show that the usage of paragraph vectors decrease the error rate (positive/negative) with 7.7\% compared to averaging the word embeddings on categorizing text as either positive or negative.
+Dai et al\cite{dai2015document} show that using paragraph vectors improves the accuracy of word embeddings with 4.4\% on triplet creation with the Wikipedia corpus and a 3.9\% improvement on the same task based on the arXiv articles.\\
+Furthermore, Le et al\cite{le2014distributed} show that the usage of paragraph vectors decrease the error rate (positive/negative) with 7.7\% compared to averaging the word embeddings on categorizing text as either positive or negative.
 While the improvement looks promising, we have to keep in mind that our task differs from earlier tasks.
@@
 The number of these grey areas increase given more categories.
-\citet{pennington2014glove} showed that the GloVe model outperforms the CBOW model, which is used in this research, on a word analogy task.
-\citet{wang2016linked} introduced the Linked Document Embedding method (LDE) method, which makes use of additional information about a document, such as citations.
+Pennington et al\cite{pennington2014glove} showed that the GloVe model outperforms the CBOW model, which is used in this research, on a word analogy task.
+Wang et al\cite{wang2016linked} introduced the Linked Document Embedding method (LDE) method, which makes use of additional information about a document, such as citations.
 Their research specifically focused on categorizing documents, showed a 5.89\% increase of the micro-F1 score on LDE compared to CBOW, and a 9.11\% increase of the macro-F1 score.
@@
 If this is the case, we could create word pair sets using the embeddings, reverse-engineering the domain specific word pair sets for future use.
-%\begin{theorem}
-%This is a sample theorem. The run-in heading is set in bold, while
-%the following text appears in italics. Definitions, lemmas,
-%propositions, and corollaries are styled the same way.
-%\end{theorem}
-%
-% the environments 'definition', 'lemma', 'proposition', 'corollary',
-% 'remark', and 'example' are defined in the LLNCS documentclass as well.
-%
-%\begin{proof}
-%Proofs, examples, and remarks have the initial word in italics,
-%while the following text appears in normal font.
-%\end{proof}
 \bibliographystyle{splncs04}
-\bibliography{Bibliography}
+\bibliography{references}
 \end{document}
